### 2017-02-18 paper.tex
initial text

% OUTLINE
% =======
%
% 1. Introduction
%
%   Here I will introduce the need for a new high-fidelity, low-frequency map of the sky. The
%   justifications are: 21 cm foreground mapping, galactic structure (?), others?
%
% 2. Observations
%
%   2.1 - Introduce the Owens Valley LWA
%   2.2 - Describe the 100 hour dataset
%   2.3 - Calibration strategy
%   2.4 - Source removal strategy
%   2.5 - Horizon RFI suppression strategy
%   2.6 - Beam fitting work
%   2.7 - Ionospheric conditions
%
% 3. Imaging
%
%   Give a brief overview of other widefield imaging algorithms. This should set the context for the
%   advantages of m-mode analysis.
%
%   3.1 - Introduce m-mode analysis imaging
%   3.2 - Describe my implementation of m-mode analysis on the ASTM
%   3.3 - L-curves (?)
%   3.4 - CLEAN
%
% 4. Results
%
%   Present sky maps with an estimate of the thermal noise in each pixel. Systematic errors will be
%   described in the following sub-sections.
%
%   4.1 - Horizon RFI
%   4.2 - Ionospheric effects
%   4.3 - Beam errors
%   4.4 - Peeling failures
%
% 5. Discussion
%
%   Compare with the Haslam map and Jayce's map.
%
% 6. Conclusion
%
% FIGURES
% =======
%
% * Antenna layout of the OVRO LWA
% * Before/after snapshot image of the RFI removal
% * Image of the empirical beam (with source tracks)
% * Plot of ionospheric scintillation and refraction of an A-team source
% * Example L-curve
% * Zoom-in of the dirty PSF
% * Sky maps with their boot-strapped thermal noise estimates
% * (Model) image of the horizontal stripes that show up if the horizon RFI is not removed
% * (Model) image of the PSF distortion from ionospheric effects (scintillation, refraction)
% * (Model) image of the systematic errors in the map created from beam errors
% * (Model) image of the errors created from sporadic peeling failures

\documentclass[twocolumn]{aastex6}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}

\renewcommand{\b}{\pmb}
\renewcommand{\d}{{\rm d}}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

\begin{document}

\title{The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array}

\author{
    Michael W. Eastwood,
    Gregg Hallinan
}

\begin{abstract}
    I present all-sky maps of the sky from the Owens Valley Long Wavelength Array.
    These maps are created from the application of $m$-mode analysis.
\end{abstract}

\section{Introduction}

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H}.  Following the epoch of
recombination the universe continued to expand and cool.  Small inhomogeneities observed in the CMB
grew larger and galaxies formed. The first stars formed and flooded the universe with light during
the cosmic dawn, bringing the dark ages to an end. Eventually the cumulative influence of these
galaxies completed a phase change in the inter-galactic medium (IGM), and the universe returned to
an ionized state following the conclusion of the epoch of reionization (EoR). Low frequency radio
telescopes are poised to provide the first direct detection of the IGM from the cosmic dawn and the
EoR using the redshifted hyperfine structure line of neutral hydrogen.

These low-frequency 21-cm cosmology experiments are limited by the dynamic range they can achieve
against the low-redshift sources of emission. Depending on the redshift, length scale, and model the
expected amplitude of the cosmological signal is 10 to 100 mK. On the other hand the galactic
synchrotron emission is 1000 to 10000 K. \todo{citation} Therefore experiments conservatively need
to achieve at least 4 orders of dynamic range. In theory this kind of dynamic range can be obtained
by exploiting the fact that the foreground emission is predominantly synchrotron emission that has a
smooth power law spectrum. On the other hand the frequency structure of the cosmological signal is
expected to be un-smooth because different frequencies trace different redshifts. This is the basic
assumption made by all published upper limits on the cosmological 21 cm power spectrum.  In practice
the interferometer itself imparts frequency structure into the measurements and therefore an
experiment's ability to separate the foreground signal from the cosmological signal can be limited
by the instrumental spectral smoothness.

Ideally the foreground removal strategy should be informed by the measured spatial and frequency
structure of all foreground components. This possibility is limited by the availability of suitable
high-fidelity low-frequency sky maps on angular scales ranging from tens of degrees to arcminutes.

The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is a data-driven
interpolation of various maps between 10 MHz and 100 GHz, but below 408 MHz, the interpolation is
largely driven by the Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H}.

\todo{TGSS, MSSS, GLEAM}

At lower frequencies, free-free absorption and synchrotron self-absorption becomes important.

Galactic structure.

Planets?

%Optical observers have become increasingly proficient at discovering high-redshift galaxies
%\citep{2013ApJS..209....3K} and quasars \citep{2011Natur.474..616M}.  While these objects have
%provided valuable insight into galaxy formation and the timing of the epoch of reionization (EoR),
%they are necessarily exceptional. Flux-limited surveys find the most luminous objects, which are not
%representative of galaxy properties as a whole.  Furthermore, the observed luminosity function of
%galaxies at $z\sim8$ needs to be extrapolated by 4 UV magnitudes below the detection threshold in
%order to provide enough ionizing photons to complete reionization on a timescale consistent with the
%electron scattering optical depth measurements from the CMB \citep{2013ApJ...768...71R}. An
%independent measurement of the state of the IGM at these redshifts would instead provide an integral
%constraint on galaxy properties that includes the important contributions of these fainter galaxies.
%
%Prior to the EoR, the IGM is predominantly composed of neutral hydrogen gas.
%
%
%The 21-cm hyperfine structure transition is one of the few optically thin
%tracers of neutral hydrogen.
%
%
%
%
%
%
%
%
%
%
%
%
%However there
%are no direct observational constraints between $z\sim 10$ and $z\sim 1100$
%(the surface of last scattering).
%
%
%
%
%
%
%
%
%
%21 cm cosmology offers us a window into an epoch of the universe that was
%previously inaccessible.  Hydrogen is the most common element in the universe,
%but the 21 cm hyperfine structure line is so weak that the transition is
%optically thin out to cosmological distances. Therefore by looking for slight
%deviations in the black-body spectrum of the CMB we can begin to probe the
%state of the IGM directly. Because the frequency of these deviations is tied to
%the cosmological redshifting of the 21 cm line, different frequencies probe
%different distances and different times in the universe's history. In this way
%21 cm cosmology can be used to study the dark ages ($z \sim 1100$ to $30$),
%cosmic dawn ($z \sim 30$ to $15$) , and the epoch of reionization ($z \sim 15$
%to $7$).
%
%The observed brightness temperature deviation due to the 21 cm transition is
%\begin{equation}\label{eq:deltaT}
%    \Delta T_B = \tau_{21} \frac{T_s - T_{CMB}}{1 + z},
%\end{equation}
%where $\tau_{21}$ is the optical depth of the 21 cm transition, $T_s$ is the spin temperature of the
%neutral hydrogen gas (the excitation temperature for the 21 cm transition), and $T_{CMB}$ is the
%temperature of the CMB at the appropriate redshift. Equation~\ref{eq:deltaT} defines the scope of 21
%cm cosmology in that it ultimately determines what can and cannot be learned from 21 cm cosmology.
%For example, if the 21 cm transition is in equilibrium with the CMB, the number of photons absorbed
%and the number of photons emitted will be equal. In this case $T_s = T_{CMB}$ and there will be no
%signal to detect. A calculation of $\tau_{21}$ yields
%\begin{equation}\label{eq:deltaT-expanded}
%    \Delta T_B \approx 27 x_{\rm HI} (1+\delta) \left(\frac{1+z}{10}\right)^{1/2}
%                       \left(\frac{T_s - T_{CMB}}{T_s}\right) \, \text{mK},
%\end{equation}
%where $x_{\rm HI}$ is the neutral fraction and $\delta$ is the fractional overdensity of baryons
%\citep{2012RPPh...75h6901P}.
%
%The cosmological 21 cm brightness temperature is therefore expected to be $\sim10$ mK. It is
%sensitive to the neutral fraction of hydrogen and density inhomogeneities. The brightness
%temperature is also sensitive to the quantity $1 - T_{CMB} / T_s$, but note that this term can vary
%from $-T_{CMB} / T_s$ (when $T_s \ll T_{CMB}$) to $1$ (when $T_s \gg T_{CMB}$). This term saturates
%when the spin temperature is large. Figure~\ref{fig:global-signal} illustrates the globally
%averaged 21 cm brightness temperature as a function of time (where $x_{\rm HI}$ and $T_s$ come from
%cosmological simulations). There are three phases where $T_s \ne T_{CMB}$:
%
%\begin{enumerate}
%    \item \emph{The dark ages} -- During this period both the matter and the radiation are cooling
%        due to the expansion of the universe. The matter ($\gamma = 5/3$) cools faster than the
%        radiation ($\gamma = 4/3$) due to the physics of adiabatic cooling. During this time the
%        universe is dense enough such that collisions are enough to couple the spin temperature to
%        the gas temperature and the result is $T_s < T_{CMB}$.
%    \item \emph{The cosmic dawn} -- Once star formation begins, the IGM is inundated with Ly$\alpha$
%        photons which scatter through the IGM. When a hydrogen atom absorbs and re-emits a
%        Ly$\alpha$ photon the spin of the electron can flip. This process is known as the
%        Wouthuysen-Field effect \citep{1952AJ.....57R..31W, 1958PIRE...46..240F}. The ultimate
%        effect of this is that the spin temperature is once again locked to the temperature of the
%        gas. X-ray heating of the IGM eventually warms the gas enough to flip the signal into
%        emission.
%    \item \emph{The epoch of reionization} -- Finally the 21 cm signal dies away as the neutral
%        fraction $x_{\rm HI} \rightarrow 0$ during the epoch of reionization.
%\end{enumerate}
%
%While Figure~\ref{fig:global-signal} shows a theoretical model for the globally averaged 21 cm
%signal as a function of redshift, there will also be spatial fluctuations associated with
%ionization, density, and temperature fluctuations according to Equation~\ref{eq:deltaT-expanded}.
%Figure~\ref{fig:power-spectrum} shows the amplitude of the three-dimensional spatial power spectrum
%as a function of redshift for a variety of theoretical models \citep{2014MNRAS.437L..36F}. The peak
%near $z\sim 30$ is driven by inhomogeneous Ly$\alpha$ flux from early star formation, while the peak
%near $z\sim 20$ is driven by inhomogeneous X-ray heating from the products of early star formation.
%The timing and amplitude of the power spectrum during the cosmic dawn is sensitive to many of the
%details of early star formation including the X-ray emissivity and star formation feedback.
%Additionally, the supersonic relative motion of the baryons relative to the dark matter following
%recombination suppresses star formation in low mass halos, enhancing the amplitude of the
%fluctuations and imprinting the signature of baryon acoustic oscillations (BAO) onto the power
%spectrum \citep{2010PhRvD..82h3520T}. However, strong Lyman-Werner feedback may temper the effects
%of baryon streaming on the power spectrum \citep{2013MNRAS.432.2909F}.
%
%21 cm cosmology is opening a new window into an epoch of the universe that is essentially
%unconstrained by observations. As a result it is a driving science case for many new and planned
%low-frequency radio observatories (MWA, LOFAR, PAPER/HERA, CHIME, SKA, and others). However this
%measurement will be incredibly challenging chiefly due to the fact that the cosmological temperature
%fluctuations are very small relative to the blinding brightness of the Milky Way galaxy's
%synchrotron emission and the sea of unresolved radio galaxies that lie between the telescope and the
%cosmological gold mine. At high galactic latitudes the brightness temperature of the sky is
%\begin{equation}
%    T_{\rm sky} \sim 180 \left(\frac{\nu}{180\,{\rm MHz}}\right)^{-2.6} \, \rm{K},
%\end{equation}
%which means that the foreground emission is $10^4$ to $10^5$ times brighter than the 21 cm
%fluctuations \citep{2006PhR...433..181F}. 21 cm cosmology is therefore a high dynamic range problem
%with strict requirements on instrumental calibration. For example, \citet{2015PhRvD..91h3514S}
%estimate that width of CHIME's antenna response pattern must be known to 0.1\%. Innovative
%calibration and data reduction strategies will be critical.

\section{Observations}

\subsection{The Owens Valley Long Wavelength Array}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{plots/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO LWA.
        The 200 meter diameter area indicated by the dashed line contains 251 antennas distributed
        in a pseudo-random configuration. The 32 filled circles are the expansion antennas built in
        early 2016 to increase the longest baseline to 1.5 km. The 5 open circles are antennas
        equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO LWA is a low-frequency
instrument with instantaneous bandwidth covering 24.768 MHz to 82.296 MHz \todo{double check this
frequency range, I think it's wrong}.  Each antenna stand hosts two perpendicular broadband dipoles
so that there are $288\times2$ signal paths in total. These signal paths feed into the 512-input
LEDA correlator, which allows the OVRO LWA to capture the entire visible hemisphere in a single
snapshot image.  In the current configuration, 32 antennas (64 signal paths) are unused.

The 288 antennas are arranged in a maximally non-redundant configuration optimized for minimum
sidelobes in snapshot imaging. 251 of these antennas are contained within a 200 m diameter core that
is independently optimized for imaging sidelobe levels. 32 antennas are placed outside of the core
in order to extend the maximum baseline length out to $\sim$1.5 km. The final 5 antennas are
equipped with noise-switched front ends for calibrated total power measurements of the global sky
brightness. These antennas are used as part of the LEDA experiment to measure the global signal of
21 cm absorption from the cosmic dawn. \todo{cite a leda paper} Calibrated total power measurements
from these antennas will be used to constrain sky modes with $l \lesssim 2$ including the monopole.

%See Figure~\ref{fig:antenna-layout} for an image of the antenna
%layout. The antennas can be categorized into 3 groups:
%\begin{enumerate}
%    \item
%        Core antennas - 251 antennas are contained within a 200 m diameter core where they are
%        arranged in a configuration optimized to reduce sidelobe levels in snapshot imaging.
%    \item
%        Total power antennas - 5 antennas are equipped with noise-switched front ends for calibrated
%        total power measurements of the sky brightness.
%    \item
%        Expansion antennas - 32 additional antennas were installed in early 2016. These antennas
%        extend the longest baselines of the OVRO LWA out to 1.5 km. This allows for $\sim10$
%        arcminute resolution in the snapshot images.
%\end{enumerate}
%When fully completed, the OVRO LWA will have 352 antennas in total spanning 2.5 km.
%
%\todo{cite Gregg's instrument paper}
%
%The field-of-view and compactness of the OVRO LWA make it a promising instrument for 21 cm
%cosmology. The field-of-view increases the number of cosmological modes measured at any instant in
%time. The inner core of 251 antennas within a 200 m diameter provides excellent brightness
%temperature sensitivity. Figure~\ref{fig:ps-sensitivity} shows the expected signal-noise ratio
%achieved by the OVRO LWA on the three-dimensional spatial power spectrum of 21 cm emission for a
%variety of models. A large integration time and careful calibration will be needed to make a
%detection.
%
%The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-antenna interferometer located at the
%Owens Valley Radio Observatory (OVRO) near Big Pine, California. Each antenna is composed of two
%crossed dipoles bringing the total number of signal paths to 576.  The OVRO LWA hosts the LEDA
%correlator that allows cross-correlation of 512 signal paths with $>50$ MHz instantaneous bandwidth.
%
%Of the 288 antennas, 251 are located within a 200 m diameter core.  The location of these antennas
%has been optimized to minimize imaging sidelobes.  5 antenna stands are dedicated to the LEDA
%experiment and have switching front-ends for total-power radiometry. The remaining 32 antennas
%extend out to 2 km baselines to improve the angular resolution of the interferometer.

\subsection{The OVRO LWA 100 Hour Dataset}

Because the correlator only accepts 512 inputs (256 antennas with 2 polarizations for each antenna),
a subset of the antennas must be selected for correlation.

Include plot of antenna layout.

The integration time is 13 seconds. This was chosen because the remainder of one sidereal day
divided into 13 second intervals is only 90 milliseconds.  Finer control of the integration time is
not possible due to technical constraints.

\subsection{Antenna Gain Calibration}

Antenna gain calibration is accomplished using an iterative method independently developed by
\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
the Julia programming language \citep{BEKS14}, and is publicly available
online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).

The antenna complex gains are updated once per day when Cas A and Cyg A are near the meridian.
These two sources are -- by an order of magnitude -- the brightest radio sources in the northern
hemisphere.  Therefore the optimal time to solve for the interferometer's gain calibration is when
Cas A and Cyg A are at high elevations. A calibration obtained in this manner is good for $>24$
hours. \todo{quantify this? how much does the next day's calibration differ?}

The flux scale is tied to the work of \citet{2016arXiv160905940P}.

\todo{sawtooth pattern removal}

\subsection{Source Removal}

At low frequencies, propagation effects through the ionosphere must be accounted for in order to
achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.

In the dataset used in this paper, scintillation and diffraction events on the timescale of a single
integration (13 seconds) are observed. Therefore the direction dependent calibration changes on
these timescales and the peeling routine must solve for one set of complex gains per source per
integration. Mild smoothing of the gain solutions along the frequency axis is possible without
degrading the dynamic range.

Given the angular resolution of the OVRO LWA and the angular extent of Cas A and Cyg A, these two
sources are marginally resolved and a simple point source model will not achieve the necessary
dynamic range. \todo{describe my source fitting routine}

\subsection{RFI Suppression}

The Owens Valley is an important source of water and power for the city of Los Angeles.
Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO
LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
them by using the curvature of the incoming wavefront. Efforts are currently underway to work with
the utility pole owners to have the arcing fixed.

In the meantime it is possible to suppress their contamination in the dataset.  The path difference
from a point source of RFI located at the position $\vec r$ to two antennas located at positions
$\vec x_1$ and $\vec x_2$ respectively is given by
\begin{equation}
    \delta = \|\vec r - \vec x_1\| - \|\vec r - \vec x_2\|\,,
\end{equation}
where $\|\cdot\|$ denotes the Euclidean norm. The contribution to the visibility observed on the
baseline between these two antennas is therefore
\begin{equation}\label{eq:rfi-contribution}
    V^\text{RFI}_\nu = F_\nu \exp\bigg(2\pi i\frac{\delta}{\lambda}\bigg)\,,
\end{equation}
where $F_\nu$ is the flux of the RFI at the frequency $\nu$ (wavelength $\lambda$).  At first glance
it might seem to be sufficient to know the location of the RFI. Then by fitting for the value of
$F_\nu$ in equation~\ref{eq:rfi-contribution} one can subtract the contribution of the RFI from each
visibility. This approach is insufficient because the RFI originates from extremely low elevations
where antenna shadowing effects are large. In practice this means that the response of each antenna
to a source near or on the horizon is unknown and inhomogeneous between antennas. Therefore a free
parameter for the response of each antenna towards the source of RFI must also be included as a free
parameter when removing the RFI.

\todo{can we take advantage of the fact that the antenna response shouldn't be changing very much
between integrations?}

If the RFI from the horizon is not adequately removed from the data set, it will introduce
systematic errors into the map of the sky.

\subsection{Fitting the Beam}

The OVRO LWA is composed of dipole antennas that are not combined into a beam prior to
cross-correlation. As a result

\subsection{Ionospheric Conditions}

\section{Imaging}

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$. A radio interferometer measures the visibilities
$V_{ij,\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
incident radiation, then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, .
\end{equation}
Imaging the output of a radio interferometer therefore consists of estimating $I_\nu(\hat r)$ given
the available measurements $V^{ij}_\nu$.

Naively one might attempt to solve equation~\ref{eq:basic-imaging} by discretizing, and subsequently
solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations then
the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
the Owens Valley LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit
complex floating point number).  This matrix equation is therefore prohibitively large, and solving
equation~\ref{eq:basic-imaging} by means of discretization is usually impossible \todo{cite Jayce's
paper (has he published that yet?) where he does this, but explain why his work is the exception
instead of the rule}.

Instead it is common to make mild assumptions that simplify equation~\ref{eq:basic-imaging} and ease
the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
$\vec b_{ij}$ lie in a plane and the field-of-view is small, equation~\ref{eq:basic-imaging} can be
well-approximated by a two-dimensional Fourier transform.

\todo{discuss w-projection}

\todo{discuss a-projection}

\citet{2017MNRAS.465.2901Z}

\subsection{$m$-Mode Analysis}

On the other hand, transit telescopes can take advantage of a symmetry in
equation~\ref{eq:basic-imaging} that greatly reduces the amount of computer time required to image
the full-sky with exact incorporation of widefield imaging effects. This technique, called $m$-mode
analysis, also obviates the need for gridding, mosaicing, and multi-scale deconvolution. Instead the
entire sky is imaged in one coherent synthesis imaging step.

In this context we will define a transit telescope as any interferometer where the response pattern
of the individual elements does not change with respect to time. This may be an interferometer like
the OVRO LWA where the correlation elements are fixed dipoles, but it may also be an interferometer
like the MWA if the steerable beams are held in a fixed position (not necessarily at zenith).

We will briefly summarize $m$-mode analysis below, but the interested reader should consult
\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete derivation.

For a transit telescope, the visibilities $V^{ij}_\nu$ are a periodic function of sidereal
time\footnote{
    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the sun)
    will violate this assumption. This paper will, however, demonstrate that the impact on the final
    maps is mild.
}.
Therefore it is a very natural operation to compute the Fourier transform of the visibilities with
respect to sidereal time $\phi\in(0,2\pi]$.
\begin{equation}
    V^{ij}_{m,\nu} = \int_0^{2\pi} V^{ij}_\nu(\phi)\exp\bigg(-im\phi\bigg)\,\d\phi
\end{equation}
The output of this Fourier transform is the set of $m$-modes $V^{ij}_{m,\nu}$ where
$m=0,\,\pm1,\,\pm2,\,\ldots$ is the Fourier conjugate variable to the sidereal time. The $m$-mode
corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly $m=1$
corresponds to the component of the visibilities that varies over half-day timescales. Larger values
of $m$ correspond to components that vary on quicker timescales.

\todo{introduce the baseline transfer function because I will want to use it in later sections}

It can be shown that there is a discrete linear relationship between the $m$-modes $V^{ij}_{m,\nu}$
and the spherical harmonic coefficients of the sky brightness $a_{lm,\nu}$.
\begin{equation}\label{eq:m-mode-sum-equation}
    V^{ij}_{m,\nu} = \sum_l B^{ij}_{lm,\nu} a_{lm,\nu}\,,
\end{equation}
where the transfer coefficients $B^{ij}_{lm,\nu}$ define the interferometer's response to the sky.
For example, the transfer coefficients are a function of the baseline and antenna primary beam
pattern.

Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation where the transfer
matrix $\b B$ is block-diagonal.
\begin{equation}
    \b B = \left(\begin{array}{cccc}
        m = 0 &&& \\
              & m=\pm1 && \\
              && m=\pm2 & \\
              &&& \ddots \\
    \end{array}\right)
\end{equation}
The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the value of $m$.
\begin{equation}\label{eq:m-mode-matrix-equation}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            m\text{-modes} \\
            \vdots \\
        \end{array}
    \right)}^{\b v}
    =
    \overbrace{\left(
        \begin{array}{ccc}
            \ddots & & \\
            & \text{transfer matrix} & \\
            & & \ddots \\
        \end{array}
    \right)}^{\b B}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            a_{lm} \\
            \vdots \\
        \end{array}
    \right)}^{\b a}
\end{equation}

In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
an interferometer like the OVRO LWA with lots of short baselines, a sensible choice is to use all
spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
is determined by the maximum baseline length of the interferometer.  For an interferometer without
short spacings, a minimum value for $l$ might also be used. This $l_\text{min}$ parameter should be
determined by the minimum baseline length.  When creating the maps presented in this paper, we use
$l_\text{min} = 0$ and $l_\text{max} = 1000$.
\todo{exclude l = 0 and cite tejas' paper}

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO LWA. Compare this number with the 5 PB required for the naive approach.  The
power of $m$-mode analysis is the block-diagonal structure of
equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
the case of the OVRO LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
$\sim10^9$ in processing time by using $m$-mode analysis.

Imaging in $m$-mode analysis essentially amounts to inverting
equation~\ref{eq:m-mode-matrix-equation} to solve for the spherical harmonic coefficients $\b a$.
The linear-least squares solution, which minimizes $\|\b v - \b B\b a\|^2$, is given by
\begin{equation}
    \b{\hat a}_\text{LLS} = (\b B^*\b B)^{-1}\b B^*\b v\,,
\end{equation}
where $^*$ indicates the conjugate-transpose. However, usually one will find that $\b B$ is not
full-rank and hence $\b B^*\b B$ is not an invertible matrix. For example, an interferometer located
in the northern hemisphere will never see a region of the southern sky centered on the southern
celestial pole. The $m$-modes contained in the vector $\b v$ must contain no information
about the sky around the southern celestial pole, and therefore the act of multiplying by $\b B$
must destroy some information about the sky. The consequence of this fact is that $\b B^*\b B$ must
have at least one zero eigenvalue, which means it is not invertible.

Another way of looking at the problem is that because the interferometer is not sensitive to part of
the southern hemisphere, there are infinitely many possible solutions to
equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well. So we need to
regularize the problem and apply an additional constraint that prefers a unique solution. For
example, you may prefer that in the absence of any information the sky should be set to zero or you
may prefer that the sky should be set to some prior expectation. The process of Tikhonov
regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for some arbitrary value of
$\epsilon > 0$ chosen by the observer. The solution that minimizes this expression is given by
\begin{equation}
    \b{\hat a}_\text{Tikhonov} = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
\end{equation}
Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
matrix's singularity.

\todo{describe how Tikhonov regularization improves the noise properties of the map}

\todo{describe the Moore-Penrose pseudoinverse and why I have elected not to use it}

While Tikhonov regularization will force unmeasured modes to zero, if a prior map of the sky already
exists, it will be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \epsilon \|\b a-\b
a_\text{prior}\|^2$.

Tikhonov regularization requires the observer to pick the value of $\epsilon$. If $\epsilon$ is too
large then too much importance is placed on minimizing the norm of the solution and the
least-squares residuals will suffer. However if $\epsilon$ is too small then the problem will be
poorly regularized and the resulting sky map may not represent the true sky.

A tool that can be used to address this problem is the L-Curve.

\subsection{$m$-Mode Analysis with the OVRO LWA}

\subsection{CLEAN}

\section{Errors}

\subsection{Horizon RFI}

However it is instructive to analyze the contaminating effect the RFI will have
on $m$-mode analysis maps of the sky. The correlation observed on a given
baseline and frequency channel for a single source of RFI is
\begin{equation}
    V(t) = I(t) B^\textrm{near-field}
\end{equation}

However we need a strategy to mitigate the RFI before imaging. A constant source attached to the
horizon has a fringe rate of zero. The only possible astronomical origins for a source with zero
fringe rate are:

\begin{enumerate}
    \item a point source located at the north or south celestial poles, and
    \item a ring of constant declination.
\end{enumerate}

Therefore while snapshot images will show the RFI source on the horizon, extended integrations will
show the RFI as rings of constant declination. We can take advantage of this discrepancy to separate
astronomical emission from terrestrial RFI.

\subsection{Scintillation}

One of the key assumptions made by $m$-mode analysis is that the sky is completely static.  We
assume that the only time-dependent behavior is the rotation of the Earth, which slowly rotates the
sky through the fringe patterns of the interferometer. At low frequencies the ionosphere violates
this assumption. In particular, ionospheric scintillation will cause even static sources to exhibit
significant variability.

The correlation observed on a given baseline for a single point source is
\begin{equation}
    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
\end{equation}
where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$
is the baseline transfer function. The transfer function is a function of
the direction to the source, which is in turn a function of the sidereal
time $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic
variability or due to scintillation, than the source flux is also a function
of the time coordinate $t$ such that
\begin{equation}
    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
\end{equation}
where $t_{\textrm{sidereal}} = (t \mod 23.9345\,\textrm{hours})$.

Now assume we have observed with our interferometer for a single sidereal day.
In order to compute the $m$-modes we must Fourier transform with respect to
sidereal time. In a real measurement this is a discrete Fourier transform of
the observed correlation with respect to time (where the sum over time is
restricted to a sidereal day). \todo{fix normalization}
\begin{equation}
    V_{\nu, m} = \sum_{t} V_\nu(t) e^{-imt}
\end{equation}
Define $V_{\nu, m}^{\textrm{static}}$ to be the observed $m$-modes if the source
was actually static ($I_\nu(t) \equiv I_{\nu,0}$). Then as a consequence of the
Fourier convolution theorem
\begin{equation}
    V_{\nu, m} = \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}.
\end{equation}

This will tend to scatter power between $m$-modes.

Simulate images of point sources with this

\subsection{Beam Errors}

\subsection{Peeling Failure}

\section{Results}

\subsection{Sky Maps}

\begin{table}[ht]
    \centering
    \begin{tabular}{ccc}
        \# & $\nu$ / MHz & $\Delta\nu$ / MHz \\ \hline
        1 & 36.528 & 0.024 \\
        2 & 41.760 & 0.024 \\
        3 & 46.992 & 0.024 \\
        4 & 52.224 & 0.024 \\
        5 & 57.456 & 0.024 \\
        6 & 62.688 & 0.024 \\
        7 & 67.920 & 0.024 \\
        8 & 73.152 & 0.024 \\
    \end{tabular}
    \caption{Summary of the produced maps}
\end{table}

\subsection{Error Maps}

\todo{Cite Abhilash, Eastwood 2016}

\section{Discussion}

\bibliographystyle{apj}
\bibliography{paper}

\end{document}

### 2017-02-20 paper.tex
elaborate a little bit on the source removal process

@@
 from these antennas will be used to constrain sky modes with $l \lesssim 2$ including the monopole.
+\todo{What values of $l$ actually contribute to the total power measurements?}
 
@@
 
+\subsubsection{Cassiopeia A and Cygnus A}
+
+Without removing bright sources from the data, sidelobes from bright sources will dominate the
+variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2016arXiv160905940P}. A
+conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
+\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
+from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
+\todo{Measure Cyg A's sidelobe levels if it is not subtracted}
+
 At low frequencies, propagation effects through the ionosphere must be accounted for in order to
 achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
-peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.
+peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
+scintillation and diffraction events on the timescale of a single integration (13 seconds) are
+observed. Therefore the direction dependent calibration changes on these timescales and the we must
+solve for one set of complex gains per source per integration.
 
-In the dataset used in this paper, scintillation and diffraction events on the timescale of a single
-integration (13 seconds) are observed. Therefore the direction dependent calibration changes on
-these timescales and the peeling routine must solve for one set of complex gains per source per
-integration. Mild smoothing of the gain solutions along the frequency axis is possible without
-degrading the dynamic range.
+The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
+is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO LWA marginally resolves both
+sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
+source model to eachs ource. This is performed by minimizing the minimizing the variance within an
+aperture located on each source after peeling. By phasing up a large number of integrations before
+imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
+We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
+until the variance within the aperture is minimized.
 
-Given the angular resolution of the OVRO LWA and the angular extent of Cas A and Cyg A, these two
-sources are marginally resolved and a simple point source model will not achieve the necessary
-dynamic range. \todo{describe my source fitting routine}
+\todo{Show a before and after with the updated source models}
 
-\subsection{RFI Suppression}
+\todo{Give a plot with the updated source models}
+
+\subsubsection{The Sun}
+
+The Sun can be trivially removed from any map of the sky by constructing the map using only data
+taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
+However the OVRO LWA 100 hour dataset consists of 100 consecutive hours of data, and hence roughly
+half of the data is from the day.
+
+The Sun is a time variable source in radio.
+
+\todo{does the previous routine work on the Sun too? worth a shot}
+
+\subsubsection{Sparking Power Lines}
 
@@
 them by using the curvature of the incoming wavefront. Efforts are currently underway to work with
-the utility pole owners to have the arcing fixed.
+the utility pole owners to have these insulators replaced.
 
@@
 
-\subsection{Horizon RFI}
+\subsection{Stationary Correlated Noise}
 
@@
 
-\subsection{Scintillation}
+\subsection{Ionospheric Scintillation}
 
@@
 
+\subsection{Ionospheric Refraction}
+
 \subsection{Beam Errors}
-
-\subsection{Peeling Failure}
 

### 2017-02-21 paper.tex
more progress...

@@
 The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is a data-driven
-interpolation of various maps between 10 MHz and 100 GHz, but below 408 MHz, the interpolation is
-largely driven by the Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H}.
+interpolation of various maps between 10 MHz and 100 GHz. However the majority of information
+contained in the GSM is derived at higher frequencies where the majority of the input maps are from.
+Below 408 MHz, the interpolation is largely driven by the Haslam 408 MHz map
+\citep{1981A&A...100..209H, 1982A&AS...47....1H}.  At lower frequencies, free-free absorption and
+synchrotron self-absorption becomes increasingly important and hence spectral indices derived at
+higher frequencies need corrections at lower frequencies.
+
+\citet{2011A&A...525A.138G}
 
 \todo{TGSS, MSSS, GLEAM}
-
-At lower frequencies, free-free absorption and synchrotron self-absorption becomes important.
 
@@
 Planets?
-
-%Optical observers have become increasingly proficient at discovering high-redshift galaxies
-%\citep{2013ApJS..209....3K} and quasars \citep{2011Natur.474..616M}.  While these objects have
-%provided valuable insight into galaxy formation and the timing of the epoch of reionization (EoR),
-%they are necessarily exceptional. Flux-limited surveys find the most luminous objects, which are not
-%representative of galaxy properties as a whole.  Furthermore, the observed luminosity function of
-%galaxies at $z\sim8$ needs to be extrapolated by 4 UV magnitudes below the detection threshold in
-%order to provide enough ionizing photons to complete reionization on a timescale consistent with the
-%electron scattering optical depth measurements from the CMB \citep{2013ApJ...768...71R}. An
-%independent measurement of the state of the IGM at these redshifts would instead provide an integral
-%constraint on galaxy properties that includes the important contributions of these fainter galaxies.
-%
-%Prior to the EoR, the IGM is predominantly composed of neutral hydrogen gas.
-%
-%
-%The 21-cm hyperfine structure transition is one of the few optically thin
-%tracers of neutral hydrogen.
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%However there
-%are no direct observational constraints between $z\sim 10$ and $z\sim 1100$
-%(the surface of last scattering).
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%21 cm cosmology offers us a window into an epoch of the universe that was
-%previously inaccessible.  Hydrogen is the most common element in the universe,
-%but the 21 cm hyperfine structure line is so weak that the transition is
-%optically thin out to cosmological distances. Therefore by looking for slight
-%deviations in the black-body spectrum of the CMB we can begin to probe the
-%state of the IGM directly. Because the frequency of these deviations is tied to
-%the cosmological redshifting of the 21 cm line, different frequencies probe
-%different distances and different times in the universe's history. In this way
-%21 cm cosmology can be used to study the dark ages ($z \sim 1100$ to $30$),
-%cosmic dawn ($z \sim 30$ to $15$) , and the epoch of reionization ($z \sim 15$
-%to $7$).
-%
-%The observed brightness temperature deviation due to the 21 cm transition is
-%\begin{equation}\label{eq:deltaT}
-%    \Delta T_B = \tau_{21} \frac{T_s - T_{CMB}}{1 + z},
-%\end{equation}
-%where $\tau_{21}$ is the optical depth of the 21 cm transition, $T_s$ is the spin temperature of the
-%neutral hydrogen gas (the excitation temperature for the 21 cm transition), and $T_{CMB}$ is the
-%temperature of the CMB at the appropriate redshift. Equation~\ref{eq:deltaT} defines the scope of 21
-%cm cosmology in that it ultimately determines what can and cannot be learned from 21 cm cosmology.
-%For example, if the 21 cm transition is in equilibrium with the CMB, the number of photons absorbed
-%and the number of photons emitted will be equal. In this case $T_s = T_{CMB}$ and there will be no
-%signal to detect. A calculation of $\tau_{21}$ yields
-%\begin{equation}\label{eq:deltaT-expanded}
-%    \Delta T_B \approx 27 x_{\rm HI} (1+\delta) \left(\frac{1+z}{10}\right)^{1/2}
-%                       \left(\frac{T_s - T_{CMB}}{T_s}\right) \, \text{mK},
-%\end{equation}
-%where $x_{\rm HI}$ is the neutral fraction and $\delta$ is the fractional overdensity of baryons
-%\citep{2012RPPh...75h6901P}.
-%
-%The cosmological 21 cm brightness temperature is therefore expected to be $\sim10$ mK. It is
-%sensitive to the neutral fraction of hydrogen and density inhomogeneities. The brightness
-%temperature is also sensitive to the quantity $1 - T_{CMB} / T_s$, but note that this term can vary
-%from $-T_{CMB} / T_s$ (when $T_s \ll T_{CMB}$) to $1$ (when $T_s \gg T_{CMB}$). This term saturates
-%when the spin temperature is large. Figure~\ref{fig:global-signal} illustrates the globally
-%averaged 21 cm brightness temperature as a function of time (where $x_{\rm HI}$ and $T_s$ come from
-%cosmological simulations). There are three phases where $T_s \ne T_{CMB}$:
-%
-%\begin{enumerate}
-%    \item \emph{The dark ages} -- During this period both the matter and the radiation are cooling
-%        due to the expansion of the universe. The matter ($\gamma = 5/3$) cools faster than the
-%        radiation ($\gamma = 4/3$) due to the physics of adiabatic cooling. During this time the
-%        universe is dense enough such that collisions are enough to couple the spin temperature to
-%        the gas temperature and the result is $T_s < T_{CMB}$.
-%    \item \emph{The cosmic dawn} -- Once star formation begins, the IGM is inundated with Ly$\alpha$
-%        photons which scatter through the IGM. When a hydrogen atom absorbs and re-emits a
-%        Ly$\alpha$ photon the spin of the electron can flip. This process is known as the
-%        Wouthuysen-Field effect \citep{1952AJ.....57R..31W, 1958PIRE...46..240F}. The ultimate
-%        effect of this is that the spin temperature is once again locked to the temperature of the
-%        gas. X-ray heating of the IGM eventually warms the gas enough to flip the signal into
-%        emission.
-%    \item \emph{The epoch of reionization} -- Finally the 21 cm signal dies away as the neutral
-%        fraction $x_{\rm HI} \rightarrow 0$ during the epoch of reionization.
-%\end{enumerate}
-%
-%While Figure~\ref{fig:global-signal} shows a theoretical model for the globally averaged 21 cm
-%signal as a function of redshift, there will also be spatial fluctuations associated with
-%ionization, density, and temperature fluctuations according to Equation~\ref{eq:deltaT-expanded}.
-%Figure~\ref{fig:power-spectrum} shows the amplitude of the three-dimensional spatial power spectrum
-%as a function of redshift for a variety of theoretical models \citep{2014MNRAS.437L..36F}. The peak
-%near $z\sim 30$ is driven by inhomogeneous Ly$\alpha$ flux from early star formation, while the peak
-%near $z\sim 20$ is driven by inhomogeneous X-ray heating from the products of early star formation.
-%The timing and amplitude of the power spectrum during the cosmic dawn is sensitive to many of the
-%details of early star formation including the X-ray emissivity and star formation feedback.
-%Additionally, the supersonic relative motion of the baryons relative to the dark matter following
-%recombination suppresses star formation in low mass halos, enhancing the amplitude of the
-%fluctuations and imprinting the signature of baryon acoustic oscillations (BAO) onto the power
-%spectrum \citep{2010PhRvD..82h3520T}. However, strong Lyman-Werner feedback may temper the effects
-%of baryon streaming on the power spectrum \citep{2013MNRAS.432.2909F}.
-%
-%21 cm cosmology is opening a new window into an epoch of the universe that is essentially
-%unconstrained by observations. As a result it is a driving science case for many new and planned
-%low-frequency radio observatories (MWA, LOFAR, PAPER/HERA, CHIME, SKA, and others). However this
-%measurement will be incredibly challenging chiefly due to the fact that the cosmological temperature
-%fluctuations are very small relative to the blinding brightness of the Milky Way galaxy's
-%synchrotron emission and the sea of unresolved radio galaxies that lie between the telescope and the
-%cosmological gold mine. At high galactic latitudes the brightness temperature of the sky is
-%\begin{equation}
-%    T_{\rm sky} \sim 180 \left(\frac{\nu}{180\,{\rm MHz}}\right)^{-2.6} \, \rm{K},
-%\end{equation}
-%which means that the foreground emission is $10^4$ to $10^5$ times brighter than the 21 cm
-%fluctuations \citep{2006PhR...433..181F}. 21 cm cosmology is therefore a high dynamic range problem
-%with strict requirements on instrumental calibration. For example, \citet{2015PhRvD..91h3514S}
-%estimate that width of CHIME's antenna response pattern must be known to 0.1\%. Innovative
-%calibration and data reduction strategies will be critical.
 
@@
 
-The antenna complex gains are updated once per day when Cas A and Cyg A are near the meridian.
-These two sources are -- by an order of magnitude -- the brightest radio sources in the northern
-hemisphere.  Therefore the optimal time to solve for the interferometer's gain calibration is when
-Cas A and Cyg A are at high elevations. A calibration obtained in this manner is good for $>24$
-hours. \todo{quantify this? how much does the next day's calibration differ?}
+The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
+are at high elevations.  These two sources are -- by an order of magnitude -- the brightest radio
+sources in the northern hemisphere.  Therefore the optimal time to solve for the interferometer's
+gain calibration is when Cas A and Cyg A are at high elevations. A calibration obtained in this
+manner is good consistent with the following day's calibration to within a 1\% error in the flux
+scale and 1$'$ error in the astrometry \todo{double check these numbers}. These residual errors are
+likely driven by differing ionospheric conditions.
 
@@
 
-\todo{sawtooth pattern removal}
+\todo{sawtooth pattern removal, does it affect phase???}
 
@@
 
-In the meantime it is possible to suppress their contamination in the dataset.  The path difference
-from a point source of RFI located at the position $\vec r$ to two antennas located at positions
-$\vec x_1$ and $\vec x_2$ respectively is given by
-\begin{equation}
-    \delta = \|\vec r - \vec x_1\| - \|\vec r - \vec x_2\|\,,
-\end{equation}
-where $\|\cdot\|$ denotes the Euclidean norm. The contribution to the visibility observed on the
-baseline between these two antennas is therefore
-\begin{equation}\label{eq:rfi-contribution}
-    V^\text{RFI}_\nu = F_\nu \exp\bigg(2\pi i\frac{\delta}{\lambda}\bigg)\,,
-\end{equation}
-where $F_\nu$ is the flux of the RFI at the frequency $\nu$ (wavelength $\lambda$).  At first glance
-it might seem to be sufficient to know the location of the RFI. Then by fitting for the value of
-$F_\nu$ in equation~\ref{eq:rfi-contribution} one can subtract the contribution of the RFI from each
-visibility. This approach is insufficient because the RFI originates from extremely low elevations
-where antenna shadowing effects are large. In practice this means that the response of each antenna
-to a source near or on the horizon is unknown and inhomogeneous between antennas. Therefore a free
-parameter for the response of each antenna towards the source of RFI must also be included as a free
-parameter when removing the RFI.
+In the meantime it is possible to suppress their contamination in the dataset. The contribution of
+these RFI sources to the visibilities can be plainly seen by averaging $>$24 hours of data with the
+phase center set to zenith. In this way, true sky components are smeared along tracks of constant
+declination while terrestrial sources (ie. the arcing power lines) are not smeared. For similar
+reasons, when constructing a map of the sky from $>$24 hours of data these sparking power lines will
+produce artifacts in the map that are smeared along tracks of constant declination. However while
+the amplitude of the RFI will fluctuate with time, its phase will be constant. Therefore if you can
+use isolate a set of model visibilities for the RFI, it can be removed from each integration by
+scaling and subtracting these model visibilities from the measured visibilities.
 
-\todo{can we take advantage of the fact that the antenna response shouldn't be changing very much
-between integrations?}
+Obtaining a model for the RFI is complicated by the fact that the contaminating sources are at
+extremely low elevations where the antenna response is maximally inhomogeneous. Therefore it is not
+enough to know the physical location of the faulty insulator generating the RFI. In addition you
+must also know the response of each antenna (amplitude and phase) in the appropriate direction. This
+motivates the use of peeling, which allows the antenna response to be a free parameter.
 
-If the RFI from the horizon is not adequately removed from the data set, it will introduce
-systematic errors into the map of the sky.
+Therefore model visibilities for the RFI can be obtained by peeling the sources after smearing the
+visibilities over $>$24 hours. These model visibilities are then scaled and subtracted from each
+integration in the data set.
 
-\subsection{Fitting the Beam}
+\todo{show an example smeared image before and after peeling}
 
-The OVRO LWA is composed of dipole antennas that are not combined into a beam prior to
-cross-correlation. As a result
+\subsection{Fitting the Antenna Response}
 
-\subsection{Ionospheric Conditions}
+In order to generate wide-field images of the sky, the response of the antenna to the sky must be
+known. Fortunately drift-scanning interferometers like the OVRO LWA can empirically measure their
+primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
+assume that the primary beam is invariant under north-south and east-west flips, and additionally
+that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
+We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
+then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
+basis functions to have the desired symmetry.
 
@@
 
+\begin{figure*}[ht]
+    \includegraphics[width=\textwidth, draft]{maps/rgb-map}
+    \caption{three color map}
+\end{figure*}
+
+\begin{figure*}[ht]
+    \centering
+    \begin{tabular}{cc}
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+    \end{tabular}
+    \caption{single channel maps}
+\end{figure*}
+
+\begin{figure*}[ht]
+    \centering
+    \begin{tabular}{cc}
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+    \end{tabular}
+    \caption{jackknifed error maps}
+\end{figure*}
+
 \begin{table}[ht]

### 2017-02-22 paper.tex
add a paragraph on removing the amplitude of the sawtooth pattern

@@
 
-\todo{sawtooth pattern removal, does it affect phase???}
+Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
+analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
+gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
+The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
+per-antenna amplitude correction that is then applied to the cross-correlations.
 
@@
 \begin{figure*}[ht]
-    \includegraphics[width=\textwidth, draft]{maps/rgb-map}
+    \includegraphics[width=\textwidth]{maps/rgb-map-small}
     \caption{three color map}

### 2017-02-24 paper.tex
add images of the smeared visibilities to illustrate the RFI

@@
     \centering
-    \includegraphics[width=\columnwidth]{plots/antenna-layout}
+    \includegraphics[width=\columnwidth]{figures/antenna-layout}
     \caption{
@@
 \todo{show an example smeared image before and after peeling}
+
+\begin{figure*}[ht]
+    \centering
+    \begin{tabular}{cccc}
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
+    \end{tabular}
+    \caption{
+        Snapshot images after smearing the visiblities over the entire 100 hour observation window.
+    }
+\end{figure*}
 

### 2017-02-24 figures/antenna-layout.jl

@@ -1,0 +1,59 @@
+using PyPlot
+
+matrix = readdlm("antenna-layout.txt");
+east = matrix[:,1];
+north = matrix[:,2];
+up = matrix[:,3];
+east -= 2
+
+core = 1:251
+leda = 252:256
+expansion = 257:288
+
+θ = linspace(0, 2π, 1000)
+circlex = 110sin(θ)
+circley = 110cos(θ)
+
+transparent = (0, 0, 0, 0)
+rc("xtick", labelsize=16)
+rc("ytick", labelsize=16)
+
+figure(1, figsize=(6,6)); clf()
+
+#subplot(1,2,1)
+scatter(east[leda], north[leda], c=transparent, s=30, lw=2)
+scatter(east[expansion], north[expansion], c="k", s=30, lw=2)
+plot(circlex, circley, "k--", lw=2)
+xticks(collect(-1250:250:500))
+yticks(collect(-500:250:1000))
+xlim(-1250, 500)
+ylim(-625, 1125)
+gca()[:set_aspect]("equal")
+gca()[:spines]["top"][:set_visible](false)
+gca()[:spines]["right"][:set_visible](false)
+gca()[:get_xaxis]()[:tick_bottom]()
+gca()[:get_yaxis]()[:tick_left]()
+grid("off")
+xlabel("distance east / meters", fontsize=16)
+ylabel("distance north / meters", fontsize=16)
+tight_layout()
+
+#subplot(1,2,2)
+#scatter(east, north, c="k", s=50, lw=0)
+#plot(circlex, circley, "k--", lw=2)
+#xticks(collect(-150:50:150))
+#yticks(collect(-150:50:150))
+#xlim(-125, 125)
+#ylim(-125, 125)
+#gca()[:set_aspect]("equal")
+#gca()[:spines]["top"][:set_visible](false)
+#gca()[:spines]["right"][:set_visible](false)
+#gca()[:get_xaxis]()[:tick_bottom]()
+#gca()[:get_yaxis]()[:tick_left]()
+#grid("off")
+#xlabel("distance east / meters", fontsize=24)
+#ylabel("distance north / meters", fontsize=24)
+#tight_layout()
+
+savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0, transparent=true)
+

### 2017-02-24 plots/antenna-layout.jl

@@ -1,59 +1,0 @@
-using PyPlot
-
-matrix = readdlm("antenna-layout.txt");
-east = matrix[:,1];
-north = matrix[:,2];
-up = matrix[:,3];
-east -= 2
-
-core = 1:251
-leda = 252:256
-expansion = 257:288
-
-θ = linspace(0, 2π, 1000)
-circlex = 110sin(θ)
-circley = 110cos(θ)
-
-transparent = (0, 0, 0, 0)
-rc("xtick", labelsize=16)
-rc("ytick", labelsize=16)
-
-figure(1, figsize=(6,6)); clf()
-
-#subplot(1,2,1)
-scatter(east[leda], north[leda], c=transparent, s=30, lw=2)
-scatter(east[expansion], north[expansion], c="k", s=30, lw=2)
-plot(circlex, circley, "k--", lw=2)
-xticks(collect(-1250:250:500))
-yticks(collect(-500:250:1000))
-xlim(-1250, 500)
-ylim(-625, 1125)
-gca()[:set_aspect]("equal")
-gca()[:spines]["top"][:set_visible](false)
-gca()[:spines]["right"][:set_visible](false)
-gca()[:get_xaxis]()[:tick_bottom]()
-gca()[:get_yaxis]()[:tick_left]()
-grid("off")
-xlabel("distance east / meters", fontsize=16)
-ylabel("distance north / meters", fontsize=16)
-tight_layout()
-
-#subplot(1,2,2)
-#scatter(east, north, c="k", s=50, lw=0)
-#plot(circlex, circley, "k--", lw=2)
-#xticks(collect(-150:50:150))
-#yticks(collect(-150:50:150))
-#xlim(-125, 125)
-#ylim(-125, 125)
-#gca()[:set_aspect]("equal")
-#gca()[:spines]["top"][:set_visible](false)
-#gca()[:spines]["right"][:set_visible](false)
-#gca()[:get_xaxis]()[:tick_bottom]()
-#gca()[:get_yaxis]()[:tick_left]()
-#grid("off")
-#xlabel("distance east / meters", fontsize=24)
-#ylabel("distance north / meters", fontsize=24)
-#tight_layout()
-
-savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0, transparent=true)
-

### 2017-02-24 paper.tex
updated figure caption

@@
     \caption{
-        Snapshot images after smearing the visiblities over the entire 100 hour observation window.
+        Dirty snapshot images after smearing the visiblities over the entire 100 hour observation
+        window.  The two bright source tracks correspond to Cas A (top track) and Cyg A (bottom
+        track) smeared along a ring of constant declination. The sources dotting the horizon are
+        faulty power line insulators.
     }

### 2017-04-03 paper.tex
paragraph on tejas' paper explaining why we subtract the monopole

@@
 $l_\text{min} = 0$ and $l_\text{max} = 1000$.
-\todo{exclude l = 0 and cite tejas' paper}
+
+The interferometer's sensitivity to $l=0$, however, deserves special consideration.
+\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that an interferometer is
+only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
+common-mode noise pick-up. In fact, the sensitivity of the interferometer is proportional to the
+amplitude of these effects. For consistency we will include $a_{00}$ while solving
+Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
+because we do not have a measurement of cross-talk or common-mode noise pick-up.
 

### 2017-04-03 paper.tex
update the Julia language paper reference

@@
 \citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
-the Julia programming language \citep{BEKS14}, and is publicly available
+the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
 online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).

### 2017-04-03 paper.tex
explain how Tikhonov regularization improves the noise properties

@@
 \renewcommand{\d}{{\rm d}}
+\newcommand{\atikh}{\b{\hat a}_\text{Tikhonov}}
 \newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
@@
 example, you may prefer that in the absence of any information the sky should be set to zero or you
-may prefer that the sky should be set to some prior expectation. The process of Tikhonov
-regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for some arbitrary value of
-$\epsilon > 0$ chosen by the observer. The solution that minimizes this expression is given by
-\begin{equation}
-    \b{\hat a}_\text{Tikhonov} = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
+may prefer that the sky should be set to some prior expectation.
+
+The process of Tikhonov regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for
+some arbitrary value of $\epsilon > 0$ chosen by the observer. The solution that minimizes this
+expression is given by
+\begin{equation}\label{eq:tikhonov-solution}
+    \atikh = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
 \end{equation}
 Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
-matrix's singularity.
+matrix's singularity. We can see this by using the singular value decomposition (SVD) of the matrix
+$\b B = \b U \b \Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
+\[
+    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,.
+\]
+The diagonal elements of $\b\Sigma$ are the singular values of $\b B$ and so the contribution of
+each singular component to the Tikhonov-regularized solution is scaled by $\sigma / (\sigma^2 +
+\epsilon)$, where $\sigma$ is the singular value for the given singular component. Tikhonov
+regularization therefore acts to suppress any component for which $\sigma\lesssim\sqrt{\epsilon}$.
+If $\sigma = 0$, the component is set to zero.
 
-\todo{describe how Tikhonov regularization improves the noise properties of the map}
+In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
+purposes we now assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
+Tikhonov-regularized spherical harmonic coefficients $\b C = \left\langle\atikh^*\atikh\right\rangle
+- \left\langle\atikh\right\rangle\left\langle\atikh^*\right\rangle$ is
+\begin{equation}
+    \b C = n \b V \b\Sigma^2 (\b\Sigma^2 + \epsilon\b I)^{-2} \b V^*\,.
+\end{equation}
+Each singular component is scaled by a factor of $\sigma^2/(\sigma^2 + \epsilon)^2$.
+In the absence of Tikhonov regularization ($\epsilon=0$)
+singular components with the smallest singular values -- the ones that the interferometer is
+the least sensitive to -- actually come to dominate the covariance of the measured spherical
+harmonic coefficients. Tikhonov regularization improves this situation by downweighting these
+components.
 

### 2017-04-05 paper.tex
s/common mode noise pickup/common mode noise
After discussion with Harish we decideded this was a better term because
"pickup" is usually referred to RFI-like things.

@@
 only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
-common-mode noise pick-up. In fact, the sensitivity of the interferometer is proportional to the
-amplitude of these effects. For consistency we will include $a_{00}$ while solving
+common-mode noise. In fact, the sensitivity of the interferometer is proportional to the amplitude
+of these effects. For consistency we will include $a_{00}$ while solving
 Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
-because we do not have a measurement of cross-talk or common-mode noise pick-up.
+because we do not have a measurement of cross-talk or common-mode noise.
 

### 2017-04-14 paper.tex
add info on l-curves and how to compute the psf

@@
 
+\subsection{$m$-Mode Analysis Imaging}
+
 Imaging in $m$-mode analysis essentially amounts to inverting
@@
 may prefer that the sky should be set to some prior expectation.
+
+\subsubsection{The Moore-Penrose Pseudoinverse}
+
+\todo{describe the Moore-Penrose pseudoinverse and why I have elected not to use it}
+
+\subsubsection{Tikhonov Regularization}
 
@@
 
-\todo{describe the Moore-Penrose pseudoinverse and why I have elected not to use it}
-
 While Tikhonov regularization will force unmeasured modes to zero, if a prior map of the sky already
@@
 
+\subsubsection{L-Curves}
+
 Tikhonov regularization requires the observer to pick the value of $\epsilon$. If $\epsilon$ is too
@@
 least-squares residuals will suffer. However if $\epsilon$ is too small then the problem will be
-poorly regularized and the resulting sky map may not represent the true sky.
+poorly regularized and the resulting sky map may not represent the true sky. Picking the value of
+$\epsilon$ therefore requires understanding the trade-off between the two norms.
 
-A tool that can be used to address this problem is the L-Curve.
+This trade-off can be analyzed quantitatively by trialing several values of $\epsilon$ and computing
+$\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in Figure \todo{create
+a figure}. The shape of this curve has a characteristic L-shape, and as a result this type of plot
+is called an L-curve \todo{reference}. The ideal value of $\epsilon$ lies near the turning point of
+the plot. At this point a small decrease in $\epsilon$ will lead to an undesired rapid increase in
+$\|\b a\|^2$, and a small increase in $\epsilon$ will lead to an undesired rapid increase in $\|\b v
+- \b B\b a\|^2$.
+
+In practice, the L-curve should be used as a guide to estimate a reasonable value of $\epsilon$.
+However better results can often be obtained by tuning the value of $\epsilon$. For instance
+increasing the value of $\epsilon$ can improve the noise properties of the map by down-weighting
+noisy modes. Decreasing the value of $\epsilon$ can improve the resolution in the map by
+up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
+choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
+imaging where robust weighting schemes can be tuned to similar effect.
 
@@
 \subsection{CLEAN}
+
+While $m$-mode analysis imaging automatically deconvolves large angular scales, point sources do not
+get deconvolved by the imaging process. This is a limitation of the set of basis functions we have
+chosen to represent the sky -- the spherical harmonics. Point sources carry power to large values of
+$l$, but the regularization will eventually begin to downweight spherical harmonics with $l$ larger
+than what the interferometer is sensitive to. This consequence of this is that point sources will
+appear in the maps with some characteristic point spread function. This point spread function may be
+computed with
+\begin{equation}
+    \b a_\text{PSF}(\theta, \phi)
+        = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
+\end{equation}
+where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
+the point spread function at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta,
+\phi)$ is the vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given
+by
+\begin{equation}
+    a_{lm, \text{PS}}(\theta, \phi) = Y_{lm}^*(\theta, \phi)\,.
+\end{equation}
+
+\todo{include a few images of the computed PSF for my maps}
+
+\todo{describe how we incorporate this into major and minor iterations}
 

### 2017-04-14 paper.tex
include a paragraph on the moore-penrose pseudoinverse

@@
 
-\subsubsection{The Moore-Penrose Pseudoinverse}
-
-\todo{describe the Moore-Penrose pseudoinverse and why I have elected not to use it}
-
 \subsubsection{Tikhonov Regularization}
@@
 imaging where robust weighting schemes can be tuned to similar effect.
+
+\subsubsection{The Moore-Penrose Pseudoinverse}
+
+The Moore-Penrose pseudoinverse (denoted in this paper with a superscript $\dagger$), is commonly
+applied to find the minimum-norm linear-least squares solution to a set of linear equations. This
+can be used in place of Tikhonov regularization as
+\begin{equation}
+    \b{\hat a}_\text{Moore-Penrose} = \b B^\dagger\b v\,.
+\end{equation}
+Much like Tikhonov regularization, the Moore-Penrose pseudoinverse sets components with small
+singular values (below some user-defined threshold) to zero. Components with large singular values
+(above the user-defined threshold) are included in the calculation at their full amplitude with no
+down-weighting of modes near the threshold. The essential difference between using the Moore-Penrose
+pseudoinverse and Tikhonov regularization is that the pseudoinverse defines a hard transition from
+on-off. Modes are either set to zero or included in the map at their full amplitude. On the other
+hand Tikhonov regularization smoothly interpolates between these behaviors. Because of this,
+Tikhonov regularization tends to produce better results in practical applications.
 

### 2017-05-05 paper.tex
add some words on terrestrial interference

@@
 pseudoinverse and Tikhonov regularization is that the pseudoinverse defines a hard transition from
-on-off. Modes are either set to zero or included in the map at their full amplitude. On the other
+on to off. Modes are either set to zero or included in the map at their full amplitude. On the other
 hand Tikhonov regularization smoothly interpolates between these behaviors. Because of this,
@@
 
-\subsection{Stationary Correlated Noise}
+\subsection{Terrestrial Interference}
+
+When writing down equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated
+voltage fluctuations measured between pairs of antennas are generated by astronomical sources of
+radio emission. In practice, this implicit assumption can be violated. For instance a low-frequency
+interferometer located in the vicinity of an arcing power line will see an additional contribution
+from the radio-frequency interference (RFI) generated by the arcing process. Similarly common-mode
+pickup along the analog signal path of the interferometer may generate an additional spurious
+contribution to the measured visibilities. While the amplitude and phase of these contaminating
+signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
+characteristic of astronomical sources.
+
+The first step in equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step we
+compute the projection of the measurement $\b v$ onto the space spanned by the columns of $\b B$.
+Each column of $\b B$ describes the interferometer's response to a corresponding spherical harmonic
+coefficient of the sky brightness distribution. Therefore the act of computing $\b B^*\b v$ is to
+project the measured $m$-modes onto the space of $m$-modes which could be generated by astronomical
+sources. The degree to which a source of terrestrial interferer will contaminate a map generated
+using $m$-mode analysis imaging is determined by its amplitude after projection.
+
+For instance, a bright interfering source might contribute $\b v_\text{terrestrial}$ to the measured
+$m$-modes. However, if $\b v_\text{terrestrial}$ is actually perpendicular to all of the columns of
+$\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = 0$.  In
+practice this is unlikely. In general the contamination is proportional to the overall amplitude of
+the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
+an astronomical signal ($\|\b B^*\b v_\text{terrestrial}\|/\|\b v_\text{terrestrial}\|$).
+
+These astronomical sources are anchored to the celestial sphere and therefore rotate
+across the sky over the course of a sidereal day. Terrestrial source of interference are not
+anchored to the celestial sphere.
+
+This characteristic motion of astronomical sources
+is a fundamental component to $m$-mode analysis imaging
+
+radio emission is astronomical. Astronomical sources are anchored to the celestial sphere and
+therefore rotate across the sky over the course of a sidereal day. However, in a practice
+
+$m$-mode analysis imaging implicitly assumes that the correlation between any two pairs of antennas
 

### 2017-05-05 paper.tex
rework the introduction

@@
 Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
-universe during the epoch of recombination \citep{2013ApJS..208...19H}.  Following the epoch of
-recombination the universe continued to expand and cool.  Small inhomogeneities observed in the CMB
-grew larger and galaxies formed. The first stars formed and flooded the universe with light during
-the cosmic dawn, bringing the dark ages to an end. Eventually the cumulative influence of these
-galaxies completed a phase change in the inter-galactic medium (IGM), and the universe returned to
-an ionized state following the conclusion of the epoch of reionization (EoR). Low frequency radio
-telescopes are poised to provide the first direct detection of the IGM from the cosmic dawn and the
-EoR using the redshifted hyperfine structure line of neutral hydrogen.
+universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
+2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
+intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
+interstellar medium (ISM). Careful measurement and removal of contaminating foreground emission is
+therefore an important component for CMB analysis \citep{2016A&A...594A..25P}. On large angular
+scales galactic synchrotron, free-free, thermal dust, and anomolous microwave emission contribute.
+On smaller angular scales point sources such as distant galaxies and quasars contribute
+\citep{2016arXiv160603606D}.
 
-These low-frequency 21-cm cosmology experiments are limited by the dynamic range they can achieve
-against the low-redshift sources of emission. Depending on the redshift, length scale, and model the
-expected amplitude of the cosmological signal is 10 to 100 mK. On the other hand the galactic
-synchrotron emission is 1000 to 10000 K. \todo{citation} Therefore experiments conservatively need
-to achieve at least 4 orders of dynamic range. In theory this kind of dynamic range can be obtained
-by exploiting the fact that the foreground emission is predominantly synchrotron emission that has a
-smooth power law spectrum. On the other hand the frequency structure of the cosmological signal is
-expected to be un-smooth because different frequencies trace different redshifts. This is the basic
-assumption made by all published upper limits on the cosmological 21 cm power spectrum.  In practice
-the interferometer itself imparts frequency structure into the measurements and therefore an
-experiment's ability to separate the foreground signal from the cosmological signal can be limited
-by the instrumental spectral smoothness.
+Propagation effects from the IGM and intervening galaxy clusters can distort the thermal spectrum of
+the CMB and impart information about the intervening material in those distortions. For instance the
+measured optical depth to Thomson scattering implies a mean redshift of the Epoch of Reionization
+(EoR) of ??? \todo{put number and citation}. The thermal Sunyaev--Zel'dovich effect does something
+\todo{thing and citation}. The kinetic Synyaev--Zel'dovich effect does another thing \todo{thing and
+citation}.
+
+At redshifts $20 \gtrsim z \gtrsim 7$ neutral hydrogen is observable as a 10 to 100 mK perturbation
+of the CMB spectrum due to the 21 cm hyperfine structure line of neutral hydrogen
+\citep{2006PhR...433..181F, 2012RPPh...75h6901P}.  The spatial power spectrum of this perturbation
+is expected to be dominated by inhomogeneous heating of the IGM at $z\sim 20$
+\citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim 7$
+\todo{citation}.
+
+\todo{discuss more interesting science to be done}
+
+There are numerous ongoing efforts to detect the cosmologically redshifted 21 cm transition
+including from PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
+\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.
+
+\todo{discuss global experiments too}
+
+These low-frequency 21 cm cosmology experiments are limited by the dynamic range they can achieve
+against low-redshift sources of emission. The brightness temperature of the galactic synchrotron
+emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
+\begin{equation}
+    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
+\end{equation}
+Therefore experiments conservatively need to achieve at least 4 orders of dynamic range.  In theory
+this kind of dynamic range can be obtained by exploiting the fact that the foreground emission is
+predominantly synchrotron emission that has a smooth power law spectrum \todo{citation}.  In
+practice the interferometer itself imparts frequency structure into the measurements and therefore
+an experiment's ability to separate the foreground signal from the cosmological signal can be
+limited by the instrumental spectral smoothness \todo{citation}.
 
@@
 \todo{TGSS, MSSS, GLEAM}
-
-Galactic structure.
-
-Planets?
 

### 2017-05-06 paper.tex
work on the observations description now

@@
     \caption{
-        This figure shows the antenna layout for the OVRO LWA.
-        The 200 meter diameter area indicated by the dashed line contains 251 antennas distributed
-        in a pseudo-random configuration. The 32 filled circles are the expansion antennas built in
-        early 2016 to increase the longest baseline to 1.5 km. The 5 open circles are antennas
-        equipped with noise-switched front ends.
+        This figure shows the antenna layout for the OVRO LWA. Black dots correspond to antennas
+        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
+        antennas equipped with noise-switched front ends.
     }
@@
 Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO LWA is a low-frequency
-instrument with instantaneous bandwidth covering 24.768 MHz to 82.296 MHz \todo{double check this
-frequency range, I think it's wrong}.  Each antenna stand hosts two perpendicular broadband dipoles
-so that there are $288\times2$ signal paths in total. These signal paths feed into the 512-input
-LEDA correlator, which allows the OVRO LWA to capture the entire visible hemisphere in a single
-snapshot image.  In the current configuration, 32 antennas (64 signal paths) are unused.
+instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
+Each antenna stand hosts two perpendicular broadband dipoles so that there are $288\times2$ signal
+paths in total. These signal paths feed into the 512-input LEDA correlator
+\citep{2015JAI.....450003K}, which allows the OVRO LWA to capture the entire visible hemisphere in a
+single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
 
-The 288 antennas are arranged in a maximally non-redundant configuration optimized for minimum
-sidelobes in snapshot imaging. 251 of these antennas are contained within a 200 m diameter core that
-is independently optimized for imaging sidelobe levels. 32 antennas are placed outside of the core
-in order to extend the maximum baseline length out to $\sim$1.5 km. The final 5 antennas are
-equipped with noise-switched front ends for calibrated total power measurements of the global sky
-brightness. These antennas are used as part of the LEDA experiment to measure the global signal of
-21 cm absorption from the cosmic dawn. \todo{cite a leda paper} Calibrated total power measurements
-from these antennas will be used to constrain sky modes with $l \lesssim 2$ including the monopole.
-\todo{What values of $l$ actually contribute to the total power measurements?}
+The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
+snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
+placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
+final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
+of the global sky brightness.  These antennas are used as part of the LEDA experiment \todo{cite
+Price et al. 2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
+Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
 
-%See Figure~\ref{fig:antenna-layout} for an image of the antenna
-%layout. The antennas can be categorized into 3 groups:
-%\begin{enumerate}
-%    \item
-%        Core antennas - 251 antennas are contained within a 200 m diameter core where they are
-%        arranged in a configuration optimized to reduce sidelobe levels in snapshot imaging.
-%    \item
-%        Total power antennas - 5 antennas are equipped with noise-switched front ends for calibrated
-%        total power measurements of the sky brightness.
-%    \item
-%        Expansion antennas - 32 additional antennas were installed in early 2016. These antennas
-%        extend the longest baselines of the OVRO LWA out to 1.5 km. This allows for $\sim10$
-%        arcminute resolution in the snapshot images.
-%\end{enumerate}
-%When fully completed, the OVRO LWA will have 352 antennas in total spanning 2.5 km.
-%
-%\todo{cite Gregg's instrument paper}
-%
-%The field-of-view and compactness of the OVRO LWA make it a promising instrument for 21 cm
-%cosmology. The field-of-view increases the number of cosmological modes measured at any instant in
-%time. The inner core of 251 antennas within a 200 m diameter provides excellent brightness
-%temperature sensitivity. Figure~\ref{fig:ps-sensitivity} shows the expected signal-noise ratio
-%achieved by the OVRO LWA on the three-dimensional spatial power spectrum of 21 cm emission for a
-%variety of models. A large integration time and careful calibration will be needed to make a
-%detection.
-%
-%The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-antenna interferometer located at the
-%Owens Valley Radio Observatory (OVRO) near Big Pine, California. Each antenna is composed of two
-%crossed dipoles bringing the total number of signal paths to 576.  The OVRO LWA hosts the LEDA
-%correlator that allows cross-correlation of 512 signal paths with $>50$ MHz instantaneous bandwidth.
-%
-%Of the 288 antennas, 251 are located within a 200 m diameter core.  The location of these antennas
-%has been optimized to minimize imaging sidelobes.  5 antenna stands are dedicated to the LEDA
-%experiment and have switching front-ends for total-power radiometry. The remaining 32 antennas
-%extend out to 2 km baselines to improve the angular resolution of the interferometer.
+\todo{cite Gregg's instrument paper}
 
-\subsection{The OVRO LWA 100 Hour Dataset}
+Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
+chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
+environment considerably. During this time the OVRO LWA operated as a zenith-pointing drift scanning
+interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
+output evenly divides a sidereal day.
 
-Because the correlator only accepts 512 inputs (256 antennas with 2 polarizations for each antenna),
-a subset of the antennas must be selected for correlation.
+\todo{describe the ionospheric conditions at the time}
 
-Include plot of antenna layout.
-
-The integration time is 13 seconds. This was chosen because the remainder of one sidereal day
-divided into 13 second intervals is only 90 milliseconds.  Finer control of the integration time is
-not possible due to technical constraints.
-
-\subsection{Antenna Gain Calibration}
+\subsection{Gain Calibration}
 
@@
 per-antenna amplitude correction that is then applied to the cross-correlations.
+
+\subsection{Primary Beam Measurements}
+
+In order to generate wide-field images of the sky, the response of the antenna to the sky must be
+known. Fortunately drift-scanning interferometers like the OVRO LWA can empirically measure their
+primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
+assume that the primary beam is invariant under north-south and east-west flips, and additionally
+that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
+We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
+then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
+basis functions to have the desired symmetry.
 
@@
 \end{figure*}
-
-\subsection{Fitting the Antenna Response}
-
-In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Fortunately drift-scanning interferometers like the OVRO LWA can empirically measure their
-primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
-assume that the primary beam is invariant under north-south and east-west flips, and additionally
-that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
-We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
-then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
-basis functions to have the desired symmetry.
 

### 2017-05-06 figures/antenna-layout.jl

@@ -1,59 +1,43 @@
 using PyPlot
 
 matrix = readdlm("antenna-layout.txt");
-east = matrix[:,1];
-north = matrix[:,2];
-up = matrix[:,3];
+east = matrix[:,1]
+north = matrix[:,2]
+up = matrix[:,3]
 east -= 2
 
 core = 1:251
 leda = 252:256
 expansion = 257:288
 
-θ = linspace(0, 2π, 1000)
-circlex = 110sin(θ)
-circley = 110cos(θ)
-
 transparent = (0, 0, 0, 0)
-rc("xtick", labelsize=16)
-rc("ytick", labelsize=16)
+rc("text", usetex=false)
+rc("font", weight="light")
+rc("axes", labelweight="light", linewidth=1.5)
+rc("xtick", labelsize=14)
+rc("ytick", labelsize=14)
 
-figure(1, figsize=(6,6)); clf()
+#close("all")
+figure(1, figsize=(6, 5)); clf()
 
-#subplot(1,2,1)
-scatter(east[leda], north[leda], c=transparent, s=30, lw=2)
-scatter(east[expansion], north[expansion], c="k", s=30, lw=2)
-plot(circlex, circley, "k--", lw=2)
-xticks(collect(-1250:250:500))
-yticks(collect(-500:250:1000))
+scatter(east[core], north[core], c="k", s=10, lw=0)
+scatter(east[leda], north[leda], marker="+", c="k", s=100, lw=1.5)
+scatter(east[expansion], north[expansion], marker="o", c=transparent, s=50, lw=1.5)
+xticks(collect(-1500:500:500))
+yticks(collect(-500:500:1000))
 xlim(-1250, 500)
-ylim(-625, 1125)
+ylim(-500, 1000)
 gca()[:set_aspect]("equal")
-gca()[:spines]["top"][:set_visible](false)
-gca()[:spines]["right"][:set_visible](false)
-gca()[:get_xaxis]()[:tick_bottom]()
-gca()[:get_yaxis]()[:tick_left]()
-grid("off")
-xlabel("distance east / meters", fontsize=16)
-ylabel("distance north / meters", fontsize=16)
-tight_layout()
-
-#subplot(1,2,2)
-#scatter(east, north, c="k", s=50, lw=0)
-#plot(circlex, circley, "k--", lw=2)
-#xticks(collect(-150:50:150))
-#yticks(collect(-150:50:150))
-#xlim(-125, 125)
-#ylim(-125, 125)
[…]

### 2017-05-06 paper.tex
touchups

@@
 $\b B = \b U \b \Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
+\begin{equation}
+    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,,
+\end{equation}
+where
 \[
-    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,.
+    \b\Sigma = \left(
+        \begin{array}{ccc}
+            \sigma_1 & & \\
+                     & \sigma_2 & \\
+                     & & \ddots \\
+        \end{array}
+    \right)\,.
 \]
 The diagonal elements of $\b\Sigma$ are the singular values of $\b B$ and so the contribution of
-each singular component to the Tikhonov-regularized solution is scaled by $\sigma / (\sigma^2 +
-\epsilon)$, where $\sigma$ is the singular value for the given singular component. Tikhonov
-regularization therefore acts to suppress any component for which $\sigma\lesssim\sqrt{\epsilon}$.
-If $\sigma = 0$, the component is set to zero.
+each singular component to the Tikhonov-regularized solution is scaled by $\sigma_i / (\sigma_i^2 +
+\epsilon)$, where $\sigma_i$ is the singular value for the $i$th singular component. Tikhonov
+regularization therefore acts to suppress any component for which $\sigma_i\lesssim\sqrt{\epsilon}$.
+If $\sigma_i = 0$, the component is set to zero.
 
 In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
-purposes we now assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
-Tikhonov-regularized spherical harmonic coefficients $\b C = \left\langle\atikh^*\atikh\right\rangle
-- \left\langle\atikh\right\rangle\left\langle\atikh^*\right\rangle$ is
+purposes we will assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
+Tikhonov-regularized spherical harmonic coefficients is
 \begin{equation}
-    \b C = n \b V \b\Sigma^2 (\b\Sigma^2 + \epsilon\b I)^{-2} \b V^*\,.
+    \b C = n \b V (\b\Sigma^2 + \epsilon\b I)^{-2} \b\Sigma^2 \b V^*\,.
 \end{equation}
-Each singular component is scaled by a factor of $\sigma^2/(\sigma^2 + \epsilon)^2$.
+Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \epsilon)^2$.
 In the absence of Tikhonov regularization ($\epsilon=0$)
@@
 choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
-imaging where robust weighting schemes can be tuned to similar effect.
+imaging where robust weighting schemes can be tuned to similar effect. \todo{citation}
 
@@
 
+\subsection{Beam Errors}
+
+\begin{itemize}
+    \item declination dependent flux scale errors
+    \item failure to reconcile observations from two separate times
+\end{itemize}
+
 \subsection{Ionospheric Scintillation}
@@
 
-\subsection{Beam Errors}
-
 \section{Results}
@@
 
-\begin{table}[ht]
+\begin{table*}[t]
     \centering
-    \begin{tabular}{ccc}
-        \# & $\nu$ / MHz & $\Delta\nu$ / MHz \\ \hline
-        1 & 36.528 & 0.024 \\
-        2 & 41.760 & 0.024 \\
-        3 & 46.992 & 0.024 \\
-        4 & 52.224 & 0.024 \\
-        5 & 57.456 & 0.024 \\
-        6 & 62.688 & 0.024 \\
-        7 & 67.920 & 0.024 \\
-        8 & 73.152 & 0.024 \\
+    \begin{tabular}{ccccc}
+        \hline\hline
+        \# & $\nu$ / MHz & $\Delta\nu$ / MHz
+           & $\theta$ / arcmin  & noise / Jy \\ \hline
+        1 & 36.528 & 0.024 & & \\
+        2 & 41.760 & 0.024 & & \\
+        3 & 46.992 & 0.024 & & \\
+        4 & 52.224 & 0.024 & & \\
+        5 & 57.456 & 0.024 & & \\
+        6 & 62.688 & 0.024 & & \\
+        7 & 67.920 & 0.024 & & \\
+        8 & 73.152 & 0.024 & & \\
+        \hline\hline
     \end{tabular}
     \caption{Summary of the produced maps}
-\end{table}
+\end{table*}
 
@@
 
-\todo{Cite Abhilash, Eastwood 2016}
+\todo{Cite Abhilash, Eastwood 2017}
 
 \section{Discussion}
+
+These maps are pretty cool.
 

### 2017-06-02 paper.tex
CMB foregrounds in introduction
lots of talking about CMB and its foregrounds, this will eventually be
an analogy to 21 cm foregrounds

@@
 intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
-interstellar medium (ISM). Careful measurement and removal of contaminating foreground emission is
-therefore an important component for CMB analysis \citep{2016A&A...594A..25P}. On large angular
-scales galactic synchrotron, free-free, thermal dust, and anomolous microwave emission contribute.
-On smaller angular scales point sources such as distant galaxies and quasars contribute
-\citep{2016arXiv160603606D}.
+interstellar medium (ISM). As photons from the CMB propagate through the intervening material
+scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
+measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free emission,
+thermal dust emission) are a nuisance and careful modeling and removal of these components is
+essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.
 
-Propagation effects from the IGM and intervening galaxy clusters can distort the thermal spectrum of
-the CMB and impart information about the intervening material in those distortions. For instance the
-measured optical depth to Thomson scattering implies a mean redshift of the Epoch of Reionization
-(EoR) of ??? \todo{put number and citation}. The thermal Sunyaev--Zel'dovich effect does something
-\todo{thing and citation}. The kinetic Synyaev--Zel'dovich effect does another thing \todo{thing and
-citation}.
+However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
+Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
+discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering attenuates the
+CMB spectrum, but implies a mean redshift to the Epoch of Reionization (EoR) of $8.8^{+1.7}_{-1.4}$
+\citep{2016A&A...594A..13P}. Inverse Compton scattering of CMB photons propagating through galaxy
+clusters produces an effect known as the Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S,
+1972CoASP...4..173S} that can be used to discover new galaxy clusters \citep{2010ApJ...722.1180V}
+and measure the distance to galaxy clusters when combined with X-ray measurements
+\citep{2006ApJ...647...25B}.
 
-At redshifts $20 \gtrsim z \gtrsim 7$ neutral hydrogen is observable as a 10 to 100 mK perturbation
-of the CMB spectrum due to the 21 cm hyperfine structure line of neutral hydrogen
-\citep{2006PhR...433..181F, 2012RPPh...75h6901P}.  The spatial power spectrum of this perturbation
-is expected to be dominated by inhomogeneous heating of the IGM at $z\sim 20$
-\citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim 7$
-\todo{citation}.
+At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
+expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
+2012RPPh...75h6901P}. The amplitude of the perturbation on a given line-of-sight is a function of
+the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
+temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  Current 21
+cm cosmology experiments can be broadly separated into two classes: global experiments that are
+aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition after
+averaging over the entire sky, and power spectrum experiments that incorporate angular information
+to attempt to measure the spatial power spectrum of cosmological 21 cm perturbations.
+
+Ongoing global experiments include EDGES, SCI-HI, LEDA, and SARAS 2 \citep{2017arXiv170306647S}.
+
+Ongoing power spectrum experiments include PAPER/HERA \citep{2015ApJ...809...61A,
+2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.
+
+\todo{discuss 21cmmc ionizing efficiency, photon mean free path, minimum halo mass}
+\todo{discuss what can be learned from global experiments}
+
+The spatial power spectrum of this perturbation is expected to be dominated
+by inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing
+ionized bubbles during the EoR at $z\sim 7$ \todo{citation}.
 
@@
 
-There are numerous ongoing efforts to detect the cosmologically redshifted 21 cm transition
-including from PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
-\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.
-
-\todo{discuss global experiments too}
+\todo{discuss global experiments too, edges, sci-hi, leda, saras 2}
 

### 2017-06-02 figures/antenna-layout.jl

@@ -13,7 +13,7 @@ expansion = 257:288
 transparent = (0, 0, 0, 0)
 rc("text", usetex=false)
 rc("font", weight="light")
-rc("axes", labelweight="light", linewidth=1.5)
+rc("axes", labelweight="light", linewidth=1.2)
 rc("xtick", labelsize=14)
 rc("ytick", labelsize=14)
 
@@ -21,8 +21,8 @@ rc("ytick", labelsize=14)
 figure(1, figsize=(6, 5)); clf()
 
 scatter(east[core], north[core], c="k", s=10, lw=0)
-scatter(east[leda], north[leda], marker="+", c="k", s=100, lw=1.5)
-scatter(east[expansion], north[expansion], marker="o", c=transparent, s=50, lw=1.5)
+scatter(east[leda], north[leda], marker="+", c="k", s=80, lw=1.2)
+scatter(east[expansion], north[expansion], marker="o", c=transparent, s=40, lw=1.2)
 xticks(collect(-1500:500:500))
 yticks(collect(-500:500:1000))
 xlim(-1250, 500)
@@ -32,8 +32,8 @@ gca()[:set_aspect]("equal")
 #gca()[:spines]["right"][:set_visible](false)
 #gca()[:get_xaxis]()[:tick_bottom]()
 #gca()[:get_yaxis]()[:tick_left]()
-gca()[:get_xaxis]()[:set_tick_params](width=1.5, size=5)
-gca()[:get_yaxis]()[:set_tick_params](width=1.5, size=5)
+gca()[:get_xaxis]()[:set_tick_params](width=1.2, size=5)
+gca()[:get_yaxis]()[:set_tick_params](width=1.2, size=5)
 grid("off")
 xlabel("distance east / m", fontsize=16)
 ylabel("distance north / m", fontsize=16)

### 2017-06-05 paper.tex
minor progress

@@
 Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
-discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering attenuates the
-CMB spectrum, but implies a mean redshift to the Epoch of Reionization (EoR) of $8.8^{+1.7}_{-1.4}$
-\citep{2016A&A...594A..13P}. Inverse Compton scattering of CMB photons propagating through galaxy
-clusters produces an effect known as the Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S,
-1972CoASP...4..173S} that can be used to discover new galaxy clusters \citep{2010ApJ...722.1180V}
-and measure the distance to galaxy clusters when combined with X-ray measurements
-\citep{2006ApJ...647...25B}.
+discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering in the IGM
+attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
+Reionization (EoR) of $8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
+Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
+new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
+combined with X-ray measurements \citep{2006ApJ...647...25B}.
+
+\todo{kinetic SZ effect puts an upper limit on the duration of reionization}
 
@@
 expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
-2012RPPh...75h6901P}. The amplitude of the perturbation on a given line-of-sight is a function of
+2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
 the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
-temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  Current 21
-cm cosmology experiments can be broadly separated into two classes: global experiments that are
-aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition after
-averaging over the entire sky, and power spectrum experiments that incorporate angular information
-to attempt to measure the spatial power spectrum of cosmological 21 cm perturbations.
-
-Ongoing global experiments include EDGES, SCI-HI, LEDA, and SARAS 2 \citep{2017arXiv170306647S}.
-
-Ongoing power spectrum experiments include PAPER/HERA \citep{2015ApJ...809...61A,
-2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.
+temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.
 
@@
 
-\todo{discuss more interesting science to be done}
+Current 21 cm cosmology experiments can be broadly separated into two classes: global experiments
+that are aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition
+after averaging over the entire sky, and power spectrum experiments that incorporate angular
+information to attempt to measure the spatial power spectrum of cosmological 21 cm perturbations.
+Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
+\todo{cite Price et al. 2017}, BIGHORNS \citep{2015PASA...32....4S}, SCI-HI
+\citep{2014ApJ...782L...9V}, and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum
+experiments include PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
+\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.
 
-\todo{discuss global experiments too, edges, sci-hi, leda, saras 2}
-
-These low-frequency 21 cm cosmology experiments are limited by the dynamic range they can achieve
-against low-redshift sources of emission. The brightness temperature of the galactic synchrotron
+Just as for CMB experiments, foreground removal or suppression is an essential component of both
+classes of 21 cm cosmology experiments. The brightness temperature of the galactic synchrotron
 emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
@@
 \end{equation}
-Therefore experiments conservatively need to achieve at least 4 orders of dynamic range.  In theory
-this kind of dynamic range can be obtained by exploiting the fact that the foreground emission is
-predominantly synchrotron emission that has a smooth power law spectrum \todo{citation}.  In
-practice the interferometer itself imparts frequency structure into the measurements and therefore
-an experiment's ability to separate the foreground signal from the cosmological signal can be
-limited by the instrumental spectral smoothness \todo{citation}.
-
-Ideally the foreground removal strategy should be informed by the measured spatial and frequency
-structure of all foreground components. This possibility is limited by the availability of suitable
-high-fidelity low-frequency sky maps on angular scales ranging from tens of degrees to arcminutes.
+Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
+foreground emission before the cosmological signal can be measured. Current foreground removal
+methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
+emission (after convolving with the instrumental response) is spectrally smooth. However the
+low-frequency radio sky is composed of several components: galactic synchrotron emission, free-free
+emission and absorption, supernova remnants, radio galaxies, and a confusing background of point
+sources.  Ideally a foreground removal strategy should be informed by the measured spatial and
+frequency structure of all foreground components. However, this possibility is limited by the
+availability of suitable high-fidelity low-frequency sky maps on angular scales ranging from tens of
+degrees to arcminutes.
 
@@
 complex floating point number).  This matrix equation is therefore prohibitively large, and solving
-equation~\ref{eq:basic-imaging} by means of discretization is usually impossible \todo{cite Jayce's
-paper (has he published that yet?) where he does this, but explain why his work is the exception
-instead of the rule}.
+equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
+\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.
 
@@
 $\vec b_{ij}$ lie in a plane and the field-of-view is small, equation~\ref{eq:basic-imaging} can be
-well-approximated by a two-dimensional Fourier transform.
+well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}.
 
@@
 \todo{discuss a-projection}
-
-\citet{2017MNRAS.465.2901Z}
 
@@
 Therefore it is a very natural operation to compute the Fourier transform of the visibilities with
-respect to sidereal time $\phi\in(0,2\pi]$.
+respect to sidereal time $\phi\in[0,2\pi)$.
 \begin{equation}

### 2017-06-26 paper.tex
s/OVRO LWA/OVRO-LWA

@@
 %
-% * Antenna layout of the OVRO LWA
+% * Antenna layout of the OVRO-LWA
 % * Before/after snapshot image of the RFI removal
@@
     \caption{
-        This figure shows the antenna layout for the OVRO LWA. Black dots correspond to antennas
+        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
         within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
@@
 
-The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO LWA is a low-frequency
+The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
+Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO-LWA is a low-frequency
 instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
@@
 paths in total. These signal paths feed into the 512-input LEDA correlator
-\citep{2015JAI.....450003K}, which allows the OVRO LWA to capture the entire visible hemisphere in a
+\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
 single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
@@
 chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
-environment considerably. During this time the OVRO LWA operated as a zenith-pointing drift scanning
+environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
 interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
@@
 The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
-are at high elevations.  These two sources are -- by an order of magnitude -- the brightest radio
-sources in the northern hemisphere.  Therefore the optimal time to solve for the interferometer's
-gain calibration is when Cas A and Cyg A are at high elevations. A calibration obtained in this
-manner is good consistent with the following day's calibration to within a 1\% error in the flux
-scale and 1$'$ error in the astrometry \todo{double check these numbers}. These residual errors are
-likely driven by differing ionospheric conditions.
+are at high elevations \todo{the rainy day dataset actually uses a shorter track of data, we should
+try using the 9 hour track again}.  These two sources are -- by an order of magnitude -- the
+brightest radio sources in the northern hemisphere.  Therefore the optimal time to solve for the
+interferometer's gain calibration is when Cas A and Cyg A are at high elevations. A calibration
+obtained in this manner is good consistent with the following day's calibration to within a 1\%
+error in the flux scale and 1$'$ error in the astrometry \todo{double check these numbers}. These
+residual errors are likely driven by differing ionospheric conditions.
 
@@
 In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Fortunately drift-scanning interferometers like the OVRO LWA can empirically measure their
+known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
 primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
@@
 The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
-is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO LWA marginally resolves both
+is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
 sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
@@
 taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
-However the OVRO LWA 100 hour dataset consists of 100 consecutive hours of data, and hence roughly
+However the OVRO-LWA 100 hour dataset consists of 100 consecutive hours of data, and hence roughly
 half of the data is from the day.
@@
 The Owens Valley is an important source of water and power for the city of Los Angeles.
-Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO
+Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO-
 LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
@@
 of the individual elements does not change with respect to time. This may be an interferometer like
-the OVRO LWA where the correlation elements are fixed dipoles, but it may also be an interferometer
+the OVRO-LWA where the correlation elements are fixed dipoles, but it may also be an interferometer
 like the MWA if the steerable beams are held in a fixed position (not necessarily at zenith).
@@
 In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
-an interferometer like the OVRO LWA with lots of short baselines, a sensible choice is to use all
+an interferometer like the OVRO-LWA with lots of short baselines, a sensible choice is to use all
 spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
@@
 64-bit complex floating point number, a single block is 500 MB for the case of single-channel
-imaging with the OVRO LWA. Compare this number with the 5 PB required for the naive approach.  The
+imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
 power of $m$-mode analysis is the block-diagonal structure of
@@
 the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
-the case of the OVRO LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
+the case of the OVRO-LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
 $\sim10^9$ in processing time by using $m$-mode analysis.
@@
 
-\subsection{$m$-Mode Analysis with the OVRO LWA}
+\subsection{$m$-Mode Analysis with the OVRO-LWA}
 

### 2017-06-26 paper.tex
fix some unicode errors and minor changes

@@
 
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
 \usepackage{amsmath}
@@
 taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
-However the OVRO-LWA 100 hour dataset consists of 100 consecutive hours of data, and hence roughly
-half of the data is from the day.
+However the dataset used in this paper consists of 28 consecutive hours. Additionally while most
+astronomical sources at these frequencies have negative spectral indices, the Sun has a large
+positive spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
+frequencies than at lower frequencies.
 
-The Sun is a time variable source in radio.
-
-\todo{does the previous routine work on the Sun too? worth a shot}
+\todo{describe sun removal -- this isn't entirely settled yet}
 
@@
 
-\begin{figure*}[ht]
-    \centering
-    \begin{tabular}{cccc}
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
-    \end{tabular}
-    \caption{
-        Dirty snapshot images after smearing the visiblities over the entire 100 hour observation
-        window.  The two bright source tracks correspond to Cas A (top track) and Cyg A (bottom
-        track) smeared along a ring of constant declination. The sources dotting the horizon are
-        faulty power line insulators.
-    }
-\end{figure*}
+%\begin{figure*}[ht]
+%    \centering
+%    \begin{tabular}{cccc}
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
+%    \end{tabular}
+%    \caption{
+%        Dirty snapshot images after smearing the visiblities over the entire 100 hour observation
+%        window.  The two bright source tracks correspond to Cas A (top track) and Cyg A (bottom
+%        track) smeared along a ring of constant declination. The sources dotting the horizon are
+%        faulty power line insulators.
+%    }
+%\end{figure*}
 
@@
 $(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
-the Owens Valley LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit
-complex floating point number).  This matrix equation is therefore prohibitively large, and solving
+the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
+floating point number).  This matrix equation is therefore prohibitively large, and solving
 equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
@@
 $\vec b_{ij}$ lie in a plane and the field-of-view is small, equation~\ref{eq:basic-imaging} can be
-well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}.
-
-\todo{discuss w-projection}
-
-\todo{discuss a-projection}
+well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
+restriction on baseline co-planarity and field-of-view can be relaxed by using W-projection
+\citep{2008ISTSP...2..647C}. Known primary beam effects can also be accounted for during imaging by
+using A-projection \citep{2013ApJ...770...91B}.
 
@@
 the OVRO-LWA where the correlation elements are fixed dipoles, but it may also be an interferometer
-like the MWA if the steerable beams are held in a fixed position (not necessarily at zenith).
+like LOFAR or the MWA if the steerable beams are held in a fixed position (not necessarily at
+zenith).
 
@@
 Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
-because we do not have a measurement of cross-talk or common-mode noise.
+because we do not have a measurement of the amplitude of cross-talk or common-mode noise, which
+would be needed to correctly calibrate $a_{00}$.
 
@@
 about the sky around the southern celestial pole, and therefore the act of multiplying by $\b B$
-must destroy some information about the sky. The consequence of this fact is that $\b B^*\b B$ must
-have at least one zero eigenvalue, which means it is not invertible.
+must destroy some information about the sky. The consequence of this fact is that $\b B$ must have
+at least one singular value that is equal to zero. It is then trivial to show that $\b B^*\b B$ must
+have at least one eigenvalue that is equal to zero, which means it is not an invertible matrix.
 
@@
 
-\subsection{$m$-Mode Analysis with the OVRO-LWA}
-
-\subsection{CLEAN}
+\subsection{Image Deconvolution}
 

### 2017-06-27 figures/antenna-layout.jl
reorganize the figures directory

@@ -1,43 +1,0 @@
-using PyPlot
-
-matrix = readdlm("antenna-layout.txt");
-east = matrix[:,1]
-north = matrix[:,2]
-up = matrix[:,3]
-east -= 2
-
-core = 1:251
-leda = 252:256
-expansion = 257:288
-
-transparent = (0, 0, 0, 0)
-rc("text", usetex=false)
-rc("font", weight="light")
-rc("axes", labelweight="light", linewidth=1.2)
-rc("xtick", labelsize=14)
-rc("ytick", labelsize=14)
-
-#close("all")
-figure(1, figsize=(6, 5)); clf()
-
-scatter(east[core], north[core], c="k", s=10, lw=0)
-scatter(east[leda], north[leda], marker="+", c="k", s=80, lw=1.2)
-scatter(east[expansion], north[expansion], marker="o", c=transparent, s=40, lw=1.2)
-xticks(collect(-1500:500:500))
-yticks(collect(-500:500:1000))
-xlim(-1250, 500)
-ylim(-500, 1000)
-gca()[:set_aspect]("equal")
-#gca()[:spines]["top"][:set_visible](false)
-#gca()[:spines]["right"][:set_visible](false)
-#gca()[:get_xaxis]()[:tick_bottom]()
-#gca()[:get_yaxis]()[:tick_left]()
-gca()[:get_xaxis]()[:set_tick_params](width=1.2, size=5)
-gca()[:get_yaxis]()[:set_tick_params](width=1.2, size=5)
-grid("off")
-xlabel("distance east / m", fontsize=16)
-ylabel("distance north / m", fontsize=16)
-tight_layout()
-
-savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0.1, transparent=true)
-

### 2017-06-27 figures/antenna-layout/antenna-layout.jl

@@ -1,0 +1,43 @@
+using PyPlot
+
+matrix = readdlm("antenna-layout.txt");
+east = matrix[:,1]
+north = matrix[:,2]
+up = matrix[:,3]
+east -= 2
+
+core = 1:251
+leda = 252:256
+expansion = 257:288
+
+transparent = (0, 0, 0, 0)
+rc("text", usetex=false)
+rc("font", weight="light")
+rc("axes", labelweight="light", linewidth=1.2)
+rc("xtick", labelsize=14)
+rc("ytick", labelsize=14)
+
+#close("all")
+figure(1, figsize=(6, 5)); clf()
+
+scatter(east[core], north[core], c="k", s=10, lw=0)
+scatter(east[leda], north[leda], marker="+", c="k", s=80, lw=1.2)
+scatter(east[expansion], north[expansion], marker="o", c=transparent, s=40, lw=1.2)
+xticks(collect(-1500:500:500))
+yticks(collect(-500:500:1000))
+xlim(-1250, 500)
+ylim(-500, 1000)
+gca()[:set_aspect]("equal")
+#gca()[:spines]["top"][:set_visible](false)
+#gca()[:spines]["right"][:set_visible](false)
+#gca()[:get_xaxis]()[:tick_bottom]()
+#gca()[:get_yaxis]()[:tick_left]()
+gca()[:get_xaxis]()[:set_tick_params](width=1.2, size=5)
+gca()[:get_yaxis]()[:set_tick_params](width=1.2, size=5)
+grid("off")
+xlabel("distance east / m", fontsize=16)
+ylabel("distance north / m", fontsize=16)
+tight_layout()
+
+savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0.1, transparent=true)
+

### 2017-06-27 figures/shrinking-script.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+convert spw04.png -resize 256x256 -set colorspace RGB spw04-small.png
+convert spw06.png -resize 256x256 -set colorspace RGB spw06-small.png
+convert spw08.png -resize 256x256 -set colorspace RGB spw08-small.png
+convert spw10.png -resize 256x256 -set colorspace RGB spw10-small.png
+convert spw12.png -resize 256x256 -set colorspace RGB spw12-small.png
+convert spw14.png -resize 256x256 -set colorspace RGB spw14-small.png
+convert spw16.png -resize 256x256 -set colorspace RGB spw16-small.png
+convert spw18.png -resize 256x256 -set colorspace RGB spw18-small.png

### 2017-06-27 figures/smeared-snapshots/shrinking-script.sh

@@ -1,9 +1,0 @@
-#!/bin/bash
-convert spw04.png -resize 256x256 -set colorspace RGB spw04-small.png
-convert spw06.png -resize 256x256 -set colorspace RGB spw06-small.png
-convert spw08.png -resize 256x256 -set colorspace RGB spw08-small.png
-convert spw10.png -resize 256x256 -set colorspace RGB spw10-small.png
-convert spw12.png -resize 256x256 -set colorspace RGB spw12-small.png
-convert spw14.png -resize 256x256 -set colorspace RGB spw14-small.png
-convert spw16.png -resize 256x256 -set colorspace RGB spw16-small.png
-convert spw18.png -resize 256x256 -set colorspace RGB spw18-small.png

### 2017-06-27 paper.tex
reorder sections
mostly elaborating on correlated rfi removal

@@
     Michael W. Eastwood,
-    Gregg Hallinan
+    Gregg Hallinan,
+    Twilight Sparkle,
+    Rainbow Dash
 }
@@
 
-\section{Observations}
-
-\subsection{The Owens Valley Long Wavelength Array}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/antenna-layout}
-    \caption{
-        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
-        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
-        antennas equipped with noise-switched front ends.
-    }
-    \label{fig:antenna-layout}
-\end{figure}
-
-The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO-LWA is a low-frequency
-instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
-Each antenna stand hosts two perpendicular broadband dipoles so that there are $288\times2$ signal
-paths in total. These signal paths feed into the 512-input LEDA correlator
-\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
-single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
-
-The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
-snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
-placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
-final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
-of the global sky brightness.  These antennas are used as part of the LEDA experiment \todo{cite
-Price et al. 2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
-Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
-
-\todo{cite Gregg's instrument paper}
-
-Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
-chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
-environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
-interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
-output evenly divides a sidereal day.
-
-\todo{describe the ionospheric conditions at the time}
-
-\subsection{Gain Calibration}
-
-Antenna gain calibration is accomplished using an iterative method independently developed by
-\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
-the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
-online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
-
-The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
-are at high elevations \todo{the rainy day dataset actually uses a shorter track of data, we should
-try using the 9 hour track again}.  These two sources are -- by an order of magnitude -- the
-brightest radio sources in the northern hemisphere.  Therefore the optimal time to solve for the
-interferometer's gain calibration is when Cas A and Cyg A are at high elevations. A calibration
-obtained in this manner is good consistent with the following day's calibration to within a 1\%
-error in the flux scale and 1$'$ error in the astrometry \todo{double check these numbers}. These
-residual errors are likely driven by differing ionospheric conditions.
-
-The flux scale is tied to the work of \citet{2016arXiv160905940P}.
-
-Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
-analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
-gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
-The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
-per-antenna amplitude correction that is then applied to the cross-correlations.
-
-\subsection{Primary Beam Measurements}
-
-In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
-primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
-assume that the primary beam is invariant under north-south and east-west flips, and additionally
-that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
-We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
-then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
-basis functions to have the desired symmetry.
-
-\subsection{Source Removal}
-
-\subsubsection{Cassiopeia A and Cygnus A}
-
-Without removing bright sources from the data, sidelobes from bright sources will dominate the
-variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2016arXiv160905940P}. A
-conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
-\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
-from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
-\todo{Measure Cyg A's sidelobe levels if it is not subtracted}
-
-At low frequencies, propagation effects through the ionosphere must be accounted for in order to
-achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
-peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
-scintillation and diffraction events on the timescale of a single integration (13 seconds) are
-observed. Therefore the direction dependent calibration changes on these timescales and the we must
-solve for one set of complex gains per source per integration.
-
-The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
-is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
-sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
-source model to eachs ource. This is performed by minimizing the minimizing the variance within an
-aperture located on each source after peeling. By phasing up a large number of integrations before
-imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
-We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
-until the variance within the aperture is minimized.
-
-\todo{Show a before and after with the updated source models}
-
-\todo{Give a plot with the updated source models}
-
-\subsubsection{The Sun}
-
-The Sun can be trivially removed from any map of the sky by constructing the map using only data
-taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
-However the dataset used in this paper consists of 28 consecutive hours. Additionally while most
-astronomical sources at these frequencies have negative spectral indices, the Sun has a large
-positive spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
-frequencies than at lower frequencies.
-
-\todo{describe sun removal -- this isn't entirely settled yet}
-
-\subsubsection{Sparking Power Lines}
-
-The Owens Valley is an important source of water and power for the city of Los Angeles.
-Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO-
-LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
-RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
-them by using the curvature of the incoming wavefront. Efforts are currently underway to work with
-the utility pole owners to have these insulators replaced.
-
-In the meantime it is possible to suppress their contamination in the dataset. The contribution of
-these RFI sources to the visibilities can be plainly seen by averaging $>$24 hours of data with the
-phase center set to zenith. In this way, true sky components are smeared along tracks of constant
-declination while terrestrial sources (ie. the arcing power lines) are not smeared. For similar
-reasons, when constructing a map of the sky from $>$24 hours of data these sparking power lines will
-produce artifacts in the map that are smeared along tracks of constant declination. However while
-the amplitude of the RFI will fluctuate with time, its phase will be constant. Therefore if you can
-use isolate a set of model visibilities for the RFI, it can be removed from each integration by
-scaling and subtracting these model visibilities from the measured visibilities.
-
-Obtaining a model for the RFI is complicated by the fact that the contaminating sources are at
-extremely low elevations where the antenna response is maximally inhomogeneous. Therefore it is not
-enough to know the physical location of the faulty insulator generating the RFI. In addition you
-must also know the response of each antenna (amplitude and phase) in the appropriate direction. This
-motivates the use of peeling, which allows the antenna response to be a free parameter.
-
-Therefore model visibilities for the RFI can be obtained by peeling the sources after smearing the
-visibilities over $>$24 hours. These model visibilities are then scaled and subtracted from each
-integration in the data set.
-
-\todo{show an example smeared image before and after peeling}
-
-%\begin{figure*}[ht]
-%    \centering
-%    \begin{tabular}{cccc}
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
-%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
-%    \end{tabular}
-%    \caption{
-%        Dirty snapshot images after smearing the visiblities over the entire 100 hour observation
-%        window.  The two bright source tracks correspond to Cas A (top track) and Cyg A (bottom
-%        track) smeared along a ring of constant declination. The sources dotting the horizon are
-%        faulty power line insulators.
-%    }
-%\end{figure*}
-
-\section{Imaging}
+\section{All-Sky Imaging}
 
@@
 spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
-block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the value of $m$.
+block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the value of $m$. Positive
+and negative values of $m$ are grouped together because the brightness of the sky is real-valued,
+and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m a_{lm}^*$.
 \begin{equation}\label{eq:m-mode-matrix-equation}
@@
 choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
-imaging where robust weighting schemes can be tuned to similar effect. \todo{citation}
+imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.
 
@@
 
-\subsection{Image Deconvolution}
+\subsection{$m$-Mode Analysis Image Deconvolution}
 
@@
 
-\section{Errors}
+\section{Observations}
 
-\subsection{Terrestrial Interference}
+\subsection{The Owens Valley Long Wavelength Array}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/antenna-layout/antenna-layout}
+    \caption{
+        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
+        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
+        antennas equipped with noise-switched front ends.
+    }
+    \label{fig:antenna-layout}
+\end{figure}
+
+The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
+Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO-LWA is a low-frequency
+instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
+Each antenna stand hosts two perpendicular broadband dipoles so that there are $288\times2$ signal
+paths in total. These signal paths feed into the 512-input LEDA correlator
+\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
+single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
+
+The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
+snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
+placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
+final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
+of the global sky brightness.  These antennas are used as part of the LEDA experiment \todo{cite
+Price et al. 2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
+Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
+
+\todo{cite Gregg's instrument paper}
+
+Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
+chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
+environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
+interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
+output evenly divides a sidereal day.
+
+\todo{describe the ionospheric conditions at the time}
+
+\subsection{Gain Calibration}
+
+Antenna gain calibration is accomplished using an iterative method independently developed by
+\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
+the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
+online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
+
+The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
+are at high elevations \todo{the rainy day dataset actually uses a shorter track of data, we should
+try using the 9 hour track again}.  These two sources are -- by an order of magnitude -- the
+brightest radio sources in the northern hemisphere.  Therefore the optimal time to solve for the
+interferometer's gain calibration is when Cas A and Cyg A are at high elevations. A calibration
+obtained in this manner is good consistent with the following day's calibration to within a 1\%
+error in the flux scale and 1$'$ error in the astrometry \todo{double check these numbers}. These
+residual errors are likely driven by differing ionospheric conditions.
+
+The flux scale is tied to the work of \citet{1977A&A....61...99B, 2012MNRAS.423L..30S,
+2017ApJS..230....7P}.
+
+Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
+analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
+gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
+The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
+per-antenna amplitude correction that is then applied to the cross-correlations.
+
+\subsection{Primary Beam Measurements}
+
+In order to generate wide-field images of the sky, the response of the antenna to the sky must be
+known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
+primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
+assume that the primary beam is invariant under north-south and east-west flips, and additionally
+that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
+We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
+then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
+basis functions to have the desired symmetry.
+
+\subsection{Source Removal}
+
+\subsubsection{Cassiopeia A and Cygnus A}
+
+Without removing bright sources from the data, sidelobes from bright sources will dominate the
+variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2017ApJS..230....7P}. A
+conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
+\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
+from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
+\todo{Measure Cyg A's sidelobe levels if it is not subtracted}
+
+At low frequencies, propagation effects through the ionosphere must be accounted for in order to
+achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
+peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
+scintillation and diffraction events on the timescale of a single integration (13 seconds) are
+observed. Therefore the direction dependent calibration changes on these timescales and the we must
+solve for one set of complex gains per source per integration.
+
+The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
+is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
+sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
+source model to eachs ource. This is performed by minimizing the minimizing the variance within an
+aperture located on each source after peeling. By phasing up a large number of integrations before
+imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
+We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
+until the variance within the aperture is minimized.
+
+\todo{Show a before and after with the updated source models}
+
+\todo{Give a plot with the updated source models}
+
+\subsubsection{The Sun}
+
+The Sun can be trivially removed from any map of the sky by constructing the map using only data
+taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
+However the dataset used in this paper consists of 28 consecutive hours. Additionally while most
+astronomical sources at these frequencies have negative spectral indices, the Sun has a large
+positive spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
+frequencies than at lower frequencies.
+
+\todo{describe sun removal -- this isn't entirely settled yet}
+
+\section{Error Analysis}
+
+\subsection{Terrestrial Interference and Pickup}
 
 When writing down equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated
-voltage fluctuations measured between pairs of antennas are generated by astronomical sources of
-radio emission. In practice, this implicit assumption can be violated. For instance a low-frequency
-interferometer located in the vicinity of an arcing power line will see an additional contribution
-from the radio-frequency interference (RFI) generated by the arcing process. Similarly common-mode
-pickup along the analog signal path of the interferometer may generate an additional spurious
-contribution to the measured visibilities. While the amplitude and phase of these contaminating
-signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
+voltage fluctuations measured between pairs of antennas are exclusively generated by astronomical
+sources of radio emission. In practice this implicit assumption can be violated. For instance a
+low-frequency interferometer located in the vicinity of an arcing power line will see an additional
+contribution from the radio-frequency interference (RFI) generated by the arcing process. Similarly
+common-mode pickup along the analog signal path of the interferometer may generate an additional
+spurious contribution to the measured visibilities. While the amplitude and phase of these
+contaminating signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
 characteristic of astronomical sources.
 
-The first step in equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step we
-compute the projection of the measurement $\b v$ onto the space spanned by the columns of $\b B$.
-Each column of $\b B$ describes the interferometer's response to a corresponding spherical harmonic
-coefficient of the sky brightness distribution. Therefore the act of computing $\b B^*\b v$ is to
-project the measured $m$-modes onto the space of $m$-modes which could be generated by astronomical
-sources. The degree to which a source of terrestrial interferer will contaminate a map generated
-using $m$-mode analysis imaging is determined by its amplitude after projection.
+The Owens Valley is an important source of water and power for the city of Los Angeles.
+Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO-
+LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
+RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
+them by using the curvature of the incoming wavefront to infer a distance. Efforts are currently
+underway to work with the utility pole owners to have these insulators replaced.
 
-For instance, a bright interfering source might contribute $\b v_\text{terrestrial}$ to the measured
-$m$-modes. However, if $\b v_\text{terrestrial}$ is actually perpendicular to all of the columns of
-$\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = 0$.  In
-practice this is unlikely. In general the contamination is proportional to the overall amplitude of
-the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
-an astronomical signal ($\|\b B^*\b v_\text{terrestrial}\|/\|\b v_\text{terrestrial}\|$).
+In the meantime it is possible to suppress their contamination in the dataset. The contribution of
+these RFI sources to the visibilities can be plainly seen by averaging $>24$ hours of data with the
+phase center set to zenith. In this way, true sky components are smeared along tracks of constant
+declination while terrestrial sources (ie. the arcing power lines or any common-mode pickup) are not
+smeared.  Obtaining a model for the RFI is complicated by the fact that the contaminating sources
+are at extremely low elevations where the antenna response is essentially unknown (and inhomogeneous
+due to antenna shadowing effects). Therefore it is not enough to know the physical location of the
+faulty insulator generating the RFI. In addition you must also know the response of each antenna
+(amplitude and phase) in the appropriate direction. This motivates the use of peeling
+\citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}, which allows the antenna response to be a free
+parameter.  Therefore model visibilities for the RFI can be obtained by peeling the sources after
+smearing the visibilities over $>24$ hours.
 
-These astronomical sources are anchored to the celestial sphere and therefore rotate
-across the sky over the course of a sidereal day. Terrestrial source of interference are not
-anchored to the celestial sphere.
+%These model visibilities are then scaled and subtracted from each
+%integration in the data set.
+%
+%
+%
+%For similar
+%reasons, when constructing a map of the sky from $>24$ hours of data these sparking power lines will
+%produce artifacts in the map that are smeared along tracks of constant declination. However while
+%the amplitude of the RFI will fluctuate with time, its phase will be constant. Therefore if you can
+%use isolate a set of model visibilities for the RFI, it can be removed from each integration by
+%scaling and subtracting these model visibilities from the measured visibilities.
+%
+%
+%
+%
+%
+%
+%The first step in equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step we
+%compute the projection of the measurement $\b v$ onto the space spanned by the columns of $\b B$.
+%Each column of $\b B$ describes the interferometer's response to a corresponding spherical harmonic
+%coefficient of the sky brightness distribution. Therefore the act of computing $\b B^*\b v$ is to
+%project the measured $m$-modes onto the space of $m$-modes which could be generated by astronomical
+%sources. The degree to which a source of terrestrial interferer will contaminate a map generated
+%using $m$-mode analysis imaging is determined by its amplitude after projection.
+%
+%For instance, a bright interfering source might contribute $\b v_\text{terrestrial}$ to the measured
+%$m$-modes. However, if $\b v_\text{terrestrial}$ is actually perpendicular to all of the columns of
+%$\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = 0$.  In
+%practice this is unlikely. In general the contamination is proportional to the overall amplitude of
+%the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
+%an astronomical signal ($\|\b B^*\b v_\text{terrestrial}\|/\|\b v_\text{terrestrial}\|$).
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%These astronomical sources are anchored to the celestial sphere and therefore rotate
+%across the sky over the course of a sidereal day. Terrestrial source of interference are not
+%anchored to the celestial sphere.
+%
+%This characteristic motion of astronomical sources
+%is a fundamental component to $m$-mode analysis imaging
+%
+%radio emission is astronomical. Astronomical sources are anchored to the celestial sphere and
+%therefore rotate across the sky over the course of a sidereal day. However, in a practice 
+%
+%$m$-mode analysis imaging implicitly assumes that the correlation between any two pairs of antennas
+%
+%
+%However it is instructive to analyze the contaminating effect the RFI will have
+%on $m$-mode analysis maps of the sky. The correlation observed on a given
+%baseline and frequency channel for a single source of RFI is
+%\begin{equation}
+%    V(t) = I(t) B^\textrm{near-field}
+%\end{equation}
+%
+%However we need a strategy to mitigate the RFI before imaging. A constant source attached to the
+%horizon has a fringe rate of zero. The only possible astronomical origins for a source with zero
+%fringe rate are:
+%
+%\begin{enumerate}
+%    \item a point source located at the north or south celestial poles, and
+%    \item a ring of constant declination.
+%\end{enumerate}
+%
+%Therefore while snapshot images will show the RFI source on the horizon, extended integrations will
+%show the RFI as rings of constant declination. We can take advantage of this discrepancy to separate
+%astronomical emission from terrestrial RFI.
+%
+%
+%
+%
+%
+%
+%
+%\todo{show an example smeared image before and after peeling}
 
-This characteristic motion of astronomical sources
-is a fundamental component to $m$-mode analysis imaging
-
-radio emission is astronomical. Astronomical sources are anchored to the celestial sphere and
-therefore rotate across the sky over the course of a sidereal day. However, in a practice
-
-$m$-mode analysis imaging implicitly assumes that the correlation between any two pairs of antennas
-
-However it is instructive to analyze the contaminating effect the RFI will have
-on $m$-mode analysis maps of the sky. The correlation observed on a given
-baseline and frequency channel for a single source of RFI is
-\begin{equation}
-    V(t) = I(t) B^\textrm{near-field}
-\end{equation}
-
-However we need a strategy to mitigate the RFI before imaging. A constant source attached to the
-horizon has a fringe rate of zero. The only possible astronomical origins for a source with zero
-fringe rate are:
-
-\begin{enumerate}
-    \item a point source located at the north or south celestial poles, and
-    \item a ring of constant declination.
-\end{enumerate}
-
-Therefore while snapshot images will show the RFI source on the horizon, extended integrations will
-show the RFI as rings of constant declination. We can take advantage of this discrepancy to separate
-astronomical emission from terrestrial RFI.
+%\begin{figure*}[ht]
+%    \centering
+%    \begin{tabular}{cccc}
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
+%        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
+%    \end{tabular}
+%    \caption{
+%        Dirty snapshot images after smearing the visiblities over the entire 100 hour observation
+%        window.  The two bright source tracks correspond to Cas A (top track) and Cyg A (bottom
+%        track) smeared along a ring of constant declination. The sources dotting the horizon are
+%        faulty power line insulators.
+%    }
+%\end{figure*}
 
@@
 
-\subsection{Ionospheric Scintillation}
+\subsection{The Ionosphere}
 
-One of the key assumptions made by $m$-mode analysis is that the sky is completely static.  We
-assume that the only time-dependent behavior is the rotation of the Earth, which slowly rotates the
-sky through the fringe patterns of the interferometer. At low frequencies the ionosphere violates
-this assumption. In particular, ionospheric scintillation will cause even static sources to exhibit
-significant variability.
+%One of the key assumptions made by $m$-mode analysis is that the sky is completely static.  We
+%assume that the only time-dependent behavior is the rotation of the Earth, which slowly rotates the
+%sky through the fringe patterns of the interferometer. At low frequencies the ionosphere violates
+%this assumption. In particular, ionospheric scintillation will cause even static sources to exhibit
+%significant variability.
+%
+%The correlation observed on a given baseline for a single point source is
+%\begin{equation}
+%    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
+%\end{equation}
+%where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$
+%is the baseline transfer function. The transfer function is a function of
+%the direction to the source, which is in turn a function of the sidereal
+%time $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic
+%variability or due to scintillation, than the source flux is also a function
+%of the time coordinate $t$ such that
+%\begin{equation}
+%    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
+%\end{equation}
+%where $t_{\textrm{sidereal}} = (t \mod 23.9345\,\textrm{hours})$.
+%
+%Now assume we have observed with our interferometer for a single sidereal day.
+%In order to compute the $m$-modes we must Fourier transform with respect to
+%sidereal time. In a real measurement this is a discrete Fourier transform of
+%the observed correlation with respect to time (where the sum over time is
+%restricted to a sidereal day). \todo{fix normalization}
+%\begin{equation}
+%    V_{\nu, m} = \sum_{t} V_\nu(t) e^{-imt}
+%\end{equation}
+%Define $V_{\nu, m}^{\textrm{static}}$ to be the observed $m$-modes if the source
+%was actually static ($I_\nu(t) \equiv I_{\nu,0}$). Then as a consequence of the
+%Fourier convolution theorem
+%\begin{equation}
+%    V_{\nu, m} = \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}.
+%\end{equation}
+%
+%This will tend to scatter power between $m$-modes.
+%
+%Simulate images of point sources with this
 
-The correlation observed on a given baseline for a single point source is
-\begin{equation}
-    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
-\end{equation}
-where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$
-is the baseline transfer function. The transfer function is a function of
-the direction to the source, which is in turn a function of the sidereal
-time $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic
-variability or due to scintillation, than the source flux is also a function
-of the time coordinate $t$ such that
-\begin{equation}
-    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
-\end{equation}
-where $t_{\textrm{sidereal}} = (t \mod 23.9345\,\textrm{hours})$.
-
-Now assume we have observed with our interferometer for a single sidereal day.
-In order to compute the $m$-modes we must Fourier transform with respect to
-sidereal time. In a real measurement this is a discrete Fourier transform of
-the observed correlation with respect to time (where the sum over time is
-restricted to a sidereal day). \todo{fix normalization}
-\begin{equation}
-    V_{\nu, m} = \sum_{t} V_\nu(t) e^{-imt}
-\end{equation}
-Define $V_{\nu, m}^{\textrm{static}}$ to be the observed $m$-modes if the source
-was actually static ($I_\nu(t) \equiv I_{\nu,0}$). Then as a consequence of the
-Fourier convolution theorem
-\begin{equation}
-    V_{\nu, m} = \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}.
-\end{equation}
-
-This will tend to scatter power between $m$-modes.
-
-Simulate images of point sources with this
-
-\subsection{Ionospheric Refraction}
+\subsection{Thermal Noise}
 
@@
 
-\begin{figure*}[ht]
-    \includegraphics[width=\textwidth]{maps/rgb-map-small}
-    \caption{three color map}
-\end{figure*}
-
-\begin{figure*}[ht]
-    \centering
-    \begin{tabular}{cc}
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-    \end{tabular}
-    \caption{single channel maps}
-\end{figure*}
-
-\begin{figure*}[ht]
-    \centering
-    \begin{tabular}{cc}
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-    \end{tabular}
-    \caption{jackknifed error maps}
-\end{figure*}
+%\begin{figure*}[ht]
+%    \includegraphics[width=\textwidth]{maps/rgb-map-small}
+%    \caption{three color map}
+%\end{figure*}
+%
+%\begin{figure*}[ht]
+%    \centering
+%    \begin{tabular}{cc}
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%    \end{tabular}
+%    \caption{single channel maps}
+%\end{figure*}
+%
+%\begin{figure*}[ht]
+%    \centering
+%    \begin{tabular}{cc}
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
+%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
+%    \end{tabular}
+%    \caption{jackknifed error maps}
+%\end{figure*}
 
@@
 
-\todo{Cite Abhilash, Eastwood 2017}
+\section{A Nearby Supernova Remnant????}
 
@@
 
-These maps are pretty cool.
+These maps are pretty cool. Any questions?
+
+\todo{Cite Abhilash, Eastwood 2017}
 

### 2017-06-28 paper.tex
add a figure corresponding to fitrfi.jl

@@
 
+\begin{figure*}[ht]
+    \centering
+    \begin{tabular}{cccc}
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/before-component-removal-spw14} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/after-component-removal-spw14} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/rfi-like-component-spw14} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/pickup-like-component-spw14} \\
+        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} \\
+    \end{tabular}
+    \caption{
+        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
+        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
+        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
+        smeared along tracks of constant declination. These images are generated using WSCLEAN
+        \citep{2014MNRAS.444..606O} \textbf{(a)} This image shows the initial data before any
+        sources have been removed. \textbf{(b)} This image shows the final state after 3
+        terrestrial sources of correlated noise have been removed. \textbf{(c)} This image
+        illustrates the contribution of an RFI source towards the north-west that was removed by
+        peeling. \textbf{(d)} This removed component is not associated with a dot on the horizon.
+        Instead it is likely associated with common-mode pickup in the analog signal chain.
+    }
+\end{figure*}
+
 When writing down equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated

### 2017-06-28 figures/smeared-images/make.jl

@@ -1,0 +1,88 @@
+using FileIO, Images, Colors, FITSIO, WCS
+
+# Note: The version of Imagemagick is doing some weird stuff with its gray scale. I think the colors
+# are non-linear with gamma = 0.4545 according to this forum post:
+# http://www.imagemagick.org/discourse-server/viewtopic.php?f=4&t=21269
+#
+# Alternatively we can just import a color map because the RGB images don't seem to have this
+# problem.
+
+# $ convert --version
+# Version: ImageMagick 6.7.7-10 2012-07-05 Q16 http://www.imagemagick.org
+# Copyright: Copyright (C) 1999-2012 ImageMagick Studio LLC
+# Features: OpenMP
+
+path = dirname(@__FILE__)
+magma = readcsv(joinpath(path, "..", "magma.csv"))
+values = linspace(0, 1, size(magma, 1))
+
+function process(filename)
+    fits = FITS(joinpath(path, "raw", filename))
+    img = read(fits[1])[:, :, 1, 1]
+    header = read_header(fits[1])
+    
+    output = zeros(RGBA{N0f8}, size(img))
+    
+    naxis = 2
+    equinox = header["EQUINOX"]
+    ctype =  String[header["CTYPE1"], header["CTYPE2"]]
+    crpix = Float64[header["CRPIX1"], header["CRPIX2"]]
+    crval = Float64[header["CRVAL1"], header["CRVAL2"]]
+    cdelt = Float64[header["CDELT1"], header["CDELT2"]]
+    cunit =  String[header["CUNIT1"], header["CUNIT2"]]
+    wcs = WCSTransform(naxis, equinox=equinox, ctype=ctype, crpix=crpix,
+                       crval=crval, cdelt=cdelt, cunit=cunit)
+    
+    center_ra, center_dec = crval[1], crval[2]
+    south_ra = center_ra
+    south_dec = center_dec - 90
+    south_pixcoords = world_to_pix(wcs, reshape([south_ra, south_dec], (2, 1)))
+    radius = hypot(crpix[1] - south_pixcoords[1], crpix[2] - south_pixcoords[2])
+    
+    max_value = 4e5
+    min_value = -3e5
+    
+    img -= min_value
+    img /= max_value - min_value
+    img = clamp.(img, 0, 1)
+    x1 = x2 = round(Int, crpix[1])
+    y1 = y2 = round(Int, crpix[2])
[…]

### 2017-06-28 paper.tex
expanded error analysis section

--- 2017-06-26 paper.tex
@@
 
-\section{Errors}
+\section{Observations}
 
-\subsection{Terrestrial Interference}
+\subsection{The Owens Valley Long Wavelength Array}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/antenna-layout/antenna-layout}
+    \caption{
+        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
+        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
+        antennas equipped with noise-switched front ends.
+    }
+    \label{fig:antenna-layout}
+\end{figure}
+
+The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
+Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO-LWA is a low-frequency
+instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
+Each antenna stand hosts two perpendicular broadband dipoles so that there are $288\times2$ signal
+paths in total. These signal paths feed into the 512-input LEDA correlator
+\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
+single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
+
+The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
+snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
+placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
+final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
+of the global sky brightness.  These antennas are used as part of the LEDA experiment \todo{cite
+Price et al. 2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
+Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
+
+\todo{cite Gregg's instrument paper}
+
+Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
+chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
+environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
+interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
+output evenly divides a sidereal day.
+
+\todo{describe the ionospheric conditions at the time}
+
+\subsection{Gain Calibration}
+
+Antenna gain calibration is accomplished using an iterative method independently developed by
+\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
+the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
+online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
+
+The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
+are at high elevations \todo{the rainy day dataset actually uses a shorter track of data, we should
+try using the 9 hour track again}.  These two sources are -- by an order of magnitude -- the
+brightest radio sources in the northern hemisphere.  Therefore the optimal time to solve for the
+interferometer's gain calibration is when Cas A and Cyg A are at high elevations. A calibration
+obtained in this manner is good consistent with the following day's calibration to within a 1\%
+error in the flux scale and 1$'$ error in the astrometry \todo{double check these numbers}. These
+residual errors are likely driven by differing ionospheric conditions.
+
+The flux scale is tied to the work of \citet{1977A&A....61...99B, 2012MNRAS.423L..30S,
+2017ApJS..230....7P}.
+
+Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
+analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
+gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
+The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
+per-antenna amplitude correction that is then applied to the cross-correlations.
+
+\subsection{Primary Beam Measurements}
+
+In order to generate wide-field images of the sky, the response of the antenna to the sky must be
+known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
+primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
+assume that the primary beam is invariant under north-south and east-west flips, and additionally
+that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
+We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
+then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
+basis functions to have the desired symmetry.
+
+\subsection{Source Removal}
+
+\subsubsection{Cassiopeia A and Cygnus A}
+
+Without removing bright sources from the data, sidelobes from bright sources will dominate the
+variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2017ApJS..230....7P}. A
+conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
+\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
+from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
+\todo{Measure Cyg A's sidelobe levels if it is not subtracted}
+
+At low frequencies, propagation effects through the ionosphere must be accounted for in order to
+achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
+peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
+scintillation and diffraction events on the timescale of a single integration (13 seconds) are
+observed. Therefore the direction dependent calibration changes on these timescales and the we must
+solve for one set of complex gains per source per integration.
+
+The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
+is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
+sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
+source model to eachs ource. This is performed by minimizing the minimizing the variance within an
+aperture located on each source after peeling. By phasing up a large number of integrations before
+imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
+We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
+until the variance within the aperture is minimized.
+
+\todo{Show a before and after with the updated source models}
+
+\todo{Give a plot with the updated source models}
+
+\subsubsection{The Sun}
+
+The Sun can be trivially removed from any map of the sky by constructing the map using only data
+taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
+However the dataset used in this paper consists of 28 consecutive hours. Additionally while most
+astronomical sources at these frequencies have negative spectral indices, the Sun has a large
+positive spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
+frequencies than at lower frequencies.
+
+\todo{describe sun removal -- this isn't entirely settled yet}
+
+\section{Error Analysis}
+
+\subsection{Terrestrial Interference and Pickup}
+
+\begin{figure*}[ht]
+    \centering
+    \begin{tabular}{cccc}
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/before-component-removal-spw14} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/after-component-removal-spw14} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/rfi-like-component-spw14} &
+        \includegraphics[width=0.22\textwidth]{figures/smeared-images/pickup-like-component-spw14} \\
+        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} \\
+    \end{tabular}
+    \caption{
+        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
+        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
+        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
+        smeared along tracks of constant declination. These images are generated using WSCLEAN
+        \citep{2014MNRAS.444..606O}, uniform weighting, and baselines shorter than 15 wavelengths
+        are flagged. \textbf{(a)} This image shows the initial data before any sources have been
+        removed. \textbf{(b)} This image shows the final state after 3 terrestrial sources of
+        correlated noise have been removed. \textbf{(c)} This image illustrates the contribution of
+        an RFI source towards the north-west that was removed by peeling. \textbf{(d)} This removed
+        component is not associated with a dot on the horizon.  Instead it is likely associated with
+        common-mode pickup in the analog signal chain.
+    }
+    \label{fig:fitrfi}
+\end{figure*}
 
 When writing down equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated
-voltage fluctuations measured between pairs of antennas are generated by astronomical sources of
-radio emission. In practice, this implicit assumption can be violated. For instance a low-frequency
-interferometer located in the vicinity of an arcing power line will see an additional contribution
-from the radio-frequency interference (RFI) generated by the arcing process. Similarly common-mode
-pickup along the analog signal path of the interferometer may generate an additional spurious
-contribution to the measured visibilities. While the amplitude and phase of these contaminating
-signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
+voltage fluctuations measured between pairs of antennas are exclusively generated by astronomical
+sources of radio emission. In practice this implicit assumption can be violated. For instance a
+low-frequency interferometer located in the vicinity of an arcing power line will see an additional
+contribution from the radio-frequency interference (RFI) generated by the arcing process. Similarly
+common-mode pickup along the analog signal path of the interferometer may generate an additional
+spurious contribution to the measured visibilities. While the amplitude and phase of these
+contaminating signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
 characteristic of astronomical sources.
+
+The Owens Valley is an important source of water and power for the city of Los Angeles.
+Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO-
+LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
+RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
+them by using the curvature of the incoming wavefront to infer a distance. Efforts are currently
+underway to work with the utility pole owners to have these insulators replaced.
+
+In the meantime it is possible to suppress their contamination in the dataset. The contribution of
+these RFI sources to the visibilities can be plainly seen by averaging $>24$ hours of data with the
+phase center set to zenith. In this way, true sky components are smeared along tracks of constant
+declination while terrestrial sources (ie. the arcing power lines or any common-mode pickup) are not
+smeared.  Obtaining a model for the RFI is complicated by the fact that the contaminating sources
+are at extremely low elevations where the antenna response is essentially unknown (and inhomogeneous
+due to antenna shadowing effects). Therefore it is not enough to know the physical location of the
+faulty insulator generating the RFI. In addition you must also know the response of each antenna
+(amplitude and phase) in the appropriate direction. This motivates the use of peeling
+\citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}, which allows the antenna response to be a free
+parameter.  Therefore model visibilities for the RFI can be obtained by peeling the sources after
+smearing the visibilities over $>24$ hours. See Figure~\ref{fig:fitrfi} for an illustration of this
+process.
+
+However while attempting to peel RFI sources from the averaged visibilities, it was discovered that
+frequently peeling would prefer to remove components from the visibilities that are not obviously
+associated with any source on the horizon or elsewhere in the sky (see panel (d) in
+Figure~\ref{fig:fitrfi}). In many cases the amplitude of these unassociated components exhibit the
+same sawtooth oscillations indicative of gain fluctuations in the analog electronics even after
+these gain fluctuations have been calibrated. This seems to imply that that these unassociated
+components originate as common-mode pickup in the analog signal chain. That is, if the pickup occurs
+somewhere in the middle of the analog signal chain, it will not see the same gain as the
+astronomical signal. Therefore correcting the temperature dependence of the gains for the
+astronomical signal does not correct the temperature dependence of the pick-up and hence it will
+have a sawtooth pattern with respect to time.
 
@@
 $m$-modes. However, if $\b v_\text{terrestrial}$ is actually perpendicular to all of the columns of
-$\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = 0$.  In
-practice this is unlikely. In general the contamination is proportional to the overall amplitude of
-the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
+$\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = \b 0$.
+In practice this is unlikely. In general the contamination is proportional to the overall amplitude
+of the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
 an astronomical signal ($\|\b B^*\b v_\text{terrestrial}\|/\|\b v_\text{terrestrial}\|$).
 
-These astronomical sources are anchored to the celestial sphere and therefore rotate
-across the sky over the course of a sidereal day. Terrestrial source of interference are not
-anchored to the celestial sphere.
+\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
+that it is actually worse than the RFI, but I don't actually know for sure}
 
-This characteristic motion of astronomical sources
-is a fundamental component to $m$-mode analysis imaging
+These terrestrial sources do not rotate with the sky and hence their contamination tends to be
+restricted to modes with small $m$. In this dataset the contamination is largely restricted to $m
+\lesssim 3$. As a result if the contamination is not suppressed, it will manifest itself as rings
+along stripes of constant declination. This effect is plainly visible in Figure \todo{make it}.
 
-radio emission is astronomical. Astronomical sources are anchored to the celestial sphere and
-therefore rotate across the sky over the course of a sidereal day. However, in a practice
+However because these rings are so distinctive in the final maps, it is possible to construct a
+Wiener filter that removes them at the cost of losing a small amount of information about
+astronomical sources.
 
-$m$-mode analysis imaging implicitly assumes that the correlation between any two pairs of antennas
-
-However it is instructive to analyze the contaminating effect the RFI will have
-on $m$-mode analysis maps of the sky. The correlation observed on a given
-baseline and frequency channel for a single source of RFI is
-\begin{equation}
-    V(t) = I(t) B^\textrm{near-field}
-\end{equation}
-
-However we need a strategy to mitigate the RFI before imaging. A constant source attached to the
-horizon has a fringe rate of zero. The only possible astronomical origins for a source with zero
-fringe rate are:
-
-\begin{enumerate}
-    \item a point source located at the north or south celestial poles, and
-    \item a ring of constant declination.
-\end{enumerate}
-
-Therefore while snapshot images will show the RFI source on the horizon, extended integrations will
-show the RFI as rings of constant declination. We can take advantage of this discrepancy to separate
-astronomical emission from terrestrial RFI.
+\todo{describe how the Wiener filter works}
 
@@
 
-\begin{itemize}
-    \item declination dependent flux scale errors
-    \item failure to reconcile observations from two separate times
-\end{itemize}
+A good model of the antenna beam is essential for widefield imaging. Because $m$-mode analysis
+imaging operates on a full sidereal day of data, images are constructed after watching each point in
+the sky move through large slices through the beam (excepting the celestial poles). The beam model
+therefore serves two purposes:
 
-\subsection{Ionospheric Scintillation}
+\begin{enumerate}
+    \item setting the flux scale as a function of declination
+    \item reconciling observations from two separate sidereal times
+\end{enumerate}
+
+In the first case, all sources at a given declination take the same path through the antenna primary
+beam. If the antenna response is overestimated along this track then all sources at this declination
+will have their flux underestimated. Similarly if the antenna response is underestimated then all
+the sources will have their flux overestimated.
+
+\todo{discuss the possibility of declination dependent flux-scale errors in these maps}
+
+The second case is more subtle. Sources are observed at a wide range of locations in the primary
+beam of the antenna. The imaging process must reconcile all of these observations together. The beam
+model essentially provides the instructions on how to do this. For example if at a time $t_1$ the
+antenna gain towards a source is $g$ and at a later time $t_2$ the antenna gain towards that same
+source (which has now moved) is $g/2$, then in order to correctly estimate the flux of the source
+the observations from time $t_1$ need to be multiplied by $1/g$ but the observations from time $t_2$
+need to be multiplied by $2/g$. A mistake in the beam model here will lead to a mistake in the
+estimated flux.  However in general the amplitude and phase of the antenna response needs to be
+known and so beam model errors can lead to observations being combined with incorrect phase as well.
+This will lead to a degraded PSF in the final map. \todo{quick simulation of this?}
+
+\subsection{The Ionosphere}
 
@@
 \end{equation}
-where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$
-is the baseline transfer function. The transfer function is a function of
-the direction to the source, which is in turn a function of the sidereal
-time $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic
-variability or due to scintillation, than the source flux is also a function
-of the time coordinate $t$ such that
+where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$ is the baseline transfer
+function. The transfer function is a function of the direction to the source, which is in turn a
+function of the sidereal time $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic
+variability or due to scintillation, than the source flux is also a function of the time coordinate
+$t$ such that
 \begin{equation}
@@
 
-Now assume we have observed with our interferometer for a single sidereal day.
-In order to compute the $m$-modes we must Fourier transform with respect to
-sidereal time. In a real measurement this is a discrete Fourier transform of
-the observed correlation with respect to time (where the sum over time is
-restricted to a sidereal day). \todo{fix normalization}
+Now assume we have observed with our interferometer for a single sidereal day.  In order to compute
+the $m$-modes we must Fourier transform with respect to sidereal time. In a real measurement this is
+a discrete Fourier transform of the observed correlation with respect to time (where the sum over
+time is restricted to a sidereal day). \todo{fix normalization}
 \begin{equation}
@@
 \end{equation}
-Define $V_{\nu, m}^{\textrm{static}}$ to be the observed $m$-modes if the source
-was actually static ($I_\nu(t) \equiv I_{\nu,0}$). Then as a consequence of the
-Fourier convolution theorem
+Define $V_{\nu, m}^{\textrm{static}}$ to be the observed $m$-modes if the source was actually static
+($I_\nu(t) \equiv I_{\nu,0}$). Then as a consequence of the Fourier convolution theorem
 \begin{equation}
@@
 
-This will tend to scatter power between $m$-modes.
+This will tend to scatter power between $m$-modes. \todo{cite richard for this}
 
-Simulate images of point sources with this
+\todo{Simulate images of point sources with this}
 
-\subsection{Ionospheric Refraction}
+\todo{I think the conclusion is sort of exactly what you would expect: refraction broadens the PSF
+while scintillation effects the flux scale, but honestly not by much because we have such large
+averages that unless the scintillation is Cauchy distributed it is not that bad..}
+
+\subsection{Thermal Noise}
+
+\todo{describe jack-knife tests}
 

### 2017-06-29 figures/antenna-layout/antenna-layout.jl
fixup figures
now using matplotlib 2 so the defaults aren't so horrendous anymore

@@ -11,32 +11,14 @@ leda = 252:256
 expansion = 257:288
 
 transparent = (0, 0, 0, 0)
-rc("text", usetex=false)
-rc("font", weight="light")
-rc("axes", labelweight="light", linewidth=1.2)
-rc("xtick", labelsize=14)
-rc("ytick", labelsize=14)
-
-#close("all")
 figure(1, figsize=(6, 5)); clf()
 
-scatter(east[core], north[core], c="k", s=10, lw=0)
-scatter(east[leda], north[leda], marker="+", c="k", s=80, lw=1.2)
-scatter(east[expansion], north[expansion], marker="o", c=transparent, s=40, lw=1.2)
-xticks(collect(-1500:500:500))
-yticks(collect(-500:500:1000))
-xlim(-1250, 500)
-ylim(-500, 1000)
+scatter(east[core], north[core], marker="o", c="k", s=8, lw=0)
+scatter(east[leda], north[leda], marker="+", c="k", s=50)
+scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
 gca()[:set_aspect]("equal")
-#gca()[:spines]["top"][:set_visible](false)
-#gca()[:spines]["right"][:set_visible](false)
-#gca()[:get_xaxis]()[:tick_bottom]()
-#gca()[:get_yaxis]()[:tick_left]()
-gca()[:get_xaxis]()[:set_tick_params](width=1.2, size=5)
-gca()[:get_yaxis]()[:set_tick_params](width=1.2, size=5)
-grid("off")
-xlabel("distance east / m", fontsize=16)
-ylabel("distance north / m", fontsize=16)
+xlabel("distance east / m", fontsize=12)
+ylabel("distance north / m", fontsize=12)
 tight_layout()
 
 savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0.1, transparent=true)

### 2017-06-29 paper.tex
fixup figures
now using matplotlib 2 so the defaults aren't so horrendous anymore
add an example l curve

@@
 \section{All-Sky Imaging}
+
+\begin{figure*}[ht]
+    \includegraphics[width=\textwidth]{maps/rgb-map-small}
+    \caption{three color map}
+    \label{fig:rgb}
+\end{figure*}
 
@@
 
-The process of Tikhonov regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for
-some arbitrary value of $\epsilon > 0$ chosen by the observer. The solution that minimizes this
+The process of Tikhonov regularization minimizes $\|\b v - \b B\b a\|^2 + \varepsilon\|\b a\|^2$ for
+some arbitrary value of $\varepsilon > 0$ chosen by the observer. The solution that minimizes this
 expression is given by
 \begin{equation}\label{eq:tikhonov-solution}
-    \atikh = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
+    \atikh = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b v\,.
 \end{equation}
-Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
+Tikhonov regularization adds a small value $\varepsilon$ to the diagonal of $\b B^*\b B$, fixing the
 matrix's singularity. We can see this by using the singular value decomposition (SVD) of the matrix
@@
 \begin{equation}
-    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,,
+    \atikh = \b V (\b\Sigma^2 + \varepsilon \b I)^{-1}\b\Sigma \b U^*\b v\,,
 \end{equation}
@@
 each singular component to the Tikhonov-regularized solution is scaled by $\sigma_i / (\sigma_i^2 +
-\epsilon)$, where $\sigma_i$ is the singular value for the $i$th singular component. Tikhonov
-regularization therefore acts to suppress any component for which $\sigma_i\lesssim\sqrt{\epsilon}$.
-If $\sigma_i = 0$, the component is set to zero.
+\varepsilon)$, where $\sigma_i$ is the singular value for the $i$th singular component. Tikhonov
+regularization therefore acts to suppress any component for which
+$\sigma_i\lesssim\sqrt{\varepsilon}$.  If $\sigma_i = 0$, the component is set to zero.
 
@@
 \begin{equation}
-    \b C = n \b V (\b\Sigma^2 + \epsilon\b I)^{-2} \b\Sigma^2 \b V^*\,.
+    \b C = n \b V (\b\Sigma^2 + \varepsilon\b I)^{-2} \b\Sigma^2 \b V^*\,.
 \end{equation}
-Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \epsilon)^2$.
-In the absence of Tikhonov regularization ($\epsilon=0$)
-singular components with the smallest singular values -- the ones that the interferometer is
-the least sensitive to -- actually come to dominate the covariance of the measured spherical
-harmonic coefficients. Tikhonov regularization improves this situation by downweighting these
-components.
+Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \varepsilon)^2$.  In the
+absence of Tikhonov regularization ($\varepsilon=0$) singular components with the smallest singular
+values -- the ones that the interferometer is the least sensitive to -- actually come to dominate
+the covariance of the measured spherical harmonic coefficients. Tikhonov regularization improves
+this situation by downweighting these components.
 
 While Tikhonov regularization will force unmeasured modes to zero, if a prior map of the sky already
-exists, it will be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \epsilon \|\b a-\b
+exists, it will be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \varepsilon \|\b a-\b
 a_\text{prior}\|^2$.
@@
 
-Tikhonov regularization requires the observer to pick the value of $\epsilon$. If $\epsilon$ is too
-large then too much importance is placed on minimizing the norm of the solution and the
-least-squares residuals will suffer. However if $\epsilon$ is too small then the problem will be
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/lcurve/lcurve}
+    \caption{
+        Example l-curve (from spw04)
+    }
+    \label{fig:lcurve}
+\end{figure}
+
+Tikhonov regularization requires the observer to pick the value of $\varepsilon$. If $\varepsilon$
+is too large then too much importance is placed on minimizing the norm of the solution and the
+least-squares residuals will suffer. However if $\varepsilon$ is too small then the problem will be
 poorly regularized and the resulting sky map may not represent the true sky. Picking the value of
-$\epsilon$ therefore requires understanding the trade-off between the two norms.
+$\varepsilon$ therefore requires understanding the trade-off between the two norms.
 
-This trade-off can be analyzed quantitatively by trialing several values of $\epsilon$ and computing
-$\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in Figure \todo{create
-a figure}. The shape of this curve has a characteristic L-shape, and as a result this type of plot
-is called an L-curve \todo{reference}. The ideal value of $\epsilon$ lies near the turning point of
-the plot. At this point a small decrease in $\epsilon$ will lead to an undesired rapid increase in
-$\|\b a\|^2$, and a small increase in $\epsilon$ will lead to an undesired rapid increase in $\|\b v
-- \b B\b a\|^2$.
+This trade-off can be analyzed quantitatively by trialing several values of $\varepsilon$ and
+computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in Figure
+\todo{create a figure}. The shape of this curve has a characteristic L-shape, and as a result this
+type of plot is called an L-curve \todo{reference}. The ideal value of $\varepsilon$ lies near the
+turning point of the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired
+rapid increase in $\|\b a\|^2$, and a small increase in $\varepsilon$ will lead to an undesired
+rapid increase in $\|\b v - \b B\b a\|^2$.
 
-In practice, the L-curve should be used as a guide to estimate a reasonable value of $\epsilon$.
-However better results can often be obtained by tuning the value of $\epsilon$. For instance
-increasing the value of $\epsilon$ can improve the noise properties of the map by down-weighting
-noisy modes. Decreasing the value of $\epsilon$ can improve the resolution in the map by
+In practice, the L-curve should be used as a guide to estimate a reasonable value of $\varepsilon$.
+However better results can often be obtained by tuning the value of $\varepsilon$. For instance
+increasing the value of $\varepsilon$ can improve the noise properties of the map by down-weighting
+noisy modes. Decreasing the value of $\varepsilon$ can improve the resolution in the map by
 up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
-choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
+choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in traditional
 imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.
@@
     \b a_\text{PSF}(\theta, \phi)
-        = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
+        = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
 \end{equation}
@@
 %\begin{figure*}[ht]
-%    \includegraphics[width=\textwidth]{maps/rgb-map-small}
-%    \caption{three color map}
-%\end{figure*}
-%
-%\begin{figure*}[ht]
 %    \centering

### 2017-06-29 figures/lcurve/make.jl

@@ -1,0 +1,20 @@
+using JLD, PyPlot
+
+path = dirname(@__FILE__)
+trials, regnorm, lsnorm = load(joinpath(path, "lcurve.jld"), "trials", "regnorm", "lsnorm")
+
+close("all")
+figure(1, figsize=(6, 4))
+plot(regnorm, lsnorm, "k-")
+for idx = 8:7:36
+    annotate(@sprintf("ε=%g", trials[idx]), xy=(regnorm[idx], lsnorm[idx]),
+             xytext=(regnorm[idx]+60000, lsnorm[idx]+20000),
+             arrowprops=Dict(:width=>1, :headwidth=>5, :headlength=>5,
+                             :shrink=>0.05, :facecolor=>"black"))
+end
+xlabel(L"\Vert a \Vert", fontsize=12)
+ylabel(L"\Vert v - Ba \Vert", fontsize=12)
+tight_layout()
+
+savefig(joinpath(path, "lcurve.pdf"), bbox_inches="tight", pad_inches=0.1, transparent=true)
+

### 2017-07-01 paper.tex
add beam plots

@@
 This trade-off can be analyzed quantitatively by trialing several values of $\varepsilon$ and
-computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in Figure
-\todo{create a figure}. The shape of this curve has a characteristic L-shape, and as a result this
-type of plot is called an L-curve \todo{reference}. The ideal value of $\varepsilon$ lies near the
+computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in
+Figure~\ref{fig:lcurve}. The shape of this curve has a characteristic L-shape, and as a result this
+type of plot is called an L-curve \todo{reference?}. The ideal value of $\varepsilon$ lies near the
 turning point of the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired
@@
 
-The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
-are at high elevations \todo{the rainy day dataset actually uses a shorter track of data, we should
-try using the 9 hour track again}.  These two sources are -- by an order of magnitude -- the
-brightest radio sources in the northern hemisphere.  Therefore the optimal time to solve for the
-interferometer's gain calibration is when Cas A and Cyg A are at high elevations. A calibration
-obtained in this manner is good consistent with the following day's calibration to within a 1\%
-error in the flux scale and 1$'$ error in the astrometry \todo{double check these numbers}. These
-residual errors are likely driven by differing ionospheric conditions.
+The antenna complex gains are measured from a 7.2 hour track of data from when Cyg A and Cas are at
+high elevations. The gains measured in this way are then used to calibrate the entire 28 hour
+dataset. Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources
+in the northern hemisphere. Therefore the optimal time to solve for the interferometer's gain
+calibration is when these sources are at high elevations. \todo{cite some statistics on how good
+this calibration is? what do I quantify?}
+
+\todo{at the moment we calibrated with the Baars spectrum for Cas. we should actually iterate once
+and use the new spectrum that comes out of the beam fitting routine}
 
@@
 
+\begin{figure*}[ht]
+    \gridline{
+        \fig{figures/beam/source-tracks}{0.45\textwidth}{(a)}
+        \fig{figures/beam/stokes-I-beam}{0.45\textwidth}{(b)}
+    }
+    \caption{
+        Example beam model (from spw04).
+    }
+    \label{fig:beam}
+\end{figure*}
+
 In order to generate wide-field images of the sky, the response of the antenna to the sky must be
@@
 that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
-We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
-then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
-basis functions to have the desired symmetry.
+These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
+antennas will contribute towards breaking these symmetries at some level. However some amount of
+symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
+when the flux of a source is unknown.
+
+We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
+3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
+those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
+$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
+zenith is constrained to be unity.
+
+\todo{plot that shows the tracks after symmetries applied and the resulting beam fit?}
 

### 2017-07-01 figures/beam/make.jl

@@ -1,0 +1,76 @@
+using JLD, PyPlot, CasaCore.Measures
+
+path = dirname(@__FILE__)
+Iimg = load(joinpath(path, "beam.jld"), "I-image")
+
+sources = Dict("Cyg A" => Direction(dir"J2000", "19h59m28.35663s", "+40d44m02.0970s"),
+               "Cas A" => Direction(dir"J2000", "23h23m24.000s", "+58d48m54.00s"),
+               "Tau A" => Direction(dir"J2000", "05h34m31.94s", "+22d00m52.2s"),
+               "Vir A" => Direction(dir"J2000", "12h30m49.42338s", "+12d23m28.0439s"),
+               "Her A" => Direction(dir"J2000", "16h51m11.4s", "+04d59m20s"),
+               "Hya A" => Direction(dir"J2000", "09h18m05.651s", "-12d05m43.99s"),
+               "Per B" => Direction(dir"J2000", "04h37m04.3753s", "+29d40m13.819s"),
+               "3C 353" => Direction(dir"J2000", "17h20m28.147s", "-00d58m47.12s"))
+
+ovro_lwa = Position(pos"ITRF", -2.40927462614919e6, -4.477838733582964e6, 3.839370728766106e6)
+
+times = linspace(4.994049600941745e9, 4.994150416022397e9, 7756)
+
+close("all")
+figure(1, figsize=(6, 4))
+circle = plt[:Circle]((0, 0), 1, alpha=0)
+gca()[:add_patch](circle)
+imshow(Iimg, extent=(-1, 1, -1, 1), interpolation="nearest", vmin=0, vmax=1,
+       cmap=get_cmap("magma"), clip_path=circle)
+gca()[:set_aspect]("equal")
+colorbar()
+xlim(-1, 1)
+ylim(-1, 1)
+xlabel("l / direction cosine", fontsize=12)
+ylabel("m / direction cosine", fontsize=12)
+tight_layout()
+savefig(joinpath(path, "stokes-I-beam.pdf"), bbox_inches="tight", pad_inches=0.1, transparent=true)
+
+figure(2, figsize=(6, 4)); clf()
+frame = ReferenceFrame()
+set!(frame, ovro_lwa)
+for name in keys(sources)
+    @show name
+    direction = sources[name]
+    l = Float64[]
+    m = Float64[]
+    for t in times
+        set!(frame, Epoch(epoch"UTC", t*seconds))
+        azel = measure(frame, direction, dir"AZEL")
+        az = longitude(azel)
[…]

### 2017-07-05 paper.tex
use aastex features

@@
 \usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{natbib}
 
@@
 \begin{figure*}[ht]
-    \includegraphics[width=\textwidth]{maps/rgb-map-small}
+    \plotone{maps/rgb-map-small}
     \caption{three color map}
@@
 \begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/lcurve/lcurve}
+    \plotone{figures/lcurve/lcurve}
     \caption{
@@
 \begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/antenna-layout/antenna-layout}
+    \plotone{figures/antenna-layout/antenna-layout}
     \caption{
@@
 \begin{figure*}[ht]
-    \gridline{
-        \fig{figures/beam/source-tracks}{0.45\textwidth}{(a)}
-        \fig{figures/beam/stokes-I-beam}{0.45\textwidth}{(b)}
-    }
+    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
     \caption{
-        Example beam model (from spw04).
+        Example Stokes-I beam model (from spw04).
     }
@@
 $Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
-zenith is constrained to be unity.
-
-\todo{plot that shows the tracks after symmetries applied and the resulting beam fit?}
+zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of the fitted beam
+model.
 
@@
 \begin{figure*}[ht]
-    \centering
-    \begin{tabular}{cccc}
-        \includegraphics[width=0.22\textwidth]{figures/smeared-images/before-component-removal-spw14} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-images/after-component-removal-spw14} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-images/rfi-like-component-spw14} &
-        \includegraphics[width=0.22\textwidth]{figures/smeared-images/pickup-like-component-spw14} \\
-        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} \\
-    \end{tabular}
+    \gridline{
+        \fig{figures/smeared-images/before-component-removal-spw14}{0.22\textwidth}{(a)}
+        \fig{figures/smeared-images/after-component-removal-spw14}{0.22\textwidth}{(b)}
+        \fig{figures/smeared-images/rfi-like-component-spw14}{0.22\textwidth}{(c)}
+        \fig{figures/smeared-images/pickup-like-component-spw14}{0.22\textwidth}{(d)}
+    }
     \caption{
@@
 
-%\begin{figure*}[ht]
-%    \centering
-%    \begin{tabular}{cc}
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%    \end{tabular}
-%    \caption{single channel maps}
-%\end{figure*}
-%
-%\begin{figure*}[ht]
-%    \centering
-%    \begin{tabular}{cc}
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
-%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
-%    \end{tabular}
-%    \caption{jackknifed error maps}
-%\end{figure*}
-
-\begin{table*}[t]
-    \centering
-    \begin{tabular}{ccccc}
-        \hline\hline
-        \# & $\nu$ / MHz & $\Delta\nu$ / MHz
-           & $\theta$ / arcmin  & noise / Jy \\ \hline
+\floattable
+\begin{deluxetable}{ccccc}
+    \tablecaption{Summary of the produced maps\label{tab:summary}}
+    \tablehead{
+        \colhead{\#} & \colhead{$\nu$ / MHz} & \colhead{$\Delta\nu$ / MHz} &
+        \colhead{$\theta$ / arcmin} & \colhead{noise / Jy}
+    }
+    \startdata
         1 & 36.528 & 0.024 & & \\
@@
         8 & 73.152 & 0.024 & & \\
-        \hline\hline
-    \end{tabular}
-    \caption{Summary of the produced maps}
-\end{table*}
+    \enddata
+\end{deluxetable}
 

### 2017-07-25 paper.tex
wip

@@
 attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
-Reionization (EoR) of $8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
+Reionization (EoR) of $z_r = 8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
 Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
 new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
-combined with X-ray measurements \citep{2006ApJ...647...25B}.
-
-\todo{kinetic SZ effect puts an upper limit on the duration of reionization}
+combined with X-ray measurements \citep{2006ApJ...647...25B}. The kinetic Sunyaev-Zel'dovich effect
+has been used to constrain the duration of reionization $\Delta z_r \le 4.4$
+\citep{2012ApJ...756...65Z}.
 
@@
 the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
-temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.
-
-\todo{discuss 21cmmc ionizing efficiency, photon mean free path, minimum halo mass}
-\todo{discuss what can be learned from global experiments}
-
-The spatial power spectrum of this perturbation is expected to be dominated
-by inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing
-ionized bubbles during the EoR at $z\sim 7$ \todo{citation}.
+temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
+power spectrum of this perturbation is expected to be dominated by inhomogeneous heating of the IGM
+at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
+7$ where a detection can constrain the ionizing efficiency of early galaxies, UV photon
+mean-free-path, and the minimum halo mass that can support star formation
+\citep{2015MNRAS.449.4246G}.
 
@@
 
-\citet{2011A&A...525A.138G}
+Recently a host of new low-frequency sky surveys have been conducted including MSSS
+\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
+\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
+catalog of radio sources. Surveys that capture the diffuse emission include at 45 MHz, where
+\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
+Frequency Sky Survey \citet{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
+and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.
 
-\todo{TGSS, MSSS, GLEAM}
+In this paper we will present a series of new low-frequency maps of the sky between 36.528 Mhz and
+73.152 Mhz, capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with
+angular resolution of roughly 10'. These maps are generated using $m$-mode analysis imaging -- a new
+imaging technique for transit telescopes.
 
@@
 \begin{figure*}[ht]
-    \plotone{maps/rgb-map-small}
+    \plotone{maps/2017-04-20-rgb-map-smaller}
     \caption{three color map}

### 2017-07-25 figures/lcurve/make.jl

@@ -1,7 +1,8 @@
 using JLD, PyPlot
 
 path = dirname(@__FILE__)
-trials, regnorm, lsnorm = load(joinpath(path, "lcurve.jld"), "trials", "regnorm", "lsnorm")
+#trials, regnorm, lsnorm = load(joinpath(path, "lcurve.jld"), "trials", "regnorm", "lsnorm")
+trials, regnorm, lsnorm = load(joinpath(path, "18.jld"), "trials", "regnorm", "lsnorm")
 
 close("all")
 figure(1, figsize=(6, 4))

### 2017-07-25 figures/psf/make.jl
add a plot of the psf

@@ -1,0 +1,30 @@
+using JLD, PyPlot
+
+path = dirname(@__FILE__)
+close("all")
+
+function plot(filename)
+    img = load(joinpath(path, filename*".jld"), "img")
+    img = img[51:151, 51:151]
+    img /= maximum(img)
+    
+    figure()
+    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    
+    imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
+           vmin=-0.2, vmax=1.0,
+           extent=(150, -150, -150, 150))
+    gca()[:set_aspect]("equal")
+    cbar = colorbar()
+    cbar[:ax][:tick_params](labelsize=16)
+    xlabel("ΔRA" * " (arcmin)", fontsize=16)
+    ylabel("Δdec" * " (arcmin)", fontsize=16)
+    tight_layout()
+
+    savefig(joinpath(path, filename*".pdf"),
+            bbox_inches="tight", pad_inches=0.1, transparent=true)
+end
+
+#plot("spw04-psf-00-degrees")
+plot("spw04-psf-45-degrees")
+

### 2017-07-25 figures/lcurve/make.jl
update the lcurve plot
and stop tracking the jld file

@@ -1,20 +1,32 @@
 using JLD, PyPlot
 
 path = dirname(@__FILE__)
-#trials, regnorm, lsnorm = load(joinpath(path, "lcurve.jld"), "trials", "regnorm", "lsnorm")
-trials, regnorm, lsnorm = load(joinpath(path, "18.jld"), "trials", "regnorm", "lsnorm")
+trials, regnorm, lsnorm = load(joinpath(path, "lcurve.jld"), "trials", "regnorm", "lsnorm")
+regnorm /= 10000
+lsnorm  /= 10000
+
+function do_annotation(idx, x, y)
+    annotate(@sprintf("ε=%g", trials[idx]), xy=(regnorm[idx], lsnorm[idx]),
+             xytext=(regnorm[idx]+x, lsnorm[idx]+y),
+             arrowprops=Dict(:width=>1, :headwidth=>5, :headlength=>5,
+                             :shrink=>0.05, :facecolor=>"black"),
+             horizontalalignment=x≤0 ? "center" : "left",
+             fontsize=16)
+end
+
 
 close("all")
-figure(1, figsize=(6, 4))
+figure(1)
+
+gca()[:tick_params](axis="both", which="major", labelsize=16)
 plot(regnorm, lsnorm, "k-")
-for idx = 8:7:36
-    annotate(@sprintf("ε=%g", trials[idx]), xy=(regnorm[idx], lsnorm[idx]),
-             xytext=(regnorm[idx]+60000, lsnorm[idx]+20000),
-             arrowprops=Dict(:width=>1, :headwidth=>5, :headlength=>5,
-                             :shrink=>0.05, :facecolor=>"black"))
-end
-xlabel(L"\Vert a \Vert", fontsize=12)
-ylabel(L"\Vert v - Ba \Vert", fontsize=12)
+do_annotation(8, 10, 10)
+do_annotation(15, 10, 10)
+do_annotation(22, 10, 10)
+do_annotation(29, 0, 10)
+do_annotation(36, 10, 10)
+xlabel(L"\Vert a \Vert" * " (arbitrary units)", fontsize=16)
+ylabel(L"\Vert v - Ba \Vert" * " (arbitrary units)", fontsize=16)
 tight_layout()
 
 savefig(joinpath(path, "lcurve.pdf"), bbox_inches="tight", pad_inches=0.1, transparent=true)

### 2017-07-25 paper.tex
continue to update text and use aastex 6.1

@@
 
-\documentclass[twocolumn]{aastex6}
+\documentclass[twocolumn]{aastex61}
 
@@
 \usepackage{amsmath}
+\usepackage[]{algorithm2e}
 
@@
 
-\author{
-    Michael W. Eastwood,
-    Gregg Hallinan,
-    Twilight Sparkle,
-    Rainbow Dash
-}
+\author{Michael W. Eastwood}
+\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+
+\author{Marin M. Anderson}
+\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+
+\author{Ryan Monroe}
+\affiliation{Department of Electrical Engineering, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+
+\author{Gregg Hallinan}
+\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+
+\author{Esayas B. Shume} % contributed ionosphere text
+\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}
 
@@
     I present all-sky maps of the sky from the Owens Valley Long Wavelength Array.
-    These maps are created from the application of $m$-mode analysis.
+    These maps are created from the application of $m$-mode analysis. \todo{Wednesday}
 \end{abstract}
+
+\keywords{
+    cosmology: observations --
+    dark ages, reionization, first stars --
+    radio continuum: galaxies --
+    radio continuum: ISM
+}
 
@@
 Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
-\todo{cite Price et al. 2017}, BIGHORNS \citep{2015PASA...32....4S}, SCI-HI
-\citep{2014ApJ...782L...9V}, and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum
-experiments include PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
-\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.
+\citep{todo_price_2017}, BIGHORNS \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V},
+and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
+\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
+\citep{2016ApJ...833..102B}.
 
@@
     \plotone{maps/2017-04-20-rgb-map-smaller}
-    \caption{three color map}
+    \caption{
+        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
+        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
+        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
+        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
+        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
+        emission is synchrotron, but the blue regions mottling the galactic plane are due to
+        free-free absorption from \ion{H}{2} regions.
+    }
     \label{fig:rgb}
@@
 the available measurements $V^{ij}_\nu$.
+
+For later convenience we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
+\begin{equation}\label{eq:baseline-transfer-function}
+    V^{ij}_\nu = \int_\text{sky} B^{ij}_\nu(\hat r) I_\nu(\hat r) \,\d\Omega \, .
+\end{equation}
+The baseline transfer function defines the response of a single baseline to the sky, and is a
+function of the antenna primary beam and baseline orientation.
 
@@
 For a transit telescope, the visibilities $V^{ij}_\nu$ are a periodic function of sidereal
-time\footnote{
+time.\footnote{
     This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the sun)
@@
     maps is mild.
-}.
+}
 Therefore it is a very natural operation to compute the Fourier transform of the visibilities with
@@
 of $m$ correspond to components that vary on quicker timescales.
-
-\todo{introduce the baseline transfer function because I will want to use it in later sections}
 
@@
     \caption{
-        Example l-curve (from spw04)
+        An example L-curve using OVRO-LWA data at 36.528 MHz. The $x$-axis is the norm of the
+        solution (in this case the spherical harmonic coefficients) given in arbitrary units. The
+        $y$-axis is the least-squares norm given in arbitrary units. $\varepsilon$ is the
+        regularization parameter. When the regularization parameter is small, the norm of the
+        solution grows rapidly. When the regularization parameter is large, the least-squares norm
+        grows rapidly. The optimal value for the regularization parameter is near
+        $\varepsilon=0.01$.
     }
@@
 Figure~\ref{fig:lcurve}. The shape of this curve has a characteristic L-shape, and as a result this
-type of plot is called an L-curve \todo{reference?}. The ideal value of $\varepsilon$ lies near the
-turning point of the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired
-rapid increase in $\|\b a\|^2$, and a small increase in $\varepsilon$ will lead to an undesired
-rapid increase in $\|\b v - \b B\b a\|^2$.
+type of plot is called an L-curve. The ideal value of $\varepsilon$ lies near the turning point of
+the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired rapid increase
+in $\|\b a\|^2$, and a small increase in $\varepsilon$ will lead to an undesired rapid increase in
+$\|\b v - \b B\b a\|^2$.
 
@@
 
-While $m$-mode analysis imaging automatically deconvolves large angular scales, point sources do not
-get deconvolved by the imaging process. This is a limitation of the set of basis functions we have
-chosen to represent the sky -- the spherical harmonics. Point sources carry power to large values of
-$l$, but the regularization will eventually begin to downweight spherical harmonics with $l$ larger
-than what the interferometer is sensitive to. This consequence of this is that point sources will
-appear in the maps with some characteristic point spread function. This point spread function may be
-computed with
+$m$-mode analysis imaging automatically deconvolves angular scales described by modes for which the
+singular values of $\b B$ are $\gg \sqrt{\varepsilon}$. For example, structures on angular scales
+smaller than $\lambda/b_\text{min}$ and larger than $\lambda/b_\text{max}$ (where $b_\text{min}$ and
+$b_\text{max}$ are the minimum and maximum baseline lengths) are generally well-measured by the
+interferometer and will be automatically deconvolved during the imaging process. However, as the
+total integration time of the data set increases, the noise in the data decreases. One consequence
+of this is that the regularization parameter $\varepsilon$ can be decreased. This increases the
+number of modes for which $\sigma_i \gg \sqrt{\varepsilon}$, and as a consequence the automatic
+deconvolution can extend to scales larger than $\lambda/b_\text{min}$ and smaller than
+$\lambda/b_\text{max}$.
+
+However point sources do not get deconvolved by the imaging process even in the limit of infinite
+SNR and $\varepsilon \rightarrow 0$. This is because point sources carry power to large values of
+$l$ and by computational necessity we truncated the spherical harmonic representation of the sky at
+some $l_\text{max}$. A consequence of this is that point sources will appear in the maps with a
+characteristic point spread function (PSF). The PSF may be computed with:
 \begin{equation}
@@
 where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
-the point spread function at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta,
-\phi)$ is the vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given
-by
+the PSF at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta, \phi)$ is the
+vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given by
 \begin{equation}
@@
 
-\todo{include a few images of the computed PSF for my maps}
+In general the PSF can be a function of the right ascension and declination. However point sources
+at the same declination take the same track through the sky and therefore (barring any ionospheric
+effects) will have the same PSF. The PSF is actually only a function of the declination. For
+example, sources at low elevations will tend to have an extended PSF along the north-south axis due
+to baseline foreshortening. An example computed PSF is shown in Figure~\ref{fig:psf}.
 
-\todo{describe how we incorporate this into major and minor iterations}
+The computed PSF as a function of frequency and declination can be used to adapt the CLEAN algorithm
+\citep{1974A&AS...15..417H} to $m$-mode analysis.
+
+\begin{algorithm}
+    \KwData{dirty maps generated from the output of Equation~\ref{eq:tikhonov-solution};}
+    \KwResult{clean maps with point sources deconvolved;}
+    pre-compute $\b M = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B$\;
+    \While{noise in map $>$ threshold}{
+        identify the pixel with the largest amplitude\;
+        compute $\b a_\text{PSF} = \b M \b a_\text{PS}$\;
+        update $\b a \leftarrow \b a - (\textit{gain})\times\b a_\text{PSF}$\;
+    }
+    convolve removed components with a CLEAN-beam and restore to the map\;
+\end{algorithm}
+
+It should be noted that for interferometers with more baselines than the number of spherical
+harmonics used in the maps, $\b M$ is a much smaller matrix than the full transfer matrix $\b B$.
+Therefore the cost of multiplying by $\b M$ can actually be dominated by the cost of computing the
+spherical harmonics describing a point source at the identified pixel.
 
@@
 
+\begin{figure}[t]
+    \plotone{figures/psf/spw04-psf-45-degrees}
+    \caption{
+        The computed PSF for the OVRO-LWA for a point source at a declination of $+45^\circ$ and
+        frequency of $36.528$ MHz.
+    }
+    \label{fig:psf}
+\end{figure}
+
 The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO-LWA is a low-frequency
-instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
-Each antenna stand hosts two perpendicular broadband dipoles so that there are $288\times2$ signal
-paths in total. These signal paths feed into the 512-input LEDA correlator
-\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
-single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
+Owens Valley Radio Observatory (OVRO) near Big Pine, California \citep{todo_hallinan_2017}.  The
+OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912
+MHz and 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
+there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
+correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
+hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
+are unused.
 
@@
 final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
-of the global sky brightness.  These antennas are used as part of the LEDA experiment \todo{cite
-Price et al. 2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
+of the global sky brightness.  These antennas are used as part of the LEDA experiment
+\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
 Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
-
-\todo{cite Gregg's instrument paper}
 
@@
 
-\todo{describe the ionospheric conditions at the time}
+The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
+$>-30$ nT during the entirety of the observing period.\footnote{
+    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
+    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}).
+}
+Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
+$\text{Dst} < -30$ nT. Therefore there were no geomagnetic storms during the time of these
+observations.
 
@@
 per-antenna amplitude correction that is then applied to the cross-correlations.
+
+\todo{tuesday}
 
@@
 
-\section{A Nearby Supernova Remnant????}
-
 \section{Discussion}
 
-These maps are pretty cool. Any questions?
+\citet{todo_mishra_2017}
 
-\todo{Cite Abhilash, Eastwood 2017}
+\todo{Wednesday}
 

### 2017-07-26 figures/flux-scale/make.jl
add plots illustrating the flux scale

@@ -1,0 +1,54 @@
+using JLD, PyPlot
+using CasaCore.Measures
+
+path = dirname(@__FILE__)
+close("all")
+
+frequencies = [3.6528e7,4.176e7,4.6992e7,5.2224e7,5.7456e7,6.2688e7,6.792e7,7.3152e7]
+exceptions = ("Cyg A", "Vir A", "Hya A", "Per B", "3C 353")
+
+calibrators, measured_fluxes, perley_fluxes, scaife_fluxes, baars_fluxes =
+    load(joinpath(path, "source-fluxes-map-wiener-filtered.jld"),
+         "calibrators", "measured_fluxes", "perley_fluxes", "scaife_fluxes", "baars_fluxes")
+
+names = collect(keys(calibrators))
+
+for (idx, name) in enumerate(names)
+    direction = calibrators[name]
+    lower = lowercase(replace(name, " ", ""))
+    if name in exceptions
+        temp = load(joinpath(path, "source-fluxes-map-$lower-peeled.jld"), "measured_fluxes")
+        measured = temp[name]
+    else
+        measured = measured_fluxes[name]
+    end
+
+    figure(idx); clf()
+    gca()[:tick_params](axis="both", which="major", labelsize=16)
+
+    plot(frequencies/1e6, measured, "ko")
+    if name in keys(perley_fluxes)
+        model = perley_fluxes[name]
+        plot(frequencies/1e6, model, "k-")
+    end
+    if name in keys(scaife_fluxes)
+        model = scaife_fluxes[name]
+        plot(frequencies/1e6, model, "k--")
+    end
+    if name in keys(baars_fluxes)
+        model = baars_fluxes[name]
+        plot(frequencies/1e6, model, "k-.")
+    end
+    xlim(35, 75)
+    ylimits = gca()[:get_ylim]()
+    ylim(0, max(100, ylimits[2]))
+    title(name, fontsize=16)
+    xlabel("Frequency (MHz)", fontsize=16)
+    ylabel("Flux (Jy)", fontsize=16)
+    grid("on")
+    tight_layout()
+
+    savefig(joinpath(path, "flux-$lower.pdf"),
+            bbox_inches="tight", pad_inches=0.1, transparent=true)
+end
+

### 2017-07-26 figures/channel-maps/make.jl
add channel maps

@@ -1,0 +1,46 @@
+using JLD, PyPlot, PyCall
+
+unshift!(PyVector(pyimport("sys")["path"]), "")
+@pyimport my_log_scale as mls
+
+path = dirname(@__FILE__)
+close("all")
+
+function plot(filename)
+    img, ν = load(joinpath(path, filename*".jld"), "image", "frequency")
+
+    max = maximum(img)/5
+    min = minimum(img)
+    base = max - min
+    
+    figure(); clf()
+    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+    imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
+           norm = mls.MyLogNormalize(min, max, base),
+           extent=(-2, 2, -1, 1),
+           clip_path=ellipse)
+    gca()[:set_aspect]("equal")
+    title(@sprintf("%.3f MHz", ν/1e6), fontsize=16)
+    axis("off")
+    cbar = colorbar(fraction=0.02)
+    cbar[:ax][:tick_params](labelsize=16)
+    tight_layout()
+
+    savefig(joinpath(path, filename*".pdf"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
+end
+
+plot("spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+plot("spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+

### 2017-07-26 paper.tex
progress towards first draft

@@
 \affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+
+\author{Lincoln Greenhill}
+\affiliation{Harvard}
+
+\author{Hugh Garsden}
+\affiliation{Harvard}
+
+\author{Stephen Bourke}
+\affiliation{Chalmers}
 
@@
 
-\section{All-Sky Imaging}
+\section{Observations}
 
@@
 \end{figure*}
+
+\subsection{The Owens Valley Long Wavelength Array}
+
+\begin{figure}[t]
+    \plotone{figures/antenna-layout/antenna-layout}
+    \caption{
+        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
+        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
+        antennas equipped with noise-switched front ends.
+    }
+    \label{fig:antenna-layout}
+\end{figure}
+
+\begin{deluxetable*}{ccccc}
+    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
+    \tablewidth{0pt}
+    \tablehead{
+        \colhead{\#} & \colhead{$\nu$ / MHz} & \colhead{$\Delta\nu$ / MHz} &
+        \colhead{$\theta$ / arcmin} & \colhead{noise / Jy}
+    }
+    \startdata
+        1 & 36.528 & 0.024 & & \\
+        2 & 41.760 & 0.024 & & \\
+        3 & 46.992 & 0.024 & & \\
+        4 & 52.224 & 0.024 & & \\
+        5 & 57.456 & 0.024 & & \\
+        6 & 62.688 & 0.024 & & \\
+        7 & 67.920 & 0.024 & & \\
+        8 & 73.152 & 0.024 & & \\
+    \enddata
+\end{deluxetable*}
+
+The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
+Owens Valley Radio Observatory (OVRO) near Big Pine, California \citep{todo_hallinan_2017}.  The
+OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912
+MHz and 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
+there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
+correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
+hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
+are unused.
+
+The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
+snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
+placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
+final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
+of the global sky brightness.  These antennas are used as part of the LEDA experiment
+\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
+Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
+
+Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
+chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
+environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
+interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
+output evenly divides a sidereal day.
+
+The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
+$>-30$ nT during the entirety of the observing period.\footnote{
+    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
+    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}).
+}
+Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
+$\text{Dst} < -30$ nT. Therefore there were no geomagnetic storms during the time of these
+observations.
+
+Antenna gain calibration is accomplished using an iterative method independently developed by
+\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
+the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
+online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
+
+The antenna complex gains are measured from a 22 minute track of data from when Cyg A and Cas are at
+high elevations. The gains measured in this way are then used to calibrate the entire 28 hour
+dataset. Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources
+in the northern hemisphere. Therefore the optimal time to solve for the interferometer's gain
+calibration is when these sources are at high elevations. The calibration sky model consists only of
+Cyg A and Cas A. The flux of Cyg A is anchored to the results of \citet{1977A&A....61...99B} while
+the flux of Cas A is measured from the data itself (using a preliminary calibration).
+
+Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
+analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
+gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
+The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
+per-antenna amplitude correction that is then applied to the cross-correlations.
+
+\subsection{Primary Beam Measurements}
+
+\begin{figure*}[ht]
+    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
+    \caption{
+        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
+        OVRO-LWA.
+        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
+        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
+    }
+    \label{fig:beam}
+\end{figure*}
+
+In order to generate wide-field images of the sky, the response of the antenna to the sky must be
+known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
+primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
+assume that the primary beam is invariant under north-south and east-west flips, and additionally
+that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
+These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
+antennas will contribute towards breaking these symmetries at some level. However some amount of
+symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
+when the flux of a source is unknown.
+
+We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
+3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
+those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
+$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
+zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of the fitted beam
+model.
+
+\subsection{Source Removal}
+
+\subsubsection{Cygnus A and Cassiopeia A}
+
+%\begin{deluxetable*}{ccccDCCD}
+%    \tablecaption{Resolved source models for Cyg A and Cas A\label{tab:resolved-source-models}}
+%    \tablewidth{0pt}
+%    \tablehead{
+%        \colhead{} & \colhead{} &
+%            \colhead{} & \colhead{} &
+%            \multicolumn2c{Amplitude} &
+%            \colhead{Major FWHM} & \colhead{Minor FWHM} &
+%            \multicolumn2c{Position angle} \\
+%        \colhead{Source} & \colhead{\#} &
+%            \colhead{RA} & \colhead{Dec} &
+%            \multicolumn2c{(relative)} &
+%            \colhead{(arcsec)} & \colhead{(arcsec)} &
+%            \multicolumn2c{(deg)}
+%    }
+%    \decimals
+%    \startdata
+%        Cyg A & 1 & & & 1.0 & 128. & 22. & -74.503 \\
+%              & 2 & & & 0.1477 & 183. & 141. & 43.449 \\[0.2cm]
+%        Cas A & 1 & & & 1.0 & 0. & 0. & 0. \\
+%              & 2 & & & 1.0 & 0. & 0. & 0. \\
+%              & 3 & & & 1.0 & 0. & 0. & 0. \\
+%    \enddata
+%\end{deluxetable*}
+
+Without removing bright sources from the data, sidelobes from bright sources will dominate the
+variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2017ApJS..230....7P}. A
+conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
+\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
+from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
+
+At low frequencies, propagation effects through the ionosphere must be accounted for in order to
+achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
+peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
+scintillation and diffraction events on the timescale of a single integration (13 seconds) are
+observed. Therefore the direction dependent calibration changes on these timescales and the we must
+solve for one set of complex gains per source per integration.
+
+The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
+is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
+sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
+source model to eachs ource. This is performed by minimizing the minimizing the variance within an
+aperture located on each source after peeling. By phasing up a large number of integrations before
+imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
+We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
+until the variance within the aperture is minimized.
+
+Armed with resolved source models for both Cyg A and Cas A, these two sources can be peeled from the
+dataset to the required dynamic range.
+
+%\todo{slice through Cyg A and Cas A to illustrate the removal process}
+%\todo{Give a plot with the updated source models}
+
+\subsubsection{Other Bright Sources}
+
+Other bright sources including Vir A, Tau A, Her A, Hya A, Per B, and 3C 353 are also removed from
+the visibilities prior to imaging. Because these sources are much fainter than Cyg A and Cas A, we
+do not need resolved source models to be able to remove these sources from the visibilities without
+residual sidelobes contaminating the image.
+
+However, the ionosphere will cause these sources to scintillate and refract. So first the position
+and flux of each source is measured separately in each channel and integration. Then the sources are
+subtracted from the visibilities using the updated position and flux of the source. The brightest of
+these sources (Vir A and Tau A) will be peeled using a direction dependent calibration when they are
+at high elevations.
+
+\subsubsection{The Sun}
+
+The sun can be trivially removed from any map of the sky by constructing the map using only data
+taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
+However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
+suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
+sun is well-resolved by the OVRO-LWA and hence a somewhat detailed source model is needed. In fact
+the optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new
+model is needed for each of the 8 channel maps produced in this paper. So while we could fit a
+limited number of Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.
+Additionally while most astronomical sources at these frequencies have negative spectral indices,
+the Sun has a large positive spectral index. Therefore more care will need to be taken in
+subtracting the Sun at higher frequencies than at lower frequencies.
+
+The strategy used for removing the Sun below 55 MHz involves fitting a shapelet
+\citep{2003MNRAS.338...35R} model to the Sun and subtracting without the use of direction dependent
+gains. The shapelet fitting is performed in the visibility space. Above 55 MHz a model is fit to the
+Sun by minimizing the residuals after peeling (in the same way that models are obtained for Cyg A
+and Cas A). The Sun is then peeled from each integration using direction dependent gains.
+
+\subsection{Flux Scale}
+
+\begin{figure*}[p]
+    \gridline{
+        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
+    }
+\end{figure*}
+\begin{figure*}[p]
+    \gridline{
+        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
+    }
+    \caption{
+        This figure shows the measured fluxes (black points) of 11 sources plotted against the
+        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
+        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
+    }
+    \label{fig:flux-scale}
+\end{figure*}
+
+The flux scale of the data was anchored to the \citet{1977A&A....61...99B} spectrum of Cyg A during
+gain calibration. However, gain calibration is also a function of the beam model and the spectrum
+used for Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature
+and \citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
+with calibrated flux measurements from one (just Cyg A) to eleven in total. However while the
+\citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
+\citet{2017ApJS..230....7P} flux scale is somewhat more limited because the lowest frequency
+observations come from the VLA 4-band system. As a consequence the \citet{2017ApJS..230....7P} flux
+scale is not valid below 50 MHz.
+
+Figure~\ref{fig:flux-scale} shows a comparison between flux measurements made using the all-sky maps
+from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
+measurements agree to better than 10\% with the \citet{2012MNRAS.423L..30S} spectra. Below 50 MHz
+there can be substantial departures with respect to the \citet{2017ApJS..230....7P} spectra (for eg.
+3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
+\citet{2015A&A...582A.123H} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
+diverge from the truth rapidly below 50 MHz.
+
+\section{All-Sky Imaging}
 
@@
 
+\begin{figure}[t]
+    \plotone{figures/psf/spw04-psf-45-degrees}
+    \caption{
+        The computed PSF for the OVRO-LWA for a point source at a declination of $+45^\circ$ and
+        frequency of $36.528$ MHz.
+    }
+    \label{fig:psf}
+\end{figure}
+
 \begin{algorithm}
@@
 spherical harmonics describing a point source at the identified pixel.
-
-\section{Observations}
-
-\subsection{The Owens Valley Long Wavelength Array}
-
-\begin{figure}[t]
-    \plotone{figures/antenna-layout/antenna-layout}
-    \caption{
-        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
-        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
-        antennas equipped with noise-switched front ends.
-    }
-    \label{fig:antenna-layout}
-\end{figure}
-
-\begin{figure}[t]
-    \plotone{figures/psf/spw04-psf-45-degrees}
-    \caption{
-        The computed PSF for the OVRO-LWA for a point source at a declination of $+45^\circ$ and
-        frequency of $36.528$ MHz.
-    }
-    \label{fig:psf}
-\end{figure}
-
-The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory (OVRO) near Big Pine, California \citep{todo_hallinan_2017}.  The
-OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912
-MHz and 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
-there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
-correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
-hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
-are unused.
-
-The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
-snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
-placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
-final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
-of the global sky brightness.  These antennas are used as part of the LEDA experiment
-\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
-Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
-
-Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
-chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
-environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
-interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
-output evenly divides a sidereal day.
-
-The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
-$>-30$ nT during the entirety of the observing period.\footnote{
-    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
-    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}).
-}
-Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
-$\text{Dst} < -30$ nT. Therefore there were no geomagnetic storms during the time of these
-observations.
-
-\subsection{Gain Calibration}
-
-Antenna gain calibration is accomplished using an iterative method independently developed by
-\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
-the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
-online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
-
-The antenna complex gains are measured from a 7.2 hour track of data from when Cyg A and Cas are at
-high elevations. The gains measured in this way are then used to calibrate the entire 28 hour
-dataset. Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources
-in the northern hemisphere. Therefore the optimal time to solve for the interferometer's gain
-calibration is when these sources are at high elevations. \todo{cite some statistics on how good
-this calibration is? what do I quantify?}
-
-\todo{at the moment we calibrated with the Baars spectrum for Cas. we should actually iterate once
-and use the new spectrum that comes out of the beam fitting routine}
-
-The flux scale is tied to the work of \citet{1977A&A....61...99B, 2012MNRAS.423L..30S,
-2017ApJS..230....7P}.
-
-Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
-analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
-gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
-The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
-per-antenna amplitude correction that is then applied to the cross-correlations.
-
-\todo{tuesday}
-
-\subsection{Primary Beam Measurements}
-
-\begin{figure*}[ht]
-    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
-    \caption{
-        Example Stokes-I beam model (from spw04).
-    }
-    \label{fig:beam}
-\end{figure*}
-
-In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
-primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
-assume that the primary beam is invariant under north-south and east-west flips, and additionally
-that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
-These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
-antennas will contribute towards breaking these symmetries at some level. However some amount of
-symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
-when the flux of a source is unknown.
-
-We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
-3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
-those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
-$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
-zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of the fitted beam
-model.
-
-\subsection{Source Removal}
-
-\subsubsection{Cassiopeia A and Cygnus A}
-
-Without removing bright sources from the data, sidelobes from bright sources will dominate the
-variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2017ApJS..230....7P}. A
-conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
-\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
-from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
-\todo{Measure Cyg A's sidelobe levels if it is not subtracted}
-
-At low frequencies, propagation effects through the ionosphere must be accounted for in order to
-achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
-peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
-scintillation and diffraction events on the timescale of a single integration (13 seconds) are
-observed. Therefore the direction dependent calibration changes on these timescales and the we must
-solve for one set of complex gains per source per integration.
-
-The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
-is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
-sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
-source model to eachs ource. This is performed by minimizing the minimizing the variance within an
-aperture located on each source after peeling. By phasing up a large number of integrations before
-imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
-We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
-until the variance within the aperture is minimized.
-
-\todo{Show a before and after with the updated source models}
-
-\todo{Give a plot with the updated source models}
-
-\subsubsection{The Sun}
-
-The Sun can be trivially removed from any map of the sky by constructing the map using only data
-taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
-However the dataset used in this paper consists of 28 consecutive hours. Additionally while most
-astronomical sources at these frequencies have negative spectral indices, the Sun has a large
-positive spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
-frequencies than at lower frequencies.
-
-\todo{describe sun removal -- this isn't entirely settled yet}
 
@@
 
-\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
-that it is actually worse than the RFI, but I don't actually know for sure}
+%\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
+%that it is actually worse than the RFI, but I don't actually know for sure}
 
@@
 
-\todo{discuss the possibility of declination dependent flux-scale errors in these maps}
+%\todo{discuss the possibility of declination dependent flux-scale errors in these maps}
 
@@
 known and so beam model errors can lead to observations being combined with incorrect phase as well.
-This will lead to a degraded PSF in the final map. \todo{quick simulation of this?}
+This will lead to a degraded PSF in the final map.
+
+%\todo{quick simulation of this?}
 
@@
 
-This will tend to scatter power between $m$-modes. \todo{cite richard for this}
+This will tend to scatter power between $m$-modes \citep{richard_ionosphere_thoughts}.
 
@@
 
-\floattable
-\begin{deluxetable}{ccccc}
-    \tablecaption{Summary of the produced maps\label{tab:summary}}
-    \tablehead{
-        \colhead{\#} & \colhead{$\nu$ / MHz} & \colhead{$\Delta\nu$ / MHz} &
-        \colhead{$\theta$ / arcmin} & \colhead{noise / Jy}
+\begin{figure*}[p]
+    \gridline{
+        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
     }
-    \startdata
-        1 & 36.528 & 0.024 & & \\
-        2 & 41.760 & 0.024 & & \\
-        3 & 46.992 & 0.024 & & \\
-        4 & 52.224 & 0.024 & & \\
-        5 & 57.456 & 0.024 & & \\
-        6 & 62.688 & 0.024 & & \\
-        7 & 67.920 & 0.024 & & \\
-        8 & 73.152 & 0.024 & & \\
-    \enddata
-\end{deluxetable}
+    \gridline{
+        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \caption{
+        Beautiful chanel maps.
+    }
+    \label{fig:channel-maps}
+\end{figure*}
 

### 2017-07-26 figures/stripe-maps/make.jl
add a map of the rfi contamination in spw14

@@ -1,0 +1,41 @@
+using JLD, PyPlot, PyCall
+
+unshift!(PyVector(pyimport("sys")["path"]), "")
+@pyimport my_log_scale as mls
+
+path = dirname(@__FILE__)
+close("all")
+
+function plot(filename1, filename2)
+    img1, ν = load(joinpath(path, filename1*".jld"), "image", "frequency")
+    img2 = load(joinpath(path, filename2*".jld"), "image")
+    img = img1-img2
+
+    max = maximum(img)
+    min = minimum(img)
+    base = max - min
+    
+    figure(figsize=(12,8)); clf()
+    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+    imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
+           extent=(-2, 2, -1, 1),
+           clip_path=ellipse)
+    gca()[:set_aspect]("equal")
+    title(@sprintf("%.3f MHz", ν/1e6), fontsize=16)
+    cbar = colorbar(fraction=0.02)
+    cbar[:ax][:tick_params](labelsize=16)
+    axis("off")
+    tight_layout()
+
+    savefig(joinpath(path, filename1*".pdf"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
+end
+
+plot("spw14-glamour-shot-map-rfi-restored-peeled-rainy-2048-galactic",
+     "spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
+

### 2017-07-26 figures/stripe-maps/my_log_scale.py

@@ -1,0 +1,16 @@
+from pylab import *
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+
+class MyLogNormalize(colors.Normalize):
+    def __init__(self, vmin=None, vmax=None, base=None, clip=False):
+        self.base = base
+        colors.Normalize.__init__(self, vmin, vmax, clip)
+
+    def __call__(self, value, clip=None):
+        base = self.base
+        out = log10(value - self.vmin + base) - log10(base)
+        out = out / (log10(self.vmax - self.vmin + base) - log10(base))
+        return np.ma.masked_array(out)
+

### 2017-07-26 paper.tex
more wip

@@
 intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
-interstellar medium (ISM). As photons from the CMB propagate through the intervening material
+interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
 scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
@@
 at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
-7$ where a detection can constrain the ionizing efficiency of early galaxies, UV photon
+7$ where a detection can constrain the ionizing efficiency of early galaxies, the UV photon
 mean-free-path, and the minimum halo mass that can support star formation
@@
 after averaging over the entire sky, and power spectrum experiments that incorporate angular
-information to attempt to measure the spatial power spectrum of cosmological 21 cm perturbations.
+information to attempt to measure the 3D spatial power spectrum of cosmological 21 cm perturbations.
 Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
@@
 emission (after convolving with the instrumental response) is spectrally smooth. However the
-low-frequency radio sky is composed of several components: galactic synchrotron emission, free-free
-emission and absorption, supernova remnants, radio galaxies, and a confusing background of point
-sources.  Ideally a foreground removal strategy should be informed by the measured spatial and
-frequency structure of all foreground components. However, this possibility is limited by the
-availability of suitable high-fidelity low-frequency sky maps on angular scales ranging from tens of
-degrees to arcminutes.
+low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
+remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and radion
+emission from a confusing background of radio sources.  Ideally a foreground removal strategy should
+be informed by the measured spatial structure and frequency spectrum of all foreground components.
+However this possibility is limited by the availability of suitable high-fidelity low-frequency sky
+maps on angular scales ranging from tens of degrees to arcminutes.
 
@@
 interpolation of various maps between 10 MHz and 100 GHz. However the majority of information
-contained in the GSM is derived at higher frequencies where the majority of the input maps are from.
-Below 408 MHz, the interpolation is largely driven by the Haslam 408 MHz map
+contained in the GSM is derived at higher frequencies where the majority of the input maps are
+located.  Below 408 MHz, the interpolation is largely driven by the Haslam 408 MHz map
 \citep{1981A&A...100..209H, 1982A&AS...47....1H}.  At lower frequencies, free-free absorption and
@@
 \citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
-catalog of radio sources. Surveys that capture the diffuse emission include at 45 MHz, where
+catalog of radio point sources. Surveys that capture the diffuse emission include at 45 MHz, where
 \citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
@@
 
-\begin{deluxetable*}{ccccc}
+\begin{deluxetable}{cCCCC}
     \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
@@
     \tablehead{
-        \colhead{\#} & \colhead{$\nu$ / MHz} & \colhead{$\Delta\nu$ / MHz} &
-        \colhead{$\theta$ / arcmin} & \colhead{noise / Jy}
+        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} \\
+        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)}
     }
     \startdata
-        1 & 36.528 & 0.024 & & \\
-        2 & 41.760 & 0.024 & & \\
-        3 & 46.992 & 0.024 & & \\
-        4 & 52.224 & 0.024 & & \\
-        5 & 57.456 & 0.024 & & \\
-        6 & 62.688 & 0.024 & & \\
-        7 & 67.920 & 0.024 & & \\
-        8 & 73.152 & 0.024 & & \\
+        1 & 36.528 & 0.024 & 16.2 \\
+        2 & 41.760 & 0.024 & 14.7 \\
+        3 & 46.992 & 0.024 & 14.2 \\
+        4 & 52.224 & 0.024 & 13.6 \\
+        5 & 57.456 & 0.024 & 13.5 \\
+        6 & 62.688 & 0.024 & 13.5 \\
+        7 & 67.920 & 0.024 & 13.5 \\
+        8 & 73.152 & 0.024 & 13.7 \\
     \enddata
-\end{deluxetable*}
+\end{deluxetable}
 
 The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory (OVRO) near Big Pine, California \citep{todo_hallinan_2017}.  The
-OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912
-MHz and 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
-there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
-correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
-hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
-are unused.
+Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
+is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz with 24
+kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
+$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
+\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
+single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
 
@@
 snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
-placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
-final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
-of the global sky brightness.  These antennas are used as part of the LEDA experiment
+placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
+5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
+the global sky brightness.  These antennas are used as part of the LEDA experiment
 \citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
@@
 
-Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
-chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
-environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
-interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
-output evenly divides a sidereal day.
+The dataset used in this paper spans 28 consecutive hours beginning at 2017-02-17 12:00:00 UTC time.
+This time was chosen based on the fact that it was raining at OVRO and rain tends to improve the
+low-frequency RFI environment considerably. During this time the OVRO-LWA operated as a
+zenith-pointing drift scanning interferometer.  The correlator dump time was selected to be 13
+seconds such that the correlator output evenly divides a sidereal day.
 
@@
 
-The antenna complex gains are measured from a 22 minute track of data from when Cyg A and Cas are at
-high elevations. The gains measured in this way are then used to calibrate the entire 28 hour
-dataset. Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources
-in the northern hemisphere. Therefore the optimal time to solve for the interferometer's gain
-calibration is when these sources are at high elevations. The calibration sky model consists only of
-Cyg A and Cas A. The flux of Cyg A is anchored to the results of \citet{1977A&A....61...99B} while
+Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources in the
+northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
+is when these sources are at high elevations.  The antenna complex gains are measured from a 22
+minute track of data from when Cyg A and Cas are at high elevations. The gains measured in this way
+are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
+Cyg A and Cas A. The model flux of Cyg A is set to the \citet{1977A&A....61...99B} spectrum while
 the flux of Cas A is measured from the data itself (using a preliminary calibration).
@@
 In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
+known. Drift-scanning interferometers like the OVRO-LWA can empirically measure their
 primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
@@
 $Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
-zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of the fitted beam
-model.
+zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
+model at 36.528 MHz. This process is repeated for each frequency channel.
 
@@
 Without removing bright sources from the data, sidelobes from bright sources will dominate the
-variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2017ApJS..230....7P}. A
+variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{1977A&A....61...99B}. A
 conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
-\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
+\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at least $-45$ dB down
 from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
@@
 
-The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
-is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
+The largest angular scale of Cas A is $\sim$8 arcminutes, and the largest angular scale of Cyg A is
+$\sim$2 arcminutes. With a $\sim10$ arcminute resolution, the OVRO-LWA marginally resolves both
 sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
-source model to eachs ource. This is performed by minimizing the minimizing the variance within an
-aperture located on each source after peeling. By phasing up a large number of integrations before
-imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
-We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
-until the variance within the aperture is minimized.
+source model to each source. This is performed by minimizing the variance within an aperture located
+on each source after peeling. By phasing up a large number of integrations before imaging (at least
+1 hour) it is possible to smear out the contribution of the rest of the sky.  We then use NLopt's
+Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until the variance
+within the aperture is minimized.
 
@@
 
-However, the ionosphere will cause these sources to scintillate and refract. So first the position
-and flux of each source is measured separately in each channel and integration. Then the sources are
+However, the ionosphere will cause these sources to scintillate and refract. So the position and
+flux of each source is measured separately in each channel and integration. The sources are then
 subtracted from the visibilities using the updated position and flux of the source. The brightest of
@@
 suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
-sun is well-resolved by the OVRO-LWA and hence a somewhat detailed source model is needed. In fact
-the optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new
-model is needed for each of the 8 channel maps produced in this paper. So while we could fit a
-limited number of Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.
-Additionally while most astronomical sources at these frequencies have negative spectral indices,
-the Sun has a large positive spectral index. Therefore more care will need to be taken in
-subtracting the Sun at higher frequencies than at lower frequencies.
+sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
+optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new model is
+needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
+Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.  Additionally while most
+astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
+spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
+frequencies than at lower frequencies.
 
@@
     }
-\end{figure*}
-\begin{figure*}[p]
-    \gridline{
-        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
-    }
     \caption{
@@
 \end{figure*}
-
-The flux scale of the data was anchored to the \citet{1977A&A....61...99B} spectrum of Cyg A during
-gain calibration. However, gain calibration is also a function of the beam model and the spectrum
-used for Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature
-and \citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
-with calibrated flux measurements from one (just Cyg A) to eleven in total. However while the
+\begin{figure*}[p]
+    \addtocounter{figure}{-1}
+    \gridline{
+        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
+    }
+    \caption{(continued)}
+\end{figure*}
+
+The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg A during gain
+calibration. However gain calibration is also a function of the beam model and the spectrum used for
+Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature and
+\citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
+with calibrated flux measurements from one (just Cyg A) to eleven in total. While the
 \citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
@@
 3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
-\citet{2015A&A...582A.123H} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
+\citet{2012MNRAS.423L..30S} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
 diverge from the truth rapidly below 50 MHz.
@@
 direction $\hat r$ and frequency $\nu$. A radio interferometer measures the visibilities
-$V_{ij,\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
+$V^{ij}_{\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
 are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
@@
 
-Naively one might attempt to solve equation~\ref{eq:basic-imaging} by discretizing, and subsequently
+Naively one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing, and subsequently
 solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
@@
 floating point number).  This matrix equation is therefore prohibitively large, and solving
-equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
+Equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
 \citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.
 
-Instead it is common to make mild assumptions that simplify equation~\ref{eq:basic-imaging} and ease
+Instead it is common to make mild assumptions that simplify Equation~\ref{eq:basic-imaging} and ease
 the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
-$\vec b_{ij}$ lie in a plane and the field-of-view is small, equation~\ref{eq:basic-imaging} can be
+$\vec b_{ij}$ lie in a plane and the field-of-view is small, Equation~\ref{eq:basic-imaging} can be
 well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
@@
 On the other hand, transit telescopes can take advantage of a symmetry in
-equation~\ref{eq:basic-imaging} that greatly reduces the amount of computer time required to image
+Equation~\ref{eq:basic-imaging} that greatly reduces the amount of computer time required to image
 the full-sky with exact incorporation of widefield imaging effects. This technique, called $m$-mode
-analysis, also obviates the need for gridding, mosaicing, and multi-scale deconvolution. Instead the
-entire sky is imaged in one coherent synthesis imaging step.
+analysis, also obviates the need for gridding and mosaicing. Instead the entire sky is imaged in one
+coherent synthesis imaging step.
 
@@
 power of $m$-mode analysis is the block-diagonal structure of
-equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
+Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
 the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
@@
 Imaging in $m$-mode analysis essentially amounts to inverting
-equation~\ref{eq:m-mode-matrix-equation} to solve for the spherical harmonic coefficients $\b a$.
+Equation~\ref{eq:m-mode-matrix-equation} to solve for the spherical harmonic coefficients $\b a$.
 The linear-least squares solution, which minimizes $\|\b v - \b B\b a\|^2$, is given by
@@
 the southern hemisphere, there are infinitely many possible solutions to
-equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well. So we need to
+Equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well. So we need to
 regularize the problem and apply an additional constraint that prefers a unique solution. For
@@
     }
+    \gridline{
+        \fig{figures/stripe-maps/spw14-glamour-shot-map-rfi-restored-peeled-rainy-2048-galactic}
+            {\textwidth}{(e)}
+    }
     \caption{
@@
         component is not associated with a dot on the horizon.  Instead it is likely associated with
-        common-mode pickup in the analog signal chain.
+        common-mode pickup in the analog signal chain. \textbf{(e)} The resulting contamination in
+        the full-sky maps from the horizon RFI and common-mode pickup. Note that because these
+        contaminating components are not moving sidereally, they tend to generate stripes along
+        lines of constant declination. The color scale is in units of Kelvin.
     }
@@
 
-When writing down equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated
+When writing down Equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated
 voltage fluctuations measured between pairs of antennas are exclusively generated by astronomical
@@
 
-The first step in equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step we
+The first step in Equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step we
 compute the projection of the measurement $\b v$ onto the space spanned by the columns of $\b B$.
@@
 \lesssim 3$. As a result if the contamination is not suppressed, it will manifest itself as rings
-along stripes of constant declination. This effect is plainly visible in Figure \todo{make it}.
+along stripes of constant declination. This effect is plainly visible in Figure~\ref{fig:fitrfi}.
 
@@
 
-\todo{describe how the Wiener filter works}
+%\todo{describe how the Wiener filter works}
 
@@
 a discrete Fourier transform of the observed correlation with respect to time (where the sum over
-time is restricted to a sidereal day). \todo{fix normalization}
+time is restricted to a sidereal day).
 \begin{equation}
@@
 \begin{equation}
-    V_{\nu, m} = \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}.
-\end{equation}
-
+    V_{\nu, m} \propto \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}.
+\end{equation}
 This will tend to scatter power between $m$-modes \citep{richard_ionosphere_thoughts}.
 
-\todo{Simulate images of point sources with this}
-
-\todo{I think the conclusion is sort of exactly what you would expect: refraction broadens the PSF
-while scintillation effects the flux scale, but honestly not by much because we have such large
-averages that unless the scintillation is Cauchy distributed it is not that bad..}
-
-\subsection{Thermal Noise}
-
-\todo{describe jack-knife tests}
+%\todo{Simulate images of point sources with this}
+%
+%\todo{I think the conclusion is sort of exactly what you would expect: refraction broadens the PSF
+%while scintillation effects the flux scale, but honestly not by much because we have such large
+%averages that unless the scintillation is Cauchy distributed it is not that bad..}
+
+%\subsection{Thermal Noise}
+%
+%\todo{describe jack-knife tests}
 
@@
 
-\subsection{Sky Maps}
+%\subsection{Sky Maps}
 
@@
     \caption{
-        Beautiful chanel maps.
+        Maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA and $m$-mode analysis
+        imaging. The properties of each map are summarized in Table~\ref{tab:summary}. The color
+        scale is logarithmic and has units of Kelvin. As described in the text, 8 bright sources
+        have been subtracted. The small blank region near the bottom of each map corresponds to the
+        region of sky within 2 degrees of the Sun at the time of the observations.
     }
@@
 
-\subsection{Error Maps}
+%\subsection{Error Maps}
 

### 2017-07-27 figures/guzman/make.jl
add guzman comparison figure

@@ -1,0 +1,25 @@
+using JLD, PyPlot
+
+path = dirname(@__FILE__)
+#close("all")
+
+guzman, lwa = load(joinpath(path, "comparison-with-guzman.jld"), "guzman", "lwa")
+
+figure(1); clf()
+θ = linspace(0, 2π, 512)
+x = 2cos.(θ)
+y = sin.(θ)
+ellipse = plt[:Polygon]([x y], alpha=0)
+gca()[:add_patch](ellipse)
+imshow((lwa-guzman)./guzman, interpolation="nearest", cmap=get_cmap("RdBu_r"),
+       vmin=-0.5, vmax=+0.5,
+       extent=(-2, 2, -1, 1), clip_path=ellipse)
+gca()[:set_aspect]("equal")
+axis("off")
+cbar = colorbar(fraction=0.02)
+cbar[:ax][:tick_params](labelsize=16)
+tight_layout()
+
+savefig(joinpath(path, "guzman-comparison.pdf"),
+        bbox_inches="tight", pad_inches=0, transparent=true)
+

### 2017-07-27 figures/haslam/make.jl
add haslm spectral index map

@@ -1,0 +1,25 @@
+using JLD, PyPlot
+
+path = dirname(@__FILE__)
+close("all")
+
+spectral_index = load(joinpath(path, "comparison-with-haslam.jld"), "index")
+
+figure(1); clf()
+θ = linspace(0, 2π, 512)
+x = 2cos.(θ)
+y = sin.(θ)
+ellipse = plt[:Polygon]([x y], alpha=0)
+gca()[:add_patch](ellipse)
+imshow(spectral_index, interpolation="nearest", cmap=get_cmap("RdBu"),
+       vmin=-2.8, vmax=-2.2,
+       extent=(-2, 2, -1, 1), clip_path=ellipse)
+gca()[:set_aspect]("equal")
+axis("off")
+cbar = colorbar(fraction=0.02)
+cbar[:ax][:tick_params](labelsize=16)
+tight_layout()
+
+savefig(joinpath(path, "haslam-spectral-index.pdf"),
+        bbox_inches="tight", pad_inches=0, transparent=true)
+

### 2017-07-27 paper.tex
wrap up first extremely rough draft
still some missing sections :(

@@
 
+\newcommand{\astrocaltech}{
+    \affiliation{
+        Department of Astronomy,
+        California Institute of Technology,
+        1200 E California Blvd,
+        Pasadena, CA 91125
+    }
+}
+
 \begin{document}
 
-\title{The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array}
+\title{
+    The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
+    with the Owens Valley Long Wavelength Array
+}
 
 \author{Michael W. Eastwood}
-\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
-
-\author{Marin M. Anderson}
-\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
-
-\author{Ryan Monroe}
-\affiliation{Department of Electrical Engineering, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+\astrocaltech
+
+%\author{Marin M. Anderson}
+%\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+%
+%\author{Ryan Monroe}
+%\affiliation{Department of Electrical Engineering, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
 
 \author{Gregg Hallinan}
-\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
-
-\author{Lincoln Greenhill}
-\affiliation{Harvard}
-
-\author{Hugh Garsden}
-\affiliation{Harvard}
-
-\author{Stephen Bourke}
-\affiliation{Chalmers}
-
-\author{Esayas B. Shume} % contributed ionosphere text
-\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}
+\astrocaltech
+
+%\author{Lincoln Greenhill}
+%\affiliation{Harvard}
+%
+%\author{Hugh Garsden}
+%\affiliation{Harvard}
+%
+%\author{Stephen Bourke}
+%\affiliation{Chalmers}
+%
+%\author{Esayas B. Shume} % contributed ionosphere text
+%\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}
 
@@
     I present all-sky maps of the sky from the Owens Valley Long Wavelength Array.
-    These maps are created from the application of $m$-mode analysis. \todo{Wednesday}
+    These maps are created from the application of $m$-mode analysis.
 \end{abstract}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 
-\section{Observations}
-
-\begin{figure*}[ht]
-    \plotone{maps/2017-04-20-rgb-map-smaller}
-    \caption{
-        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
-        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
-        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
-        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
-        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
-        emission is synchrotron, but the blue regions mottling the galactic plane are due to
-        free-free absorption from \ion{H}{2} regions.
-    }
-    \label{fig:rgb}
-\end{figure*}
-
-\subsection{The Owens Valley Long Wavelength Array}
-
-\begin{figure}[t]
-    \plotone{figures/antenna-layout/antenna-layout}
-    \caption{
-        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
-        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
-        antennas equipped with noise-switched front ends.
-    }
-    \label{fig:antenna-layout}
-\end{figure}
-
-\begin{deluxetable}{cCCCC}
-    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
-    \tablewidth{0pt}
-    \tablehead{
-        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} \\
-        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)}
-    }
-    \startdata
-        1 & 36.528 & 0.024 & 16.2 \\
-        2 & 41.760 & 0.024 & 14.7 \\
-        3 & 46.992 & 0.024 & 14.2 \\
-        4 & 52.224 & 0.024 & 13.6 \\
-        5 & 57.456 & 0.024 & 13.5 \\
-        6 & 62.688 & 0.024 & 13.5 \\
-        7 & 67.920 & 0.024 & 13.5 \\
-        8 & 73.152 & 0.024 & 13.7 \\
-    \enddata
-\end{deluxetable}
-
-The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
-is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz with 24
-kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
-$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
-\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
-single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
-
-The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
-snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
-placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
-5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
-the global sky brightness.  These antennas are used as part of the LEDA experiment
-\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
-Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
-
-The dataset used in this paper spans 28 consecutive hours beginning at 2017-02-17 12:00:00 UTC time.
-This time was chosen based on the fact that it was raining at OVRO and rain tends to improve the
-low-frequency RFI environment considerably. During this time the OVRO-LWA operated as a
-zenith-pointing drift scanning interferometer.  The correlator dump time was selected to be 13
-seconds such that the correlator output evenly divides a sidereal day.
-
-The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
-$>-30$ nT during the entirety of the observing period.\footnote{
-    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
-    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}).
-}
-Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
-$\text{Dst} < -30$ nT. Therefore there were no geomagnetic storms during the time of these
-observations.
-
-Antenna gain calibration is accomplished using an iterative method independently developed by
-\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
-the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
-online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
-
-Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources in the
-northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
-is when these sources are at high elevations.  The antenna complex gains are measured from a 22
-minute track of data from when Cyg A and Cas are at high elevations. The gains measured in this way
-are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
-Cyg A and Cas A. The model flux of Cyg A is set to the \citet{1977A&A....61...99B} spectrum while
-the flux of Cas A is measured from the data itself (using a preliminary calibration).
-
-Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
-analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
-gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
-The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
-per-antenna amplitude correction that is then applied to the cross-correlations.
-
-\subsection{Primary Beam Measurements}
-
-\begin{figure*}[ht]
-    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
-    \caption{
-        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
-        OVRO-LWA.
-        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
-        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
-    }
-    \label{fig:beam}
-\end{figure*}
-
-In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Drift-scanning interferometers like the OVRO-LWA can empirically measure their
-primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
-assume that the primary beam is invariant under north-south and east-west flips, and additionally
-that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
-These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
-antennas will contribute towards breaking these symmetries at some level. However some amount of
-symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
-when the flux of a source is unknown.
-
-We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
-3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
-those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
-$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
-zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
-model at 36.528 MHz. This process is repeated for each frequency channel.
-
-\subsection{Source Removal}
-
-\subsubsection{Cygnus A and Cassiopeia A}
-
-%\begin{deluxetable*}{ccccDCCD}
-%    \tablecaption{Resolved source models for Cyg A and Cas A\label{tab:resolved-source-models}}
-%    \tablewidth{0pt}
-%    \tablehead{
-%        \colhead{} & \colhead{} &
-%            \colhead{} & \colhead{} &
-%            \multicolumn2c{Amplitude} &
-%            \colhead{Major FWHM} & \colhead{Minor FWHM} &
-%            \multicolumn2c{Position angle} \\
-%        \colhead{Source} & \colhead{\#} &
-%            \colhead{RA} & \colhead{Dec} &
-%            \multicolumn2c{(relative)} &
-%            \colhead{(arcsec)} & \colhead{(arcsec)} &
-%            \multicolumn2c{(deg)}
-%    }
-%    \decimals
-%    \startdata
-%        Cyg A & 1 & & & 1.0 & 128. & 22. & -74.503 \\
-%              & 2 & & & 0.1477 & 183. & 141. & 43.449 \\[0.2cm]
-%        Cas A & 1 & & & 1.0 & 0. & 0. & 0. \\
-%              & 2 & & & 1.0 & 0. & 0. & 0. \\
-%              & 3 & & & 1.0 & 0. & 0. & 0. \\
-%    \enddata
-%\end{deluxetable*}
-
-Without removing bright sources from the data, sidelobes from bright sources will dominate the
-variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{1977A&A....61...99B}. A
-conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
-\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at least $-45$ dB down
-from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
-
-At low frequencies, propagation effects through the ionosphere must be accounted for in order to
-achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
-peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
-scintillation and diffraction events on the timescale of a single integration (13 seconds) are
-observed. Therefore the direction dependent calibration changes on these timescales and the we must
-solve for one set of complex gains per source per integration.
-
-The largest angular scale of Cas A is $\sim$8 arcminutes, and the largest angular scale of Cyg A is
-$\sim$2 arcminutes. With a $\sim10$ arcminute resolution, the OVRO-LWA marginally resolves both
-sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
-source model to each source. This is performed by minimizing the variance within an aperture located
-on each source after peeling. By phasing up a large number of integrations before imaging (at least
-1 hour) it is possible to smear out the contribution of the rest of the sky.  We then use NLopt's
-Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until the variance
-within the aperture is minimized.
-
-Armed with resolved source models for both Cyg A and Cas A, these two sources can be peeled from the
-dataset to the required dynamic range.
-
-%\todo{slice through Cyg A and Cas A to illustrate the removal process}
-%\todo{Give a plot with the updated source models}
-
-\subsubsection{Other Bright Sources}
-
-Other bright sources including Vir A, Tau A, Her A, Hya A, Per B, and 3C 353 are also removed from
-the visibilities prior to imaging. Because these sources are much fainter than Cyg A and Cas A, we
-do not need resolved source models to be able to remove these sources from the visibilities without
-residual sidelobes contaminating the image.
-
-However, the ionosphere will cause these sources to scintillate and refract. So the position and
-flux of each source is measured separately in each channel and integration. The sources are then
-subtracted from the visibilities using the updated position and flux of the source. The brightest of
-these sources (Vir A and Tau A) will be peeled using a direction dependent calibration when they are
-at high elevations.
-
-\subsubsection{The Sun}
-
-The sun can be trivially removed from any map of the sky by constructing the map using only data
-taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
-However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
-suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
-sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
-optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new model is
-needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
-Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.  Additionally while most
-astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
-spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
-frequencies than at lower frequencies.
-
-The strategy used for removing the Sun below 55 MHz involves fitting a shapelet
-\citep{2003MNRAS.338...35R} model to the Sun and subtracting without the use of direction dependent
-gains. The shapelet fitting is performed in the visibility space. Above 55 MHz a model is fit to the
-Sun by minimizing the residuals after peeling (in the same way that models are obtained for Cyg A
-and Cas A). The Sun is then peeled from each integration using direction dependent gains.
-
-\subsection{Flux Scale}
-
-\begin{figure*}[p]
-    \gridline{
-        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
-    }
-    \caption{
-        This figure shows the measured fluxes (black points) of 11 sources plotted against the
-        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
-        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
-    }
-    \label{fig:flux-scale}
-\end{figure*}
-\begin{figure*}[p]
-    \addtocounter{figure}{-1}
-    \gridline{
-        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
-    }
-    \caption{(continued)}
-\end{figure*}
-
-The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg A during gain
-calibration. However gain calibration is also a function of the beam model and the spectrum used for
-Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature and
-\citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
-with calibrated flux measurements from one (just Cyg A) to eleven in total. While the
-\citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
-\citet{2017ApJS..230....7P} flux scale is somewhat more limited because the lowest frequency
-observations come from the VLA 4-band system. As a consequence the \citet{2017ApJS..230....7P} flux
-scale is not valid below 50 MHz.
-
-Figure~\ref{fig:flux-scale} shows a comparison between flux measurements made using the all-sky maps
-from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
-measurements agree to better than 10\% with the \citet{2012MNRAS.423L..30S} spectra. Below 50 MHz
-there can be substantial departures with respect to the \citet{2017ApJS..230....7P} spectra (for eg.
-3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
-\citet{2012MNRAS.423L..30S} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
-diverge from the truth rapidly below 50 MHz.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{All-Sky Imaging}
@@
 
-\subsection{$m$-Mode Analysis Image Deconvolution}
+\subsection{CLEAN}
 
@@
 
-\begin{figure}[t]
-    \plotone{figures/psf/spw04-psf-45-degrees}
-    \caption{
-        The computed PSF for the OVRO-LWA for a point source at a declination of $+45^\circ$ and
-        frequency of $36.528$ MHz.
-    }
-    \label{fig:psf}
-\end{figure}
-
 \begin{algorithm}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Observations}
+
+\subsection{The Owens Valley Long Wavelength Array}
+
+\begin{figure}[ht]
+    \plotone{figures/antenna-layout/antenna-layout}
+    \caption{
+        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
+        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
+        antennas equipped with noise-switched front ends.
+    }
+    \label{fig:antenna-layout}
+\end{figure}
+
+\begin{figure}[ht]
+    \plotone{figures/psf/spw04-psf-45-degrees}
+    \caption{
+        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
+        declination of $+45^\circ$ and frequency of $36.528$ MHz.
+    }
+    \label{fig:psf}
+\end{figure}
+
+The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
+Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
+is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz with 24
+kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
+$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
+\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
+single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
+
+The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
+snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
+placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
+5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
+the global sky brightness.  These antennas are used as part of the LEDA experiment
+\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
+Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
+
+\subsection{The Rainy Day Dataset}
+
+The dataset used in this paper spans 28 consecutive hours beginning at 2017-02-17 12:00:00 UTC time.
+This time was chosen based on the fact that it was raining at OVRO and rain tends to improve the
+low-frequency RFI environment considerably. During this time the OVRO-LWA operated as a
+zenith-pointing drift scanning interferometer.  The correlator dump time was selected to be 13
+seconds such that the correlator output evenly divides a sidereal day.
+
+The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
+$>-30$ nT during the entirety of the observing period.\footnote{
+    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
+    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}).
+}
+Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
+$\text{Dst} < -30$ nT. Therefore there were no geomagnetic storms during the time of these
+observations.
+
+\subsection{Gain Calibration}
+
+Antenna gain calibration is accomplished using an iterative method independently developed by
+\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
+the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
+online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
+
+Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources in the
+northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
+is when these sources are at high elevations.  The antenna complex gains are measured from a 22
+minute track of data from when Cyg A and Cas are at high elevations. The gains measured in this way
+are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
+Cyg A and Cas A. The model flux of Cyg A is set to the \citet{1977A&A....61...99B} spectrum while
+the flux of Cas A is measured from the data itself (using a preliminary calibration).
+
+Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
+analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
+gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
+The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
+per-antenna amplitude correction that is then applied to the cross-correlations.
+
+\subsection{Primary Beam Measurements}
+
+\begin{figure*}[ht]
+    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
+    \caption{
+        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
+        OVRO-LWA.
+        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
+        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
+    }
+    \label{fig:beam}
+\end{figure*}
+
+In order to generate wide-field images of the sky, the response of the antenna to the sky must be
+known. Drift-scanning interferometers like the OVRO-LWA can empirically measure their
+primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
+assume that the primary beam is invariant under north-south and east-west flips, and additionally
+that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
+These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
+antennas will contribute towards breaking these symmetries at some level. However some amount of
+symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
+when the flux of a source is unknown.
+
+We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
+3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
+those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
+$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
+zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
+model at 36.528 MHz. This process is repeated for each frequency channel.
+
+\subsection{Source Removal}
+
+\subsubsection{Cygnus A and Cassiopeia A}
+
+%\begin{deluxetable*}{ccccDCCD}
+%    \tablecaption{Resolved source models for Cyg A and Cas A\label{tab:resolved-source-models}}
+%    \tablewidth{0pt}
+%    \tablehead{
+%        \colhead{} & \colhead{} &
+%            \colhead{} & \colhead{} &
+%            \multicolumn2c{Amplitude} &
+%            \colhead{Major FWHM} & \colhead{Minor FWHM} &
+%            \multicolumn2c{Position angle} \\
+%        \colhead{Source} & \colhead{\#} &
+%            \colhead{RA} & \colhead{Dec} &
+%            \multicolumn2c{(relative)} &
+%            \colhead{(arcsec)} & \colhead{(arcsec)} &
+%            \multicolumn2c{(deg)}
+%    }
+%    \decimals
+%    \startdata
+%        Cyg A & 1 & & & 1.0 & 128. & 22. & -74.503 \\
+%              & 2 & & & 0.1477 & 183. & 141. & 43.449 \\[0.2cm]
+%        Cas A & 1 & & & 1.0 & 0. & 0. & 0. \\
+%              & 2 & & & 1.0 & 0. & 0. & 0. \\
+%              & 3 & & & 1.0 & 0. & 0. & 0. \\
+%    \enddata
+%\end{deluxetable*}
+
+Without removing bright sources from the data, sidelobes from bright sources will dominate the
+variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{1977A&A....61...99B}. A
+conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
+\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at least $-45$ dB down
+from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
+
+At low frequencies, propagation effects through the ionosphere must be accounted for in order to
+achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
+peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
+scintillation and diffraction events on the timescale of a single integration (13 seconds) are
+observed. Therefore the direction dependent calibration changes on these timescales and the we must
+solve for one set of complex gains per source per integration.
+
+The largest angular scale of Cas A is $\sim$8 arcminutes, and the largest angular scale of Cyg A is
+$\sim$2 arcminutes. With a $\sim10$ arcminute resolution, the OVRO-LWA marginally resolves both
+sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
+source model to each source. This is performed by minimizing the variance within an aperture located
+on each source after peeling. By phasing up a large number of integrations before imaging (at least
+1 hour) it is possible to smear out the contribution of the rest of the sky.  We then use NLopt's
+Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until the variance
+within the aperture is minimized.
+
+Armed with resolved source models for both Cyg A and Cas A, these two sources can be peeled from the
+dataset to the required dynamic range.
+
+%\todo{slice through Cyg A and Cas A to illustrate the removal process}
+%\todo{Give a plot with the updated source models}
+
+\subsubsection{Other Bright Sources}
+
+Other bright sources including Vir A, Tau A, Her A, Hya A, Per B, and 3C 353 are also removed from
+the visibilities prior to imaging. Because these sources are much fainter than Cyg A and Cas A, we
+do not need resolved source models to be able to remove these sources from the visibilities without
+residual sidelobes contaminating the image.
+
+However, the ionosphere will cause these sources to scintillate and refract. So the position and
+flux of each source is measured separately in each channel and integration. The sources are then
+subtracted from the visibilities using the updated position and flux of the source. The brightest of
+these sources (Vir A and Tau A) will be peeled using a direction dependent calibration when they are
+at high elevations.
+
+\subsubsection{The Sun}
+
+The sun can be trivially removed from any map of the sky by constructing the map using only data
+taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
+However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
+suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
+sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
+optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new model is
+needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
+Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.  Additionally while most
+astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
+spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
+frequencies than at lower frequencies.
+
+The strategy used for removing the Sun below 55 MHz involves fitting a shapelet
+\citep{2003MNRAS.338...35R} model to the Sun and subtracting without the use of direction dependent
+gains. The shapelet fitting is performed in the visibility space. Above 55 MHz a model is fit to the
+Sun by minimizing the residuals after peeling (in the same way that models are obtained for Cyg A
+and Cas A). The Sun is then peeled from each integration using direction dependent gains.
+
+\subsection{Flux Scale}
+
+\begin{figure*}[p]
+    \gridline{
+        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
+        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
+    }
+    \caption{
+        This figure shows the measured fluxes (black points) of 11 sources plotted against the
+        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
+        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
+    }
+    \label{fig:flux-scale}
+\end{figure*}
+
+The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg A during gain
+calibration. However gain calibration is also a function of the beam model and the spectrum used for
+Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature and
+\citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
+with calibrated flux measurements from one (just Cyg A) to eleven in total. While the
+\citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
+\citet{2017ApJS..230....7P} flux scale is somewhat more limited because the lowest frequency
+observations come from the VLA 4-band system. As a consequence the \citet{2017ApJS..230....7P} flux
+scale is not valid below 50 MHz.
+
+Figure~\ref{fig:flux-scale} shows a comparison between flux measurements made using the all-sky maps
+from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
+measurements agree to better than 10\% with the \citet{2012MNRAS.423L..30S} spectra. Below 50 MHz
+there can be substantial departures with respect to the \citet{2017ApJS..230....7P} spectra (for eg.
+3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
+\citet{2012MNRAS.423L..30S} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
+diverge from the truth rapidly below 50 MHz.
+
+%\subsection{Dedistortion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
+\begin{deluxetable*}{CCCCCC}
+    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
+    \tablewidth{0pt}
+    \tablehead{
+        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} &
+            \colhead{Noise} & \colhead{Noise} \\
+        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)} &
+            \colhead{(K)} & \colhead{(Jy)}
+    }
+    \startdata
+    1 & 36.528 & 0.024 & 16.2 & 372.8 \\
+    2 & 41.760 & 0.024 & 14.7 & 321.2 \\
+    3 & 46.992 & 0.024 & 14.2 & 247.0 \\
+    4 & 52.224 & 0.024 & 13.6 & 205.7 \\
+    5 & 57.456 & 0.024 & 13.5 & 167.7 \\
+    6 & 62.688 & 0.024 & 13.5 & 137.6 \\
+    7 & 67.920 & 0.024 & 13.5 & 114.9 \\
+    8 & 73.152 & 0.024 & 13.7 &  93.4 \\
+    \enddata
+\end{deluxetable*}
+
+\begin{figure*}[ht]
+    \plotone{maps/2017-04-20-rgb-map-smaller}
+    \caption{
+        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
+        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
+        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
+        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
+        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
+        emission is synchrotron, but the blue regions mottling the galactic plane are due to
+        free-free absorption from \ion{H}{2} regions.
+    }
+    \label{fig:rgb}
+\end{figure*}
+
+\begin{figure*}[p]
+    \gridline{
+        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
+            {0.48\textwidth}{}
+    }
+    \caption{
+        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
+        and $m$-mode analysis imaging. The properties of each map are summarized in
+        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
+        described in the text, 8 bright sources have been subtracted. The small blank region near
+        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
+        time of the observations.
+    }
+    \label{fig:channel-maps}
+\end{figure*}
+
+\begin{figure*}[p]
+    \gridline{
+        \fig{figures/jackknife-maps/4.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/jackknife-maps/6.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/jackknife-maps/8.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/jackknife-maps/10.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/jackknife-maps/12.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/jackknife-maps/14.pdf}
+            {0.48\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/jackknife-maps/16.pdf}
+            {0.48\textwidth}{}
+        \fig{figures/jackknife-maps/18.pdf}
+            {0.48\textwidth}{}
+    }
+    \caption{
+        The jackknife estimated standard deviation corresponding to the maps presented in
+        Figure~\ref{fig:channel-maps}. The color scale is logarithmic and has units of Kelvin.
+    }
+    \label{fig:jackknife-maps}
+\end{figure*}
+
+Eight sky maps are presented in Figure~\ref{fig:channel-maps}. Their properties are briefly
+summarized in Table~\ref{tab:summary}. In this section we will describe the new imaging technique
+used to generate these maps.
+
+%\todo{text}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Error Analysis}
 
+\subsection{Jackknife Resampling}
+
+%\todo{text}
+
 \subsection{Terrestrial Interference and Pickup}
 
-\begin{figure*}[ht]
+\begin{figure*}[p]
     \gridline{
@@
 
-\section{Results}
-
 %\subsection{Sky Maps}
 
-\begin{figure*}[p]
-    \gridline{
-        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
+%\subsection{Error Maps}
+
+%\citet{todo_mishra_2017}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Comparisons with Other Sky Maps}
+
+%\subsection{The Global Sky Model}
+%
+%The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z}
+
+\subsection{Haslam 408 MHz Map}
+
+\begin{figure}[t]
+    \plotone{figures/haslam/haslam-spectral-index}
     \caption{
-        Maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA and $m$-mode analysis
-        imaging. The properties of each map are summarized in Table~\ref{tab:summary}. The color
-        scale is logarithmic and has units of Kelvin. As described in the text, 8 bright sources
-        have been subtracted. The small blank region near the bottom of each map corresponds to the
-        region of sky within 2 degrees of the Sun at the time of the observations.
-    }
-    \label{fig:channel-maps}
-\end{figure*}
-
-%\subsection{Error Maps}
-
-\section{Discussion}
-
-\citet{todo_mishra_2017}
-
-\todo{Wednesday}
+        The spectral index between the reprocessed Haslam 408 MHz map and the OVRO-LWA maps
+        (degraded to 56 arcmin resolution).  The larger blue patch around the south celestial pole
+        corresponds to where the OVRO-LWA map has a blank region.
+    }
+    \label{fig:haslam-spectral-index}
+\end{figure}
+
+The Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H} was reprocessed by
+\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources. In
+order to compare the OVRO-LWA maps with the lower resolution Haslam map, the OVRO-LWA maps were
+degraded to 56 arcmin resolution. A spectral index map computed between the OVRO-LWA maps and the
+Haslam map is shown in Figure~\ref{fig:haslam-spectral-index}.
+
+\subsection{Guzm\'{a}n 45 MHz Map}
+
+\begin{figure}[t]
+    \plotone{figures/guzman/guzman-comparison}
+    \caption{
+        This Mollweide projection map compares the fractional difference between the Guzm\'{a}n 45
+        MHz map, and the OVRO-LWA map at 46.992 MHz (degraded to $5^\circ$ resolution). A positive
+        value indicates regions where the OVRO-LWA map has more emission that the Guzm\'{a}n map,
+        and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
+        OVRO-LWA map. The red patch around the north celestial pole corresponds to where the
+        Guzm\'{a}n map has a blank region.  The larger blue patch around the south celestial pole
+        corresponds to where the OVRO-LWA map has a blank region. Note also that the OVRO-LWA map
+        has several bright point sources subtracted that are not subtracted from the Guzm\'{a}n map.
+    }
+    \label{fig:guzman-comparison}
+\end{figure}
+
+A direct comparison between the OVRO-LWA at 46.992 MHz and the Guzm\'{a}n 45 MHz map
+\citep{2011A&A...525A.138G} can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this
+comparison the OVRO-LWA map was degraded to a 5$^\circ$ resolution by convolving with a Gaussian
+kernel.  This figure shows that the majority of the galactic synchrotron emission is consistent
+between the two maps to better than 5\% however there are patches (particularly near the north
+celestial pole) where there is a discrepancy on the order of 20\%.  Off of the galactic plane, the
+OVRO-LWA map underestimates the flux compared to the Guzm\'{a}n map by a factor of 20\%. This can be
+attributed to the absence of zero-spacing data.
+
+%\subsection{LWA1 Sky Survey}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+
+%\todo{text}
 

### 2017-07-27 figures/flux-scale/make.jl

@@ -23,7 +23,7 @@ for (idx, name) in enumerate(names)
         measured = measured_fluxes[name]
     end
 
-    figure(idx); clf()
+    figure(idx, figsize=(6, 3)); clf()
     gca()[:tick_params](axis="both", which="major", labelsize=16)
 
     plot(frequencies/1e6, measured, "ko")

### 2017-07-27 figures/guzman/make.jl

@@ -1,7 +1,7 @@
 using JLD, PyPlot
 
 path = dirname(@__FILE__)
-#close("all")
+close("all")
 
 guzman, lwa = load(joinpath(path, "comparison-with-guzman.jld"), "guzman", "lwa")
 

### 2017-07-27 figures/jackknife-maps/make.jl

@@ -1,0 +1,66 @@
+using LibHealpix, PyPlot, PyCall
+
+unshift!(PyVector(pyimport("sys")["path"]), "")
+@pyimport my_log_scale as mls
+
+path = dirname(@__FILE__)
+close("all")
+
+const c = 2.99792e8 # m/s
+const k = 1.38065e-23 # J/K
+const Jy = 1e-26 # one Jansky in mks units
+
+# Jackknife variance estimator
+# https://en.wikipedia.org/wiki/Jackknife_resampling#Variance_estimation
+
+function plot(combined, odd, even, ν)
+    combined_map = readhealpix(joinpath(path, combined))
+    odd_map  = readhealpix(joinpath(path, odd))
+    even_map = readhealpix(joinpath(path, even))
+
+    λ = c/ν
+    factor = Jy*λ^2/(2k)
+    combined_map = combined_map .* factor
+    odd_map  =  odd_map .* factor
+    even_map = even_map .* factor
+
+    variance = 0.5 .* ((odd_map - combined_map).^2 .+ (even_map .- combined_map).^2)
+    standard_deviation = sqrt.(variance)
+    @show median(standard_deviation)
+
+    img = mollweide(standard_deviation)
+    max = maximum(img)/10
+    min = minimum(img)
+    base = max - min
+
+    figure(); clf()
+    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+    imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
+           norm = mls.MyLogNormalize(min, max, base),
+           extent=(-2, 2, -1, 1),
+           clip_path=ellipse)
+    gca()[:set_aspect]("equal")
+    title(@sprintf("%.3f MHz", ν/1e6), fontsize=16)
+    axis("off")
+    cbar = colorbar(fraction=0.02)
+    cbar[:ax][:tick_params](labelsize=16)
+    tight_layout()
+
+    savefig(joinpath(path, replace(combined, ".fits", ".pdf")),
+            bbox_inches="tight", pad_inches=0, transparent=true)
+end
+
[…]

### 2017-07-27 paper.tex
improve the flux-scale figure so that plots aren't falling off the page

@@
 \begin{figure*}[p]
-    \gridline{
-        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
-        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
-    }
+    \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
     \caption{
         This figure shows the measured fluxes (black points) of 11 sources plotted against the
-        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
-        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
+        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
+        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
+        (dot-dash line).
     }

### 2017-07-27 figures/flux-scale/make.jl

@@ -1,18 +1,25 @@
+#!/usr/bin/env julia
+
 using JLD, PyPlot
 using CasaCore.Measures
 
 path = dirname(@__FILE__)
 close("all")
 
-frequencies = [3.6528e7,4.176e7,4.6992e7,5.2224e7,5.7456e7,6.2688e7,6.792e7,7.3152e7]
+frequencies = [3.6528e7, 4.176e7, 4.6992e7, 5.2224e7, 5.7456e7, 6.2688e7, 6.792e7, 7.3152e7]
 exceptions = ("Cyg A", "Vir A", "Hya A", "Per B", "3C 353")
+cutoff = frequencies .> 50e6 # Perley fluxes only valid above 50 MHz
 
 calibrators, measured_fluxes, perley_fluxes, scaife_fluxes, baars_fluxes =
     load(joinpath(path, "source-fluxes-map-wiener-filtered.jld"),
          "calibrators", "measured_fluxes", "perley_fluxes", "scaife_fluxes", "baars_fluxes")
 
-names = collect(keys(calibrators))
+# manually spell this out so that we can pick the order of the plots
+#names = collect(keys(calibrators))
+names = ("Cyg A", "Hya A", "Lyn A", "Per B", "Vir A", "3C 48", "3C 147", "3C 286", "3C 295",
+         "3C 353", "3C 380")
 
+figure(1, figsize=(10, 10)); clf()
 for (idx, name) in enumerate(names)
     direction = calibrators[name]
     lower = lowercase(replace(name, " ", ""))
@@ -23,32 +30,40 @@ for (idx, name) in enumerate(names)
         measured = measured_fluxes[name]
     end
 
-    figure(idx, figsize=(6, 3)); clf()
-    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    subplot(4, 3, idx)
+    gca()[:tick_params](axis="both", which="major", labelsize=14)
 
-    plot(frequencies/1e6, measured, "ko")
+    max_value = maximum(measured)
+    plot(frequencies/1e6, measured, "ko", zorder=3)
     if name in keys(perley_fluxes)
         model = perley_fluxes[name]
-        plot(frequencies/1e6, model, "k-")
+        plot(frequencies[cutoff]/1e6, model[cutoff], "k-", zorder=3)
+        plot(frequencies/1e6, model, "k:", zorder=2)
+        max_value = max(max_value, maximum(model))
     end
     if name in keys(scaife_fluxes)
[…]

### 2017-08-01 paper.tex
fix some plots

@@
 
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
+
 \renewcommand{\b}{\pmb}
+\newcommand{\tbf}{\textbf}
 \renewcommand{\d}{{\rm d}}
 \newcommand{\atikh}{\b{\hat a}_\text{Tikhonov}}
-\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
 
@@
 \begin{document}
+
+\watermark{draft}
 
@@
 
-\begin{figure*}[p]
+\begin{figure*}[ht]
     \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
@@
 
-\begin{deluxetable*}{CCCCCC}
-    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
-    \tablewidth{0pt}
-    \tablehead{
-        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} &
-            \colhead{Noise} & \colhead{Noise} \\
-        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)} &
-            \colhead{(K)} & \colhead{(Jy)}
-    }
-    \startdata
-    1 & 36.528 & 0.024 & 16.2 & 372.8 \\
-    2 & 41.760 & 0.024 & 14.7 & 321.2 \\
-    3 & 46.992 & 0.024 & 14.2 & 247.0 \\
-    4 & 52.224 & 0.024 & 13.6 & 205.7 \\
-    5 & 57.456 & 0.024 & 13.5 & 167.7 \\
-    6 & 62.688 & 0.024 & 13.5 & 137.6 \\
-    7 & 67.920 & 0.024 & 13.5 & 114.9 \\
-    8 & 73.152 & 0.024 & 13.7 &  93.4 \\
-    \enddata
-\end{deluxetable*}
+\begin{table*}[ht]
+    \centering
+    \begin{tabular}{cccccc}
+        \hline
+        \hline
+        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} & \multicolumn2c{\tbf{Thermal Noise}} \\
+        \cline{5-6}
+        \tbf{\#} & (MHz)  & (MHz)          & (arcmin)  & (K) & (Jy) \\
+        \hline
+        1 & 36.528 & 0.024 & 16.2 & 372.8 & \\
+        2 & 41.760 & 0.024 & 14.7 & 321.2 & \\
+        3 & 46.992 & 0.024 & 14.2 & 247.0 & \\
+        4 & 52.224 & 0.024 & 13.6 & 205.7 & \\
+        5 & 57.456 & 0.024 & 13.5 & 167.7 & \\
+        6 & 62.688 & 0.024 & 13.5 & 137.6 & \\
+        7 & 67.920 & 0.024 & 13.5 & 114.9 & \\
+        8 & 73.152 & 0.024 & 13.7 &  93.4 & \\
+        \hline \hline
+    \end{tabular}
+    \caption{Summary of the generated all-sky maps\label{tab:summary}}
+\end{table*}
+
+%\begin{figure*}[p]
+%    \centering
+%    \includegraphics[width=0.9\textheight, angle=90]{maps/2017-04-20-rgb-map-smaller}
+%    \caption{
+%        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
+%        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
+%        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
+%        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
+%        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
+%        emission is synchrotron, but the blue regions mottling the galactic plane are due to
+%        free-free absorption from \ion{H}{2} regions.
+%    }
+%    \label{fig:rgb}
+%\end{figure*}
 
 \begin{figure*}[ht]
-    \plotone{maps/2017-04-20-rgb-map-smaller}
-    \caption{
-        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
-        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
-        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
-        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
-        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
-        emission is synchrotron, but the blue regions mottling the galactic plane are due to
-        free-free absorption from \ion{H}{2} regions.
-    }
-    \label{fig:rgb}
-\end{figure*}
-
-\begin{figure*}[p]
-    \gridline{
-        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
-            {0.48\textwidth}{}
-    }
+    \includegraphics[width=\textwidth]{figures/channel-maps/channel-maps}
     \caption{

### 2017-08-01 figures/channel-maps/fetch.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw06/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw08/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw12/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw16/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+

### 2017-08-01 figures/channel-maps/make.jl

@@ -1,20 +1,24 @@
+#!/usr/bin/env julia
+
 using JLD, PyPlot, PyCall
 
 unshift!(PyVector(pyimport("sys")["path"]), "")
 @pyimport my_log_scale as mls
-
-path = dirname(@__FILE__)
 close("all")
 
-function plot(filename)
+path = dirname(@__FILE__)
+
+figure(1, figsize=(10, 8)); clf()
+for (idx, spw) in enumerate(4:2:18)
+    str = @sprintf("spw%02d", spw)
+    filename = "$str-glamour-shot-map-wiener-filtered-rainy-2048-galactic"
     img, ν = load(joinpath(path, filename*".jld"), "image", "frequency")
 
     max = maximum(img)/5
     min = minimum(img)
     base = max - min
     
-    figure(); clf()
-    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    subplot(4, 2, idx)
     θ = linspace(0, 2π, 512)
     x = 2cos.(θ)
     y = sin.(θ)
@@ -23,24 +27,23 @@ function plot(filename)
     imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
            norm = mls.MyLogNormalize(min, max, base),
            extent=(-2, 2, -1, 1),
-           clip_path=ellipse)
+           clip_path=ellipse, zorder=10)
+    xlim(-2, 2)
+    ylim(-1, 1)
     gca()[:set_aspect]("equal")
-    title(@sprintf("%.3f MHz", ν/1e6), fontsize=16)
+    gca()[:get_xaxis]()[:set_visible](false)
+    gca()[:get_yaxis]()[:set_visible](false)
+    title(@sprintf("%.3f MHz", ν/1e6), fontsize=10)
     axis("off")
-    cbar = colorbar(fraction=0.02)
-    cbar[:ax][:tick_params](labelsize=16)
-    tight_layout()
+    cbar = colorbar(fraction=0.07, orientation="vertical")
+    cbar[:ax][:tick_params](labelsize=12)
+    cbar[:set_label]("Temperature (K)", fontsize=10, rotation=270)
+    cbar[:ax][:get_yaxis]()[:set_label_coords](12.0, 0.5)
 
-    savefig(joinpath(path, filename*".pdf"),
-            bbox_inches="tight", pad_inches=0, transparent=true)
 end
+tight_layout()
[…]

### 2017-08-01 figures/flux-scale/fetch.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-wiener-filtered.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-cyga-peeled.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-vira-peeled.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-hyaa-peeled.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-perb-peeled.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-3c353-peeled.jld .
+

### 2017-08-01 figures/flux-scale/make.jl

@@ -59,7 +59,7 @@ for (idx, name) in enumerate(names)
     idx < 9 && plt[:setp](gca()[:get_xticklabels](), visible=false)
     idx ≥ 9 && xlabel("Frequency (MHz)", fontsize=14)
     mod(idx, 3) == 1 && ylabel("Flux (Jy)", fontsize=14)
-    mod(idx, 3) == 1 && gca()[:get_yaxis]()[:set_label_coords](-0.30,0.5)
+    mod(idx, 3) == 1 && gca()[:get_yaxis]()[:set_label_coords](-0.30, 0.5)
     grid("on")
 end
 tight_layout()

### 2017-08-17 paper.tex
wip

@@
 \usepackage{amsmath}
-\usepackage[]{algorithm2e}
+
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\newcommand*\Let[2]{\State #1 $\gets$ #2}
+\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
+\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}
 
@@
 interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
-scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
-measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free emission,
-thermal dust emission) are a nuisance and careful modeling and removal of these components is
-essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.
+scattering, absorption, or additional emission can perturb or corrupt the thermal CMB spectrum. In
+order to measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free
+emission, thermal dust emission) are a nuisance and careful modeling and removal of these components
+is essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.
 
@@
 temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
-power spectrum of this perturbation is expected to be dominated by inhomogeneous heating of the IGM
+power spectrum of this perturbation is thought to be dominated by inhomogeneous heating of the IGM
 at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
@@
 low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
-remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and radion
-emission from a confusing background of radio sources.  Ideally a foreground removal strategy should
-be informed by the measured spatial structure and frequency spectrum of all foreground components.
-However this possibility is limited by the availability of suitable high-fidelity low-frequency sky
-maps on angular scales ranging from tens of degrees to arcminutes.
+remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and a confusing
+background of radio sources.  Ideally a foreground removal strategy should be informed by the
+measured spatial structure and frequency spectrum of all foreground components.  However this
+possibility is limited by the availability of suitable high-fidelity low-frequency sky maps on
+angular scales ranging from tens of degrees to arcminutes.
 
@@
 \citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
-Frequency Sky Survey \citet{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
+Frequency Sky Survey \citep{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
 and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.
@@
 \end{equation}
-Imaging the output of a radio interferometer therefore consists of estimating $I_\nu(\hat r)$ given
-the available measurements $V^{ij}_\nu$.
+Constructing an image from the output of a radio interferometer therefore consists of estimating
+$I_\nu(\hat r)$ given the available measurements $V^{ij}_\nu$.
 
@@
 The baseline transfer function defines the response of a single baseline to the sky, and is a
-function of the antenna primary beam and baseline orientation.
+function of the antenna primary beam, and baseline length and orientation.
 
@@
 solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
-baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations then
+baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations, then
 the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
@@
 
-It can be shown that there is a discrete linear relationship between the $m$-modes $V^{ij}_{m,\nu}$
-and the spherical harmonic coefficients of the sky brightness $a_{lm,\nu}$.
+It can be shown that there is a discrete linear relationship between the measured $m$-modes
+$V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky brightness $a_{lm,\nu}$.
 \begin{equation}\label{eq:m-mode-sum-equation}
@@
 where the transfer coefficients $B^{ij}_{lm,\nu}$ define the interferometer's response to the sky.
-For example, the transfer coefficients are a function of the baseline and antenna primary beam
-pattern.
+These transfer coefficients are computed from the spherical harmonic transform of the baseline
+transfer function defined by Equation~\ref{eq:baseline-transfer-function}.
 
@@
 matrix $\b B$ is block-diagonal.
-\begin{equation}
-    \b B = \left(\begin{array}{cccc}
-        m = 0 &&& \\
-              & m=\pm1 && \\
-              && m=\pm2 & \\
-              &&& \ddots \\
-    \end{array}\right)
-\end{equation}
-The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
-spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
-block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the value of $m$. Positive
-and negative values of $m$ are grouped together because the brightness of the sky is real-valued,
-and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m a_{lm}^*$.
 \begin{equation}\label{eq:m-mode-matrix-equation}
@@
 \end{equation}
+\begin{equation}
+    \b B = \left(\begin{array}{cccc}
+        m = 0 &&& \\
+              & m=\pm1 && \\
+              && m=\pm2 & \\
+              &&& \ddots \\
+    \end{array}\right)
+\end{equation}
+The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
+spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
+block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the absolute value of $m$.
+Positive and negative values of $m$ are grouped together because the brightness of the sky is
+real-valued, and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m
+a_{lm}^*$.
 
@@
 
-The interferometer's sensitivity to $l=0$, however, deserves special consideration.
-\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that an interferometer is
-only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
-common-mode noise. In fact, the sensitivity of the interferometer is proportional to the amplitude
-of these effects. For consistency we will include $a_{00}$ while solving
-Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
-because we do not have a measurement of the amplitude of cross-talk or common-mode noise, which
-would be needed to correctly calibrate $a_{00}$.
+The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
+\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that a baseline with
+nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
+fact the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
+baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
+case the antennas are so close together that voltage fluctuations in one antenna can couple into the
+other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
+measured and calibrated.
 
@@
 Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
-the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
-the case of the OVRO-LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
-$\sim10^9$ in processing time by using $m$-mode analysis.
+the computational complexity involved in inverting a single block is reduced by a factor of $N^3$
+relative to a dense matrix. However we must invert $N$ blocks, so the overall computational savings
+is proportional to $N^2$.  For the case of the OVRO-LWA the equation breaks up into $\sim10^3$
+blocks and so we save a factor of $\sim10^6$ in processing time by using $m$-mode analysis.
 
@@
         solution grows rapidly. When the regularization parameter is large, the least-squares norm
-        grows rapidly. The optimal value for the regularization parameter is near
-        $\varepsilon=0.01$.
+        grows rapidly.
     }
@@
 
-$m$-mode analysis imaging automatically deconvolves angular scales described by modes for which the
-singular values of $\b B$ are $\gg \sqrt{\varepsilon}$. For example, structures on angular scales
-smaller than $\lambda/b_\text{min}$ and larger than $\lambda/b_\text{max}$ (where $b_\text{min}$ and
-$b_\text{max}$ are the minimum and maximum baseline lengths) are generally well-measured by the
-interferometer and will be automatically deconvolved during the imaging process. However, as the
-total integration time of the data set increases, the noise in the data decreases. One consequence
-of this is that the regularization parameter $\varepsilon$ can be decreased. This increases the
-number of modes for which $\sigma_i \gg \sqrt{\varepsilon}$, and as a consequence the automatic
-deconvolution can extend to scales larger than $\lambda/b_\text{min}$ and smaller than
-$\lambda/b_\text{max}$.
-
-However point sources do not get deconvolved by the imaging process even in the limit of infinite
-SNR and $\varepsilon \rightarrow 0$. This is because point sources carry power to large values of
-$l$ and by computational necessity we truncated the spherical harmonic representation of the sky at
-some $l_\text{max}$. A consequence of this is that point sources will appear in the maps with a
-characteristic point spread function (PSF). The PSF may be computed with:
-\begin{equation}
+In traditional radio astronomy imaging, the CLEAN algorithm \citep{1974A&AS...15..417H} is used to
+interpolate the measured visibilities onto the $uv$-plane. In the absence of this interpolation,
+gaps in the interferometer's $uv$-coverage are assumed to be zero, and in the image plane sources
+are convolved with a point spread function (PSF) that is characteristic of the $uv$-coverage.
+Fundamentally, the interferometer's PSF in the dirty images is determined by which modes were
+assumed to be zero in the initial imaging process.
+
+In $m$-mode analysis imaging, we assumed modes were zero in two separate ways:
+\begin{enumerate}
+    \item We selected a set of spherical harmonic coefficients $a_{lm}$ to describe the sky
+        brightness distribution. All modes with $l>l_\text{max}$ are neglected and assumed to be
+        zero.
+    \item Tikhonov regularization forces linear combinations of spherical harmonic coefficients with
+        $\sigma_i \lesssim \sqrt{\varepsilon}$ towards zero.
+\end{enumerate}
+As a consequence the final map of the sky is not assembled from a complete set of spherical
+harmonics. Therefore just as in traditional imaging, $m$-mode analysis imaging produces dirty maps
+where sources are convolved with a PSF.  This PSF can be improved by increasing the number and
+variety of baselines, which increases the number of modes where $\sigma_i \gg \sqrt{\varepsilon}$.
+Alternatively by collecting more data, the signal-noise ratio of the measured $m$-modes increases,
+which allows the observer to lower the value of $\varepsilon$ without increasing the noise in the
+maps.  Finally, the CLEAN algorithm can be applied to interpolate some of the missing information
+that was assumed to be zero.
+
+The PSF of a dirty $m$-mode analysis map may be computed with
+\begin{equation}\label{eq:psf}
     \b a_\text{PSF}(\theta, \phi)
@@
 \begin{equation}
-    a_{lm, \text{PS}}(\theta, \phi) = Y_{lm}^*(\theta, \phi)\,.
-\end{equation}
-
+    \b a_\text{PS}(\theta, \phi) = \begin{pmatrix}
+        \vdots \\
+        Y_{lm}^*(\theta, \phi) \\
+        \vdots \\
+    \end{pmatrix}
+    = \begin{pmatrix}
+        \vdots \\
+        Y_{lm}^*(\theta, 0)\times e^{im\phi} \\
+        \vdots \\
+    \end{pmatrix} \,.
+\end{equation}
 In general the PSF can be a function of the right ascension and declination. However point sources
 at the same declination take the same track through the sky and therefore (barring any ionospheric
-effects) will have the same PSF. The PSF is actually only a function of the declination. For
+effects) will have the same PSF. The PSF is therefore only a function of the declination. For
 example, sources at low elevations will tend to have an extended PSF along the north-south axis due
-to baseline foreshortening. An example computed PSF is shown in Figure~\ref{fig:psf}.
-
-The computed PSF as a function of frequency and declination can be used to adapt the CLEAN algorithm
-\citep{1974A&AS...15..417H} to $m$-mode analysis.
-
-\begin{algorithm}
-    \KwData{dirty maps generated from the output of Equation~\ref{eq:tikhonov-solution};}
-    \KwResult{clean maps with point sources deconvolved;}
-    pre-compute $\b M = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B$\;
-    \While{noise in map $>$ threshold}{
-        identify the pixel with the largest amplitude\;
-        compute $\b a_\text{PSF} = \b M \b a_\text{PS}$\;
-        update $\b a \leftarrow \b a - (\textit{gain})\times\b a_\text{PSF}$\;
-    }
-    convolve removed components with a CLEAN-beam and restore to the map\;
-\end{algorithm}
-
-It should be noted that for interferometers with more baselines than the number of spherical
-harmonics used in the maps, $\b M$ is a much smaller matrix than the full transfer matrix $\b B$.
-Therefore the cost of multiplying by $\b M$ can actually be dominated by the cost of computing the
-spherical harmonics describing a point source at the identified pixel.
+to baseline foreshortening. An example computed PSF is shown in Figure~\ref{fig:psf}.  Adapting
+CLEAN for $m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of
+declinations, or a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.
+
+\todo{cite lincoln's paper on cleaning with a changing psf}
+
+For an interferometer with more baselines than spherical harmonics used in the maps (eg. the
+OVRO-LWA), $\b B^*\b B$ can be a much smaller matrix than the full transfer matrix $\b B$. Therefore
+pre-computing $\b B^*\b B$ can allow the entire matrix to fit into memory on a single machine. This
+greatly reduces the amount of disk I/O necessary for solving Equation~\ref{eq:psf}.
+
+Additionally we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
+U^*\b U$, where $\b U$ is an upper-triangular matrix. Inverting an upper triangular matrix is an
+$\mathcal{O}(N^2)$ operation (instead of $\mathcal{O}(N^3)$ for a general matrix inverse).\footnote{
+    Inverting a matrix is numerically unstable and should be avoided. Instead of computing $\b
+    U^{-1}$, the linear equation $\b U\b x = \b y$ is solved each time the matrix inverse is needed.
+}
+Equation~\ref{eq:psf} can then be rapidly evaluated from right to left as:
+\begin{equation}\label{eq:rapid-psf}
+    \b a_\text{PSF} =
+        \b U^{-1}\,\big(\b U^*\big)^{-1}\,\big(\b B^*\b B\big)\,\b a_\text{PS}\,.
+\end{equation}
+Furthermore, Equation~\ref{eq:rapid-psf} does not need to be separately evaluated for each CLEAN
+component. Instead we can identify $N$ CLEAN components, accumulate $\b a_\text{PS}$ for each
+component, and evaluate Equation~\ref{eq:rapid-psf} on the accumulation. This can greatly reduce the
+number of times this equation needs to be evaluated, but care must be taken to ensure that the $N$
+components are not so close together that sidelobes from one may interact with another.
+
+\todo{describe blurring to avoid cleaning the diffuse emission}
+
+Altogether the adaptation of CLEAN applied to the maps presented in this paper is summarized below.
+\begin{algorithmic}[1]
+    \Require{$\b a$ is the solution to Equation~\ref{eq:tikhonov-solution}}
+    \Function{CLEAN}{$\b a$}
+    \Let{$\b M$}{$\b B^*\b B^*$}
+    \Let{$\b U$}{${\rm chol}(\b B)$} \Comment{Cholesky decomposition}
+    \While{noise in map $>$ threshold}
+    \State find $N$ pixels with the largest residual flux
+    \Let{$\b x$}{$\sum_{i=1}^N \,(\text{pixel flux}) \times \b a_\text{PS}(\theta_i, \phi_i)$}
+    \Let{$\b y$}{$\b U^{-1}\big(\b U^*\big)^{-1}\b M\b x$}
+    \Let{$\b a$}{$\b a - (\text{loop gain})\times\b y$}
+    \State record subtracted components
+    \EndWhile
+    \Let{$\b a$}{$\b a + (\text{restored components})$}
+    \State \Return{$\b a$}
+    \EndFunction
+\end{algorithmic}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
     \plotone{figures/antenna-layout/antenna-layout}
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
     \plotone{figures/psf/spw04-psf-45-degrees}
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[t]
     \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
@@
 
-%\todo{slice through Cyg A and Cas A to illustrate the removal process}
-%\todo{Give a plot with the updated source models}
+\todo{slice through Cyg A and Cas A to illustrate the removal process}
+
+\todo{Give a plot with the updated source models}
 
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[t]
     \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
@@
 
-\begin{table*}[ht]
+\begin{table*}[t]
     \centering
-    \begin{tabular}{cccccc}
+    \begin{tabular}{cccccccccc}
         \hline
         \hline
-        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} & \multicolumn2c{\tbf{Thermal Noise}} \\
+        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} &
+            \multicolumn2c{\tbf{Thermal Noise}} &&
+            \multicolumn2c{\tbf{Spherical Harmonics}} &
+            \tbf{Singular Values} \\
         \cline{5-6}
-        \tbf{\#} & (MHz)  & (MHz)          & (arcmin)  & (K) & (Jy) \\
+        \cline{8-9}
+        \tbf{\#} & MHz & MHz & arcmin &
+            K & Jy &&
+            $l=0$ & $m=0$ &
+            fraction $>\sqrt{\varepsilon}$ \\
         \hline
-        1 & 36.528 & 0.024 & 16.2 & 372.8 & \\
-        2 & 41.760 & 0.024 & 14.7 & 321.2 & \\
-        3 & 46.992 & 0.024 & 14.2 & 247.0 & \\
-        4 & 52.224 & 0.024 & 13.6 & 205.7 & \\
-        5 & 57.456 & 0.024 & 13.5 & 167.7 & \\
-        6 & 62.688 & 0.024 & 13.5 & 137.6 & \\
-        7 & 67.920 & 0.024 & 13.5 & 114.9 & \\
-        8 & 73.152 & 0.024 & 13.7 &  93.4 & \\
+        1 & 36.528 & 0.024 & 16.2 & 372.8 & & & no & yes \\
+        2 & 41.760 & 0.024 & 14.7 & 321.2 & & & no & yes \\
+        3 & 46.992 & 0.024 & 14.2 & 247.0 & & & no & no \\
+        4 & 52.224 & 0.024 & 13.6 & 205.7 & & & no & no \\
+        5 & 57.456 & 0.024 & 13.5 & 167.7 & & & no & no \\
+        6 & 62.688 & 0.024 & 13.5 & 137.6 & & & no & no \\
+        7 & 67.920 & 0.024 & 13.5 & 114.9 & & & no & no \\
+        8 & 73.152 & 0.024 & 13.7 &  93.4 & & & no & no \\
         \hline \hline
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[t]
     \includegraphics[width=\textwidth]{figures/channel-maps/channel-maps}
@@
 
-%\todo{text}
+\todo{text}
 
@@
 
-%\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
-%that it is actually worse than the RFI, but I don't actually know for sure}
+\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
+that it is actually worse than the RFI, but I don't actually know for sure}
 
@@
 
-%\todo{describe how the Wiener filter works}
+\todo{describe how the Wiener filter works}
 
@@
 
-%\todo{discuss the possibility of declination dependent flux-scale errors in these maps}
+\todo{discuss the possibility of declination dependent flux-scale errors in these maps}
 
@@
 
-%\todo{quick simulation of this?}
+\todo{quick simulation of this?}
 
@@
 
-%\todo{Simulate images of point sources with this}
-%
-%\todo{I think the conclusion is sort of exactly what you would expect: refraction broadens the PSF
-%while scintillation effects the flux scale, but honestly not by much because we have such large
-%averages that unless the scintillation is Cauchy distributed it is not that bad..}
+\todo{Simulate images of point sources with this}
+
+\todo{I think the conclusion is sort of exactly what you would expect: refraction broadens the PSF
+while scintillation effects the flux scale, but honestly not by much because we have such large
+averages that unless the scintillation is Cauchy distributed it is not that bad..}
 

### 2017-08-17 figures/antenna-layout/make.jl

@@ -1,24 +1,27 @@
+#!/usr/bin/env julia
+
 using PyPlot
 
-matrix = readdlm("antenna-layout.txt");
-east = matrix[:,1]
-north = matrix[:,2]
-up = matrix[:,3]
+path = dirname(@__FILE__)
+matrix = readdlm(joinpath(path, "antenna-layout.txt"))
+east  = matrix[:, 1]
+north = matrix[:, 2]
+up    = matrix[:, 3]
 east -= 2
 
 core = 1:251
 leda = 252:256
 expansion = 257:288
 
-transparent = (0, 0, 0, 0)
-figure(1, figsize=(6, 5)); clf()
+figure(); clf()
+gca()[:tick_params](axis="both", which="major", labelsize=16)
 
 scatter(east[core], north[core], marker="o", c="k", s=8, lw=0)
 scatter(east[leda], north[leda], marker="+", c="k", s=50)
 scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
 gca()[:set_aspect]("equal")
-xlabel("distance east / m", fontsize=12)
-ylabel("distance north / m", fontsize=12)
+xlabel("distance east (m)", fontsize=16)
+ylabel("distance north (m)", fontsize=16)
 tight_layout()
 
 savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0.1, transparent=true)

### 2017-08-17 figures/channel-maps/make.jl

@@ -46,4 +46,6 @@ gcf()[:subplots_adjust](hspace=0.25, wspace=-0.05)
 
 savefig(joinpath(path, "channel-maps.pdf"),
         bbox_inches="tight", pad_inches=0, transparent=true)
+savefig(joinpath(path, "channel-maps.png"),
+        bbox_inches="tight", pad_inches=0, transparent=true)
 

### 2017-08-17 paper.tex
combine the antenna layout and psf plots

@@
     Inverting a matrix is numerically unstable and should be avoided. Instead of computing $\b
-    U^{-1}$, the linear equation $\b U\b x = \b y$ is solved each time the matrix inverse is needed.
+    A^{-1}$, the linear equation $\b A\b x = \b b$ is solved each time the matrix inverse is needed.
 }
@@
 
-\begin{figure}[t]
-    \plotone{figures/antenna-layout/antenna-layout}
+\begin{figure*}[t]
+    \includegraphics[width=\textwidth]{figures/psf/psf}
     \caption{
+        \textbf{(left panel)}
         This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
@@
         antennas equipped with noise-switched front ends.
-    }
-    \label{fig:antenna-layout}
-\end{figure}
-
-\begin{figure}[t]
-    \plotone{figures/psf/spw04-psf-45-degrees}
-    \caption{
+        \textbf{(middle panel)}
         The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
         declination of $+45^\circ$ and frequency of $36.528$ MHz.
+        \textbf{(right panel)}
+        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
+        declination of $+45^\circ$ and frequency of $73.152$ MHz.
     }
     \label{fig:psf}
-\end{figure}
+\end{figure*}
 
@@
 the global sky brightness.  These antennas are used as part of the LEDA experiment
-\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
-Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
+\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.  The
+left panel of Figure~\ref{fig:psf} is a diagram of the antenna configuration.
 

### 2017-08-17 figures/antenna-layout/make.jl

@@ -1,28 +1,0 @@
-#!/usr/bin/env julia
-
-using PyPlot
-
-path = dirname(@__FILE__)
-matrix = readdlm(joinpath(path, "antenna-layout.txt"))
-east  = matrix[:, 1]
-north = matrix[:, 2]
-up    = matrix[:, 3]
-east -= 2
-
-core = 1:251
-leda = 252:256
-expansion = 257:288
-
-figure(); clf()
-gca()[:tick_params](axis="both", which="major", labelsize=16)
-
-scatter(east[core], north[core], marker="o", c="k", s=8, lw=0)
-scatter(east[leda], north[leda], marker="+", c="k", s=50)
-scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
-gca()[:set_aspect]("equal")
-xlabel("distance east (m)", fontsize=16)
-ylabel("distance north (m)", fontsize=16)
-tight_layout()
-
-savefig("antenna-layout.pdf", bbox_inches="tight", pad_inches=0.1, transparent=true)
-

### 2017-08-17 figures/psf/make.jl

@@ -1,30 +1,70 @@
+#!/usr/bin/env julia
+
 using JLD, PyPlot
 
 path = dirname(@__FILE__)
-close("all")
+figure(1, figsize=(15, 5)); clf()
 
-function plot(filename)
+# Create the antenna layout panel
+
+matrix = readdlm(joinpath(path, "antenna-layout.txt"))
+east  = matrix[:, 1]
+north = matrix[:, 2]
+up    = matrix[:, 3]
+east -= 2
+
+core = 1:251
+leda = 252:256
+expansion = 257:288
+
+subplot(1, 3, 1)
+gca()[:tick_params](axis="both", which="major", labelsize=14)
+
+scatter(east[core], north[core], marker="o", c="k", s=6, lw=0)
+scatter(east[leda], north[leda], marker="+", c="k", s=50)
+scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
+gca()[:set_aspect]("equal")
+xlabel("distance east (m)", fontsize=14)
+ylabel("distance north (m)", fontsize=14)
+
+# Create the psf panels
+
+frequencies = [3.6528e7, 7.3152e7]
+filenames = ["spw04-psf-+45-degrees", "spw18-psf-+45-degrees"]
+
+global _im
+for idx = 1:length(filenames)
+    subplot(1, 3, idx+1)
+    filename = filenames[idx]
+
     img = load(joinpath(path, filename*".jld"), "img")
     img = img[51:151, 51:151]
-    img /= maximum(img)
     
-    figure()
-    gca()[:tick_params](axis="both", which="major", labelsize=16)
+    gca()[:tick_params](axis="both", which="major", labelsize=14)
     
-    imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
-           vmin=-0.2, vmax=1.0,
-           extent=(150, -150, -150, 150))
+    _im = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
+                 vmin=-0.2, vmax=1.0,
+                 extent=(150, -150, -150, 150))
     gca()[:set_aspect]("equal")
-    cbar = colorbar()
-    cbar[:ax][:tick_params](labelsize=16)
-    xlabel("ΔRA" * " (arcmin)", fontsize=16)
-    ylabel("Δdec" * " (arcmin)", fontsize=16)
-    tight_layout()
-
[…]

### 2017-08-17 paper.tex
give the antenna beam figure the same treatment as the psf figure

@@
 \begin{figure*}[t]
-    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
+    \includegraphics[width=\textwidth]{figures/beam/beam}
     \caption{
-        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
+        \textbf{(left panel)}
+        The tracks traced through the sky by the 8 brightest point sources visible to the
         OVRO-LWA.
-        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
+        \textbf{(middle panel)}
+        The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
+        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
+        \textbf{(right panel)}
+        The amplitude of the OVRO-LWA beam at 73.152 MHz as a result of the beam model
         fit using Zernike polynomials and the symmetry assumptions outlined in the text.

### 2017-08-17 figures/beam/fetch.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/beam.jld spw04-beam.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/beam.jld spw18-beam.jld
+

### 2017-08-17 figures/beam/make.jl

@@ -1,7 +1,11 @@
+#!/usr/bin/env julia
+
 using JLD, PyPlot, CasaCore.Measures
 
 path = dirname(@__FILE__)
-Iimg = load(joinpath(path, "beam.jld"), "I-image")
+figure(1, figsize=(15, 5)); clf()
+
+# Create the source track panel
 
 sources = Dict("Cyg A" => Direction(dir"J2000", "19h59m28.35663s", "+40d44m02.0970s"),
                "Cas A" => Direction(dir"J2000", "23h23m24.000s", "+58d48m54.00s"),
@@ -16,26 +20,10 @@ ovro_lwa = Position(pos"ITRF", -2.40927462614919e6, -4.477838733582964e6, 3.8393
 
 times = linspace(4.994049600941745e9, 4.994150416022397e9, 7756)
 
-close("all")
-figure(1, figsize=(6, 4))
-circle = plt[:Circle]((0, 0), 1, alpha=0)
-gca()[:add_patch](circle)
-imshow(Iimg, extent=(-1, 1, -1, 1), interpolation="nearest", vmin=0, vmax=1,
-       cmap=get_cmap("magma"), clip_path=circle)
-gca()[:set_aspect]("equal")
-colorbar()
-xlim(-1, 1)
-ylim(-1, 1)
-xlabel("l / direction cosine", fontsize=12)
-ylabel("m / direction cosine", fontsize=12)
-tight_layout()
-savefig(joinpath(path, "stokes-I-beam.pdf"), bbox_inches="tight", pad_inches=0.1, transparent=true)
-
-figure(2, figsize=(6, 4)); clf()
+subplot(1, 3, 1)
 frame = ReferenceFrame()
 set!(frame, ovro_lwa)
 for name in keys(sources)
-    @show name
     direction = sources[name]
     l = Float64[]
     m = Float64[]
@@ -53,24 +41,64 @@ for name in keys(sources)
         end
     end
     mmin = minimum(m[.!isnan.(m)])
-    annotate(name, xy=(0, mmin+0.01), horizontalalignment="center")
+    if name == "3C 353"
+        annotate(name, xy=(0, mmin+0.01), horizontalalignment="center",
+                 fontsize=12)
+    else
+        annotate(name, xy=(0, mmin+0.02), horizontalalignment="center",
+                 fontsize=12)
+    end
     plot(l, m, "k-")
 end
 θ = linspace(0, 2π, 1000)
[…]

### 2017-08-17 figures/psf/fetch.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/tmp/spw04-psf-+45-degrees.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/tmp/spw18-psf-+45-degrees.jld .
+

### 2017-09-03 figures/scintillation/fetch.sh
minor changes to scintillation plot

@@ -2,7 +2,4 @@
 
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/light-curves-rainy.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/expected-light-curves-rainy.jld .
-#scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/beam.jld spw18-beam.jld
-#scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/tmp/scintillation.jld spw04-scintillation.jld
-#scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/tmp/scintillation.jld spw18-scintillation.jld
 

### 2017-09-03 figures/scintillation/make.jl

@@ -34,17 +34,22 @@ end
 subplot(1, 2, 1)
 gca()[:tick_params](axis="both", which="major", labelsize=12)
 plot_light_curve( 4, 1, ".", "#d62728", "36.528 MHz")
+#plot_light_curve(10, 1, ".", "#2ca02c", "52.224 MHz")
 plot_light_curve(18, 1, ".", "#1f77b4", "73.152 MHz")
 text(0.95, 0.95, names[4][1],
      transform=gca()[:transAxes], fontsize=14, fontweight="bold",
      horizontalalignment="right", verticalalignment="top",
      color="black", zorder=2)
 #legend("upper right")
-text(0.95, 0.86, "36.528 MHz",
+text(0.95, 0.87, "36.528 MHz",
      transform=gca()[:transAxes], fontsize=12, fontweight="bold",
      horizontalalignment="right", verticalalignment="top",
      color="#d62728", zorder=2)
-text(0.95, 0.77, "73.152 MHz",
+#text(0.95, 0.79, "52.224 MHz",
+#     transform=gca()[:transAxes], fontsize=12, fontweight="bold",
+#     horizontalalignment="right", verticalalignment="top",
+#     color="#2ca02c", zorder=2)
+text(0.95, 0.79, "73.152 MHz",
      transform=gca()[:transAxes], fontsize=12, fontweight="bold",
      horizontalalignment="right", verticalalignment="top",
      color="#1f77b4", zorder=2)
@@ -62,17 +67,22 @@ annotate("occulted by\nmountains", xy=(22, 1000), xytext=(21, 3000),
 subplot(1, 2, 2)
 gca()[:tick_params](axis="both", which="major", labelsize=12)
 plot_light_curve( 4, 2, ".", "#d62728", "36.528 MHz")
+#plot_light_curve(10, 2, ".", "#2ca02c", "52.224 MHz")
 plot_light_curve(18, 2, ".", "#1f77b4", "73.152 MHz")
 text(0.95, 0.95, names[4][2],
      transform=gca()[:transAxes], fontsize=14, fontweight="bold",
      horizontalalignment="right", verticalalignment="top",
      color="black", zorder=2)
 #legend("upper right")
-text(0.95, 0.86, "36.528 MHz",
+text(0.95, 0.87, "36.528 MHz",
      transform=gca()[:transAxes], fontsize=12, fontweight="bold",
      horizontalalignment="right", verticalalignment="top",
[…]

### 2017-09-03 figures/refraction/fetch.sh
merge the scintillation and refraction plots

@@ -1,4 +1,0 @@
-#!/bin/bash
-
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/refraction-curves-rainy.jld .
-

### 2017-09-03 figures/refraction/make.jl

@@ -1,86 +1,0 @@
-#!/usr/bin/env julia
-
-using JLD, PyPlot, CasaCore.Measures
-
-path = dirname(@__FILE__)
-figure(1, figsize=(12, 6)); clf()
-
-names, t, δra, δdec, flags = load(joinpath(path, "refraction-curves-rainy.jld"),
-                                  "names", "t", "dra", "ddec", "flags")
-
-function plot_ra(spw, src, color)
-    f = flags[spw][src, :]
-    x = copy(t[spw])
-    y = δra[spw][src, :]
-    x -= x[1]
-    x /= 3600
-    y = 60rad2deg.(y)
-    x[f] = NaN
-    y[f] = NaN
-    plot(x, y, "-", color=color, lw=1)
-end
-
-function plot_dec(spw, src, color)
-    f = flags[spw][src, :]
-    x = copy(t[spw])
-    y = δdec[spw][src, :]
-    x -= x[1]
-    x /= 3600
-    y = 60rad2deg.(y)
-    x[f] = NaN
-    y[f] = NaN
-    plot(x, y, "-", color=color, lw=1)
-end
-
-subplot(2, 2, 1)
-gca()[:tick_params](axis="both", which="major", labelsize=12)
-axhline(0, c="0.75", lw=1)
-plot_ra( 4, 1, "#d62728")
-plot_ra(18, 1, "#1f77b4")
-xlim(0, 28)
-ylim(-25, 25)
-ylabel("ΔRA (arcmin)", fontsize=12)
-plt[:setp](gca()[:get_xticklabels](), visible=false)
-text(0.05, 0.95, "Cyg A",
-     transform=gca()[:transAxes], fontsize=14, fontweight="bold",
-     horizontalalignment="left", verticalalignment="top",
-     color="black", zorder=2)
-
-subplot(2, 2, 2)
-gca()[:tick_params](axis="both", which="major", labelsize=12)
-axhline(0, c="0.75", lw=1)
-plot_ra( 4, 2, "#d62728")
-plot_ra(18, 2, "#1f77b4")
-xlim(0, 28)
-ylim(-25, 25)
-plt[:setp](gca()[:get_xticklabels](), visible=false)
-text(0.05, 0.95, "Cas A",
-     transform=gca()[:transAxes], fontsize=14, fontweight="bold",
-     horizontalalignment="left", verticalalignment="top",
-     color="black", zorder=2)
-
[…]

### 2017-09-03 figures/scintillation-refraction/fetch.sh

@@ -2,4 +2,5 @@
 
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/light-curves-rainy.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/expected-light-curves-rainy.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/refraction-curves-rainy.jld .
 

### 2017-09-03 figures/scintillation-refraction/make.jl

@@ -1,0 +1,115 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot, CasaCore.Measures
+
+path = dirname(@__FILE__)
+figure(1, figsize=(12, 8)); clf()
+
+names, t, I, flags = load(joinpath(path, "light-curves-rainy.jld"),
+                          "names", "t", "I", "flags")
+
+names′, t′, I′, flags′ = load(joinpath(path, "expected-light-curves-rainy.jld"),
+                              "names", "t", "I", "flags")
+
+names, _, δra, δdec, flags_offset = load(joinpath(path, "refraction-curves-rainy.jld"),
+                                         "names", "t", "dra", "ddec", "flags")
+
+
+function plot_light_curve(spw, src, marker, color, label)
+    f = flags[spw][src, :]
+    x = copy(t[spw])
+    y = I[spw][src, :]
+    x -= x[1]
+    x /= 3600
+    x = x[.!f]
+    y = y[.!f]
+    scatter(x, y, marker=marker, color=color, s=10, edgecolors="w", lw=0, label=label)
+
+    f = flags′[spw][src, :]
+    x = copy(t′[spw])
+    y = I′[spw][src, :]
+    x -= x[1]
+    x /= 3600
+    x[f] = NaN
+    y[f] = NaN
+    plot(x, y, "k-", lw=1, label="_nolegend_")
+end
+
+function plot_offset(spw, src, color)
+    f = flags_offset[spw][src, :]
+    x = copy(t[spw])
+    y1 = δra[spw][src, :]
+    y2 = δdec[spw][src, :]
+    y = hypot.(y1, y2)
+    x -= x[1]
+    x /= 3600
+    y = 60rad2deg.(y)
+    x[f] = NaN
+    y[f] = NaN
+    plot(x, y, "-", color=color, lw=1)
+end
+
+subplot(4, 1, 1)
+gca()[:tick_params](axis="both", which="major", labelsize=12)
+plot_light_curve( 4, 1, ".", "#d62728", "36.528 MHz")
+plot_light_curve(18, 1, ".", "#1f77b4", "73.152 MHz")
+text(0.01, 0.95, "(a) Cyg A",
+     transform=gca()[:transAxes], fontsize=14, fontweight="bold",
+     horizontalalignment="left", verticalalignment="top",
+     color="black", zorder=2)
+xlim(0, 28)
+ylim(0, 35000)
+ylabel("apparent flux (Jy)", fontsize=12)
[…]

### 2017-09-03 figures/scintillation/make.jl

@@ -1,97 +1,0 @@
-#!/usr/bin/env julia
-
-using JLD, PyPlot, CasaCore.Measures
-
-path = dirname(@__FILE__)
-figure(1, figsize=(12, 4)); clf()
-
-names, t, I, flags = load(joinpath(path, "light-curves-rainy.jld"),
-                          "names", "t", "I", "flags")
-
-names′, t′, I′, flags′ = load(joinpath(path, "expected-light-curves-rainy.jld"),
-                              "names", "t", "I", "flags")
-
-function plot_light_curve(spw, src, marker, color, label)
-    f = flags[spw][src, :]
-    x = copy(t[spw])
-    y = I[spw][src, :]
-    x -= x[1]
-    x /= 3600
-    x = x[.!f]
-    y = y[.!f]
-    scatter(x, y, marker=marker, color=color, s=10, edgecolors="w", lw=0, label=label)
-
-    f = flags′[spw][src, :]
-    x = copy(t′[spw])
-    y = I′[spw][src, :]
-    x -= x[1]
-    x /= 3600
-    x[f] = NaN
-    y[f] = NaN
-    plot(x, y, "k-", lw=1, label="_nolegend_")
-end
-
-subplot(1, 2, 1)
-gca()[:tick_params](axis="both", which="major", labelsize=12)
-plot_light_curve( 4, 1, ".", "#d62728", "36.528 MHz")
-#plot_light_curve(10, 1, ".", "#2ca02c", "52.224 MHz")
-plot_light_curve(18, 1, ".", "#1f77b4", "73.152 MHz")
-text(0.95, 0.95, names[4][1],
-     transform=gca()[:transAxes], fontsize=14, fontweight="bold",
-     horizontalalignment="right", verticalalignment="top",
-     color="black", zorder=2)
-#legend("upper right")
-text(0.95, 0.87, "36.528 MHz",
-     transform=gca()[:transAxes], fontsize=12, fontweight="bold",
-     horizontalalignment="right", verticalalignment="top",
-     color="#d62728", zorder=2)
-#text(0.95, 0.79, "52.224 MHz",
-#     transform=gca()[:transAxes], fontsize=12, fontweight="bold",
-#     horizontalalignment="right", verticalalignment="top",
-#     color="#2ca02c", zorder=2)
-text(0.95, 0.79, "73.152 MHz",
-     transform=gca()[:transAxes], fontsize=12, fontweight="bold",
-     horizontalalignment="right", verticalalignment="top",
[…]

### 2017-09-03 figures/antenna-layout/make.jl
split out the antenna layout from the psf plot

@@ -1,0 +1,33 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot
+
+path = dirname(@__FILE__)
+figure(1, figsize=(6, 6)); clf()
+
+# Create the antenna layout panel
+
+matrix = readdlm(joinpath(path, "antenna-layout.txt"))
+east  = matrix[:, 1]
+north = matrix[:, 2]
+up    = matrix[:, 3]
+east -= 2
+
+core = 1:251
+leda = 252:256
+expansion = 257:288
+
+gca()[:tick_params](axis="both", which="major", labelsize=12)
+
+scatter(east[core], north[core], marker=".", c="k", s=20, lw=0)
+scatter(east[leda], north[leda], marker="+", c="k", s=50)
+scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
+gca()[:set_aspect]("equal")
+xlabel("distance east (m)", fontsize=12)
+ylabel("distance north (m)", fontsize=12)
+
+tight_layout()
+
+savefig(joinpath(path, "antenna-layout.pdf"),
+        bbox_inches="tight", pad_inches=0, transparent=true)
+

### 2017-09-03 figures/psf/fetch.sh

@@ -1,5 +1,6 @@
 #!/bin/bash
 
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/tmp/spw04-psf-+45-degrees.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/tmp/spw10-psf-+45-degrees.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/tmp/spw18-psf-+45-degrees.jld .
 

### 2017-09-03 figures/psf/make.jl

@@ -1,69 +1,64 @@
 #!/usr/bin/env julia
 
-using JLD, PyPlot
+using JLD, PyPlot, PyCall
+
+@pyimport mpl_toolkits.axes_grid1 as tk
 
 path = dirname(@__FILE__)
-figure(1, figsize=(15, 5)); clf()
+figure(1, figsize=(12, 4)); clf()
 
-# Create the antenna layout panel
+frequencies = [3.6528e7, 5.2224e7, 7.3152e7]
+filenames = ["spw04-psf-+45-degrees", "spw10-psf-+45-degrees", "spw18-psf-+45-degrees"]
 
-matrix = readdlm(joinpath(path, "antenna-layout.txt"))
-east  = matrix[:, 1]
-north = matrix[:, 2]
-up    = matrix[:, 3]
-east -= 2
-
-core = 1:251
-leda = 252:256
-expansion = 257:288
-
-subplot(1, 3, 1)
-gca()[:tick_params](axis="both", which="major", labelsize=14)
-
-scatter(east[core], north[core], marker="o", c="k", s=6, lw=0)
-scatter(east[leda], north[leda], marker="+", c="k", s=50)
-scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
-gca()[:set_aspect]("equal")
-xlabel("distance east (m)", fontsize=14)
-ylabel("distance north (m)", fontsize=14)
-
-# Create the psf panels
-
-frequencies = [3.6528e7, 7.3152e7]
-filenames = ["spw04-psf-+45-degrees", "spw18-psf-+45-degrees"]
-
-global _im
-for idx = 1:length(filenames)
-    subplot(1, 3, idx+1)
-    filename = filenames[idx]
-
+function plot_image(filename)
     img = load(joinpath(path, filename*".jld"), "img")
     img = img[51:151, 51:151]
-    
-    gca()[:tick_params](axis="both", which="major", labelsize=14)
-    
-    _im = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
+    gca()[:tick_params](axis="both", which="major", labelsize=12)
+    gca()[:set_aspect]("equal")
+    out = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
                  vmin=-0.2, vmax=1.0,
                  extent=(150, -150, -150, 150))
[…]

### 2017-09-03 figures/psf/make.jl
rm a line I forgot to delete

@@ -30,8 +30,6 @@ function label(idx)
          color="white", zorder=2)
 end
 
-g = gs.GridSpec(1, 3, height_ratios=[1])
-
 ax = gca()
 divider = tk.make_axes_locatable(ax)
 

### 2017-09-04 figures/beam/fetch.sh
put source tracks on top of the beam model

@@ -1,5 +1,6 @@
 #!/bin/bash
 
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/beam.jld spw04-beam.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/beam.jld spw10-beam.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/beam.jld spw18-beam.jld
 

### 2017-09-04 figures/beam/make.jl

@@ -1,11 +1,12 @@
 #!/usr/bin/env julia
 
-using JLD, PyPlot, CasaCore.Measures
+using JLD, PyPlot, PyCall, CasaCore.Measures
+
+@pyimport mpl_toolkits.axes_grid1 as tk
+@pyimport matplotlib.patheffects as pe
 
 path = dirname(@__FILE__)
-figure(1, figsize=(15, 5)); clf()
-
-# Create the source track panel
+figure(1, figsize=(12, 4)); clf()
 
 sources = Dict("Cyg A" => Direction(dir"J2000", "19h59m28.35663s", "+40d44m02.0970s"),
                "Cas A" => Direction(dir"J2000", "23h23m24.000s", "+58d48m54.00s"),
@@ -17,18 +18,17 @@ sources = Dict("Cyg A" => Direction(dir"J2000", "19h59m28.35663s", "+40d44m02.09
                "3C 353" => Direction(dir"J2000", "17h20m28.147s", "-00d58m47.12s"))
 
 ovro_lwa = Position(pos"ITRF", -2.40927462614919e6, -4.477838733582964e6, 3.839370728766106e6)
-
 times = linspace(4.994049600941745e9, 4.994150416022397e9, 7756)
 
-subplot(1, 3, 1)
+tracks = Dict{String, Tuple{Vector{Float64}, Vector{Float64}}}()
 frame = ReferenceFrame()
-set!(frame, ovro_lwa)
+Measures.set!(frame, ovro_lwa)
 for name in keys(sources)
     direction = sources[name]
     l = Float64[]
     m = Float64[]
     for t in times
-        set!(frame, Epoch(epoch"UTC", t*seconds))
+        Measures.set!(frame, Epoch(epoch"UTC", t*seconds))
         azel = measure(frame, direction, dir"AZEL")
         az = longitude(azel)
         el =  latitude(azel)
@@ -40,64 +40,77 @@ for name in keys(sources)
             push!(m, NaN)
         end
     end
-    mmin = minimum(m[.!isnan.(m)])
-    if name == "3C 353"
-        annotate(name, xy=(0, mmin+0.01), horizontalalignment="center",
-                 fontsize=12)
-    else
-        annotate(name, xy=(0, mmin+0.02), horizontalalignment="center",
-                 fontsize=12)
-    end
-    plot(l, m, "k-")
+    tracks[name] = (l, m)
 end
[…]

### 2017-09-04 figures/flux-scale/fetch.sh
add error bars to the flux scale plot

@@ -1,9 +1,4 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-wiener-filtered.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-cyga-peeled.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-vira-peeled.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-hyaa-peeled.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-perb-peeled.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/source-fluxes-map-3c353-peeled.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spectra.jld .
 

### 2017-09-04 figures/flux-scale/make.jl

@@ -4,66 +4,64 @@ using JLD, PyPlot
 using CasaCore.Measures
 
 path = dirname(@__FILE__)
-close("all")
 
 frequencies = [3.6528e7, 4.176e7, 4.6992e7, 5.2224e7, 5.7456e7, 6.2688e7, 6.792e7, 7.3152e7]
-exceptions = ("Cyg A", "Vir A", "Hya A", "Per B", "3C 353")
-cutoff = frequencies .> 50e6 # Perley fluxes only valid above 50 MHz
+model_frequencies = linspace(10e6, 100e6, 201)
 
-calibrators, measured_fluxes, perley_fluxes, scaife_fluxes, baars_fluxes =
-    load(joinpath(path, "source-fluxes-map-wiener-filtered.jld"),
-         "calibrators", "measured_fluxes", "perley_fluxes", "scaife_fluxes", "baars_fluxes")
+everything, odd, even, baars, perley, scaife =
+    load(joinpath(path, "spectra.jld"),
+         "everything", "odd", "even", "baars", "perley", "scaife")
+
 
 # manually spell this out so that we can pick the order of the plots
-#names = collect(keys(calibrators))
 names = ("Cyg A", "Hya A", "Lyn A", "Per B", "Vir A", "3C 48", "3C 147", "3C 286", "3C 295",
          "3C 353", "3C 380")
 
-figure(1, figsize=(10, 10)); clf()
+figure(1, figsize=(12, 10)); clf()
 for (idx, name) in enumerate(names)
-    direction = calibrators[name]
-    lower = lowercase(replace(name, " ", ""))
-    if name in exceptions
-        temp = load(joinpath(path, "source-fluxes-map-$lower-peeled.jld"), "measured_fluxes")
-        measured = temp[name]
-    else
-        measured = measured_fluxes[name]
-    end
+    μ = everything[name]
+    σ = sqrt.(0.5*(abs2.(odd[name]-μ) + abs2.(even[name]-μ)))
+    max_value = maximum(μ)
 
     subplot(4, 3, idx)
-    gca()[:tick_params](axis="both", which="major", labelsize=14)
+    gca()[:tick_params](axis="both", which="major", labelsize=12)
+    errorbar(frequencies/1e6, μ, yerr=σ, fmt="k.", zorder=3)
 
-    max_value = maximum(measured)
-    plot(frequencies/1e6, measured, "ko", zorder=3)
-    if name in keys(perley_fluxes)
[…]

### 2017-09-05 figures/channel-maps/fetch.sh
update the channel maps figure and make them larger

@@ -1,11 +1,34 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw06/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw08/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw12/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw16/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-odd-restored-registered-rainy.jld spw04-odd.jld
[…]

### 2017-09-05 figures/channel-maps/make.jl

@@ -4,26 +4,38 @@ using JLD, PyPlot, PyCall
 
 unshift!(PyVector(pyimport("sys")["path"]), "")
 @pyimport my_log_scale as mls
-close("all")
+@pyimport mpl_toolkits.axes_grid1 as tk
 
 path = dirname(@__FILE__)
 
-figure(1, figsize=(10, 8)); clf()
-for (idx, spw) in enumerate(4:2:18)
-    str = @sprintf("spw%02d", spw)
-    filename = "$str-glamour-shot-map-wiener-filtered-rainy-2048-galactic"
-    img, ν = load(joinpath(path, filename*".jld"), "image", "frequency")
+function decide_on_color_scale(img)
+    pixels = vec(img)
+    pixels = pixels[pixels .!= 0]
+    sort!(pixels)
+    N = length(pixels)
+    min = pixels[round(Int, 0.00001N+1)]
+    max = pixels[round(Int, 0.999N+1)]
+    min, max, (max-min)/10
+end
 
-    max = maximum(img)/5
-    min = minimum(img)
-    base = max - min
-    
-    subplot(4, 2, idx)
+for (idx, spw) in enumerate(4:2:18)
+    figure(idx, figsize=(12, 5)); clf()
+
+    str = @sprintf("spw%02d", spw)
+    img, ν   = load(joinpath(path, "$str.jld"), "image", "frequency")
+    img_odd  = load(joinpath(path, "$str-odd.jld"),  "image")
+    img_even = load(joinpath(path, "$str-even.jld"), "image")
+
+    #variance = 0.5 .* ((img_odd - img).^2 .+ (img_even .- img).^2)
+    #standard_deviation = sqrt.(variance)
+
     θ = linspace(0, 2π, 512)
     x = 2cos.(θ)
     y = sin.(θ)
+
     ellipse = plt[:Polygon]([x y], alpha=0)
     gca()[:add_patch](ellipse)
+    min, max, base = decide_on_color_scale(img)
     imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
            norm = mls.MyLogNormalize(min, max, base),
            extent=(-2, 2, -1, 1),
@@ -33,19 +45,42 @@ for (idx, spw) in enumerate(4:2:18)
     gca()[:set_aspect]("equal")
     gca()[:get_xaxis]()[:set_visible](false)
     gca()[:get_yaxis]()[:set_visible](false)
[…]

### 2017-09-05 figures/channel-maps/my_log_scale.py

@@ -10,7 +10,10 @@ class MyLogNormalize(colors.Normalize):
 
     def __call__(self, value, clip=None):
         base = self.base
-        out = log10(value - self.vmin + base) - log10(base)
-        out = out / (log10(self.vmax - self.vmin + base) - log10(base))
+        value = maximum(value, self.vmin)
+        value = minimum(value, self.vmax)
+        numerator   = log10(    value - self.vmin + base) - log10(base)
+        denominator = log10(self.vmax - self.vmin + base) - log10(base)
+        out = numerator / denominator
         return np.ma.masked_array(out)
 

### 2017-09-05 paper.tex
commit channel maps and latex updates

--- 2017-08-17 paper.tex
@@
 
-Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
-universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
-2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
-intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
-interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
-scattering, absorption, or additional emission can perturb or corrupt the thermal CMB spectrum. In
-order to measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free
-emission, thermal dust emission) are a nuisance and careful modeling and removal of these components
-is essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.
-
-However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
-Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
-discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering in the IGM
-attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
-Reionization (EoR) of $z_r = 8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
-Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
-new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
-combined with X-ray measurements \citep{2006ApJ...647...25B}. The kinetic Sunyaev-Zel'dovich effect
-has been used to constrain the duration of reionization $\Delta z_r \le 4.4$
-\citep{2012ApJ...756...65Z}.
+\todo{this entire section needs a rewrite, it is way too rambling}
+
+%Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
+%universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
+%2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
+%intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
+%interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
+%scattering, absorption, or additional emission can perturb or corrupt the thermal CMB spectrum. In
+%order to measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free
+%emission, thermal dust emission) are a nuisance and careful modeling and removal of these components
+%is essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.
+%
+%However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
+%Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
+%discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering in the IGM
+%attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
+%Reionization (EoR) of $z_r = 8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
+%Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
+%new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
+%combined with X-ray measurements \citep{2006ApJ...647...25B}. The kinetic Sunyaev-Zel'dovich effect
+%has been used to constrain the duration of reionization $\Delta z_r \le 4.4$
+%\citep{2012ApJ...756...65Z}.
 
@@
 \begin{figure}[t]
-    \plotone{figures/lcurve/lcurve}
+    \includegraphics[width=\columnwidth]{figures/lcurve/lcurve}
     \caption{
@@
     \Function{CLEAN}{$\b a$}
-    \Let{$\b M$}{$\b B^*\b B^*$}
-    \Let{$\b U$}{${\rm chol}(\b B)$} \Comment{Cholesky decomposition}
+    \Let{$\b M$}{$\b B^*\b B$}
+    \Let{$\b U$}{${\rm chol}(\b M + \varepsilon\b I)$} \Comment{Cholesky decomposition}
     \While{noise in map $>$ threshold}
@@
 
-\begin{figure*}[t]
-    \includegraphics[width=\textwidth]{figures/psf/psf}
+\begin{figure}[t]
+    \includegraphics[width=\columnwidth]{figures/antenna-layout/antenna-layout}
     \caption{
-        \textbf{(left panel)}
         This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
@@
         antennas equipped with noise-switched front ends.
-        \textbf{(middle panel)}
+    }
+    \label{fig:antenna-layout}
+\end{figure}
+
+\begin{figure*}[t]
+    \includegraphics[width=\textwidth]{figures/psf/psf}
+    \caption{
+        \textit{(left panel)}
+        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
+        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
+        antennas equipped with noise-switched front ends.
+        \textit{(middle panel)}
         The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
         declination of $+45^\circ$ and frequency of $36.528$ MHz.
-        \textbf{(right panel)}
+        \textit{(right panel)}
         The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
@@
 
-\subsection{The Rainy Day Dataset}
-
 The dataset used in this paper spans 28 consecutive hours beginning at 2017-02-17 12:00:00 UTC time.
-This time was chosen based on the fact that it was raining at OVRO and rain tends to improve the
-low-frequency RFI environment considerably. During this time the OVRO-LWA operated as a
-zenith-pointing drift scanning interferometer.  The correlator dump time was selected to be 13
-seconds such that the correlator output evenly divides a sidereal day.
-
-The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
-$>-30$ nT during the entirety of the observing period.\footnote{
-    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
-    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}).
-}
-Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
-$\text{Dst} < -30$ nT. Therefore there were no geomagnetic storms during the time of these
-observations.
+During this time the OVRO-LWA operated as a zenith-pointing drift scanning interferometer.  The
+correlator dump time was selected to be 13 seconds such that the correlator output evenly divides a
+sidereal day.
 
@@
 \begin{figure*}[t]
-    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
+    \includegraphics[width=\textwidth]{figures/beam/beam}
     \caption{
-        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
+        \textit{(left panel)}
+        The tracks traced through the sky by the 8 brightest point sources visible to the
         OVRO-LWA.
-        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
+        \textit{(middle panel)}
+        The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
+        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
+        \textit{(right panel)}
+        The amplitude of the OVRO-LWA beam at 73.152 MHz as a result of the beam model
         fit using Zernike polynomials and the symmetry assumptions outlined in the text.
@@
 model at 36.528 MHz. This process is repeated for each frequency channel.
+
+\subsection{Ionospheric Conditions}
+
+\begin{figure}[t]
+    \includegraphics[width=\columnwidth]{figures/vtec/vtec}
+    \caption{
+        The median vertical TEC within 200 km of OVRO during the time of the observation. The gray
+        shaded regions indicate times outside of the observing period. The gray vertical lines
+        indicate sunrise and sunset (as labeled).
+    }
+    \label{fig:vtec}
+\end{figure}
+
+\begin{figure*}[t]
+    \includegraphics[width=\textwidth]{figures/scintillation-refraction/scintillation-refraction}
+    \caption{
+        Light curves for Cyg A and Cas A.
+    }
+    \label{fig:scintillation}
+\end{figure*}
+
+The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
+$>-30$ nT during the entirety of the observing period.\footnote{
+    The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
+    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}). Accessed 2017-07-25.
+}
+Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
+$\text{Dst} < -30$ nT. Stronger geomagnetic storms have $\text{Dst} \ll -30$ nT.
+
+Figure~\ref{fig:vtec} shows the median vertical total electron content (TEC) above OVRO measured
+with the GIM \todo{citation}. The median is computed over all GPS measurements within 200 km of the
+observatory. Over the observing period the TEC smoothly varies from 20 TECU at midday to 5 TECU
+during the night. However, this measurement is sensitive to large scale fluctuations in the
+ionosphere and doesn't capture small scale fluctuations.
 
@@
     \centering
-    \begin{tabular}{cccccccccc}
+    \begin{tabular}{ccccccccc}
         \hline
@@
             \multicolumn2c{\tbf{Thermal Noise}} &&
-            \multicolumn2c{\tbf{Spherical Harmonics}} &
-            \tbf{Singular Values} \\
+            \multicolumn2c{\tbf{Singular Values}} \\
         \cline{5-6}
@@
             K & Jy &&
-            $l=0$ & $m=0$ &
-            fraction $>\sqrt{\varepsilon}$ \\
+            fraction $>\sqrt{\varepsilon}$ &
+            fraction $>10\sqrt{\varepsilon}$ \\
         \hline
-        1 & 36.528 & 0.024 & 16.2 & 372.8 & & & no & yes \\
-        2 & 41.760 & 0.024 & 14.7 & 321.2 & & & no & yes \\
-        3 & 46.992 & 0.024 & 14.2 & 247.0 & & & no & no \\
-        4 & 52.224 & 0.024 & 13.6 & 205.7 & & & no & no \\
-        5 & 57.456 & 0.024 & 13.5 & 167.7 & & & no & no \\
-        6 & 62.688 & 0.024 & 13.5 & 137.6 & & & no & no \\
-        7 & 67.920 & 0.024 & 13.5 & 114.9 & & & no & no \\
-        8 & 73.152 & 0.024 & 13.7 &  93.4 & & & no & no \\
+        1 & 36.528 & 0.024 &  &  & & & \\
+        2 & 41.760 & 0.024 &  &  & & & \\
+        3 & 46.992 & 0.024 &  &  & & & \\
+        4 & 52.224 & 0.024 &  &  & & & \\
+        5 & 57.456 & 0.024 &  &  & & & \\
+        6 & 62.688 & 0.024 &  &  & & & \\
+        7 & 67.920 & 0.024 &  &  & & & \\
+        8 & 73.152 & 0.024 &  &  & & & \\
         \hline \hline
@@
 
-\begin{figure*}[t]
-    \includegraphics[width=\textwidth]{figures/channel-maps/channel-maps}
+\begin{figure*}[p]
+    \centering
+    \begin{tabular}{c}
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw04} \\
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw06} \\
+    \end{tabular}
     \caption{
-        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
-        and $m$-mode analysis imaging. The properties of each map are summarized in
-        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
-        described in the text, 8 bright sources have been subtracted. The small blank region near
-        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
-        time of the observations.
+        channel maps r kewl
     }
@@
 
+\addtocounter{figure}{-1}
 \begin{figure*}[p]
-    \gridline{
-        \fig{figures/jackknife-maps/4.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/jackknife-maps/6.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/jackknife-maps/8.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/jackknife-maps/10.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/jackknife-maps/12.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/jackknife-maps/14.pdf}
-            {0.48\textwidth}{}
-    }
-    \gridline{
-        \fig{figures/jackknife-maps/16.pdf}
-            {0.48\textwidth}{}
-        \fig{figures/jackknife-maps/18.pdf}
-            {0.48\textwidth}{}
-    }
+    \centering
+    \begin{tabular}{c}
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw08} \\
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw10} \\
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw12} \\
+    \end{tabular}
     \caption{
-        The jackknife estimated standard deviation corresponding to the maps presented in
-        Figure~\ref{fig:channel-maps}. The color scale is logarithmic and has units of Kelvin.
-    }
-    \label{fig:jackknife-maps}
+        continued
+    }
 \end{figure*}
+
+\addtocounter{figure}{-1}
+\begin{figure*}[p]
+    \centering
+    \begin{tabular}{c}
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw14} \\
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw16} \\
+        \includegraphics[height=0.32\textheight]{figures/channel-maps/spw18} \\
+    \end{tabular}
+    \caption{
+        continued
+    }
+\end{figure*}
+
+%\begin{figure*}[t]
+%    \includegraphics[width=\textwidth]{figures/channel-maps/channel-maps}
+%    \caption{
+%        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
+%        and $m$-mode analysis imaging. The properties of each map are summarized in
+%        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
+%        described in the text, 8 bright sources have been subtracted. The small blank region near
+%        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
+%        time of the observations.
+%    }
+%    \label{fig:channel-maps}
+%\end{figure*}
+%
+%\begin{figure*}[p]
+%    \gridline{
+%        \fig{figures/jackknife-maps/4.pdf}
+%            {0.48\textwidth}{}
+%        \fig{figures/jackknife-maps/6.pdf}
+%            {0.48\textwidth}{}
+%    }
+%    \gridline{
+%        \fig{figures/jackknife-maps/8.pdf}
+%            {0.48\textwidth}{}
+%        \fig{figures/jackknife-maps/10.pdf}
+%            {0.48\textwidth}{}
+%    }
+%    \gridline{
+%        \fig{figures/jackknife-maps/12.pdf}
+%            {0.48\textwidth}{}
+%        \fig{figures/jackknife-maps/14.pdf}
+%            {0.48\textwidth}{}
+%    }
+%    \gridline{
+%        \fig{figures/jackknife-maps/16.pdf}
+%            {0.48\textwidth}{}
+%        \fig{figures/jackknife-maps/18.pdf}
+%            {0.48\textwidth}{}
+%    }
+%    \caption{
+%        The jackknife estimated standard deviation corresponding to the maps presented in
+%        Figure~\ref{fig:channel-maps}. The color scale is logarithmic and has units of Kelvin.
+%    }
+%    \label{fig:jackknife-maps}
+%\end{figure*}
 

### 2017-09-05 figures/ionospheric-simulations/fetch.sh
add plots illustrating the effect of the ionosphere

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/base-image.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/scintillation-flux.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/refraction-position.jld .
+

### 2017-09-05 figures/ionospheric-simulations/make.jl

@@ -1,0 +1,71 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot, PyCall
+
+@pyimport mpl_toolkits.axes_grid1 as tk
+
+path = dirname(@__FILE__)
+figure(1, figsize=(12, 4)); clf()
+
+max = 1.0
+min = 0.0
+
+function plot_image(filename)
+    global max, min
+    img = load(joinpath(path, filename*".jld"), "img")
+    if filename == "base-image"
+        max = maximum(img)
+        img ./= max
+        min = minimum(img)
+    else
+        img ./= max
+    end
+    img = img[51:151, 51:151]
+    gca()[:tick_params](axis="both", which="major", labelsize=12)
+    gca()[:set_aspect]("equal")
+    out = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
+                 vmin=-0.1, vmax=0.3,
+                 extent=(150, -150, -150, 150))
+    xlim(140, -140)
+    ylim(-140, 140)
+    out
+end
+
+function label(string)
+    text(0.95, 0.95, string,
+         transform=gca()[:transAxes], fontsize=16, fontweight="bold",
+         horizontalalignment="right", verticalalignment="top",
+         color="white", zorder=2)
+end
+
+ax = gca()
+divider = tk.make_axes_locatable(ax)
+
+_im = plot_image("base-image")
+label("no ionosphere")
+xlabel("ΔRA (arcmin)", fontsize=12)
+ylabel("Δdec (arcmin)", fontsize=12)
+
+_ax = divider[:append_axes]("right", size="100%", pad=0.10)
+plot_image("scintillation-flux")
+label("scintillation only")
+xlabel("ΔRA (arcmin)", fontsize=12)
+plt[:setp](gca()[:get_yticklabels](), visible=false)
+
+_ax = divider[:append_axes]("right", size="100%", pad=0.10)
+plot_image("refraction-position")
+label("refraction only")
+xlabel("ΔRA (arcmin)", fontsize=12)
+plt[:setp](gca()[:get_yticklabels](), visible=false)
+
+cax = divider[:append_axes]("right", size="5%", pad=0.10)
+cbar = colorbar(_im, cax=cax)
+cbar[:ax][:tick_params](labelsize=12)
+cbar[:set_label]("normalized amplitude", fontsize=12, rotation=270)
+cbar[:ax][:get_yaxis]()[:set_label_coords](5.5, 0.5)
[…]

### 2017-09-05 figures/vtec/fetch.sh
add vtec plot

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/tmp/ionosphere.jld .
+

### 2017-09-05 figures/vtec/make.jl

@@ -1,0 +1,65 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot, CasaCore.Measures
+
+path = dirname(@__FILE__)
+figure(1, figsize=(6, 4)); clf()
+
+utc, vobs, north_vobs, south_vobs = load(joinpath(path, "ionosphere.jld"), "utc", "vobs",
+                                         "north_vobs", "south_vobs")
+utc -= 12
+
+# find sunrise and sunset
+sun = Direction(dir"SUN")
+ovro_lwa = Position(pos"ITRF", -2.40927462614919e6, -4.477838733582964e6, 3.839370728766106e6)
+times = linspace(4.994049600941745e9, 4.994150416022397e9, 7756)
+
+frame = ReferenceFrame()
+set!(frame, ovro_lwa)
+elevation = zeros(length(times))
+for idx = 1:length(times)
+    set!(frame, Epoch(epoch"UTC", times[idx]*seconds))
+    azel = measure(frame, sun, dir"AZEL")
+    elevation[idx] = latitude(azel)
+end
+sunrise = Float64[]
+sunset = Float64[]
+for idx = 1:length(times)-1
+    if elevation[idx] ≤ 0 && elevation[idx+1] > 0
+        push!(sunrise, (times[idx]-times[1])/3600)
+    elseif elevation[idx] > 0 && elevation[idx+1] ≤ 0
+    push!(sunset, (times[idx]-times[1])/3600)
+    end
+end
+
+plot(utc, vobs, "k-", label="all receivers")
+#plot(utc, north_vobs, "-", c="C0", label="north of OVRO")
+#plot(utc, south_vobs, "-", c="C1", label="south of OVRO")
+axvspan(minimum(utc), 0, alpha=0.15, color="black")
+axvspan(28, maximum(utc), 0, alpha=0.15, color="black")
+for t in sunrise
+    axvline(t, lw=1, color="0.75", zorder=0)
+    annotate("sunrise", xy=(t, 0.3), fontsize=12,
+             horizontalalignment="right",
+             verticalalignment="bottom",
+             rotation=90)
+end
+for t in sunset
+    axvline(t, lw=1, color="0.75", zorder=0)
+    annotate("sunset", xy=(t, 0.3), fontsize=12,
+             horizontalalignment="right",
+             verticalalignment="bottom",
+             rotation=90)
+end
+
+gca()[:tick_params](axis="both", which="major", labelsize=13)
[…]

### 2017-09-06 figures/stripe-maps/make.jl
update the terrestrial rfi figures

@@ -1,41 +1,0 @@
-using JLD, PyPlot, PyCall
-
-unshift!(PyVector(pyimport("sys")["path"]), "")
-@pyimport my_log_scale as mls
-
-path = dirname(@__FILE__)
-close("all")
-
-function plot(filename1, filename2)
-    img1, ν = load(joinpath(path, filename1*".jld"), "image", "frequency")
-    img2 = load(joinpath(path, filename2*".jld"), "image")
-    img = img1-img2
-
-    max = maximum(img)
-    min = minimum(img)
-    base = max - min
-    
-    figure(figsize=(12,8)); clf()
-    gca()[:tick_params](axis="both", which="major", labelsize=16)
-    θ = linspace(0, 2π, 512)
-    x = 2cos.(θ)
-    y = sin.(θ)
-    ellipse = plt[:Polygon]([x y], alpha=0)
-    gca()[:add_patch](ellipse)
-    imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
-           extent=(-2, 2, -1, 1),
-           clip_path=ellipse)
-    gca()[:set_aspect]("equal")
-    title(@sprintf("%.3f MHz", ν/1e6), fontsize=16)
-    cbar = colorbar(fraction=0.02)
-    cbar[:ax][:tick_params](labelsize=16)
-    axis("off")
-    tight_layout()
-
-    savefig(joinpath(path, filename1*".pdf"),
-            bbox_inches="tight", pad_inches=0, transparent=true)
-end
-
-plot("spw14-glamour-shot-map-rfi-restored-peeled-rainy-2048-galactic",
-     "spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic")
-

### 2017-09-06 figures/stripe-maps/my_log_scale.py

@@ -1,16 +1,0 @@
-from pylab import *
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.colors as colors
-
-class MyLogNormalize(colors.Normalize):
-    def __init__(self, vmin=None, vmax=None, base=None, clip=False):
-        self.base = base
-        colors.Normalize.__init__(self, vmin, vmax, clip)
-
-    def __call__(self, value, clip=None):
-        base = self.base
-        out = log10(value - self.vmin + base) - log10(base)
-        out = out / (log10(self.vmax - self.vmin + base) - log10(base))
-        return np.ma.masked_array(out)
-

### 2017-09-06 figures/terrestrial-interference/fetch.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/map-rfi-subtracted-peeled-rainy-2048-galactic.fits .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/map-rfi-restored-peeled-rainy-2048-galactic.fits .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/tmp/fitrfi-rfi-restored-peeled-rainy-*.fits .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/tmp/fitrfi-test-start-rfi-restored-peeled-rainy.fits .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw14/tmp/fitrfi-test-finish-rfi-restored-peeled-rainy.fits .
+

### 2017-09-06 figures/terrestrial-interference/make.jl

@@ -1,0 +1,166 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot, PyCall, FITSIO, WCS, LibHealpix
+
+@pyimport mpl_toolkits.axes_grid1 as tk
+@pyimport matplotlib.gridspec as gridspec
+
+path = dirname(@__FILE__)
+
+figure(1, figsize=(12, 5)); clf()
+
+function decide_on_color_scale(img, f=0.9)
+    img ./= maximum(img)
+    pixels = vec(img)
+    pixels = pixels[pixels .!= 0]
+    pixels = abs.(pixels)
+    sort!(pixels)
+    N = length(pixels)
+    scale = pixels[round(Int, f*N+1)]
+    scale
+end
+
+map1 = readhealpix(joinpath(path, "map-rfi-restored-peeled-rainy-2048-galactic.fits"))
+map2 = readhealpix(joinpath(path, "map-rfi-subtracted-peeled-rainy-2048-galactic.fits"))
+δ = map2-map1
+img = mollweide(δ, (2048, 4096))
+scale = decide_on_color_scale(img)
+
+θ = linspace(0, 2π, 512)
+x = 2cos.(θ)
+y = sin.(θ)
+
+ellipse = plt[:Polygon]([x y], alpha=0)
+gca()[:add_patch](ellipse)
+imshow(img, interpolation="nearest", cmap=get_cmap("magma"),
+       vmin=-scale, vmax=+scale,
+       extent=(-2, 2, -1, 1),
+       clip_path=ellipse, zorder=10)
+xlim(-2, 2)
+ylim(-1, 1)
+gca()[:set_aspect]("equal")
+gca()[:get_xaxis]()[:set_visible](false)
+gca()[:get_yaxis]()[:set_visible](false)
+axis("off")
+
+#txt = text(0.01, 0.98, "(d)",
+#           transform=gca()[:transAxes], fontsize=14, fontweight="bold",
+#           horizontalalignment="left", verticalalignment="top",
+#           color="black", zorder=2)
+
+cbar = colorbar()
+cbar[:ax][:tick_params](labelsize=12)
+cbar[:set_label]("normalized amplitude", fontsize=12, rotation=270)
+cbar[:ax][:get_yaxis]()[:set_label_coords](4.5, 0.5)
+
+tight_layout()
+
+savefig(joinpath(path, "rings.pdf"),
+        bbox_inches="tight", pad_inches=0, transparent=true)
+
+figure(2, figsize=(12, 4)); clf()
+
[…]

### 2017-09-13 figures/spectral-index/fetch.sh
figure for the internal spectral index

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/internal-spectral-index-adaptive.jld .
+#scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/better-spectral-index.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/glamour-map-restored-registered-rainy.jld spw10.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/glamour-map-restored-registered-rainy.jld spw18.jld
+

### 2017-09-13 figures/spectral-index/make.jl

@@ -1,0 +1,132 @@
+#!/usr/bin/env julia
+
+using JLD, LibHealpix, PyPlot, PyCall
+using Colors, PerceptualColourMaps
+
+@pyimport mpl_toolkits.axes_grid1 as tk
+
+path = dirname(@__FILE__)
+
+function go()
+    slope, jackknives, residual = load(joinpath(path, "internal-spectral-index-adaptive.jld"),
+                                       "slope", "jackknives", "delta_residual")
+
+    ν1 = 36.528
+    ν2 = 52.224
+    ν3 = 73.152
+    brightness1 = load(joinpath(path, "spw04.jld"), "image")
+    brightness2 = load(joinpath(path, "spw10.jld"), "image")
+    brightness3 = load(joinpath(path, "spw18.jld"), "image")
+    
+    cmap_samples = cmap("D4", reverse=true)
+    
+    img = zeros(size(brightness1)..., 3)
+    for y = 1:size(img, 2), x = 1:size(img, 1)
+        img[x, y, 1] = brightness1[x, y] * (ν1/ν3)^2.5
+        img[x, y, 2] = brightness2[x, y] * (ν2/ν3)^2.5
+        img[x, y, 3] = brightness3[x, y]
+    end
+
+    figure(1, figsize=(12, 5)); clf()
+
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+
+    function decide_on_color_scale(img)
+        pixels = vec(img)
+        pixels = pixels[pixels .!= 0]
+        sort!(pixels)
+        N = length(pixels)
+        min = pixels[round(Int, 0.00001N+1)]
+        max = pixels[round(Int, 0.999N+1)]
+        min, max, (max-min)/10
+    end
+
+    img_min, img_max, img_base = decide_on_color_scale(img)
+    @show img_min img_max img_base
+    @show minimum(img) maximum(img)
+    img = clamp.(img, img_min, img_max)
+    img = (log10.(img - img_min + img_base) - log10.(img_base)) ./
+            (log10.(img_max - img_min + img_base) - log10.(img_base))
+    imshow(img, interpolation="nearest",
+           extent=(-2, 2, -1, 1),
+           clip_path=ellipse)
+
[…]

### 2017-09-14 paper.tex
lots and lots of changes, I think I have a second draft now

@@
 
-\usepackage{algorithm}
 \usepackage[noend]{algpseudocode}
@@
 \algrenewcommand\algorithmicensure{\textbf{Postcondition:}}
+
+\usepackage{tablefootnote}
 
@@
 
-\watermark{draft}
+%\watermark{draft}
 
@@
 
-%\author{Marin M. Anderson}
-%\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
-%
-%\author{Ryan Monroe}
-%\affiliation{Department of Electrical Engineering, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
+\author{Marin M. Anderson}
+\astrocaltech
+
+\author{Ryan M. Monroe}
+\astrocaltech
 
@@
 
+\author{Other People}
+\affiliation{
+    At some institution
+}
+
 %\author{Lincoln Greenhill}
@@
 
+\correspondingauthor{Michael W. Eastwood}
+\email{mweastwood@astro.caltech.edu}
+
 \begin{abstract}
-    I present all-sky maps of the sky from the Owens Valley Long Wavelength Array.
-    These maps are created from the application of $m$-mode analysis.
+    A host of new low-frequency radio telescopes are attempting to detect the 21~cm transition at
+    cosmological distances. These measurements hold promise to directly probe star and galaxy
+    formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range they can
+    achieve against foreground sources of low-frequency radio emission. Consequently, there is a
+    growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for use in
+    foreground modeling and removal.  We use the Owens Valley Long Wavelength Array (OVRO-LWA) to
+    generate 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and
+    at frequencies evenly spaced between 36.528 MHz and 73.152 MHz.  Existing full-sky maps at these
+    frequencies have angular resolutions $\ge 2^\circ$ and so these maps are a 10-fold improvement
+    in angular resolution.  The thermal noise in each map is $\sim$800 mJy/beam.  These maps are
+    generated from the application of a new widefield imaging technique for drift-scanning
+    interferometers, Tikhonov-regularized $m$-mode analysis imaging. This algorithm constructs
+    images of the entire sky in a single synthesis imaging step with exact treatment of widefield
+    effects. We additionally introduce this technique and describe how CLEAN can be adapted to
+    deconvolve maps generated by $m$-mode analysis imaging.
 \end{abstract}
@@
 
-\todo{this entire section needs a rewrite, it is way too rambling}
-
-%Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
-%universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
-%2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
-%intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
-%interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
-%scattering, absorption, or additional emission can perturb or corrupt the thermal CMB spectrum. In
-%order to measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free
-%emission, thermal dust emission) are a nuisance and careful modeling and removal of these components
-%is essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.
-%
-%However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
-%Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
-%discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering in the IGM
-%attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
-%Reionization (EoR) of $z_r = 8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
-%Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
-%new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
-%combined with X-ray measurements \citep{2006ApJ...647...25B}. The kinetic Sunyaev-Zel'dovich effect
-%has been used to constrain the duration of reionization $\Delta z_r \le 4.4$
-%\citep{2012ApJ...756...65Z}.
-
-At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
+At redshifts $20 \gtrsim z \gtrsim 7$ the 21~cm hyperfine structure line of neutral hydrogen is
 expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
@@
 
-Current 21 cm cosmology experiments can be broadly separated into two classes: global experiments
-that are aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition
+Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
+that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
 after averaging over the entire sky, and power spectrum experiments that incorporate angular
-information to attempt to measure the 3D spatial power spectrum of cosmological 21 cm perturbations.
+information to attempt to measure the 3D spatial power spectrum of cosmological 21~cm perturbations.
 Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
@@
 \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
-\citep{2016ApJ...833..102B}.
+\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.
 
 Just as for CMB experiments, foreground removal or suppression is an essential component of both
-classes of 21 cm cosmology experiments. The brightness temperature of the galactic synchrotron
+classes of 21~cm cosmology experiments. The brightness temperature of the galactic synchrotron
 emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
@@
 background of radio sources.  Ideally a foreground removal strategy should be informed by the
-measured spatial structure and frequency spectrum of all foreground components.  However this
-possibility is limited by the availability of suitable high-fidelity low-frequency sky maps on
-angular scales ranging from tens of degrees to arcminutes.
-
-The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is a data-driven
-interpolation of various maps between 10 MHz and 100 GHz. However the majority of information
-contained in the GSM is derived at higher frequencies where the majority of the input maps are
-located.  Below 408 MHz, the interpolation is largely driven by the Haslam 408 MHz map
-\citep{1981A&A...100..209H, 1982A&AS...47....1H}.  At lower frequencies, free-free absorption and
-synchrotron self-absorption becomes increasingly important and hence spectral indices derived at
-higher frequencies need corrections at lower frequencies.
+measured spatial structure and frequency spectrum of all foreground components.  This possibility is
+limited by the availability of suitable high-fidelity low-frequency sky maps on angular scales
+ranging from tens of degrees to arcminutes.
+
+The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is currently the most
+commonly used foreground model. The GSM is a data-driven interpolation of various maps between 10
+MHz and 100 GHz. However the majority of information contained in the GSM is derived at frequencies
+$>1.4$ GHz where the majority of the modern, high-fidelity input maps are located.  Below 408 MHz,
+the GSM is largely driven by the Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H,
+2015MNRAS.451.4311R}. As a consequence, the GSM is not a faithful representation of the sky below
+200 MHz. For instance, \citet{2017MNRAS.469.4537D} report errors of $\pm 50\%$ between the GSM and
+their own maps at 74 MHz. This is largely due to the increasing contribution of free-free absorption
+and modifications to the synchrotron spectral index at low frequencies.
 
@@
 
-In this paper we will present a series of new low-frequency maps of the sky between 36.528 Mhz and
-73.152 Mhz, capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with
-angular resolution of roughly 10'. These maps are generated using $m$-mode analysis imaging -- a new
-imaging technique for transit telescopes.
+This paper presents a series of new low-frequency maps of the sky between 36.528~Mhz and 73.152~Mhz,
+capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with angular
+resolution of $\sim 15$~arcmin. We aim for these maps to inform foreground removal strategies in
+21~cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
+at these frequencies. The maps will be made freely available online at the Legacy Archive for
+Microwave Background Data Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.
+
+The structure of this paper is as follows. In \S\ref{sec:imaging}, we present Tikhonov-regularized
+$m$-mode analysis imaging, a new imaging technique that allows us to image the entire visible sky in
+one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
+describe our observations with the Owens Valley Long Wavelength Array (OVRO-LWA). In
+\S\ref{sec:results} we present the sky maps, and in \S\ref{sec:error} we discuss some of the sources
+of error present in the maps. Finally in \S\ref{sec:compare} the new sky maps are compared against
+other low-frequency sky maps, and in \S\ref{sec:conclusion} we present our conclusions.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{All-Sky Imaging}
+\section{All-Sky Imaging}\label{sec:imaging}
 
@@
 \end{equation}
-Constructing an image from the output of a radio interferometer therefore consists of estimating
-$I_\nu(\hat r)$ given the available measurements $V^{ij}_\nu$.
+Constructing an image from the output of a radio interferometer consists of estimating $I_\nu(\hat
+r)$ given the available measurements $V^{ij}_\nu$.
 
@@
 }
-Therefore it is a very natural operation to compute the Fourier transform of the visibilities with
+Therefore it is a natural operation to compute the Fourier transform of the visibilities with
 respect to sidereal time $\phi\in[0,2\pi)$.
@@
 determined by the minimum baseline length.  When creating the maps presented in this paper, we use
-$l_\text{min} = 0$ and $l_\text{max} = 1000$.
+$l_\text{min} = 0$ and $l_\text{max} = 1000$. %\todo{this choice of lmax restricts resolution at
+%higher frequencies}
 
@@
 other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
-measured and calibrated.
+measured and calibrated. Consequently we set $a_{00}=0$ in our analysis.
 
@@
 
-This trade-off can be analyzed quantitatively by trialing several values of $\varepsilon$ and
+This trade-off can be analyzed quantitatively by trialing several values of $\varepsilon$, and
 computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in
@@
 
-\subsection{CLEAN}
+\subsection{CLEAN}\label{sec:clean}
 
@@
 interpolate the measured visibilities onto the $uv$-plane. In the absence of this interpolation,
-gaps in the interferometer's $uv$-coverage are assumed to be zero, and in the image plane sources
-are convolved with a point spread function (PSF) that is characteristic of the $uv$-coverage.
-Fundamentally, the interferometer's PSF in the dirty images is determined by which modes were
-assumed to be zero in the initial imaging process.
+gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the image plane --
+sources are convolved with a point spread function (PSF) that is characteristic of the
+$uv$-coverage.  Fundamentally, the interferometer's PSF in the dirty images is determined by which
+modes were assumed to be zero in the initial imaging process.
 
@@
 example, sources at low elevations will tend to have an extended PSF along the north-south axis due
-to baseline foreshortening. An example computed PSF is shown in Figure~\ref{fig:psf}.  Adapting
-CLEAN for $m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of
-declinations, or a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.
-
-\todo{cite lincoln's paper on cleaning with a changing psf}
+to baseline foreshortening. Some examples PSFs are shown in Figure~\ref{fig:psf}.  Adapting CLEAN
+for $m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of declinations,
+or a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.
+
+%\citep{2011MNRAS.413..411B} % I think Lincoln wants me to cite this paper
 
@@
 
-\todo{describe blurring to avoid cleaning the diffuse emission}
+%\todo{describe blurring to avoid cleaning the diffuse emission}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Observations}
+\section{Observations}\label{sec:observations}
 
@@
         This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
-        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
-        antennas equipped with noise-switched front ends.
+        within the 200 m diameter core of the array. The 32 triangles are the expansion antennas
+        built in early 2016 in order to increase the longest baseline to $\sim1.5$ km. The 5 crosses
+        are antennas equipped with noise-switched front ends.
     }
@@
     \caption{
-        \textit{(left panel)}
-        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
-        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
-        antennas equipped with noise-switched front ends.
-        \textit{(middle panel)}
-        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
-        declination of $+45^\circ$ and frequency of $36.528$ MHz.
-        \textit{(right panel)}
-        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
-        declination of $+45^\circ$ and frequency of $73.152$ MHz.
+        This figure shows the $m$-mode analysis imaging PSF at $\delta = +45^\circ$ at 3 separate
+        frequencies: 36.528 MHz (left panel), 52.224 MHz (middle panel), and 73.152 MHz (right
+        panel). The PSF is computed by evaluating Equation~\ref{eq:psf}.
     }
@@
 snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
-placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
+placed outside of the core in order to extend the maximum baseline length to $\sim$1.5~km. The final
 5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
 the global sky brightness.  These antennas are used as part of the LEDA experiment
-\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.  The
-left panel of Figure~\ref{fig:psf} is a diagram of the antenna configuration.
+\citep{todo_price_2017} to measure the global signal of 21~cm absorption from the cosmic dawn.
+Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
 
@@
 
-\subsection{Gain Calibration}
+\subsection{Gain Calibration}\label{sec:gaincal}
 
@@
 the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
-online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3+).
-
-Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources in the
+online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
+any later version).
+
+Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
 northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
 is when these sources are at high elevations.  The antenna complex gains are measured from a 22
-minute track of data from when Cyg A and Cas are at high elevations. The gains measured in this way
+minute track of data from when Cyg~A and Cas are at high elevations. The gains measured in this way
 are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
-Cyg A and Cas A. The model flux of Cyg A is set to the \citet{1977A&A....61...99B} spectrum while
-the flux of Cas A is measured from the data itself (using a preliminary calibration).
+Cyg~A and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while
+the flux of Cas~A is measured from the data itself (using a preliminary calibration).  Residual
+errors in the astrometry are corrected post-imaging by registering the images with respect to all
+VLSSr \citep{2014MNRAS.440..327L} sources brighter than 30~Jy. Additional cuts are made to ensure
+that sources aren't too close to each other or other bright sources.
 
@@
 
-\subsection{Primary Beam Measurements}
+\subsection{Primary Beam Measurements}\label{sec:beam}
 
@@
     \caption{
-        \textit{(left panel)}
-        The tracks traced through the sky by the 8 brightest point sources visible to the
-        OVRO-LWA.
-        \textit{(middle panel)}
-        The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
-        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
-        \textit{(right panel)}
-        The amplitude of the OVRO-LWA beam at 73.152 MHz as a result of the beam model
-        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
+        This figure shows the empirical fits to the OVRO-LWA Stokes-I primary beam (the response of
+        the $x$- and $y$-dipoles has been summed) at three frequencies: 36.528 MHz (left panel),
+        52.224 MHz (middle panel), and 73.152 MHz (right panel). The source tracks used to measure
+        the beam model are overlaid. From north to south, these tracks correspond to Cas~A, Cyg~A,
+        Per~B, Tau~A, Vir~A, Her~A, 3C~353, and Hya~A.  The fitting process is described in
+        \S\ref{sec:beam}, and residuals for Cyg~A and Cas~A can be seen in
+        Figure~\ref{fig:scintillation}.
     }
@@
 
-We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
-3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
+We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A, Per~B, and
+3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
 those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
-$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
-zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
-model at 36.528 MHz. This process is repeated for each frequency channel.
+$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$) and the beam amplitude
+at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
+model at several frequencies. This process is repeated for each frequency channel.
 
@@
     \caption{
-        Light curves for Cyg A and Cas A.
+        \textbf{(a, b)} These panels show the measured apparent flux of Cyg~A and Cas~A at 36.528
+        MHz (red points) and 73.152 MHz (blue points) as a function of time over the observing
+        period. The solid black curves show the expected flux computed using the empirical beam
+        model fits. The thermal noise contribution to each point is about 50 Jy. The majority of the
+        scatter is due to ionospheric scintillation.  Cyg~A is occulted by the White Mountains when
+        it is low on the horizon to the east.
+        \textbf{(c, d)} These panels show the measured position offset of Cyg~A and Cas~A relative
+        to their true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue line).
     }
@@
 
-Figure~\ref{fig:vtec} shows the median vertical total electron content (TEC) above OVRO measured
-with the GIM \todo{citation}. The median is computed over all GPS measurements within 200 km of the
-observatory. Over the observing period the TEC smoothly varies from 20 TECU at midday to 5 TECU
-during the night. However, this measurement is sensitive to large scale fluctuations in the
-ionosphere and doesn't capture small scale fluctuations.
+Despite the mild conditions, low frequency interferometric observations are still affected by the
+index of refraction in the ionosphere.  Figure~\ref{fig:vtec} shows the median vertical total
+electron content (TEC) above OVRO measured from GPS \citep{1999JASTP..61.1205I}. The median is
+computed over all GPS measurements within 200 km of the observatory. Over the observing period the
+TEC smoothly varies from 20 TECU at midday to 5 TECU during the night. However, this measurement is
+only sensitive to large scale fluctuations in the ionosphere and doesn't capture small scale
+fluctuations.
+
+Small scale fluctuations are best characterized by source scintillation and refractive offsets.
+Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
+function of time over the entire observing period. Both sources exhibit rapid scintillation on the
+timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
+A to have a measured flux of 30,000 Jy in one integration, and 20,000 Jy in the next. The measured
+position offset of each source is a measurement of the ionospheric phase gradient across the array.
+This varies on slower 10 minute timescales refracting each source by as much as 20 arcmin (at 36.528
+MHz) from their true astronomical positions as waves in the ionosphere pass through the line of
+sight. The impact of these effects on the sky maps is simulated in \S\ref{sec:ionosphere}.
 
@@
 
-%\begin{deluxetable*}{ccccDCCD}
-%    \tablecaption{Resolved source models for Cyg A and Cas A\label{tab:resolved-source-models}}
-%    \tablewidth{0pt}
-%    \tablehead{
-%        \colhead{} & \colhead{} &
-%            \colhead{} & \colhead{} &
-%            \multicolumn2c{Amplitude} &
-%            \colhead{Major FWHM} & \colhead{Minor FWHM} &
-%            \multicolumn2c{Position angle} \\
-%        \colhead{Source} & \colhead{\#} &
-%            \colhead{RA} & \colhead{Dec} &
-%            \multicolumn2c{(relative)} &
-%            \colhead{(arcsec)} & \colhead{(arcsec)} &
-%            \multicolumn2c{(deg)}
-%    }
-%    \decimals
-%    \startdata
-%        Cyg A & 1 & & & 1.0 & 128. & 22. & -74.503 \\
-%              & 2 & & & 0.1477 & 183. & 141. & 43.449 \\[0.2cm]
-%        Cas A & 1 & & & 1.0 & 0. & 0. & 0. \\
-%              & 2 & & & 1.0 & 0. & 0. & 0. \\
-%              & 3 & & & 1.0 & 0. & 0. & 0. \\
-%    \enddata
-%\end{deluxetable*}
-
 Without removing bright sources from the data, sidelobes from bright sources will dominate the
-variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{1977A&A....61...99B}. A
-conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
-\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at least $-45$ dB down
-from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
+variance in the sky maps.  At 74 MHz Cyg~A is a 15,000~Jy source \citep{1977A&A....61...99B}. A
+conservative estimate for the confusion limit at 74 MHz with a 15~arcmin beam is 1000~mJy
+\citep{2014MNRAS.440..327L}. Therefore we require that Cyg~A's sidelobes be at least $-45$~dB down
+from the main lobe to prevent Cyg~A's sidelobes from dominating the variance in the image.
 
@@
 peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
-scintillation and diffraction events on the timescale of a single integration (13 seconds) are
-observed. Therefore the direction dependent calibration changes on these timescales and the we must
-solve for one set of complex gains per source per integration.
-
-The largest angular scale of Cas A is $\sim$8 arcminutes, and the largest angular scale of Cyg A is
-$\sim$2 arcminutes. With a $\sim10$ arcminute resolution, the OVRO-LWA marginally resolves both
-sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
-source model to each source. This is performed by minimizing the variance within an aperture located
-on each source after peeling. By phasing up a large number of integrations before imaging (at least
-1 hour) it is possible to smear out the contribution of the rest of the sky.  We then use NLopt's
-Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until the variance
-within the aperture is minimized.
-
-Armed with resolved source models for both Cyg A and Cas A, these two sources can be peeled from the
-dataset to the required dynamic range.
-
-\todo{slice through Cyg A and Cas A to illustrate the removal process}
-
-\todo{Give a plot with the updated source models}
+scintillation and refractive-offset events on the timescale of a single integration (13 seconds) are
+observed (see Figure~\ref{fig:scintillation}. Therefore the direction dependent calibration changes
+on these timescales and the we must solve for one set of complex gains per source per integration.
+
+The largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale of Cyg~A is
+$\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines, the OVRO-LWA marginally
+resolves both sources. A resolved source model is needed for both sources. We fit a self-consistent
+resolved source model to each source. This is performed by minimizing the variance within an
+aperture located on each source after peeling. By phasing up a large number of integrations before
+imaging (at least 1 hour) it is possible to smear out the contribution of the rest of the sky.  We
+then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until
+the variance within the aperture is minimized.  Armed with resolved source models for both Cyg~A and
+Cas~A, these two sources can be peeled from the dataset to the required dynamic range.
 
@@
 
-Other bright sources including Vir A, Tau A, Her A, Hya A, Per B, and 3C 353 are also removed from
-the visibilities prior to imaging. Because these sources are much fainter than Cyg A and Cas A, we
+Other bright sources namely Vir~A, Tau~A, Her~A, Hya~A, Per~B, and 3C~353 are also removed from
+the visibilities prior to imaging. Because these sources are much fainter than Cyg~A and Cas~A, we
 do not need resolved source models to be able to remove these sources from the visibilities without
@@
 subtracted from the visibilities using the updated position and flux of the source. The brightest of
-these sources (Vir A and Tau A) will be peeled using a direction dependent calibration when they are
+these sources (Vir~A and Tau~A) are peeled using a direction dependent calibration when they are
 at high elevations.
@@
 needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
-Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.  Additionally while most
+Gaussian components to Cyg~A and Cas~A, this is insufficient for the Sun.  Additionally while most
 astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
@@
 gains. The shapelet fitting is performed in the visibility space. Above 55 MHz a model is fit to the
-Sun by minimizing the residuals after peeling (in the same way that models are obtained for Cyg A
-and Cas A). The Sun is then peeled from each integration using direction dependent gains.
+Sun by minimizing the residuals after peeling (in the same way that models are obtained for Cyg~A
+and Cas~A). The Sun is then peeled from each integration using direction dependent gains.
 
@@
 
-The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg A during gain
+The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg~A during gain
 calibration. However gain calibration is also a function of the beam model and the spectrum used for
-Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature and
-\citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
-with calibrated flux measurements from one (just Cyg A) to eleven in total. While the
-\citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
-\citet{2017ApJS..230....7P} flux scale is somewhat more limited because the lowest frequency
-observations come from the VLA 4-band system. As a consequence the \citet{2017ApJS..230....7P} flux
-scale is not valid below 50 MHz.
+Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival date from the
+literature and \citet{2017ApJS..230....7P} (hereafter PB17) using the VLA has expanded the number of
+low-frequency radio sources with calibrated flux measurements from one (just Cyg~A) to eleven in
+total. While the SH12 flux scale is valid between 30 MHz and 300 MHz, the PB17 flux scale is
+somewhat more limited because the lowest frequency observations come from the VLA 4-band system. As
+a consequence the PB17 flux scale is not valid below 50 MHz.
 
@@
 from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
-measurements agree to better than 10\% with the \citet{2012MNRAS.423L..30S} spectra. Below 50 MHz
-there can be substantial departures with respect to the \citet{2017ApJS..230....7P} spectra (for eg.
-3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
-\citet{2012MNRAS.423L..30S} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
-diverge from the truth rapidly below 50 MHz.
-
-%\subsection{Dedistortion}
+measurements agree to between 5 and 10\% with the SH12 spectra. Below 50 MHz there can be
+substantial departures with respect to the extrapolated PB17 spectra (for eg.  3C 286, 3C 295, and
+3C 380), but it is usually the case that we have much better agreement with the SH12 spectra. This
+indicates that the PB17 spectra cannot be extrapolated below 50 MHz.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-
-\begin{table*}[t]
-    \centering
-    \begin{tabular}{ccccccccc}
-        \hline
-        \hline
-        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} &
-            \multicolumn2c{\tbf{Thermal Noise}} &&
-            \multicolumn2c{\tbf{Singular Values}} \\
-        \cline{5-6}
-        \cline{8-9}
-        \tbf{\#} & MHz & MHz & arcmin &
-            K & Jy &&
-            fraction $>\sqrt{\varepsilon}$ &
-            fraction $>10\sqrt{\varepsilon}$ \\
-        \hline
-        1 & 36.528 & 0.024 &  &  & & & \\
-        2 & 41.760 & 0.024 &  &  & & & \\
-        3 & 46.992 & 0.024 &  &  & & & \\
-        4 & 52.224 & 0.024 &  &  & & & \\
-        5 & 57.456 & 0.024 &  &  & & & \\
-        6 & 62.688 & 0.024 &  &  & & & \\
-        7 & 67.920 & 0.024 &  &  & & & \\
-        8 & 73.152 & 0.024 &  &  & & & \\
-        \hline \hline
-    \end{tabular}
-    \caption{Summary of the generated all-sky maps\label{tab:summary}}
-\end{table*}
-
-%\begin{figure*}[p]
-%    \centering
-%    \includegraphics[width=0.9\textheight, angle=90]{maps/2017-04-20-rgb-map-smaller}
-%    \caption{
-%        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
-%        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
-%        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
-%        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
-%        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
-%        emission is synchrotron, but the blue regions mottling the galactic plane are due to
-%        free-free absorption from \ion{H}{2} regions.
-%    }
-%    \label{fig:rgb}
-%\end{figure*}
-
-\begin{figure*}[p]
+\section{Results}\label{sec:results}
+
+\begin{figure*}[ht]
     \centering
@@
     \caption{
-        channel maps r kewl
+        These 8 panels illustrate (with a Mollweide projection and logarithmic color scale) the 8
+        full-sky maps generated with Tikhonov-regularized $m$-mode analysis imaging and the
+        OVRO-LWA.  Each map covers the sky north of $\delta=-30^\circ$ with angular resolution of
+        $\sim15$ arcmin. Eight bright sources have been removed from the map (Cyg~A, Cas~A, Vir~A,
+        Tau~A, Her~A, Hya~A, Per~B, and 3C~353). The small blank region near $l=+45.7^\circ$,
+        $b=-47.9^\circ$ corresponds to the location of the Sun during the observation period.  A
+        detailed summary of the properties of each map is given in Table~\ref{tab:summary}.
     }
@@
 
-%\begin{figure*}[t]
-%    \includegraphics[width=\textwidth]{figures/channel-maps/channel-maps}
-%    \caption{
-%        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
-%        and $m$-mode analysis imaging. The properties of each map are summarized in
-%        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
-%        described in the text, 8 bright sources have been subtracted. The small blank region near
-%        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
-%        time of the observations.
-%    }
-%    \label{fig:channel-maps}
-%\end{figure*}
-%
-%\begin{figure*}[p]
-%    \gridline{
-%        \fig{figures/jackknife-maps/4.pdf}
-%            {0.48\textwidth}{}
-%        \fig{figures/jackknife-maps/6.pdf}
-%            {0.48\textwidth}{}
-%    }
-%    \gridline{
-%        \fig{figures/jackknife-maps/8.pdf}
-%            {0.48\textwidth}{}
-%        \fig{figures/jackknife-maps/10.pdf}
-%            {0.48\textwidth}{}
-%    }
-%    \gridline{
-%        \fig{figures/jackknife-maps/12.pdf}
-%            {0.48\textwidth}{}
-%        \fig{figures/jackknife-maps/14.pdf}
-%            {0.48\textwidth}{}
-%    }
-%    \gridline{
-%        \fig{figures/jackknife-maps/16.pdf}
-%            {0.48\textwidth}{}
-%        \fig{figures/jackknife-maps/18.pdf}
-%            {0.48\textwidth}{}
-%    }
-%    \caption{
-%        The jackknife estimated standard deviation corresponding to the maps presented in
-%        Figure~\ref{fig:channel-maps}. The color scale is logarithmic and has units of Kelvin.
-%    }
-%    \label{fig:jackknife-maps}
-%\end{figure*}
-
-Eight sky maps are presented in Figure~\ref{fig:channel-maps}. Their properties are briefly
-summarized in Table~\ref{tab:summary}. In this section we will describe the new imaging technique
-used to generate these maps.
-
-\todo{text}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
+    \caption{
+        This Mollweide-projected map is constructed from 3 maps of the sky at 36.528~MHz (red),
+        52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
+        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}). The
+        local spectral index (estimated by means of a local T-T plot) is overlaid as a contour plot.
+        \todo{
+            The spectral index near the galactic plane is very wrong because the local T-T plot is
+            contaminated with multiple types of emission. I need to redo this plot by replacing the
+            galactic plane with hand-picked regions for estimating the spectral index.
+        }
+    }
+    \label{fig:internal-spectral-index}
+\end{figure*}
+
+\begin{table*}[t]
+    \centering
+    \begin{tabular}{ccccccccc}
+        \hline
+        \hline
+        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM}\footnote{
+                The full-width half-maximum (FWHM) of the synthesized beam at $\delta=+45^\circ$.
+            }&
+            \multicolumn2c{\tbf{Thermal Noise}\footnote{
+                Measured with a jackknife and splitting the dataset into even- and odd-numbered
+                integrations.
+            }} &&
+            \multicolumn2c{\tbf{Singular Values}\footnote{
+                Singular values of the transfer matrix compared with the value of the regularization
+                parameter $\varepsilon$ used while solving Equation~\ref{eq:tikhonov-solution}. As
+                discussed in the text, singular vectors with corresponding singular values $\sigma
+                \ll \sqrt{\varepsilon}$ are set to zero by the Tikhonov regularization procedure.
+            }} \\
+        \cline{5-6}
+        \cline{8-9}
+        \tbf{\#} & MHz & MHz & arcmin &
+            K & mJy/beam &&
+            fraction $>\sqrt{\varepsilon}$ &
+            fraction $>\sqrt{10\varepsilon}$ \\
+        \hline
+        1 & 36.528 & 0.024 & 18.5 & 595. & 799. && 0.391 & 0.077 \\
+        2 & 41.760 & 0.024 & 17.2 & 541. & 824. && 0.480 & 0.070 \\
+        3 & 46.992 & 0.024 & 16.3 & 417. & 717. && 0.504 & 0.056 \\
+        4 & 52.224 & 0.024 & 15.6 & 418. & 814. && 0.535 & 0.053 \\
+        5 & 57.456 & 0.024 & 15.4 & 354. & 819. && 0.542 & 0.049 \\
+        6 & 62.688 & 0.024 & 15.3 & 309. & 843. && 0.540 & 0.046 \\
+        7 & 67.920 & 0.024 & 15.3 & 281. & 894. && 0.529 & 0.047 \\
+        8 & 73.152 & 0.024 & 15.7 & 154. & 598. && 0.512 & 0.051 \\
+        \hline \hline
+    \end{tabular}
+    \caption{A summary of the generated all-sky maps}
+    \label{tab:summary}
+\end{table*}
+
+Eight sky maps were constructed using Tikhonov-regularized $m$-mode analysis imaging and cleaning
+with observations from the OVRO-LWA. These maps are shown in Figure~\ref{fig:channel-maps}. Each map
+covers the sky north of $\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution resolution. The
+8 brightest northern hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A,
+Her~A, Hya~A, Per~B, and 3C~353). There is a small blank region near $l=+45.7^\circ$,
+$b=-47.9^\circ$ corresponding to the position of the Sun during the observing window. The properties
+of each map, including frequency, bandwidth, angular resolution, and thermal noise are presented in
+Table~\ref{tab:summary}.
+
+Due to the considerations presented by \citet{2016ApJ...826..116V}, each of these maps is monopole
+subtracted. Consequently a simple pixel-by-pixel powerlaw fit will be unduly effected by the choice
+of zero-level correction. Instead, temperature-temperature plots (T-T plot) can be used to measure
+the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}. This
+method relies on the assumption that all pixels in a given region are described by the same power
+law. In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated within a
+region $\sim10^\circ$ across by constructing a local T-T plot at every pixel between the maps at
+36.528~MHz and 73.152~MHz. The spectral index contours are overlaid on a 3-color image constructed
+from the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz where the increasing contribution of
+free-free absorption in the galactic plane is apparent as blue regions. Similarly the spectral index
+can be seen to steepen as galactic latitude increases (this is a transition from blue to white to
+yellow that is also evident in the spectral index contours).
+
+In order to suppress sources of terrestrial interference, all spherical harmonics with $m=0$, or
+$m=1$ and $l>100$ are filtered from the map (where the spherical harmonics are defined in the J2017
+coordinate system). As will be discussed in \S\ref{sec:rfi}, these spherical harmonics are
+particularly susceptible to contamination by RFI and common-mode problems. As a consequence,
+astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
+This tends to create rings around the NCP at the declination of bright point sources. These rings
+are naturally removed from the map during CLEANing as long as this filtering step is including in
+the PSF calculation.
+
+The thermal noise in each map is empirically measured using jackknife resampling. The dataset is
+split into even- and odd-numbered integrations. These two groups are imaged and cleaned
+independently, before being compared against the maps constructed from all of the available data
+using the standard jackknife variance estimator. This estimate of the variance includes all sources
+of error that operate on $\sim13$ second timescales (the integration time), but does not account for
+more slowly varying effects (for example, sidereal variation in the system temperature or day-night
+fluctuations in the ionosphere). These thermal noise calculations are summarized in
+Table~\ref{tab:summary}.  VLSSr source counts \citep{2014MNRAS.440..327L} suggest that the confusion
+limit at 74 MHz and 15 arcmin angular resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.
+Each channel map achieves thermal noise $<900$ mJy and therefore each map is likely at or near the
+confusion limit.
+
+Each map from Figure~\ref{fig:channel-maps} is freely available online in Healpix format
+\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Error Analysis}
-
-\subsection{Jackknife Resampling}
-
-\todo{text}
-
-\subsection{Terrestrial Interference and Pickup}
-
-\begin{figure*}[p]
-    \gridline{
-        \fig{figures/smeared-images/before-component-removal-spw14}{0.22\textwidth}{(a)}
-        \fig{figures/smeared-images/after-component-removal-spw14}{0.22\textwidth}{(b)}
-        \fig{figures/smeared-images/rfi-like-component-spw14}{0.22\textwidth}{(c)}
-        \fig{figures/smeared-images/pickup-like-component-spw14}{0.22\textwidth}{(d)}
-    }
-    \gridline{
-        \fig{figures/stripe-maps/spw14-glamour-shot-map-rfi-restored-peeled-rainy-2048-galactic}
-            {\textwidth}{(e)}
-    }
-    \caption{
-        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
-        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
-        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
-        smeared along tracks of constant declination. These images are generated using WSCLEAN
-        \citep{2014MNRAS.444..606O}, uniform weighting, and baselines shorter than 15 wavelengths
-        are flagged. \textbf{(a)} This image shows the initial data before any sources have been
-        removed. \textbf{(b)} This image shows the final state after 3 terrestrial sources of
-        correlated noise have been removed. \textbf{(c)} This image illustrates the contribution of
-        an RFI source towards the north-west that was removed by peeling. \textbf{(d)} This removed
-        component is not associated with a dot on the horizon.  Instead it is likely associated with
-        common-mode pickup in the analog signal chain. \textbf{(e)} The resulting contamination in
-        the full-sky maps from the horizon RFI and common-mode pickup. Note that because these
-        contaminating components are not moving sidereally, they tend to generate stripes along
-        lines of constant declination. The color scale is in units of Kelvin.
+\section{Error Analysis}\label{sec:error}
+
+\subsection{Terrestrial Interference and Pickup}\label{sec:rfi}
+
+\begin{figure*}[t]
+    \includegraphics[width=\textwidth]{figures/terrestrial-interference/smeared}
+    \caption{
+        This figure illustrates terrestrial sources of correlated noise that are apparent after
+        averaging the visibilities at 62.688 MHz over the entire 28 hour observing period (keeping
+        the phase center at zenith such that astronomical sources of radio emission are smeared
+        along tracks of constant declination). Each panel represents a different component that is
+        removed from the visibilities. The images are generated using WSCLEAN
+        \citep{2014MNRAS.444..606O}, uniform weighting, and only baselines longer than 15
+        wavelengths. Panels (a) and (b) illustrate components that appear noise-like in image-space,
+        but are in fact a constant-offset to the measured visibilities likely associated with
+        cross-talk or common-mode pickup. Panel (c) illustrates a component that is clearly
+        associated with an RFI source on the horizon to the west-north-west of the OVRO-LWA. This
+        RFI source is likely an arcing power line.  Figure~\ref{fig:rings} illustrates the
+        characteristic ring-like artifacts introduced into the maps if these 3 components are not
+        removed prior to $m$-mode analysis imaging.
     }
     \label{fig:fitrfi}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[height=0.32\textheight]{figures/terrestrial-interference/rings}
+    \caption{
+        This is a Mollweide-projected image of the artifacts introduced to the $m$-mode analysis
+        maps by the three terrestrial sources shown in Figure~\ref{fig:rings}. Because these sources
+        are not moving through the sky sidereally, they tend to be smeared along rings of constant
+        declination. The spurs seemingly radiating from the north celestial pole are a Moir\'{e}
+        pattern (ie. an artifact of the pixelization).
+    }
+    \label{fig:rings}
 \end{figure*}
@@
 phase center set to zenith. In this way, true sky components are smeared along tracks of constant
-declination while terrestrial sources (ie. the arcing power lines or any common-mode pickup) are not
-smeared.  Obtaining a model for the RFI is complicated by the fact that the contaminating sources
-are at extremely low elevations where the antenna response is essentially unknown (and inhomogeneous
-due to antenna shadowing effects). Therefore it is not enough to know the physical location of the
-faulty insulator generating the RFI. In addition you must also know the response of each antenna
-(amplitude and phase) in the appropriate direction. This motivates the use of peeling
-\citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}, which allows the antenna response to be a free
-parameter.  Therefore model visibilities for the RFI can be obtained by peeling the sources after
-smearing the visibilities over $>24$ hours. See Figure~\ref{fig:fitrfi} for an illustration of this
-process.
-
-However while attempting to peel RFI sources from the averaged visibilities, it was discovered that
+declination while terrestrial sources (ie. the arcing power lines or any contribution due to
+common-mode pickup) are not smeared.  Obtaining a model for the RFI is complicated by the fact that
+the contaminating sources are at extremely low elevations where the antenna response is essentially
+unknown (and inhomogeneous due to antenna shadowing effects). Therefore it is not enough to know the
+physical location of the faulty insulator generating the RFI. In addition you must also know the
+response of each antenna (amplitude and phase) in the appropriate direction. This motivates the use
+of peeling, which allows the antenna response to be a free parameter.  Therefore model visibilities
+for the RFI can be obtained by peeling the sources after smearing the visibilities over $>24$ hours.
+See Figure~\ref{fig:fitrfi} for an illustration of some of the removed components at 62.688 MHz.
+
+While attempting to peel RFI sources from the averaged visibilities, it was discovered that
 frequently peeling would prefer to remove components from the visibilities that are not obviously
-associated with any source on the horizon or elsewhere in the sky (see panel (d) in
-Figure~\ref{fig:fitrfi}). In many cases the amplitude of these unassociated components exhibit the
-same sawtooth oscillations indicative of gain fluctuations in the analog electronics even after
-these gain fluctuations have been calibrated. This seems to imply that that these unassociated
-components originate as common-mode pickup in the analog signal chain. That is, if the pickup occurs
-somewhere in the middle of the analog signal chain, it will not see the same gain as the
-astronomical signal. Therefore correcting the temperature dependence of the gains for the
-astronomical signal does not correct the temperature dependence of the pick-up and hence it will
-have a sawtooth pattern with respect to time.
+associated with any source on the horizon or elsewhere in the sky (see panels (a) and (b) in
+Figure~\ref{fig:fitrfi}).  These components appear noise-like in the images, but they are actually a
+constant offset to the measured visibilities and are therefore likely associated with cross-talk or
+some form of common-mode pickup. If these components are not subtracted from the measured
+visibilities, they contribute ring-like structures into the sky maps as seen in
+Figure~\ref{fig:rings}. This figure is not a simulation, but rather a difference between maps
+created before and after measuring and subtracting the components in Figure~\ref{fig:fitrfi} from
+each integration.
 
@@
 
-\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
-that it is actually worse than the RFI, but I don't actually know for sure}
+\todo{Compute B*v for Figure~\ref{fig:fitrfi} to show that the pick-up is pretty bad. My expectation
+is that it is actually worse than the RFI, but I don't actually know for sure}
 
@@
 restricted to modes with small $m$. In this dataset the contamination is largely restricted to $m
-\lesssim 3$. As a result if the contamination is not suppressed, it will manifest itself as rings
+\lesssim 1$. Although the RFI is capable of fluctuating on short timescales, in practice the
+artifacts it introduces seems to be restricted to small $m$ (presumably because the phase is not
+fluctuating).  As a result if the contamination is not suppressed, it will manifest itself as rings
 along stripes of constant declination. This effect is plainly visible in Figure~\ref{fig:fitrfi}.
-
-However because these rings are so distinctive in the final maps, it is possible to construct a
-Wiener filter that removes them at the cost of losing a small amount of information about
-astronomical sources.
-
-\todo{describe how the Wiener filter works}
+Because of the distinctive ring-like pattern created by terrestrial sources, we chose to discard
+spherical harmonics with either $m=0$ or $m=1$ and $l>100$ in order to further suppress the
+contamination.
 
@@
 imaging operates on a full sidereal day of data, images are constructed after watching each point in
-the sky move through large slices through the beam (excepting the celestial poles). The beam model
+the sky move through a large slice of the beam (excepting the celestial poles). The beam model
 therefore serves two purposes:
@@
 will have their flux underestimated. Similarly if the antenna response is underestimated then all
-the sources will have their flux overestimated.
-
-\todo{discuss the possibility of declination dependent flux-scale errors in these maps}
+the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
+show a clear pattern with declination. Two sources show a clear systematic error at all frequencies:
+3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first southernmost
+source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable declination to
+Lyn A, which appears if anything to have its flux overestimated. The absence of a coherent pattern
+doesn't eliminate the possibility of beam errors effecting the flux scale, but it does mean that
+these errors are at least comparable to the errors inherent to the flux scale itself.
 
@@
 known and so beam model errors can lead to observations being combined with incorrect phase as well.
-This will lead to a degraded PSF in the final map.
-
-\todo{quick simulation of this?}
-
-\subsection{The Ionosphere}
+This will lead to a degraded PSF in the final map. This effect is negligible compared to the
+ionospheric effects discussed in \S\ref{sec:ionosphere}.
+
+\subsection{The Ionosphere}\label{sec:ionosphere}
+
+\begin{figure*}[t]
+    \includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
+    \caption{
+        This figure illustrates the corrupting influence of the ionosphere at 36.528 MHz. Each panel
+        shows the simulated PSF at the position of Cas~A. The left panel shows the PSF in the event
+        that there is no ionospheric scintillation and no refractive offsets. This is the PSF used
+        to deconvolve the maps with CLEAN. The middle panel shows the PSF with the measured
+        ionospheric scintillation for Cas~A from Figure~\ref{fig:scintillation} but no refractive
+        offsets. The right panel shows the PSF with the measured refractive offsets for Cas~A from
+        Figure~\ref{fig:scintillation} but no scintillation. This demonstrates that the long
+        synthesis images generated by $m$-mode analysis imaging are relatively insensitive to
+        scintillation, but uncorrected refractive offsets can limit the achievable dynamic range.
+    }
+    \label{fig:ionospheric-simulations}
+\end{figure*}
 
@@
 this assumption. In particular, ionospheric scintillation will cause even static sources to exhibit
-significant variability.
+significant variability (see Figure~\ref{fig:scintillation}).
 
@@
 where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$ is the baseline transfer
-function. The transfer function is a function of the direction to the source, which is in turn a
-function of the sidereal time $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic
-variability or due to scintillation, than the source flux is also a function of the time coordinate
-$t$ such that
+function defined by Equation~\ref{eq:baseline-transfer-function}. The transfer function is a
+function of the direction to the source, which is in turn a function of the sidereal time
+$t_{\textrm{sidereal}}$. If the source is varying, from intrinsic variability or due to
+scintillation, than the source flux is also a function of the time coordinate $t$ such that
 \begin{equation}
@@
 
-Now assume we have observed with our interferometer for a single sidereal day.  In order to compute
-the $m$-modes we must Fourier transform with respect to sidereal time. In a real measurement this is
-a discrete Fourier transform of the observed correlation with respect to time (where the sum over
-time is restricted to a sidereal day).
-\begin{equation}
-    V_{\nu, m} = \sum_{t} V_\nu(t) e^{-imt}
-\end{equation}
-Define $V_{\nu, m}^{\textrm{static}}$ to be the observed $m$-modes if the source was actually static
-($I_\nu(t) \equiv I_{\nu,0}$). Then as a consequence of the Fourier convolution theorem
-\begin{equation}
-    V_{\nu, m} \propto \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}.
-\end{equation}
-This will tend to scatter power between $m$-modes \citep{richard_ionosphere_thoughts}.
-
-\todo{Simulate images of point sources with this}
-
-\todo{I think the conclusion is sort of exactly what you would expect: refraction broadens the PSF
-while scintillation effects the flux scale, but honestly not by much because we have such large
-averages that unless the scintillation is Cauchy distributed it is not that bad..}
-
-%\subsection{Thermal Noise}
-%
-%\todo{describe jack-knife tests}
-
-%\subsection{Sky Maps}
-
-%\subsection{Error Maps}
-
-%\citet{todo_mishra_2017}
+In order to compute the $m$-modes we must Fourier transform with respect to the sidereal time. As a
+consequence of the Fourier convolution theorem we find:
+\begin{equation}\label{eq:no-longer-block-diagonal}
+    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,.
+\end{equation}
+where $V_{\nu, m}^{\textrm{static}}$ is the set of observed $m$-modes if the source was actually
+static, and $I_{\nu, m-m^\prime}$ is the Fourier transform of the light curve $I_{\nu}(t)$.
+Equation~\ref{eq:no-longer-block-diagonal} indicates that power is scattered between different
+values of $m$. As a consequence, the true transfer matrix, which is exactly block diagonal in the
+ideal case, is no longer truly block diagonal \citep{richard_ionosphere_thoughts}.
+
+The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
+arising from ionospheric fluctuations. The effect of this can be seen in
+Figure~\ref{fig:ionospheric-simulations}. In this simulation a point source is placed at the
+location of Cas A. In the first panel the source flux traces the beam model exactly and the source
+is always located exactly at the location of Cas A. In the middle panel, the source is allowed to
+scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of the point
+source is effectively unchanged from the ideal PSF. In the right panel, the source position is
+allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The refractive offsets
+lead to a clear degradation of the sidelobes. Because the sidelobes are altered from that of the
+ideal PSF, refractive offsets will restrict the dynamic range it is possible to obtain with the
+CLEAN algorithm described in \S\ref{sec:clean}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparisons with Other Sky Maps}
-
-%\subsection{The Global Sky Model}
-%
-%The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z}
-
-\subsection{Haslam 408 MHz Map}
-
-\begin{figure}[t]
-    \plotone{figures/haslam/haslam-spectral-index}
-    \caption{
-        The spectral index between the reprocessed Haslam 408 MHz map and the OVRO-LWA maps
-        (degraded to 56 arcmin resolution).  The larger blue patch around the south celestial pole
-        corresponds to where the OVRO-LWA map has a blank region.
-    }
-    \label{fig:haslam-spectral-index}
-\end{figure}
-
-The Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H} was reprocessed by
-\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources. In
-order to compare the OVRO-LWA maps with the lower resolution Haslam map, the OVRO-LWA maps were
-degraded to 56 arcmin resolution. A spectral index map computed between the OVRO-LWA maps and the
-Haslam map is shown in Figure~\ref{fig:haslam-spectral-index}.
+\section{Comparisons with Other Sky Maps}\label{sec:compare}
 
@@
 
-\begin{figure}[t]
-    \plotone{figures/guzman/guzman-comparison}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[height=0.32\textheight]{figures/guzman/guzman}
     \caption{
@@
     \label{fig:guzman-comparison}
-\end{figure}
-
-A direct comparison between the OVRO-LWA at 46.992 MHz and the Guzm\'{a}n 45 MHz map
+\end{figure*}
+
+A direct comparison between the OVRO-LWA maps interpolated to 45 MHz and the Guzm\'{a}n 45 MHz map
 \citep{2011A&A...525A.138G} can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this
 comparison the OVRO-LWA map was degraded to a 5$^\circ$ resolution by convolving with a Gaussian
-kernel.  This figure shows that the majority of the galactic synchrotron emission is consistent
-between the two maps to better than 5\% however there are patches (particularly near the north
-celestial pole) where there is a discrepancy on the order of 20\%.  Off of the galactic plane, the
-OVRO-LWA map underestimates the flux compared to the Guzm\'{a}n map by a factor of 20\%. This can be
-attributed to the absence of zero-spacing data.
-
-%\subsection{LWA1 Sky Survey}
+kernel, and the Guzm\'{a}n map has had spherical harmonics with $m=0$ discarded in order to make it
+consistent with the maps presented in this paper. This figure shows a $\sim20\%$ excess of emission
+in the galactic plane that is consistent with the discrepancy observed by the LWA1 sky survey
+\citep{2017MNRAS.469.4537D}. However, while the LWA1 sky survey has an excess of emission near the
+north galactic pole, no such excess is observed in this work. Instead there is a 10\% excess of
+emission near the south galactic pole. Elsewhere off the plane of the galaxy the discrepancy can be
+as much as $-20\%$.
+
+\subsection{Haslam 408 MHz Map}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[height=0.32\textheight]{figures/haslam/haslam-spectral-index}
+    \caption{
+        The spectral index between the reprocessed Haslam 408 MHz map and the 73.152 MHz map
+        (degraded to 56 arcmin resolution). The white regions of the plot correspond to areas where
+        there was a negative correlation between the brightness temperature at 73.152 MHz and at 408
+        MHz. This can either be due to the presence of multiple emission mechanisms in close
+        proximity to each other or due to insufficient dynamic range in temperature leading to
+        effectively no correlation between the two temperatures. Regardless, a single power law is
+        insufficient to describe the data in these areas.
+        \todo{
+            Cas A is the extremely blue feature in this plot. It needs to be blotted out because
+            it's not present in my maps, but it is present in the Haslam maps. For whatever reason
+            this isn't a problem with Cyg A.
+        }
+    }
+    \label{fig:haslam-spectral-index}
+\end{figure*}
+
+The Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H} was reprocessed by
+\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources. In
+order to compare the OVRO-LWA maps with the lower resolution Haslam map, the OVRO-LWA maps were
+degraded to 56 arcmin resolution and the spectral index between the 73.152 MHz map and the 408 MHz
+Haslam map was computed by means of a T-T plot at each pixel in the maps (in order to obviate the
+need for a zero-level correction to the 73.152 MHz map). The results of this computation are shown
+in Figure~\ref{fig:haslam-spectral-index}. Because this comparison uses a local T-T plot to estimate
+the spectral index, the angular resolution of this computation is somewhat degraded relative to
+other comparisons in the literature but the spectral indices in
+Figure~\ref{fig:haslam-spectral-index} are robust to errors in the zero-level in either map.
+
+The primary difference between the spectral index derived between 73.152 MHz and 408 MHz
+(Figure~\ref{fig:haslam-spectral-index}), and the spectral index derived between 36.528 MHz and
+73.152 MHz (Figure~\ref{fig:internal-spectral-index}) is the appearance of a multitude of \ion{H}{2}
+regions that dot the galactic plane in the latter. The free-free absorption from these \ion{H}{2}
+regions contributes to an overall flattening of the spectral index in the galactic plane that is
+also seen at higher frequencies.
+
+%\subsection{The Global Sky Model}?
+%\subsection{LWA1 Sky Survey}?
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-
-\todo{text}
+\section{Conclusion}\label{sec:conclusion}
+
+In this work we presented a new imaging technique -- Tikhonov regularized $m$-mode analysis imaging
+and cleaning -- for drift-scanning telescopes like the OVRO-LWA.  This technique exactly corrects
+for widefield effects in interferometric imaging, but offers a $\sim10^6$ times speed-up relative to
+the naive approach for the OVRO-LWA. We applied this technique to a 28 hour dataset and generated 8
+sky maps between 36.528~MHz and 73.152~MHz. These sky maps are a substantial improvement over
+existing maps at these frequencies due to their 15~arcmin angular resolution and $<600$~K thermal
+noise. The point source flux scale is consistent with that defined by \citet{2012MNRAS.423L..30S} to
+about 5\% and large angular scales are consistent with the work of \citet{2011A&A...525A.138G} to
+within 20\%.  These maps are primarily intended to be used as part of a foreground modeling and
+subtraction routine for 21~cm cosmology experiments.
+
+At frequencies above $\sim55$~MHz, the angular resolution of these maps is limited by the selection
+of $l_\text{max}=1000$. Future work will increase $l_\text{max}$ to remove this restriction, as well
+as include more time and bandwidth to improve the thermal noise. The usage of nighttime only data
+can help mitigate dynamic range limitations from the ionosphere and also prevent the Sun from
+showing up in the maps. Observations could also be extended to slightly higher and lower frequencies
+($\sim27$ to $85$~MHz) to take advantage of the full frequency range of the OVRO-LWA. The higher
+frequencies are particularly interesting in order to maximize the overlap with the MWA in the
+southern hemisphere, which could be used to fill-in the hole around the southern celestial pole.
 

### 2017-09-14 figures/guzman/make.jl

@@ -1,6 +1,6 @@
 #!/usr/bin/env julia
 
-using JLD, PyPlot, LibHealpix
+using JLD, PyPlot, LibHealpix, PerceptualColourMaps
 
 path = dirname(@__FILE__)
 
@@ -16,6 +16,7 @@ y = sin.(θ)
 ellipse = plt[:Polygon]([x y], alpha=0)
 gca()[:add_patch](ellipse)
 imshow(img, interpolation="nearest", cmap=get_cmap("RdBu_r"),
+                                    #cmap=ColorMap(cmap("D4")),
        vmin=-0.5, vmax=+0.5,
        extent=(-2, 2, -1, 1),
        clip_path=ellipse, zorder=10)

### 2017-09-14 figures/haslam/fetch.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/haslam-spectral-index.jld .
+

### 2017-09-14 figures/haslam/make.jl

@@ -1,25 +1,72 @@
-using JLD, PyPlot
+#!/usr/bin/env julia
+
+using JLD, LibHealpix, PyPlot, PyCall
+using Colors, PerceptualColourMaps
+
+@pyimport mpl_toolkits.axes_grid1 as tk
 
 path = dirname(@__FILE__)
-close("all")
 
-spectral_index = load(joinpath(path, "comparison-with-haslam.jld"), "index")
+function go()
+    slope, residual = load(joinpath(path, "haslam-spectral-index.jld"), "slope", "residual")
 
-figure(1); clf()
-θ = linspace(0, 2π, 512)
-x = 2cos.(θ)
-y = sin.(θ)
-ellipse = plt[:Polygon]([x y], alpha=0)
-gca()[:add_patch](ellipse)
-imshow(spectral_index, interpolation="nearest", cmap=get_cmap("RdBu"),
-       vmin=-2.8, vmax=-2.2,
-       extent=(-2, 2, -1, 1), clip_path=ellipse)
-gca()[:set_aspect]("equal")
-axis("off")
-cbar = colorbar(fraction=0.02)
-cbar[:ax][:tick_params](labelsize=16)
-tight_layout()
+    ν1 = 73.152
+    ν2 = 408
+    
+    cmap_samples = cmap("D4", reverse=true)
 
-savefig(joinpath(path, "haslam-spectral-index.pdf"),
-        bbox_inches="tight", pad_inches=0, transparent=true)
+    figure(1, figsize=(12, 5)); clf()
+
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+
+    map = RingHealpixMap(solve_for_spectral_index(slope, ν1, ν2))
+    img = mollweide(map, (4096, 2048))
+    img[img .== 0] = NaN # this deletes contours around the edge of the map
+    cs = contourf(img, -3.5:0.1:-1.5,
+                  extent=(-2, 2, 1, -1), origin="lower",
+                  cmap=ColorMap(cmap_samples),
+                  #linewidths=1,
+                  clip_path=ellipse)
+
+    cbar = colorbar()
+    #cbar[:lines][1][:set](linewidth=55)
+    cbar[:ax][:tick_params](labelsize=12)
[…]

### 2017-09-21 paper.tex
fix some typos and compute B*v for the rfi

@@
 that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
-after averaging over the entire sky, and power spectrum experiments that incorporate angular
-information to attempt to measure the 3D spatial power spectrum of cosmological 21~cm perturbations.
-Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
-\citep{todo_price_2017}, BIGHORNS \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V},
-and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
+after averaging over the entire sky (otherwise known as the monopole), and power spectrum
+experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
+of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
+\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{todo_price_2017}, BIGHORNS
+\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
+\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
 \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
@@
 
-This paper presents a series of new low-frequency maps of the sky between 36.528~Mhz and 73.152~Mhz,
+This paper presents a series of new low-frequency maps of the sky between 36.528~MHz and 73.152~MHz,
 capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with angular
@@
         characteristic ring-like artifacts introduced into the maps if these 3 components are not
-        removed prior to $m$-mode analysis imaging.
+        removed prior to $m$-mode analysis imaging. The component shown in panel (a) has about twice
+        the amplitude ($\|\b v_\text{terrestrial}\|$) of panels (b) and (c), and for all three
+        components $\|\b B^*\b v_\text{terrestrial}\|/(\|\b B\|\|\b v_\text{terrestrial}\|) \sim
+        0.035$.
     }
@@
         This is a Mollweide-projected image of the artifacts introduced to the $m$-mode analysis
-        maps by the three terrestrial sources shown in Figure~\ref{fig:rings}. Because these sources
-        are not moving through the sky sidereally, they tend to be smeared along rings of constant
-        declination. The spurs seemingly radiating from the north celestial pole are a Moir\'{e}
-        pattern (ie. an artifact of the pixelization).
+        maps by the three terrestrial sources shown in Figure~\ref{fig:fitrfi}. Because these
+        sources are not moving through the sky sidereally, they tend to be smeared along rings of
+        constant declination. The spurs seemingly radiating from the north celestial pole are a
+        Moir\'{e} pattern (ie. an artifact of the pixelization).
     }
@@
 of the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
-an astronomical signal ($\|\b B^*\b v_\text{terrestrial}\|/\|\b v_\text{terrestrial}\|$).
-
-\todo{Compute B*v for Figure~\ref{fig:fitrfi} to show that the pick-up is pretty bad. My expectation
-is that it is actually worse than the RFI, but I don't actually know for sure}
+an astronomical signal ($\|\b B^*\b v_\text{terrestrial}\|/(\|\b B\|\|\b v_\text{terrestrial}\|)$).
 

### 2017-09-21 paper.tex
this is the draft I'm taking to gregg's house

@@
 At redshifts $20 \gtrsim z \gtrsim 7$ the 21~cm hyperfine structure line of neutral hydrogen is
-expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
-2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
-the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
-temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
-power spectrum of this perturbation is thought to be dominated by inhomogeneous heating of the IGM
-at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
-7$ where a detection can constrain the ionizing efficiency of early galaxies, the UV photon
-mean-free-path, and the minimum halo mass that can support star formation
+expected to produce a 10 to 100 mK perturbation in the Cosmic Microwave Background (CMB) spectrum
+\citep{2006PhR...433..181F, 2012RPPh...75h6901P}. The amplitude of this perturbation on a given
+line-of-sight is a function of the neutral fraction of hydrogen, the baryon overdensity, the spin
+temperature relative to the CMB temperature at the given redshift, and the line-of-sight peculiar
+velocity of the gas.  The spatial power spectrum of this perturbation is thought to be dominated by
+inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized
+bubbles during the EoR at $z\sim 7$ where a detection can constrain the ionizing efficiency of early
+galaxies, the UV photon mean-free-path, and the minimum halo mass that can support star formation
 \citep{2015MNRAS.449.4246G}.
@@
 
-It can be shown that there is a discrete linear relationship between the measured $m$-modes
-$V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky brightness $a_{lm,\nu}$.
+\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} show that there is a discrete linear relationship
+between the measured $m$-modes $V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky
+brightness $a_{lm,\nu}$.
 \begin{equation}\label{eq:m-mode-sum-equation}
@@
 Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
-is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz with 24
-kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
-$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
-\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
-single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.
+is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and
+with 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
+there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
+correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
+hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
+are unused.
 
 The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
-snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
-placed outside of the core in order to extend the maximum baseline length to $\sim$1.5~km. The final
-5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
-the global sky brightness.  These antennas are used as part of the LEDA experiment
-\citep{todo_price_2017} to measure the global signal of 21~cm absorption from the cosmic dawn.
-Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.
+snapshot imaging (see Figure~\ref{fig:antenna-layout}).  251 of the antennas are contained within a
+200 m diameter core. 32 antennas are placed outside of the core in order to extend the maximum
+baseline length to $\sim$1.5~km. The final 5 antennas are equipped with noise-switched front ends
+for calibrated total power measurements of the global sky brightness.  These antennas are used as
+part of the LEDA experiment \citep{todo_price_2017} to measure the global signal of 21~cm absorption
+from the cosmic dawn.
 
@@
 
-\subsection{Source Removal}
+\subsection{Source Removal}\label{sec:source-removal}
 
@@
         local spectral index (estimated by means of a local T-T plot) is overlaid as a contour plot.
-        \todo{
-            The spectral index near the galactic plane is very wrong because the local T-T plot is
-            contaminated with multiple types of emission. I need to redo this plot by replacing the
-            galactic plane with hand-picked regions for estimating the spectral index.
-        }
     }
@@
 8 brightest northern hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A,
-Her~A, Hya~A, Per~B, and 3C~353). There is a small blank region near $l=+45.7^\circ$,
-$b=-47.9^\circ$ corresponding to the position of the Sun during the observing window. The properties
-of each map, including frequency, bandwidth, angular resolution, and thermal noise are presented in
-Table~\ref{tab:summary}.
+Her~A, Hya~A, Per~B, and 3C~353) as describe in \S\ref{sec:source-removal}. There is a small blank
+region near $l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the
+observing window. The properties of each map, including frequency, bandwidth, angular resolution,
+and thermal noise are presented in Table~\ref{tab:summary}.
 
@@
 coordinate system). As will be discussed in \S\ref{sec:rfi}, these spherical harmonics are
-particularly susceptible to contamination by RFI and common-mode problems. As a consequence,
+particularly susceptible to contamination by RFI and common-mode pickup. As a consequence,
 astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
@@
 sky through the fringe patterns of the interferometer. At low frequencies the ionosphere violates
-this assumption. In particular, ionospheric scintillation will cause even static sources to exhibit
-significant variability (see Figure~\ref{fig:scintillation}).
+this assumption. In particular, ionospheric scintillation and refractive offsets will cause even
+static sources to exhibit significant variability (see Figure~\ref{fig:scintillation}).
 
@@
     \caption{
-        The spectral index between the reprocessed Haslam 408 MHz map and the 73.152 MHz map
-        (degraded to 56 arcmin resolution). The white regions of the plot correspond to areas where
-        there was a negative correlation between the brightness temperature at 73.152 MHz and at 408
-        MHz. This can either be due to the presence of multiple emission mechanisms in close
-        proximity to each other or due to insufficient dynamic range in temperature leading to
-        effectively no correlation between the two temperatures. Regardless, a single power law is
-        insufficient to describe the data in these areas.
-        \todo{
-            Cas A is the extremely blue feature in this plot. It needs to be blotted out because
-            it's not present in my maps, but it is present in the Haslam maps. For whatever reason
-            this isn't a problem with Cyg A.
-        }
+        The contours show the spectral index between the reprocessed Haslam 408 MHz map and the
+        73.152 MHz map (degraded to 56 arcmin resolution). These contours are overlaid on the same
+        3-color map as in Figure~\ref{fig:internal-spectral-index}. The regions with shallow
+        spectral index between 73.152 MHz and 408 MHz coincide with regions with large free-free
+        absorption that is evident between 36.528 MHz and 73.152 MHz.
     }
@@
 degraded to 56 arcmin resolution and the spectral index between the 73.152 MHz map and the 408 MHz
-Haslam map was computed by means of a T-T plot at each pixel in the maps (in order to obviate the
-need for a zero-level correction to the 73.152 MHz map). The results of this computation are shown
-in Figure~\ref{fig:haslam-spectral-index}. Because this comparison uses a local T-T plot to estimate
-the spectral index, the angular resolution of this computation is somewhat degraded relative to
-other comparisons in the literature but the spectral indices in
-Figure~\ref{fig:haslam-spectral-index} are robust to errors in the zero-level in either map.
+Haslam map was computed by means of a local T-T plot at each pixel in the maps (in order to obviate
+the need for a zero-level correction to the 73.152 MHz map). The results of this computation are
+shown in Figure~\ref{fig:haslam-spectral-index}. Because this comparison uses a local T-T plot to
+estimate the spectral index, the angular resolution of this computation is somewhat degraded
+relative to other comparisons in the literature but the spectral indices in
+Figure~\ref{fig:haslam-spectral-index} are robust to zero-level errors in either map.
 
@@
 as include more time and bandwidth to improve the thermal noise. The usage of nighttime only data
-can help mitigate dynamic range limitations from the ionosphere and also prevent the Sun from
-showing up in the maps. Observations could also be extended to slightly higher and lower frequencies
-($\sim27$ to $85$~MHz) to take advantage of the full frequency range of the OVRO-LWA. The higher
-frequencies are particularly interesting in order to maximize the overlap with the MWA in the
-southern hemisphere, which could be used to fill-in the hole around the southern celestial pole.
+can help mitigate dynamic range limitations from the ionosphere and also eliminate solar sidelobe
+residuals. Observations could also be extended to slightly higher and lower frequencies ($\sim27$ to
+$85$~MHz) to take advantage of the full frequency range of the OVRO-LWA. The higher frequencies are
+particularly interesting in order to maximize the overlap with the MWA in the southern hemisphere,
+which could be used to fill-in the hole around the southern celestial pole.
 

### 2017-09-21 figures/haslam/fetch.sh

@@ -1,4 +1,7 @@
 #!/bin/bash
 
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/haslam-spectral-index.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/glamour-map-restored-registered-rainy.jld spw10.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/glamour-map-restored-registered-rainy.jld spw18.jld
 

### 2017-09-21 figures/haslam/make.jl

@@ -8,12 +8,25 @@ using Colors, PerceptualColourMaps
 path = dirname(@__FILE__)
 
 function go()
-    slope, residual = load(joinpath(path, "haslam-spectral-index.jld"), "slope", "residual")
+    slope, residual, mask = load(joinpath(path, "haslam-spectral-index.jld"),
+                                 "slope", "residual", "mask")
 
-    ν1 = 73.152
-    ν2 = 408
+    ν1 = 36.528
+    ν2 = 52.224
+    ν3 = 73.152
+    ν4 = 408
+    brightness1 = load(joinpath(path, "spw04.jld"), "image")
+    brightness2 = load(joinpath(path, "spw10.jld"), "image")
+    brightness3 = load(joinpath(path, "spw18.jld"), "image")
     
     cmap_samples = cmap("D4", reverse=true)
+
+    img = zeros(size(brightness1)..., 3)
+    for y = 1:size(img, 2), x = 1:size(img, 1)
+        img[x, y, 1] = brightness1[x, y] * (ν1/ν3)^2.5
+        img[x, y, 2] = brightness2[x, y] * (ν2/ν3)^2.5
+        img[x, y, 3] = brightness3[x, y]
+    end
 
     figure(1, figsize=(12, 5)); clf()
 
@@ -23,20 +36,23 @@ function go()
     ellipse = plt[:Polygon]([x y], alpha=0)
     gca()[:add_patch](ellipse)
 
-    map = RingHealpixMap(solve_for_spectral_index(slope, ν1, ν2))
-    img = mollweide(map, (4096, 2048))
-    img[img .== 0] = NaN # this deletes contours around the edge of the map
-    cs = contourf(img, -3.5:0.1:-1.5,
-                  extent=(-2, 2, 1, -1), origin="lower",
-                  cmap=ColorMap(cmap_samples),
-                  #linewidths=1,
-                  clip_path=ellipse)
+    function decide_on_color_scale(img)
+        pixels = vec(img)
+        pixels = pixels[pixels .!= 0]
+        sort!(pixels)
+        N = length(pixels)
+        min = pixels[round(Int, 0.00001N+1)]
+        max = pixels[round(Int, 0.999N+1)]
+        min, max, (max-min)/10
+    end
 
-    cbar = colorbar()
-    #cbar[:lines][1][:set](linewidth=55)
-    cbar[:ax][:tick_params](labelsize=12)
[…]

### 2017-09-21 figures/spectral-index/fetch.sh

@@ -1,7 +1,6 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/internal-spectral-index-adaptive.jld .
-#scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/better-spectral-index.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/internal-spectral-index.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/glamour-map-restored-registered-rainy.jld spw10.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/glamour-map-restored-registered-rainy.jld spw18.jld

### 2017-09-21 figures/spectral-index/make.jl

@@ -8,8 +8,9 @@ using Colors, PerceptualColourMaps
 path = dirname(@__FILE__)
 
 function go()
-    slope, jackknives, residual = load(joinpath(path, "internal-spectral-index-adaptive.jld"),
-                                       "slope", "jackknives", "delta_residual")
+    slope, jackknives, residual, masks = load(joinpath(path, "internal-spectral-index.jld"),
+                                              "slope", "jackknives", "residual", "masks")
+    mask = Vector{Bool}(masks[1] .== 1)
 
     ν1 = 36.528
     ν2 = 52.224
@@ -46,8 +47,6 @@ function go()
     end
 
     img_min, img_max, img_base = decide_on_color_scale(img)
-    @show img_min img_max img_base
-    @show minimum(img) maximum(img)
     img = clamp.(img, img_min, img_max)
     img = (log10.(img - img_min + img_base) - log10.(img_base)) ./
             (log10.(img_max - img_min + img_base) - log10.(img_base))
@@ -55,30 +54,35 @@ function go()
            extent=(-2, 2, -1, 1),
            clip_path=ellipse)
 
-    map = RingHealpixMap(solve_for_spectral_index(slope[20.0], ν1, ν3))
-    img = mollweide(map, (4096, 2048))
-    img[img .== 0] = NaN # this deletes contours around the edge of the map
-    cs = contour(img, -3.5:0.25:-2.0,
-                 extent=(-2, 2, 1, -1), origin="lower",
-                 cmap=ColorMap(cmap_samples),
-                 linewidths=1,
-                 clip_path=ellipse)
-    #clabel(cs, inline=true, fontsize=8, fontweight="bold", fmt="%1.2f")
-
-    cbar = colorbar()
-    cbar[:lines][1][:set](linewidth=55)
-    cbar[:ax][:tick_params](labelsize=12)
-    cbar[:set_label]("local spectral index", fontsize=12, rotation=270)
-    cbar[:ax][:get_yaxis]()[:set_label_coords](4.5, 0.5)
-
     xlim(-2, 2)
     ylim(-1, 1)
     gca()[:set_aspect]("equal")
     gca()[:get_xaxis]()[:set_visible](false)
     gca()[:get_yaxis]()[:set_visible](false)
     axis("off")
-
     tight_layout()
+
+    #savefig(joinpath(path, "ovro-lwa-sky-map.png"),
[…]

### 2017-09-23 paper.tex
address Gregg's comments

@@
     generate 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and
-    at frequencies evenly spaced between 36.528 MHz and 73.152 MHz.  Existing full-sky maps at these
-    frequencies have angular resolutions $\ge 2^\circ$ and so these maps are a 10-fold improvement
-    in angular resolution.  The thermal noise in each map is $\sim$800 mJy/beam.  These maps are
-    generated from the application of a new widefield imaging technique for drift-scanning
+    at frequencies evenly spaced between 36.528~MHz and 73.152~MHz with 24~kHz bandwidth.  Existing
+    full-sky maps at these frequencies have angular resolutions $\ge 2^\circ$ and so these maps are
+    a 10-fold improvement in angular resolution.  The thermal noise in each map is $\sim$800
+    mJy/beam.  Future iterations will incorporate total power radiometry, and additional bandwidth
+    and integration time. This will improve the thermal noise while simultaneously pushing to higher
+    angular resolutions with the planned expansion of the OVRO-LWA to 2.6~km baselines. These maps
+    are generated from the application of a new widefield imaging technique for drift-scanning
     interferometers, Tikhonov-regularized $m$-mode analysis imaging. This algorithm constructs
@@
     effects. We additionally introduce this technique and describe how CLEAN can be adapted to
-    deconvolve maps generated by $m$-mode analysis imaging.
+    deconvolve maps generated by $m$-mode analysis imaging.  These maps serve as a first step on the
+    path to the use of more sophisticated foreground filters in 21~cm cosmology incorporating the
+    measured angular and frequency structure of all foreground contaminants.
 \end{abstract}
@@
 of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
-\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{todo_price_2017}, BIGHORNS
+\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{price_2017}, BIGHORNS
 \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
@@
 \end{equation}
-Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
+Therefore experiments conservatively need to achieve 5 orders of dynamic range against this
 foreground emission before the cosmological signal can be measured. Current foreground removal
 methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
-emission (after convolving with the instrumental response) is spectrally smooth. However the
-low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
-remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and a confusing
-background of radio sources.  Ideally a foreground removal strategy should be informed by the
-measured spatial structure and frequency spectrum of all foreground components.  This possibility is
-limited by the availability of suitable high-fidelity low-frequency sky maps on angular scales
-ranging from tens of degrees to arcminutes.
+emission is spectrally smooth. However the low-frequency radio sky is composed of several
+components: galactic synchrotron emission, supernova remnants, radio galaxies, free-free emission
+and absorption from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally a
+foreground removal strategy should be informed by the measured spatial structure and frequency
+spectrum of all foreground components.  This possibility is limited by the availability of suitable
+high-fidelity low-frequency sky maps on angular scales ranging from tens of degrees to arcminutes.
 
@@
 $>1.4$ GHz where the majority of the modern, high-fidelity input maps are located.  Below 408 MHz,
-the GSM is largely driven by the Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H,
-2015MNRAS.451.4311R}. As a consequence, the GSM is not a faithful representation of the sky below
-200 MHz. For instance, \citet{2017MNRAS.469.4537D} report errors of $\pm 50\%$ between the GSM and
-their own maps at 74 MHz. This is largely due to the increasing contribution of free-free absorption
-and modifications to the synchrotron spectral index at low frequencies.
+the GSM is a strong function of the Haslam 408 MHz map \citep{1981A&A...100..209H,
+1982A&AS...47....1H, 2015MNRAS.451.4311R}. As a consequence, the GSM is not a faithful
+representation of the sky below 200 MHz. For instance, \citet{2017MNRAS.469.4537D} report errors of
+$\pm 50\%$ between the GSM and their own maps at 74 MHz. This is largely due to the increasing
+contribution of free-free absorption and modifications to the synchrotron spectral index at low
+frequencies.
 
@@
 \citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
-catalog of radio point sources. Surveys that capture the diffuse emission include at 45 MHz, where
-\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
-Frequency Sky Survey \citep{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
-and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.
+catalog of radio point sources. At 45 MHz, \citet{2011A&A...525A.138G} created a map of the sky that
+captures the diffuse emission with 5$^\circ$ resolution.  The LWA1 Low Frequency Sky Survey
+\citep{2017MNRAS.469.4537D} similarly maps the sky at a range of frequencies between 35~MHz and
+80~MHz with resolution between 4.5$^\circ$ and 2$^\circ$.
 
@@
 21~cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
-at these frequencies. The maps will be made freely available online at the Legacy Archive for
-Microwave Background Data Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.
+at these frequencies. We anticipate additional anciliary science taking advantage of the combination
+of high fidelity and high resolution of these maps, including but not limited to studies of the
+cosmic ray emissivity at low frequencies, searches for giant radio galaxies, and constraining the
+galactic synchrotron spectrum. The maps will be made freely available online at the Legacy Archive
+for Microwave Background Data Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.
 
@@
 time.\footnote{
-    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the sun)
+    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the Sun)
     will violate this assumption. This paper will, however, demonstrate that the impact on the final
@@
 short spacings, a minimum value for $l$ might also be used. This $l_\text{min}$ parameter should be
-determined by the minimum baseline length.  When creating the maps presented in this paper, we use
-$l_\text{min} = 0$ and $l_\text{max} = 1000$. %\todo{this choice of lmax restricts resolution at
-%higher frequencies}
+determined by the minimum baseline length. A rough estimate of $l$ for a baseline of length $b$ at
+frequency $\nu$ is $l \sim \pi b\nu/c$. For the OVRO-LWA we therefore adapt $l_\text{min}=0$ and
+$l_\text{max}=1000$ across all frequencies. However this choice of $l_\text{max}$ actually limits
+the angular resolution above 55~MHz, and therefore future work will increase $l_\text{max}$ to
+obtain better angular resolution.
 
@@
 other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
-measured and calibrated. Consequently we set $a_{00}=0$ in our analysis.
+measured and calibrated. Consequently we set $a_{00}=0$ in our analysis. In the future this will be
+addressed with the inclusion of calibrated total power radiometry.
 
@@
 64-bit complex floating point number, a single block is 500 MB for the case of single-channel
-imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
+imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.  The
 power of $m$-mode analysis is the block-diagonal structure of
@@
 In traditional radio astronomy imaging, the CLEAN algorithm \citep{1974A&AS...15..417H} is used to
-interpolate the measured visibilities onto the $uv$-plane. In the absence of this interpolation,
+interpolate between measured visibilities on the $uv$-plane. In the absence of this interpolation,
 gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the image plane --
 sources are convolved with a point spread function (PSF) that is characteristic of the
-$uv$-coverage.  Fundamentally, the interferometer's PSF in the dirty images is determined by which
-modes were assumed to be zero in the initial imaging process.
+$uv$-coverage.  Fundamentally, the interferometer's PSF is determined by which modes were assumed to
+be zero in the initial imaging process.
 
@@
 
+In summary, Tikhonov-regularized $m$-mode analysis imaging constructs a widefield synthesis image of
+the sky from a complete earth rotation, and  with exact treatment of widefield-effects. This is
+accomplished by solving a regularized block-diagonal matrix equation
+(Equation~\ref{eq:tikhonov-solution}). The solution to this equation generates a map where
+sources are convolved with a PSF characteristic of the interferometer (a function of the frequency,
+antenna response, and baseline distribution with a full Earth rotation). The CLEAN algorithm is
+adopted to deconvolve the PSF and produce the final sky maps.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
+Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The OVRO-LWA
 is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and
@@
 for calibrated total power measurements of the global sky brightness.  These antennas are used as
-part of the LEDA experiment \citep{todo_price_2017} to measure the global signal of 21~cm absorption
-from the cosmic dawn.
+part of the LEDA experiment \citep{price_2017} to measure the global signal of 21~cm absorption from
+the cosmic dawn. A final stage of construction will involve 64 antennas installed on long baselines
+out to a maximum length of 2.6~km.
 
@@
 
-Antenna gain calibration is accomplished using an iterative method independently developed by
-\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
-the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
+Antenna gain calibration is accomplished using alternating least squares otherwise known as
+``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}.  \citet{2008ISTSP...2..707M} and
+\citet{2014A&A...571A..97S}. The calibration routine is written in the Julia programming language
+\citep{doi:10.1137/141000671}, and is publicly available
 online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
@@
 VLSSr \citep{2014MNRAS.440..327L} sources brighter than 30~Jy. Additional cuts are made to ensure
-that sources aren't too close to each other or other bright sources.
+that sources aren't too close to each other or other bright sources, and that the VLSSr flux density
+matches is consistent with the flux density measured by the OVRO-LWA.
 
@@
 timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
-A to have a measured flux of 30,000 Jy in one integration, and 20,000 Jy in the next. The measured
+A to have a measured flux variations of 50\% between adjacent 13 second integrations.  The measured
 position offset of each source is a measurement of the ionospheric phase gradient across the array.
@@
 
-The sun can be trivially removed from any map of the sky by constructing the map using only data
+The Sun can be trivially removed from any map of the sky by constructing the map using only data
 taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
 However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
-suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
-sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
-optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new model is
+suppress the contribution of the Sun to the maps with the goal of suppressing its sidelobes.  The
+Sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
+optical depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new model is
 needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
+    \includegraphics[width=\textwidth]{figures/spectral-index/ovro-lwa-sky-map.pdf}
     \caption{
@@
         52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
-        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}). The
-        local spectral index (estimated by means of a local T-T plot) is overlaid as a contour plot.
+        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
+    }
+    \label{fig:three-color}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
+    \caption{
+        This plot shows the local spectral index (estimated by means of a local T-T plot) as a
+        contour plot. The contours are overlaid on the three-color image from
+        Figure~\ref{three-color}.
     }
@@
 source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable declination to
-Lyn A, which appears if anything to have its flux overestimated. The absence of a coherent pattern
+Lyn A, which appears, if anything, to have its flux overestimated. The absence of a coherent pattern
 doesn't eliminate the possibility of beam errors effecting the flux scale, but it does mean that
-these errors are at least comparable to the errors inherent to the flux scale itself.
+these errors are at least comparable to the errors inherent to the flux scale itself. On the other
+hand, the spectral indices presented in Figure~\ref{fig:internal-spectral-index} are systematically
+flatter from declinations between $-20^\circ$ and $-30^\circ$. This indicates the existence of beam
+errors at elevations $\lesssim20^\circ$.
 
@@
         73.152 MHz map (degraded to 56 arcmin resolution). These contours are overlaid on the same
-        3-color map as in Figure~\ref{fig:internal-spectral-index}. The regions with shallow
-        spectral index between 73.152 MHz and 408 MHz coincide with regions with large free-free
-        absorption that is evident between 36.528 MHz and 73.152 MHz.
+        three-color map from Figure~\ref{fig:three-color}. The regions with shallow spectral index
+        between 73.152 MHz and 408 MHz coincide with regions with large free-free absorption that is
+        evident between 36.528 MHz and 73.152 MHz.
     }

### 2017-09-23 figures/channel-maps/make.jl

@@ -1,6 +1,6 @@
 #!/usr/bin/env julia
 
-using JLD, PyPlot, PyCall
+using JLD, PyPlot, PyCall, LibHealpix
 
 unshift!(PyVector(pyimport("sys")["path"]), "")
 @pyimport my_log_scale as mls
@@ -22,12 +22,15 @@ for (idx, spw) in enumerate(4:2:18)
     figure(idx, figsize=(12, 5)); clf()
 
     str = @sprintf("spw%02d", spw)
-    img, ν   = load(joinpath(path, "$str.jld"), "image", "frequency")
+    img, ν, map = load(joinpath(path, "$str.jld"), "image", "frequency", "map")
     img_odd  = load(joinpath(path, "$str-odd.jld"),  "image")
     img_even = load(joinpath(path, "$str-even.jld"), "image")
 
     #variance = 0.5 .* ((img_odd - img).^2 .+ (img_even .- img).^2)
     #standard_deviation = sqrt.(variance)
+
+    writehealpix(@sprintf("ovro-lwa-sky-map-%6.3fMHz.fits", ν/1e6), RingHealpixMap(map),
+                 replace=true, coordsys="G")
 
     θ = linspace(0, 2π, 512)
     x = 2cos.(θ)

### 2017-09-23 figures/spectral-index/make.jl

@@ -62,8 +62,11 @@ function go()
     axis("off")
     tight_layout()
 
-    #savefig(joinpath(path, "ovro-lwa-sky-map.png"),
-    #        bbox_inches="tight", pad_inches=0, transparent=true)
+    savefig(joinpath(path, "ovro-lwa-sky-map.png"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
+
+    savefig(joinpath(path, "ovro-lwa-sky-map.pdf"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
 
     map = RingHealpixMap(solve_for_spectral_index(slope, ν1, ν3))
     img = mollweide(map, (4096, 2048))

### 2017-09-26 paper.tex
fix a typo in a cross-reference
add a discussion of polarization leakage

@@
 
-\subsection{$m$-Mode Analysis Imaging}
+\subsection{$m$-Mode Analysis Imaging}\label{sec:mmode-imaging}
 
@@
 
-Antenna gain calibration is accomplished using alternating least squares otherwise known as
-``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}.  \citet{2008ISTSP...2..707M} and
-\citet{2014A&A...571A..97S}. The calibration routine is written in the Julia programming language
-\citep{doi:10.1137/141000671}, and is publicly available
+Antenna gain calibration is accomplished using a variant of alternating least squares colloquially
+known as ``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}. The calibration routine is
+written in the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
 online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
@@
         contour plot. The contours are overlaid on the three-color image from
-        Figure~\ref{three-color}.
+        Figure~\ref{fig:three-color}.
     }
@@
 
+\subsection{Polarization Leakage}
+
+\citet{2015PhRvD..91h3514S} describe how to generalize $m$-mode analysis to account for a polarized
+sky observed with a polarized antenna beam. Heretofore this generalization has been neglected in the
+discussion of $m$-mode analysis imaging.  At low frequencies, increasingly rapid Faraday rotation
+leads to depolarization. Therefore polarization fractions are generally expected to decrease at low
+frequencies (varying with ionospheric conditions). \citet{2016ApJ...830...38L} detected the presence
+of diffuse polarized emission on degree angular scales with the MWA, also finding typical
+depolarization ratios of $\sim0.3$ for pulsars at 154~MHz relative to 1.4~GHz, although there was a
+large variance between pulsars. Even more depolarization is expected at frequencies $\le
+73.152$~MHz, but crossed-dipole antennas with extremely large primary beams will naturally introduce
+large polarization leakage terms at low elevations.  It is instructive to compute what impact this
+will have on the unpolarized imaging process.
+
+In order to understand the effect of polarization leakage, a point source with 10\% polarization in
+Stokes-$Q$ was simulated at the location of Cas A.  The simulated visibilities were computed using
+the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
+every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
+Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
+rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about 7 hours
+every day skirting the horizon where the polarization leakage is large, so by placing the simulated
+source at the location of Cas A, we are engineering a situation where the polarization leakage from
+Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
+maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
+PSF.
+
 \subsection{The Ionosphere}\label{sec:ionosphere}

### 2017-10-04 paper.tex
big set of changes trying to address some of joe's comments

@@
 of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
-\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{price_2017}, BIGHORNS
+\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
 \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
@@
 direction $\hat r$ and frequency $\nu$.  A radio interferometer measures the visibilities
-$V^{ij}_{\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
-are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
-incident radiation, then
+$V^{ij,pq}_{\nu}$ between pairs of antennas numbered $i$ and $j$ respectively, and between
+polarizations labeled $p$ and $q$ respectively. We will neglect subtleties associated with polarized
+imaging, so the Stokes-$I$ visibilities are constructed from the sum of the $xx$ and $yy$
+correlations such that $V^{ij}_{\nu} = (V^{ij,xx}_{\nu}+V^{ij,yy}_{\nu})/2$.  If the antennas are
+separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes an antenna's response to the
+incident Stokes-$I$ radiation (here assumed to be the same for each antenna), then
 \begin{equation}\label{eq:basic-imaging}
@@
 
-\subsection{$m$-Mode Analysis}
+\subsection{$m$-Mode Analysis}\label{sec:mmode-analysis}
 
@@
 analysis, also obviates the need for gridding and mosaicing. Instead the entire sky is imaged in one
-coherent synthesis imaging step.
-
-In this context we will define a transit telescope as any interferometer where the response pattern
-of the individual elements does not change with respect to time. This may be an interferometer like
-the OVRO-LWA where the correlation elements are fixed dipoles, but it may also be an interferometer
-like LOFAR or the MWA if the steerable beams are held in a fixed position (not necessarily at
-zenith).
-
-We will briefly summarize $m$-mode analysis below, but the interested reader should consult
-\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete derivation.
+coherent synthesis imaging step.  We will briefly summarize $m$-mode analysis below, but the
+interested reader should consult \citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete
+derivation.
+
+In the context of $m$-mode analysis a transit telescope is any interferometer for which the response
+pattern of the individual elements does not change with respect to time. This may be an
+interferometer like the OVRO-LWA where the correlation elements are fixed dipoles, but it may also
+be an interferometer like LOFAR or the MWA if the steerable beams are held in a fixed position (not
+necessarily at zenith). The interferometer also does not necessarily have to be homogeneous.
+Heterogeneous arrays composed of several different types of antennas are allowed as long as care is
+taken to generalize Equation~\ref{eq:basic-imaging} for a heterogeneous array.
 
@@
 \end{equation}
-where the transfer coefficients $B^{ij}_{lm,\nu}$ define the interferometer's response to the sky.
-These transfer coefficients are computed from the spherical harmonic transform of the baseline
-transfer function defined by Equation~\ref{eq:baseline-transfer-function}.
+where the transfer coefficients $B^{ij}_{lm,\nu}$ are computed from the spherical harmonic transform
+of the baseline transfer function defined by Equation~\ref{eq:baseline-transfer-function}. These
+transfer coefficients define the interferometers response to the corresponding spherical harmonic
+coefficients.
 
@@
 In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
-an interferometer like the OVRO-LWA with lots of short baselines, a sensible choice is to use all
+an interferometer like the OVRO-LWA with many short baselines, a sensible choice is to use all
 spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
@@
 determined by the minimum baseline length. A rough estimate of $l$ for a baseline of length $b$ at
-frequency $\nu$ is $l \sim \pi b\nu/c$. For the OVRO-LWA we therefore adapt $l_\text{min}=0$ and
-$l_\text{max}=1000$ across all frequencies. However this choice of $l_\text{max}$ actually limits
-the angular resolution above 55~MHz, and therefore future work will increase $l_\text{max}$ to
-obtain better angular resolution.
+frequency $\nu$ is $l \sim \pi b\nu/c$. Based on this estimate for the OVRO-LWA and other
+computational considerations we therefore adapt $l_\text{min}=1$ and $l_\text{max}=1000$ across all
+frequencies. However this choice of $l_\text{max}$ actually limits the angular resolution above
+55~MHz, and therefore future work will increase $l_\text{max}$ to obtain better angular resolution.
 
@@
 other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
-measured and calibrated. Consequently we set $a_{00}=0$ in our analysis. In the future this will be
-addressed with the inclusion of calibrated total power radiometry.
+measured and calibrated. Consequently we set $a_{00}=0$ in our analysis. In the future this
+limitation will be addressed with the inclusion of calibrated total power radiometry.
 
@@
 64-bit complex floating point number, a single block is 500 MB for the case of single-channel
-imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.  The
-power of $m$-mode analysis is the block-diagonal structure of
-Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
-the computational complexity involved in inverting a single block is reduced by a factor of $N^3$
-relative to a dense matrix. However we must invert $N$ blocks, so the overall computational savings
-is proportional to $N^2$.  For the case of the OVRO-LWA the equation breaks up into $\sim10^3$
-blocks and so we save a factor of $\sim10^6$ in processing time by using $m$-mode analysis.
+imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.
+However, with additional bandwidth these blocks quickly become unwieldy and so as a first pass the
+analysis in this paper is restricted to single-channel imaging. Note also that for the OVRO-LWA
+$N_\text{base} \gg l_\text{max}$, so there are more measurements than unknowns in
+Equation~\ref{eq:m-mode-matrix-equation}.
+
+The power of $m$-mode analysis is the block-diagonal structure of
+Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
+operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$.  By splitting the
+equation into $N$ independent blocks, the number of floating point operations required to operate on
+the full matrix is reduced by a factor of $N^2$. This computational savings is what makes this
+matrix algebra approach to interferometric imaging feasible.
 
@@
 \end{equation}
-where $^*$ indicates the conjugate-transpose. However, usually one will find that $\b B$ is not
-full-rank and hence $\b B^*\b B$ is not an invertible matrix. For example, an interferometer located
-in the northern hemisphere will never see a region of the southern sky centered on the southern
-celestial pole. The $m$-modes contained in the vector $\b v$ must contain no information
-about the sky around the southern celestial pole, and therefore the act of multiplying by $\b B$
-must destroy some information about the sky. The consequence of this fact is that $\b B$ must have
-at least one singular value that is equal to zero. It is then trivial to show that $\b B^*\b B$ must
-have at least one eigenvalue that is equal to zero, which means it is not an invertible matrix.
+where $^*$ indicates the conjugate-transpose.
+
+However, usually one will find that $\b B$ is not full-rank and hence $\b B^*\b B$ is not an
+invertible matrix. For example, an interferometer located in the northern hemisphere will never see
+a region of the southern sky centered on the southern celestial pole. The $m$-modes contained in the
+vector $\b v$ must contain no information about the sky around the southern celestial pole, and
+therefore the act of multiplying by $\b B$ must destroy some information about the sky. The
+consequence of this fact is that $\b B$ must have at least one singular value that is equal to zero.
+It is then trivial to show that $\b B^*\b B$ must have at least one eigenvalue that is equal to
+zero, which means it is not an invertible matrix.
 
@@
 the southern hemisphere, there are infinitely many possible solutions to
-Equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well. So we need to
-regularize the problem and apply an additional constraint that prefers a unique solution. For
-example, you may prefer that in the absence of any information the sky should be set to zero or you
-may prefer that the sky should be set to some prior expectation.
+Equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well.  We will
+regularize the problem and apply an additional constraint that prefers a unique yet physically
+reasonable solution.
 
@@
 Tikhonov regularization adds a small value $\varepsilon$ to the diagonal of $\b B^*\b B$, fixing the
-matrix's singularity. We can see this by using the singular value decomposition (SVD) of the matrix
-$\b B = \b U \b \Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
+matrix's singularity. By using the singular value decomposition (SVD) of the matrix $\b B = \b U \b
+\Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
 \begin{equation}
@@
 \]
-The diagonal elements of $\b\Sigma$ are the singular values of $\b B$ and so the contribution of
-each singular component to the Tikhonov-regularized solution is scaled by $\sigma_i / (\sigma_i^2 +
+The diagonal elements of $\b\Sigma$ are the singular values of $\b B$. The contribution of each
+singular component to the Tikhonov-regularized solution is scaled by $\sigma_i / (\sigma_i^2 +
 \varepsilon)$, where $\sigma_i$ is the singular value for the $i$th singular component. Tikhonov
@@
 While Tikhonov regularization will force unmeasured modes to zero, if a prior map of the sky already
-exists, it will be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \varepsilon \|\b a-\b
+exists, it would be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \varepsilon \|\b a-\b
 a_\text{prior}\|^2$.
@@
     \caption{
-        An example L-curve using OVRO-LWA data at 36.528 MHz. The $x$-axis is the norm of the
-        solution (in this case the spherical harmonic coefficients) given in arbitrary units. The
-        $y$-axis is the least-squares norm given in arbitrary units. $\varepsilon$ is the
-        regularization parameter. When the regularization parameter is small, the norm of the
-        solution grows rapidly. When the regularization parameter is large, the least-squares norm
-        grows rapidly.
+        An example L-curve computed from OVRO-LWA data at 36.528~MHz by trialing 200 different
+        values of the regularization parameter $\varepsilon$. The $x$-axis is the norm of the
+        solution (in this case the spherical harmonic coefficients) given in arbitrary units, and
+        the $y$-axis is the least-squares norm given in arbitrary units Where the regularization
+        parameter is small, the norm of the solution grows rapidly. Where the regularization
+        parameter is large, the least-squares norm grows rapidly.
     }
@@
 choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in traditional
-imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.
+imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.  For the
+OVRO-LWA we selected $\varepsilon = 0.01$ across all frequency channels. The distribution of
+singular values of the transfer matrix with respect to $\sqrt{\varepsilon}$ is summarized in
+Table~\ref{tab:summary}.
 
@@
 
+\subsubsection{Other Regularization Schemes}
+
+In compressed-sensing applications, the $L^1$-norm is used in place of the $L^2$-norm in order to
+encourage sparsity in the reconstructed signal. By expressing the sky in terms of spherical
+harmonics there is no such expectation of sparsity in the solution, and so the $L^1$-norm is
+inappropriate for this application.
+
+Wiener filtering can also be used in place of Tikhonov regularization in the event that the observer
+has a prior expectation on the covariance of the spherical harmonic coefficients in order to
+interpolate missing information. This technique is demonstrated for simulated measurements by
+\citet{2016arXiv161203255B}.
+
+In this work we elect to pursue Tikhonv regularization due to its computational simplicity, smooth
+down-weighting of noisy modes, and independence of prior information.
+
 \subsection{CLEAN}\label{sec:clean}
 
-In traditional radio astronomy imaging, the CLEAN algorithm \citep{1974A&AS...15..417H} is used to
-interpolate between measured visibilities on the $uv$-plane. In the absence of this interpolation,
-gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the image plane --
-sources are convolved with a point spread function (PSF) that is characteristic of the
-$uv$-coverage.  Fundamentally, the interferometer's PSF is determined by which modes were assumed to
-be zero in the initial imaging process.
+In traditional radio astronomy imaging, CLEAN \citep{1974A&AS...15..417H} is a physically motivated
+algorithm that interpolates between measured visibilities on the $uv$-plane. In the absence of this
+interpolation, gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the
+image plane -- sources are convolved with a point spread function (PSF) that is characteristic of
+the $uv$-coverage.  Fundamentally, the interferometer's PSF is determined by which modes were
+assumed to be zero in the initial imaging process.
 
@@
 harmonics. Therefore just as in traditional imaging, $m$-mode analysis imaging produces dirty maps
-where sources are convolved with a PSF.  This PSF can be improved by increasing the number and
-variety of baselines, which increases the number of modes where $\sigma_i \gg \sqrt{\varepsilon}$.
-Alternatively by collecting more data, the signal-noise ratio of the measured $m$-modes increases,
-which allows the observer to lower the value of $\varepsilon$ without increasing the noise in the
-maps.  Finally, the CLEAN algorithm can be applied to interpolate some of the missing information
-that was assumed to be zero.
+in which sources are convolved with a PSF.  This PSF can be improved by increasing the number and
+variety of baselines, which increases the number of modes for which $\sigma_i \gg
+\sqrt{\varepsilon}$.  Alternatively by collecting more data, the signal-noise ratio of the measured
+$m$-modes increases, which allows the observer to lower the value of $\varepsilon$ without
+increasing the noise in the maps.  Finally, the CLEAN algorithm can be applied to interpolate some
+of the missing information that was assumed to be zero.
 
@@
 example, sources at low elevations will tend to have an extended PSF along the north-south axis due
-to baseline foreshortening. Some examples PSFs are shown in Figure~\ref{fig:psf}.  Adapting CLEAN
-for $m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of declinations,
-or a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.
+to baseline foreshortening. For the OVRO-LWA antenna configuration
+(Figure~\ref{fig:antenna-layout}), example PSFs at three separate frequencies are shown in
+Figure~\ref{fig:psf}.  Adapting CLEAN for $m$-mode analysis requires either pre-computing
+Equation~\ref{eq:psf} at a grid of declinations, or a method for rapidly evaluating
+Equation~\ref{eq:psf} on the fly.
 
@@
 $\mathcal{O}(N^2)$ operation (instead of $\mathcal{O}(N^3)$ for a general matrix inverse).\footnote{
-    Inverting a matrix is numerically unstable and should be avoided. Instead of computing $\b
-    A^{-1}$, the linear equation $\b A\b x = \b b$ is solved each time the matrix inverse is needed.
+    Instead of computing $\b A^{-1}$, we solve the linear equation $\b A\b x = \b b$ each time the
+    matrix inverse is needed so as to avoid numerical instabilities.
 }
@@
         within the 200 m diameter core of the array. The 32 triangles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to $\sim1.5$ km. The 5 crosses
-        are antennas equipped with noise-switched front ends.
+        built in early 2016 in order to increase the longest baseline to $\sim1.5$ km. The red dots
+        are core antennas that are disconnected from the correlator in order to accommodate these
+        antennas. The 5 crosses are antennas equipped with noise-switched front ends.
     }
@@
 \begin{figure*}[t]
-    \includegraphics[width=\textwidth]{figures/psf/psf}
-    \caption{
-        This figure shows the $m$-mode analysis imaging PSF at $\delta = +45^\circ$ at 3 separate
-        frequencies: 36.528 MHz (left panel), 52.224 MHz (middle panel), and 73.152 MHz (right
-        panel). The PSF is computed by evaluating Equation~\ref{eq:psf}.
+    \begin{tabular}{c}
+        \includegraphics[width=\textwidth]{figures/psf/psf+75} \\
+        \includegraphics[width=\textwidth]{figures/psf/psf+45} \\
+        \includegraphics[width=\textwidth]{figures/psf/psf+0} \\
+    \end{tabular}
+    \caption{
+        The $m$-mode analysis imaging PSF at three declinations (top row: $\delta=+75^\circ$, middle
+        row: $\delta=+45^\circ$, bottom row: $\delta=+0^\circ$) and three frequencies (left column:
+        36.528~MHz, middle column: 52.224~MHz, right column: 73.152~MHz).  The PSF is computed by
+        evaluating Equation~\ref{eq:psf}. Above 55~MHz, the angular extent of the PSF does not
+        follow the expected scaling with frequency because the angular resolution is limited by the
+        selection of $l_\text{max}=1000$. The FWHM at $\delta=+45^\circ$ is listed in
+        Table~\ref{tab:summary}.
     }
@@
 The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The OVRO-LWA
-is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and
-with 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
-there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
-correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
-hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
-are unused.
+Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The OVRO-LWA is a
+low-frequency instrument with instantaneous bandwidth covering 27~MHz to 85~MHz and with 24~kHz
+channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
+$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
+\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
+single snapshot image.
 
 The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
-snapshot imaging (see Figure~\ref{fig:antenna-layout}).  251 of the antennas are contained within a
-200 m diameter core. 32 antennas are placed outside of the core in order to extend the maximum
-baseline length to $\sim$1.5~km. The final 5 antennas are equipped with noise-switched front ends
-for calibrated total power measurements of the global sky brightness.  These antennas are used as
-part of the LEDA experiment \citep{price_2017} to measure the global signal of 21~cm absorption from
-the cosmic dawn. A final stage of construction will involve 64 antennas installed on long baselines
-out to a maximum length of 2.6~km.
+snapshot imaging (see Figure~\ref{fig:antenna-layout}).  Of these 288 antennas, 251 are contained
+within a 200 m diameter core, 32 are placed outside of the core in order to extend the maximum
+baseline length to $\sim$1.5~km, and the final 5 antennas are equipped with noise-switched front
+ends for calibrated total power measurements of the global sky brightness.  These antennas are used
+as part of the LEDA experiment \citep{2017arXiv170909313P} to measure the global signal of 21~cm
+absorption from the cosmic dawn. In the current configuration 32 antennas (64 signal paths) from the
+core are disconnected from the correlator in order to accommodate the 32 antennas on longer
+baselines. A final stage of construction will involve 64 additional antennas installed on long
+baselines out to a maximum length of 2.6~km.
 
@@
 correlator dump time was selected to be 13 seconds such that the correlator output evenly divides a
-sidereal day.
-
-\subsection{Gain Calibration}\label{sec:gaincal}
-
-Antenna gain calibration is accomplished using a variant of alternating least squares colloquially
-known as ``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}. The calibration routine is
-written in the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
-online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
-any later version).
+sidereal day. Due to the computational considerations presented in \S\ref{sec:mmode-analysis}, eight
+24~kHz channels are selected for imaging from this dataset: 36.528~MHz, 41.760~MHz, 46.992~MHz,
+52.224~MHz, 57.456~MHz, 62.688~MHz, 67.920~MHz, and 73.152~MHz.
+
+\subsection{Complex Gain Calibration}\label{sec:gaincal}
+
+The complex gain calibration is responsible for correcting per-antenna amplitude and phase errors.
+This is accomplished using a sky model and a variant of alternating least squares colloquially known
+as ``Stefcal''
+\citep{2008ISTSP...2..707M, 2014A&A...571A..97S}\footnote{
+    The calibration routine is written in the Julia programming language
+    \citep{doi:10.1137/141000671}, and is publicly available online
+    (\url{https://github.com/mweastwood/TTCal.jl}) under an open source license (GPLv3 or any later
+    version).
+}.
 
@@
 is when these sources are at high elevations.  The antenna complex gains are measured from a 22
-minute track of data from when Cyg~A and Cas are at high elevations. The gains measured in this way
-are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
-Cyg~A and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while
-the flux of Cas~A is measured from the data itself (using a preliminary calibration).  Residual
-errors in the astrometry are corrected post-imaging by registering the images with respect to all
-VLSSr \citep{2014MNRAS.440..327L} sources brighter than 30~Jy. Additional cuts are made to ensure
-that sources aren't too close to each other or other bright sources, and that the VLSSr flux density
-matches is consistent with the flux density measured by the OVRO-LWA.
-
-Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
-analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
+minute track of data when Cyg~A and Cas are at high elevations. The gains measured in this way are
+then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of Cyg~A
+and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while the flux
+of Cas~A is measured from the data itself (using a preliminary calibration solved for with a
+fiducial Cas~A spectrum).
+
+Calibrating in this manner generates $\sim$ arcminute errors in the astrometry of the final sky maps
+due to ionospheric refractive offsets during the time of calibration.  These residual errors in the
+astrometry are corrected post-imaging by registering the images with respect to all VLSSr
+\citep{2014MNRAS.440..327L} sources that are bright ($>30$~Jy with a consistent flux density
+measured with the OVRO-LWA), and not too close to other bright sources (at least $1^\circ$
+separation).
+
+Temperature fluctuations of the analog electronics generate 0.1~dB sawtooth oscillations in the
+analog gain. These oscillations occur with a variable 15 to 17 minute period associated with HVAC
+cooling cycles within the electronics shelter that houses these electronics.  The amplitude of these
 gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
@@
     \caption{
-        This figure shows the empirical fits to the OVRO-LWA Stokes-I primary beam (the response of
-        the $x$- and $y$-dipoles has been summed) at three frequencies: 36.528 MHz (left panel),
-        52.224 MHz (middle panel), and 73.152 MHz (right panel). The source tracks used to measure
-        the beam model are overlaid. From north to south, these tracks correspond to Cas~A, Cyg~A,
-        Per~B, Tau~A, Vir~A, Her~A, 3C~353, and Hya~A.  The fitting process is described in
-        \S\ref{sec:beam}, and residuals for Cyg~A and Cas~A can be seen in
-        Figure~\ref{fig:scintillation}.
+        Empirical fits to the OVRO-LWA Stokes-I primary beam (the response of the $x$- and
+        $y$-dipoles has been summed) at three frequencies: 36.528 MHz (left panel), 52.224 MHz
+        (middle panel), and 73.152 MHz (right panel). The source tracks used to measure the beam
+        model are overlaid. From north to south, these tracks correspond to Cas~A, Cyg~A, Per~B,
+        Tau~A, Vir~A, Her~A, 3C~353, and Hya~A.  The fitting process is described in
+        \S\ref{sec:beam}, and residuals for Cyg~A and Cas~A are in Figure~\ref{fig:scintillation}.
     }
@@
 In order to generate wide-field images of the sky, the response of the antenna to the sky must be
-known. Drift-scanning interferometers like the OVRO-LWA can empirically measure their
-primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
-assume that the primary beam is invariant under north-south and east-west flips, and additionally
-that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
-These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
-antennas will contribute towards breaking these symmetries at some level. However some amount of
-symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
-when the flux of a source is unknown.
-
-We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A, Per~B, and
+known. Drift-scanning interferometers like the OVRO-LWA can empirically measure their primary beam
+under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. The symmetry assumptions are
+necessary to break the degeneracy between source flux and beam amplitude when the flux of the source
+is unknown. In this work we assume symmetries that are apparent in the antenna design, but
+real-world defects and coupling with nearby antennas will contribute towards breaking these
+symmetries at some level. In particular we assume that the $x$- and $y$-dipoles have the same
+response to the sky after rotating one by 90$^\circ$, and that the beam is invariant under
+north-south and east-west flips.
+
+We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A,
+Per~B\footnote{
+    At 74~MHz, Per~B is about two times brighter than Per~A.
+}, and
 3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
@@
 
+\begin{figure*}[t]
+    \includegraphics[width=\textwidth]{figures/scintillation-refraction/scintillation-refraction}
+    \caption{
+        (a, b) These panels show the measured apparent flux of Cyg~A and Cas~A at 36.528 MHz (red
+        points) and 73.152 MHz (blue points) as a function of time over the observing period. The
+        solid black curves show the expected flux computed using the empirical beam model fits. The
+        thermal noise contribution to each point is about 50 Jy.  Cyg~A is occulted by the White
+        Mountains when it is low on the horizon to the east.
+        (c, d) These panels show the measured position offset of Cyg~A and Cas~A relative to their
+        true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue line).
+    }
+    \label{fig:scintillation}
+\end{figure*}
+
 \begin{figure}[t]
@@
 
-\begin{figure*}[t]
-    \includegraphics[width=\textwidth]{figures/scintillation-refraction/scintillation-refraction}
-    \caption{
-        \textbf{(a, b)} These panels show the measured apparent flux of Cyg~A and Cas~A at 36.528
-        MHz (red points) and 73.152 MHz (blue points) as a function of time over the observing
-        period. The solid black curves show the expected flux computed using the empirical beam
-        model fits. The thermal noise contribution to each point is about 50 Jy. The majority of the
-        scatter is due to ionospheric scintillation.  Cyg~A is occulted by the White Mountains when
-        it is low on the horizon to the east.
-        \textbf{(c, d)} These panels show the measured position offset of Cyg~A and Cas~A relative
-        to their true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue line).
-    }
-    \label{fig:scintillation}
-\end{figure*}
-
-The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index was
+The geomagnetic conditions during this time were mild. The Disturbance storm time (Dst) index, which
+measures the $z$-component of the interplanetary magnetic field, was
 $>-30$ nT during the entirety of the observing period.\footnote{
@@
 Following the classification scheme of \citet{2008GMS...181.....K}, a weak geomagnetic storm has
-$\text{Dst} < -30$ nT. Stronger geomagnetic storms have $\text{Dst} \ll -30$ nT.
+$\text{Dst} < -30$ nT. Stronger geomagnetic storms have $\text{Dst} < -50$ nT.
 
@@
 TEC smoothly varies from 20 TECU at midday to 5 TECU during the night. However, this measurement is
-only sensitive to large scale fluctuations in the ionosphere and doesn't capture small scale
+only sensitive to large scale fluctuations in the ionosphere and does not capture small scale
 fluctuations.
@@
 timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
-A to have a measured flux variations of 50\% between adjacent 13 second integrations.  The measured
-position offset of each source is a measurement of the ionospheric phase gradient across the array.
-This varies on slower 10 minute timescales refracting each source by as much as 20 arcmin (at 36.528
-MHz) from their true astronomical positions as waves in the ionosphere pass through the line of
-sight. The impact of these effects on the sky maps is simulated in \S\ref{sec:ionosphere}.
+A to have a measured flux variations of 50\% between adjacent 13 second integrations.  The variance
+at 36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
+origin. The measured position offset of each source is a measurement of the ionospheric phase
+gradient across the array.  This varies on slower 10 minute timescales refracting each source by as
+much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the ionosphere
+pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe $\sim
+1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on similar
+$\sim10$ minute timescales.  The impact of these effects on the sky maps is simulated in
+\S\ref{sec:ionosphere}.
 
@@
 
-Without removing bright sources from the data, sidelobes from bright sources will dominate the
-variance in the sky maps.  At 74 MHz Cyg~A is a 15,000~Jy source \citep{1977A&A....61...99B}. A
-conservative estimate for the confusion limit at 74 MHz with a 15~arcmin beam is 1000~mJy
-\citep{2014MNRAS.440..327L}. Therefore we require that Cyg~A's sidelobes be at least $-45$~dB down
-from the main lobe to prevent Cyg~A's sidelobes from dominating the variance in the image.
-
-At low frequencies, propagation effects through the ionosphere must be accounted for in order to
-achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
-peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
-scintillation and refractive-offset events on the timescale of a single integration (13 seconds) are
-observed (see Figure~\ref{fig:scintillation}. Therefore the direction dependent calibration changes
-on these timescales and the we must solve for one set of complex gains per source per integration.
+Due to the rapid and large ionospheric fluctuations seen in Figure~\ref{fig:scintillation}, CLEAN
+cannot be relied on to accurately deconvolve bright sources.  However, without removing bright
+sources from the data, sidelobes from these sources will dominate the variance in the sky maps.  At
+74~MHz Cyg~A is a 15,000~Jy source \citep{1977A&A....61...99B}. A conservative estimate for the
+confusion limit at 74 MHz with a 15~arcmin beam is 1000~mJy \citep{2014MNRAS.440..327L}. Therefore
+we require that Cyg~A's sidelobes be at least $-45$~dB down from the main lobe to prevent Cyg~A's
+sidelobes from dominating the variance in the image.
+
+In order to account for propagation effects through the ionosphere direction-dependent calibration
+and peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S} must be used.  Direction-dependent
+calibration allows the per-antenna amplitude and phase towards a bright astronomical source to be
+free parameters. In the dataset used in this paper, scintillation and refractive-offset events on
+the timescale of a single integration (13 seconds) are observed (Figure~\ref{fig:scintillation}).
+Therefore the direction dependent calibration changes on these timescales and we must solve for one
+set of complex gains per source per integration.
 
 The largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale of Cyg~A is
-$\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines, the OVRO-LWA marginally
-resolves both sources. A resolved source model is needed for both sources. We fit a self-consistent
-resolved source model to each source. This is performed by minimizing the variance within an
-aperture located on each source after peeling. By phasing up a large number of integrations before
-imaging (at least 1 hour) it is possible to smear out the contribution of the rest of the sky.  We
-then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until
-the variance within the aperture is minimized.  Armed with resolved source models for both Cyg~A and
-Cas~A, these two sources can be peeled from the dataset to the required dynamic range.
+$\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at 73~MHz, the OVRO-LWA
+marginally resolves both sources. A resolved source model is needed for both sources. We fit a
+self-consistent resolved source model to each source. This is performed by minimizing the variance
+within an aperture located on each source after peeling. By phasing up a large number of
+integrations before imaging (at least 1 hour) it is possible to smear out the contribution of the
+rest of the sky.  We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a
+source model until the variance within the aperture is minimized. Cyg~A is modeled with 2 Gaussian
+components, while Cas~A is modeled with 3~Gaussian components. Armed with these  source models, both
+sources can be peeled from the dataset to the required dynamic range.
 
@@
 
-However, the ionosphere will cause these sources to scintillate and refract. So the position and
-flux of each source is measured separately in each channel and integration. The sources are then
+However, the ionosphere will cause these sources to scintillate and refract. The position and flux
+of each source is measured separately in each channel and integration. The sources are then
 subtracted from the visibilities using the updated position and flux of the source. The brightest of
-these sources (Vir~A and Tau~A) are peeled using a direction dependent calibration when they are
-at high elevations.
+these sources (Vir~A and Tau~A) are peeled using a direction dependent calibration when they are at
+high elevations.
 
@@
 The Sun can be trivially removed from any map of the sky by constructing the map using only data
-taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
-However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
-suppress the contribution of the Sun to the maps with the goal of suppressing its sidelobes.  The
-Sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
-optical depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new model is
-needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
-Gaussian components to Cyg~A and Cas~A, this is insufficient for the Sun.  Additionally while most
-astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
-spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
-frequencies than at lower frequencies.
+collected at night. A map of the entire sky can be obtained by using observations spaced 6 months
+apart.  However the dataset used in this paper consists of 28 consecutive hours. Therefore we
+attempt to suppress the contribution of the Sun to the maps with the goal of suppressing its
+sidelobes.  The Sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In
+fact the optical depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new
+model is needed at each frequency. While we could fit a limited number of Gaussian components to
+Cyg~A and Cas~A, this is insufficient for the Sun.  Additionally while most astronomical sources at
+these frequencies have negative spectral indices, the Sun has a positive spectral index. Therefore
+more care will need to be taken in subtracting the Sun at higher frequencies than at lower
+frequencies.
 
@@
     \caption{
-        This figure shows the measured fluxes (black points) of 11 sources plotted against the
-        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
-        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
-        (dot-dash line).
+        Measured fluxes (black points) of 11 sources plotted against the published spectra from
+        \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line below 50 MHz),
+        \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
     }
@@
         OVRO-LWA.  Each map covers the sky north of $\delta=-30^\circ$ with angular resolution of
-        $\sim15$ arcmin. Eight bright sources have been removed from the map (Cyg~A, Cas~A, Vir~A,
+        $\sim15$ arcmin. Eight bright sources have been removed from each map (Cyg~A, Cas~A, Vir~A,
         Tau~A, Her~A, Hya~A, Per~B, and 3C~353). The small blank region near $l=+45.7^\circ$,
@@
         combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
+        Therefore regions with a spectral index of $-2.5$ appear white. Areas with a steeper index
+        appear red and areas with a flatter spectral index appear blue.
     }
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
-    \caption{
+    \includegraphics[width=\textwidth]{figures/spectral-index/better-internal-spectral-index}
+    \caption{
+        \todo{updated this caption}
         This plot shows the local spectral index (estimated by means of a local T-T plot) as a
         contour plot. The contours are overlaid on the three-color image from
-        Figure~\ref{fig:three-color}.
+        Figure~\ref{fig:three-color}. The spectral index fit along the galactic plane is masked
+        because T-T plots assume a single emission mechanism operates in a given region. Along the
+        galactic plane free-free dominated regions lie in close proximity to synchrotron dominated
+        regions. This introduces large systematic errors to the power-law fit unless care is taken
+        to cleanly separate the two types of emission mechanisms.
     }
@@
             }&
-            \multicolumn2c{\tbf{Thermal Noise}\footnote{
+            \multicolumn2c{\tbf{Noise}\footnote{
                 Measured with a jackknife and splitting the dataset into even- and odd-numbered
-                integrations.
+                integrations. This estimate therefore includes all noise sources that act on the
+                timescale of a single 13 second integration (eg. thermal, ionospheric, etc.).
             }} &&
-            \multicolumn2c{\tbf{Singular Values}\footnote{
+            \multicolumn2c{\tbf{Fraction of Modes}\footnote{
                 Singular values of the transfer matrix compared with the value of the regularization
@@
             K & mJy/beam &&
-            fraction $>\sqrt{\varepsilon}$ &
-            fraction $>\sqrt{10\varepsilon}$ \\
+            with $\sigma>\sqrt{\varepsilon}$ &
+            with $\sigma>\sqrt{10\varepsilon}$ \\
         \hline
@@
 Eight sky maps were constructed using Tikhonov-regularized $m$-mode analysis imaging and cleaning
-with observations from the OVRO-LWA. These maps are shown in Figure~\ref{fig:channel-maps}. Each map
-covers the sky north of $\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution resolution. The
-8 brightest northern hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A,
-Her~A, Hya~A, Per~B, and 3C~353) as describe in \S\ref{sec:source-removal}. There is a small blank
-region near $l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the
-observing window. The properties of each map, including frequency, bandwidth, angular resolution,
-and thermal noise are presented in Table~\ref{tab:summary}.
+with observations from the OVRO-LWA. Each map is individually shown in
+Figure~\ref{fig:channel-maps}, and Figure~\ref{fig:three-color} is a three-color image constructed
+from the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz. The maps cover the sky north of
+$\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution resolution. The 8 brightest northern
+hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A, Her~A, Hya~A, Per~B,
+and 3C~353) as described in \S\ref{sec:source-removal}, and there is a small blank region near
+$l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the observing
+window. The properties of each map, including frequency, bandwidth, angular resolution, and thermal
+noise are presented in Table~\ref{tab:summary}.
 
 Due to the considerations presented by \citet{2016ApJ...826..116V}, each of these maps is monopole
-subtracted. Consequently a simple pixel-by-pixel powerlaw fit will be unduly effected by the choice
-of zero-level correction. Instead, temperature-temperature plots (T-T plot) can be used to measure
-the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}. This
-method relies on the assumption that all pixels in a given region are described by the same power
-law. In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated within a
-region $\sim10^\circ$ across by constructing a local T-T plot at every pixel between the maps at
-36.528~MHz and 73.152~MHz. The spectral index contours are overlaid on a 3-color image constructed
-from the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz where the increasing contribution of
-free-free absorption in the galactic plane is apparent as blue regions. Similarly the spectral index
-can be seen to steepen as galactic latitude increases (this is a transition from blue to white to
-yellow that is also evident in the spectral index contours).
+subtracted ($a_{00}=0$). Consequently a simple pixel-by-pixel powerlaw fit will be unduly affected
+by the choice of zero-level correction. Instead, temperature-temperature plots (T-T plot) can be
+used to measure the spectral index independently of any zero-level corrections
+\citep{1962MNRAS.124..297T}. This method relies on the assumption that all pixels in a given region
+are described by the same power law. In Figure~\ref{fig:internal-spectral-index} the spectral index
+is locally estimated within a region $\sim10^\circ$ across by constructing a local T-T plot at every
+pixel between the maps at 36.528~MHz and 73.152~MHz. The spectral index contours are overlaid on the
+3-color image from Figure~\ref{fig:three-color} where free-free regions responsible for flattening
+the spectral index in the galactic plane are plainly visible as extended blue blobs.  Similarly the
+spectral index can be seen to steepen as galactic latitude increases (this is a transition from blue
+to white to yellow that is also evident in the spectral index contours).
 
@@
 astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
-This tends to create rings around the NCP at the declination of bright point sources. These rings
-are naturally removed from the map during CLEANing as long as this filtering step is including in
-the PSF calculation.
-
-The thermal noise in each map is empirically measured using jackknife resampling. The dataset is
-split into even- and odd-numbered integrations. These two groups are imaged and cleaned
-independently, before being compared against the maps constructed from all of the available data
-using the standard jackknife variance estimator. This estimate of the variance includes all sources
-of error that operate on $\sim13$ second timescales (the integration time), but does not account for
-more slowly varying effects (for example, sidereal variation in the system temperature or day-night
-fluctuations in the ionosphere). These thermal noise calculations are summarized in
-Table~\ref{tab:summary}.  VLSSr source counts \citep{2014MNRAS.440..327L} suggest that the confusion
-limit at 74 MHz and 15 arcmin angular resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.
-Each channel map achieves thermal noise $<900$ mJy and therefore each map is likely at or near the
-confusion limit.
+This filtering creates negative rings around the NCP at the declination of bright point sources.
+These rings are naturally removed from the map during CLEANing as long as this filtering step is
+including in the PSF calculation.
+
+The noise in each map is empirically measured using jackknife resampling. The dataset is split into
+even- and odd-numbered integrations. These two groups are imaged and cleaned independently, before
+being compared against the maps constructed from all of the available data using the standard
+jackknife variance estimator. This estimate of the variance includes all sources of error that
+operate on $\sim13$ second timescales (the integration time) such as thermal noise in rapid
+ionospheric fluctuations, but does not account for more slowly varying effects (for example,
+sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
+noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
+\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
+resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
+noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
 
@@
     \caption{
-        This figure illustrates terrestrial sources of correlated noise that are apparent after
-        averaging the visibilities at 62.688 MHz over the entire 28 hour observing period (keeping
-        the phase center at zenith such that astronomical sources of radio emission are smeared
-        along tracks of constant declination). Each panel represents a different component that is
-        removed from the visibilities. The images are generated using WSCLEAN
-        \citep{2014MNRAS.444..606O}, uniform weighting, and only baselines longer than 15
-        wavelengths. Panels (a) and (b) illustrate components that appear noise-like in image-space,
-        but are in fact a constant-offset to the measured visibilities likely associated with
-        cross-talk or common-mode pickup. Panel (c) illustrates a component that is clearly
-        associated with an RFI source on the horizon to the west-north-west of the OVRO-LWA. This
-        RFI source is likely an arcing power line.  Figure~\ref{fig:rings} illustrates the
-        characteristic ring-like artifacts introduced into the maps if these 3 components are not
-        removed prior to $m$-mode analysis imaging. The component shown in panel (a) has about twice
-        the amplitude ($\|\b v_\text{terrestrial}\|$) of panels (b) and (c), and for all three
-        components $\|\b B^*\b v_\text{terrestrial}\|/(\|\b B\|\|\b v_\text{terrestrial}\|) \sim
-        0.035$.
+        Terrestrial sources of correlated noise that are apparent after averaging the visibilities
+        at 62.688 MHz over the entire 28 hour observing period (keeping the phase center at zenith
+        such that astronomical sources of radio emission are smeared along tracks of constant
+        declination). Each panel represents a different component that is removed from the
+        visibilities. The images are generated using WSClean \citep{2014MNRAS.444..606O}, uniform
+        weighting, and only baselines longer than 15 wavelengths. Panels (a) and (b) illustrate
+        components that appear noise-like in image-space, but are in fact a constant-offset to the
+        measured visibilities likely associated with cross-talk or common-mode pickup. Panel (c)
+        illustrates a component that is clearly associated with an RFI source on the horizon to the
+        west-north-west of the OVRO-LWA. This RFI source is likely an arcing power line.
+        Figure~\ref{fig:rings} illustrates the characteristic ring-like artifacts introduced into
+        the maps if these 3 components are not removed prior to $m$-mode analysis imaging. The
+        component shown in panel (a) has about twice the amplitude ($\|\b v_\text{terrestrial}\|$)
+        of panels (b) and (c), and for all three components $\|\b B^*\b v_\text{terrestrial}\|/(\|\b
+        B\|\|\b v_\text{terrestrial}\|) \sim 0.035$.
     }
@@
 
-When writing down Equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated
-voltage fluctuations measured between pairs of antennas are exclusively generated by astronomical
-sources of radio emission. In practice this implicit assumption can be violated. For instance a
-low-frequency interferometer located in the vicinity of an arcing power line will see an additional
-contribution from the radio-frequency interference (RFI) generated by the arcing process. Similarly
-common-mode pickup along the analog signal path of the interferometer may generate an additional
-spurious contribution to the measured visibilities. While the amplitude and phase of these
-contaminating signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
+When writing Equation~\ref{eq:basic-imaging}, it is implicitly assumed that the correlated voltage
+fluctuations measured between pairs of antennas are exclusively generated by astronomical sources of
+radio emission. In practice this assumption can be violated. For instance a low-frequency
+interferometer located in the vicinity of an arcing power line will see an additional contribution
+from the radio-frequency interference (RFI) generated by the arcing process. Similarly common-mode
+pickup along the analog signal path of the interferometer may generate an additional spurious
+contribution to the measured visibilities. While the amplitude and phase of these contaminating
+signals may fluctuate with time, they do not sweep across the sky at the sidereal rate
 characteristic of astronomical sources.
@@
 The Owens Valley is an important source of water and power for the city of Los Angeles.
-Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO-
-LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
-RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
-them by using the curvature of the incoming wavefront to infer a distance. Efforts are currently
-underway to work with the utility pole owners to have these insulators replaced.
+Unfortunately this means that high voltage power lines run along the valley $\gtrsim10$~km to the
+west of the OVRO-LWA. Some of these power line poles have faulty insulators that arc and produce
+pulsed, broadband RFI. Because these poles exist in the near-field of the array, we have been able
+to localize some of them by using the curvature of the incoming wavefront to infer a distance.
+Efforts are currently underway to work with the utility pole owners to have these insulators
+replaced.
 
@@
 unknown (and inhomogeneous due to antenna shadowing effects). Therefore it is not enough to know the
-physical location of the faulty insulator generating the RFI. In addition you must also know the
-response of each antenna (amplitude and phase) in the appropriate direction. This motivates the use
-of peeling, which allows the antenna response to be a free parameter.  Therefore model visibilities
-for the RFI can be obtained by peeling the sources after smearing the visibilities over $>24$ hours.
-See Figure~\ref{fig:fitrfi} for an illustration of some of the removed components at 62.688 MHz.
+physical location of the faulty insulator generating the RFI. In addition we must know the response
+of each antenna (amplitude and phase) in the appropriate direction. This motivates the use of
+peeling, which allows the antenna response to be a free parameter.  Therefore model visibilities for
+the RFI can be obtained by peeling the sources after smearing the visibilities over $>24$ hours.
+Figure~\ref{fig:fitrfi} shows an illustration of some of the removed components at 62.688 MHz.
 
 While attempting to peel RFI sources from the averaged visibilities, it was discovered that
-frequently peeling would prefer to remove components from the visibilities that are not obviously
-associated with any source on the horizon or elsewhere in the sky (see panels (a) and (b) in
+frequently peeling would remove components from the visibilities that are not obviously associated
+with any source on the horizon or elsewhere in the sky (see panels (a) and (b) in
 Figure~\ref{fig:fitrfi}).  These components appear noise-like in the images, but they are actually a
@@
 restricted to modes with small $m$. In this dataset the contamination is largely restricted to $m
-\lesssim 1$. Although the RFI is capable of fluctuating on short timescales, in practice the
-artifacts it introduces seems to be restricted to small $m$ (presumably because the phase is not
+\lesssim 1$. Although the RFI is capable of fluctuating on short timescales, in this case the
+artifacts it introduces seem to be restricted to small $m$ (presumably because the phase is not
 fluctuating).  As a result if the contamination is not suppressed, it will manifest itself as rings
 along stripes of constant declination. This effect is plainly visible in Figure~\ref{fig:fitrfi}.
-Because of the distinctive ring-like pattern created by terrestrial sources, we chose to discard
-spherical harmonics with either $m=0$ or $m=1$ and $l>100$ in order to further suppress the
-contamination.
+Because of the distinctive ring-like pattern created by terrestrial sources, we additionally chose
+to discard spherical harmonics with either $m=0$ or $m=1$ and $l>100$ in order to further suppress
+the contamination.
+
+\subsection{The Ionosphere}\label{sec:ionosphere}
+
+\begin{figure*}[t]
+    \centering
+    \begin{tabular}{cc}
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-4} &
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-18} \\
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-4} &
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-18} \\
+    \end{tabular}
+    %\includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
+    \caption{
+        This figure illustrates the corrupting influence of the ionosphere at 36.528~MHz (left
+        column) compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF
+        for a source at the location of Cas~A.  Each panel illustrates the percent difference
+        (relative to the peak flux of the uncorrupted PSF) due to including an ionospheric effect.
+        In the top row, the simulated source scintillates using the measured light-curve for Cas~A
+        in Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
+        its true position using the measured refractive offsets for Cas~A in
+        Figure~\ref{fig:scintillation}.
+    }
+    \label{fig:ionospheric-simulations}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/postage-stamps/3C134}
+    \caption{
+        A zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
+        (right panel). At 36.528~MHz there are $\sim10\%$ artifacts around 3C~134 that persist after
+        CLEANing due to ionospheric effects. As expected for an ionospheric origin, these artifacts
+        decrease in amplitude as frequency increases.
+    }
+    \label{fig:3C134}
+\end{figure*}
+
+One of the key assumptions made by $m$-mode analysis is that the sky is static.  We assume that the
+only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
+fringe patterns of the interferometer. At low frequencies the ionosphere violates this assumption.
+In particular, ionospheric scintillation and refractive offsets will cause even static sources to
+exhibit significant variability (Figure~\ref{fig:scintillation}).
+
+The correlation observed on a given baseline for a single point source is
+\begin{equation}
+    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
+\end{equation}
+where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$ is the baseline transfer
+function defined by Equation~\ref{eq:baseline-transfer-function}. The transfer function is a
+function of the direction to the source, which is in turn a function of the sidereal time
+$t_{\textrm{sidereal}}$. If the source is varying, from intrinsic variability or due to
+scintillation, than the source flux is also a function of the time coordinate $t$ such that
+\begin{equation}
+    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
+\end{equation}
+where $t_{\textrm{sidereal}} = (t \mod 23^h56^m)$.
+
+In order to compute the $m$-modes we must take the Fourier transform with respect to the sidereal
+time. As a consequence of the Fourier convolution theorem we find:
+\begin{equation}\label{eq:no-longer-block-diagonal}
+    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,.
+\end{equation}
+where $V_{\nu, m}^{\textrm{static}}$ is the set of observed $m$-modes if the source was actually
+static, and $I_{\nu, m-m^\prime}$ is the Fourier transform of the light curve $I_{\nu}(t)$.
+Equation~\ref{eq:no-longer-block-diagonal} indicates that power is scattered between different
+values of $m$. As a consequence, the true transfer matrix, which is exactly block diagonal in the
+ideal case, is no longer truly block diagonal \citep{richard_ionosphere_thoughts}.
+
+The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
+arising from ionospheric fluctuations. The effect of this can be seen in
+Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
+at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
+source is always located exactly at the location of Cas A. In the middle panel, the source is
+allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
+the point source is effectively unchanged from the ideal PSF. In the right panel, the source
+position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
+refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
+from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
+obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
+Figure~\ref{fig:3c134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
+expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
+73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
+vicinity of bright point sources.
 
@@
 
-A good model of the antenna beam is essential for widefield imaging. Because $m$-mode analysis
-imaging operates on a full sidereal day of data, images are constructed after watching each point in
-the sky move through a large slice of the beam (excepting the celestial poles). The beam model
-therefore serves two purposes:
+A model of the antenna beam is essential for widefield imaging. Because $m$-mode analysis imaging
+operates on a full sidereal day of data, images are constructed after watching each point in the sky
+move through a large slice of the beam (excepting the celestial poles). The beam model therefore
+serves two purposes:
 
@@
 the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
-show a clear pattern with declination. Two sources show a clear systematic error at all frequencies:
-3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first southernmost
-source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable declination to
-Lyn A, which appears, if anything, to have its flux overestimated. The absence of a coherent pattern
-doesn't eliminate the possibility of beam errors effecting the flux scale, but it does mean that
-these errors are at least comparable to the errors inherent to the flux scale itself. On the other
-hand, the spectral indices presented in Figure~\ref{fig:internal-spectral-index} are systematically
-flatter from declinations between $-20^\circ$ and $-30^\circ$. This indicates the existence of beam
-errors at elevations $\lesssim20^\circ$.
+show a clear pattern with declination. Two sources have a clear systematic offset at all
+frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
+southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
+declination to Lyn A, which appears, if anything, to have its flux overestimated. The absence of a
+coherent pattern does not eliminate the possibility of beam errors effecting the flux scale, but it
+does mean that these errors are at least comparable to the errors inherent to the flux scale itself.
 
 The second case is more subtle. Sources are observed at a wide range of locations in the primary
-beam of the antenna. The imaging process must reconcile all of these observations together. The beam
-model essentially provides the instructions on how to do this. For example if at a time $t_1$ the
-antenna gain towards a source is $g$ and at a later time $t_2$ the antenna gain towards that same
-source (which has now moved) is $g/2$, then in order to correctly estimate the flux of the source
-the observations from time $t_1$ need to be multiplied by $1/g$ but the observations from time $t_2$
-need to be multiplied by $2/g$. A mistake in the beam model here will lead to a mistake in the
-estimated flux.  However in general the amplitude and phase of the antenna response needs to be
-known and so beam model errors can lead to observations being combined with incorrect phase as well.
-This will lead to a degraded PSF in the final map. This effect is negligible compared to the
-ionospheric effects discussed in \S\ref{sec:ionosphere}.
+beam of the antenna. The imaging process must reconcile all of these observations together, and the
+beam model provides the instructions for how to do this. In the event of an error in the beam model,
+it can be expected that the beam will introduce errors into the sky maps that will limit the dynamic
+range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulate the effect of
+beam errors on a cosmological analysis concluding that the beam must be known to one part in $10^4$.
+Our requirements are significantly less stringent because we are estimating the sky brightness
+instead of estimating the amplitude of a faint cosmological signal in the presence of foreground
+emission that dominates the signal by 5 orders of magnitude. In fact in \S\ref{sec:ionopshere} we
+found that ionospheric effects likely dominate over other sources of error that affect the PSF
+shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
+limit the effect of beam errors on the PSF to at least less than those introduced by the ionosphere.
 
@@
 
-\subsection{The Ionosphere}\label{sec:ionosphere}
-
-\begin{figure*}[t]
-    \includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
-    \caption{
-        This figure illustrates the corrupting influence of the ionosphere at 36.528 MHz. Each panel
-        shows the simulated PSF at the position of Cas~A. The left panel shows the PSF in the event
-        that there is no ionospheric scintillation and no refractive offsets. This is the PSF used
-        to deconvolve the maps with CLEAN. The middle panel shows the PSF with the measured
-        ionospheric scintillation for Cas~A from Figure~\ref{fig:scintillation} but no refractive
-        offsets. The right panel shows the PSF with the measured refractive offsets for Cas~A from
-        Figure~\ref{fig:scintillation} but no scintillation. This demonstrates that the long
-        synthesis images generated by $m$-mode analysis imaging are relatively insensitive to
-        scintillation, but uncorrected refractive offsets can limit the achievable dynamic range.
-    }
-    \label{fig:ionospheric-simulations}
-\end{figure*}
-
-One of the key assumptions made by $m$-mode analysis is that the sky is completely static.  We
-assume that the only time-dependent behavior is the rotation of the Earth, which slowly rotates the
-sky through the fringe patterns of the interferometer. At low frequencies the ionosphere violates
-this assumption. In particular, ionospheric scintillation and refractive offsets will cause even
-static sources to exhibit significant variability (see Figure~\ref{fig:scintillation}).
-
-The correlation observed on a given baseline for a single point source is
-\begin{equation}
-    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
-\end{equation}
-where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$ is the baseline transfer
-function defined by Equation~\ref{eq:baseline-transfer-function}. The transfer function is a
-function of the direction to the source, which is in turn a function of the sidereal time
-$t_{\textrm{sidereal}}$. If the source is varying, from intrinsic variability or due to
-scintillation, than the source flux is also a function of the time coordinate $t$ such that
-\begin{equation}
-    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
-\end{equation}
-where $t_{\textrm{sidereal}} = (t \mod 23.9345\,\textrm{hours})$.
-
-In order to compute the $m$-modes we must Fourier transform with respect to the sidereal time. As a
-consequence of the Fourier convolution theorem we find:
-\begin{equation}\label{eq:no-longer-block-diagonal}
-    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,.
-\end{equation}
-where $V_{\nu, m}^{\textrm{static}}$ is the set of observed $m$-modes if the source was actually
-static, and $I_{\nu, m-m^\prime}$ is the Fourier transform of the light curve $I_{\nu}(t)$.
-Equation~\ref{eq:no-longer-block-diagonal} indicates that power is scattered between different
-values of $m$. As a consequence, the true transfer matrix, which is exactly block diagonal in the
-ideal case, is no longer truly block diagonal \citep{richard_ionosphere_thoughts}.
-
-The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
-arising from ionospheric fluctuations. The effect of this can be seen in
-Figure~\ref{fig:ionospheric-simulations}. In this simulation a point source is placed at the
-location of Cas A. In the first panel the source flux traces the beam model exactly and the source
-is always located exactly at the location of Cas A. In the middle panel, the source is allowed to
-scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of the point
-source is effectively unchanged from the ideal PSF. In the right panel, the source position is
-allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The refractive offsets
-lead to a clear degradation of the sidelobes. Because the sidelobes are altered from that of the
-ideal PSF, refractive offsets will restrict the dynamic range it is possible to obtain with the
-CLEAN algorithm described in \S\ref{sec:clean}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
-        OVRO-LWA map. The red patch around the north celestial pole corresponds to where the
-        Guzm\'{a}n map has a blank region.  The larger blue patch around the south celestial pole
-        corresponds to where the OVRO-LWA map has a blank region. Note also that the OVRO-LWA map
-        has several bright point sources subtracted that are not subtracted from the Guzm\'{a}n map.
+        OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
+        subtracted from the OVRO-LWA maps but not the Guzm\'{a}n map.
     }
@@
     \centering
-    \includegraphics[height=0.32\textheight]{figures/haslam/haslam-spectral-index}
-    \caption{
+    \includegraphics[height=0.32\textheight]{figures/haslam/better-haslam-spectral-index}
+    \caption{
+        \todo{update caption}
         The contours show the spectral index between the reprocessed Haslam 408 MHz map and the
@@
 and cleaning -- for drift-scanning telescopes like the OVRO-LWA.  This technique exactly corrects
-for widefield effects in interferometric imaging, but offers a $\sim10^6$ times speed-up relative to
-the naive approach for the OVRO-LWA. We applied this technique to a 28 hour dataset and generated 8
-sky maps between 36.528~MHz and 73.152~MHz. These sky maps are a substantial improvement over
-existing maps at these frequencies due to their 15~arcmin angular resolution and $<600$~K thermal
-noise. The point source flux scale is consistent with that defined by \citet{2012MNRAS.423L..30S} to
-about 5\% and large angular scales are consistent with the work of \citet{2011A&A...525A.138G} to
-within 20\%.  These maps are primarily intended to be used as part of a foreground modeling and
-subtraction routine for 21~cm cosmology experiments.
+for widefield effects in interferometric imaging with a single synthesis imaging step.  We applied
+Tikhonov regularized $m$-mode analysis imaging to a 28 hour dataset and generated 8 sky maps between
+36.528~MHz and 73.152~MHz.  These sky maps are a substantial improvement over existing maps at these
+frequencies due to their 15~arcmin angular resolution and $<600$~K thermal noise. The point source
+flux scale is consistent with that defined by \citet{2012MNRAS.423L..30S} to about 5\% and large
+angular scales are consistent with the work of \citet{2011A&A...525A.138G} to within 20\%.  These
+maps are primarily intended to be used as part of a foreground modeling and subtraction routine for
+21~cm cosmology experiments.
 
@@
 
+\acknowledgments
+This work is dedicated to the memory of Professor Marjorie Corcoran, who was an influential mentor
+to M.~W.~Eastwood.
+
 \bibliographystyle{apj}

### 2017-10-04 figures/antenna-layout/make.jl

@@ -16,10 +16,13 @@ east -= 2
 core = 1:251
 leda = 252:256
 expansion = 257:288
+off = [collect(57:64); collect(121:128); collect(185:192); collect(239:246)]
+core = setdiff(core, off)
 
 gca()[:tick_params](axis="both", which="major", labelsize=12)
 
 scatter(east[core], north[core], marker=".", c="k", s=20, lw=0)
+scatter(east[off], north[off], marker=".", c="r", s=20, lw=0)
 scatter(east[leda], north[leda], marker="+", c="k", s=50)
 scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
 gca()[:set_aspect]("equal")

### 2017-10-04 figures/channel-maps/make.jl

@@ -50,6 +50,11 @@ for (idx, spw) in enumerate(4:2:18)
     gca()[:get_yaxis]()[:set_visible](false)
     axis("off")
 
+    tight_layout()
+
+    savefig(joinpath(path, "$str-notext.pdf"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
+
     txt = text(0.01, 0.98, @sprintf("%.3f MHz", ν/1e6),
                transform=gca()[:transAxes], fontsize=14, fontweight="bold",
                horizontalalignment="left", verticalalignment="top",
@@ -79,8 +84,6 @@ for (idx, spw) in enumerate(4:2:18)
     #cbar[:ax][:tick_params](labelsize=12)
     #cbar[:set_label]("brightness temperature (K)", fontsize=12, rotation=270)
     #cbar[:ax][:get_yaxis]()[:set_label_coords](4.5, 0.5)
-
-    tight_layout()
 
     savefig(joinpath(path, "$str.pdf"),
             bbox_inches="tight", pad_inches=0, transparent=true)

### 2017-10-04 figures/haslam/fetch.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/haslam-spectral-index.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/haslam-spectral-index-updated.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/glamour-map-restored-registered-rainy.jld spw10.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/glamour-map-restored-registered-rainy.jld spw18.jld

### 2017-10-04 figures/haslam/make.jl

@@ -8,8 +8,8 @@ using Colors, PerceptualColourMaps
 path = dirname(@__FILE__)
 
 function go()
-    slope, residual, mask = load(joinpath(path, "haslam-spectral-index.jld"),
-                                 "slope", "residual", "mask")
+    slope, R², mask = load(joinpath(path, "haslam-spectral-index-updated.jld"),
+                           "slope", "coefficient-of-determination", "mask")
 
     ν1 = 36.528
     ν2 = 52.224
@@ -63,10 +63,14 @@ function go()
     tight_layout()
 
     map = RingHealpixMap(clamp.(solve_for_spectral_index(slope, ν3, ν4), -3.5, -1.5))
-    img = mollweide(map, (4096, 2048))
-    mask_img = mollweide(RingHealpixMap(mask), (4096, 2048))
+    img = mollweide(map, (2048, 4096))
+    mask_img = mollweide(RingHealpixMap(mask), (2048, 4096))
+    R²_img = mollweide(RingHealpixMap(R²), (2048, 4096))
     img[mask_img] = NaN
     img[img .== 0] = NaN # this deletes contours around the edge of the map
+    R²_img[mask_img] = NaN
+    R²_img[img .== 0] = NaN # this deletes contours around the edge of the map
+
     cs = contour(img, -3.5:0.1:-1.5,
                  extent=(-2, 2, 1, -1), origin="lower",
                  #cmap=ColorMap(cmap_samples),
@@ -82,6 +86,39 @@ function go()
 
     savefig(joinpath(path, "haslam-spectral-index.pdf"),
             bbox_inches="tight", pad_inches=0, transparent=true)
+
+    figure(2, figsize=(12, 5)); clf()
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+
+    xlim(-2, 2)
+    ylim(-1, 1)
+    gca()[:set_aspect]("equal")
+    gca()[:get_xaxis]()[:set_visible](false)
+    gca()[:get_yaxis]()[:set_visible](false)
+    axis("off")
+    tight_layout()
+
+    cs1 = contour(R²_img, [0.7, 0.9, 1.0],
+                  extent=(-2, 2, 1, -1), origin="lower",
+                  linewidths=1,
+                  colors="k",
+                  clip_path=ellipse)
[…]

### 2017-10-04 figures/ionospheric-simulations/fetch.sh

@@ -1,6 +1,10 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/base-image.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/scintillation-flux.jld .
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/refraction-position.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/base-image-4.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/scintillation-flux-4.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/refraction-position-4.jld .
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/base-image-18.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/scintillation-flux-18.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/IonosphereSimulations/refraction-position-18.jld .
 

### 2017-10-04 figures/ionospheric-simulations/make.jl

@@ -5,67 +5,68 @@ using JLD, PyPlot, PyCall
 @pyimport mpl_toolkits.axes_grid1 as tk
 
 path = dirname(@__FILE__)
-figure(1, figsize=(12, 4)); clf()
 
-max = 1.0
-min = 0.0
-
-function plot_image(filename)
-    global max, min
+function plot_image(spw, filename)
     img = load(joinpath(path, filename*".jld"), "img")
-    if filename == "base-image"
-        max = maximum(img)
-        img ./= max
-        min = minimum(img)
-    else
-        img ./= max
-    end
+    img′ = load(joinpath(path, "base-image-$spw.jld"), "img")
+    img .-= img′
+    img ./= maximum(img′)
+    img .*= 100
+
+    max = maximum(abs.(img))
+    min = -max
+
+
     img = img[51:151, 51:151]
     gca()[:tick_params](axis="both", which="major", labelsize=12)
     gca()[:set_aspect]("equal")
     out = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
-                 vmin=-0.1, vmax=0.3,
+                 vmin=min, vmax=max,
                  extent=(150, -150, -150, 150))
     xlim(140, -140)
     ylim(-140, 140)
     out
 end
 
-function label(string)
-    text(0.95, 0.95, string,
-         transform=gca()[:transAxes], fontsize=16, fontweight="bold",
+function label(spw, string)
+    ν = spw == 4 ? "36.528 MHz" : "73.152 MHz"
+    text(0.05, 0.95, string,
+         transform=gca()[:transAxes], fontsize=14, fontweight="bold",
+         horizontalalignment="left", verticalalignment="top",
+         color="white", zorder=2)
+    text(0.95, 0.95, ν,
+         transform=gca()[:transAxes], fontsize=14, fontweight="bold",
          horizontalalignment="right", verticalalignment="top",
          color="white", zorder=2)
 end
 
-ax = gca()
-divider = tk.make_axes_locatable(ax)
+for (idx, stuff) in enumerate(((4, "scintillation-flux"), (4, "refraction-position"),
+                               (18, "scintillation-flux"), (18, "refraction-position")))
+    spw, filename = stuff
+    figure(idx, figsize=(6, 4)); clf()
+    ax = gca()
[…]

### 2017-10-04 figures/postage-stamps/fetch.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/postage-stamp-3C134.jld 3C134-spw04.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/postage-stamp-3C134.jld 3C134-spw10.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/postage-stamp-3C134.jld 3C134-spw18.jld
+

### 2017-10-04 figures/postage-stamps/make.jl

@@ -1,0 +1,66 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot, PyCall
+
+@pyimport mpl_toolkits.axes_grid1 as tk
+
+path = dirname(@__FILE__)
+
+figure(1, figsize=(12, 4)); clf()
+
+frequencies = [3.6528e7, 5.2224e7, 7.3152e7]
+filenames = ["3C134-spw04", "3C134-spw10", "3C134-spw18"]
+
+function plot_image(filename)
+    img = load(joinpath(path, filename*".jld"), "img")
+    img = img[51:151, 51:151].'
+    img ./= maximum(img)
+    gca()[:tick_params](axis="both", which="major", labelsize=12)
+    gca()[:set_aspect]("equal")
+    out = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
+                 origin="lower",
+                 vmin=-0.1, vmax=0.3,
+                 extent=(150, -150, -150, 150))
+    xlim(140, -140)
+    ylim(-140, 140)
+    out
+end
+
+function label(idx)
+    text(0.95, 0.95, @sprintf("%.3f MHz", frequencies[idx]/1e6),
+         transform=gca()[:transAxes], fontsize=16, fontweight="bold",
+         horizontalalignment="right", verticalalignment="top",
+         color="white", zorder=2)
+end
+
+ax = gca()
+divider = tk.make_axes_locatable(ax)
+
+_im = plot_image(filenames[1])
+label(1)
+xlabel("ΔRA (arcmin)", fontsize=12)
+ylabel("Δdec (arcmin)", fontsize=12)
+
+_ax = divider[:append_axes]("right", size="100%", pad=0.10)
+plot_image(filenames[2])
+label(2)
+xlabel("ΔRA (arcmin)", fontsize=12)
+plt[:setp](gca()[:get_yticklabels](), visible=false)
+
+_ax = divider[:append_axes]("right", size="100%", pad=0.10)
+plot_image(filenames[3])
+label(3)
+xlabel("ΔRA (arcmin)", fontsize=12)
+plt[:setp](gca()[:get_yticklabels](), visible=false)
+
+cax = divider[:append_axes]("right", size="5%", pad=0.10)
+cbar = colorbar(_im, cax=cax)
+cbar[:ax][:tick_params](labelsize=12)
+cbar[:set_label]("normalized amplitude", fontsize=12, rotation=270)
[…]

### 2017-10-04 figures/psf/fetch.sh

@@ -4,3 +4,11 @@ scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/wor
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/tmp/spw10-psf-+45-degrees.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/tmp/spw18-psf-+45-degrees.jld .
 
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/tmp/spw04-psf-+75-degrees.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/tmp/spw10-psf-+75-degrees.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/tmp/spw18-psf-+75-degrees.jld .
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/tmp/spw04-psf-+0-degrees.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/tmp/spw10-psf-+0-degrees.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/tmp/spw18-psf-+0-degrees.jld .
+

### 2017-10-04 figures/psf/make.jl

@@ -5,59 +5,70 @@ using JLD, PyPlot, PyCall
 @pyimport mpl_toolkits.axes_grid1 as tk
 
 path = dirname(@__FILE__)
-figure(1, figsize=(12, 4)); clf()
+for (idx, str) in enumerate(("+45", "+75", "+0"))
+    figure(idx, figsize=(12, 4)); clf()
 
-frequencies = [3.6528e7, 5.2224e7, 7.3152e7]
-filenames = ["spw04-psf-+45-degrees", "spw10-psf-+45-degrees", "spw18-psf-+45-degrees"]
+    dec = parse(str)
+    frequencies = [3.6528e7, 5.2224e7, 7.3152e7]
+    filenames = ["spw04-psf-$str-degrees", "spw10-psf-$str-degrees", "spw18-psf-$str-degrees"]
+    
+    function plot_image(filename)
+        img = load(joinpath(path, filename*".jld"), "img")
+        img = img[51:151, 51:151].'
+        gca()[:tick_params](axis="both", which="major", labelsize=12)
+        gca()[:set_aspect]("equal")
+        out = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
+                     origin="lower",
+                     vmin=-0.1, vmax=0.3,
+                     extent=(150, -150, -150, 150))
+        xlim(140, -140)
+        ylim(-140, 140)
+        out
+    end
 
-function plot_image(filename)
-    img = load(joinpath(path, filename*".jld"), "img")
-    img = img[51:151, 51:151]
-    gca()[:tick_params](axis="both", which="major", labelsize=12)
-    gca()[:set_aspect]("equal")
-    out = imshow(img.', interpolation="nearest", cmap=get_cmap("magma"),
-                 vmin=-0.1, vmax=0.3,
-                 extent=(150, -150, -150, 150))
-    xlim(140, -140)
-    ylim(-140, 140)
-    out
+    function label(idx)
+        text(0.95, 0.95, @sprintf("%.3f MHz", frequencies[idx]/1e6),
+             transform=gca()[:transAxes], fontsize=16, fontweight="bold",
+             horizontalalignment="right", verticalalignment="top",
+             color="white", zorder=2)
+        text(0.05, 0.95, @sprintf("δ=+%02d°", dec),
[…]

### 2017-10-04 figures/spectral-index/fetch.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/internal-spectral-index.jld .
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/internal-spectral-index-updated.jld .
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/glamour-map-restored-registered-rainy.jld spw10.jld
 scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/glamour-map-restored-registered-rainy.jld spw18.jld

### 2017-10-04 figures/spectral-index/make.jl

@@ -8,9 +8,8 @@ using Colors, PerceptualColourMaps
 path = dirname(@__FILE__)
 
 function go()
-    slope, jackknives, residual, masks = load(joinpath(path, "internal-spectral-index.jld"),
-                                              "slope", "jackknives", "residual", "masks")
-    mask = Vector{Bool}(masks[1] .== 1)
+    slope, R², mask = load(joinpath(path, "internal-spectral-index-updated.jld"),
+                           "slope", "coefficient-of-determination", "mask")
 
     ν1 = 36.528
     ν2 = 52.224
@@ -69,10 +68,14 @@ function go()
             bbox_inches="tight", pad_inches=0, transparent=true)
 
     map = RingHealpixMap(solve_for_spectral_index(slope, ν1, ν3))
-    img = mollweide(map, (4096, 2048))
-    mask_img = mollweide(RingHealpixMap(mask), (4096, 2048))
+    img = mollweide(map, (2048, 4096))
+    mask_img = mollweide(RingHealpixMap(mask), (2048, 4096))
+    R²_img = mollweide(RingHealpixMap(R²), (2048, 4096))
     img[mask_img] = NaN
     img[img .== 0] = NaN # this deletes contours around the edge of the map
+    R²_img[mask_img] = NaN
+    R²_img[img .== 0] = NaN # this deletes contours around the edge of the map
+
     cs = contour(img, -3.5:0.1:-1.5,
                  extent=(-2, 2, 1, -1), origin="lower",
                  #cmap=ColorMap(cmap_samples),
@@ -89,6 +92,39 @@ function go()
 
     savefig(joinpath(path, "internal-spectral-index.pdf"),
             bbox_inches="tight", pad_inches=0, transparent=true)
+
+    figure(2, figsize=(12, 5)); clf()
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+
+    xlim(-2, 2)
+    ylim(-1, 1)
+    gca()[:set_aspect]("equal")
+    gca()[:get_xaxis]()[:set_visible](false)
+    gca()[:get_yaxis]()[:set_visible](false)
+    axis("off")
+    tight_layout()
+
+    cs1 = contour(R²_img, [0.7, 0.9, 1.0],
+                  extent=(-2, 2, 1, -1), origin="lower",
+                  linewidths=1,
[…]

### 2017-10-10 figures/lwa1/fetch.sh
add a figure comparing with the lwa1 sky survey

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/lwa1-comparison.jld .
+

### 2017-10-10 figures/lwa1/make.jl

@@ -1,0 +1,54 @@
+#!/usr/bin/env julia
+
+using JLD, PyPlot, LibHealpix
+
+path = dirname(@__FILE__)
+
+originals, lwa1, ovro, masks = load(joinpath(path, "lwa1-comparison.jld"),
+                                    "lwa1-original", "lwa1", "ovro", "masks")
+ν = ["38 MHz", "40 MHz", "45 MHz", "50 MHz", "60 MHz", "70 MHz"]
+
+figure(1, figsize=(12, 8)); clf()
+axes = []
+for idx = 1:6
+    global _im
+    subplot2grid((3, 2), (div(idx-1, 2), mod(idx-1, 2)))
+    push!(axes, gca())
+
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+
+    δ = (ovro[idx]-lwa1[idx])./originals[idx]
+    δ[.!masks[idx]] = NaN
+    _im = imshow(mollweide(RingHealpixMap(δ)), interpolation="nearest",
+                 vmin=-0.5, vmax=+0.5,
+                 cmap=get_cmap("RdBu_r"),
+                 extent=(-2, 2, -1, 1),
+                 clip_path=ellipse, zorder=1)
+    xlim(-2, 2)
+    ylim(-1, 1)
+    gca()[:set_aspect]("equal")
+    gca()[:get_xaxis]()[:set_visible](false)
+    gca()[:get_yaxis]()[:set_visible](false)
+    axis("off")
+
+    text(0.01, 0.99, ν[idx],
+         transform=gca()[:transAxes], fontsize=16, fontweight="bold",
+         horizontalalignment="left", verticalalignment="top",
+         color="black", zorder=2)
+end
+
+tight_layout()
+cbar = colorbar(_im, ax=axes)
+
+gcf()[:subplots_adjust](hspace=0.05, wspace=0.05, right=0.8)
+cbar[:ax][:tick_params](labelsize=12)
+cbar[:set_label]("fractional difference", fontsize=12, rotation=270)
+cbar[:ax][:get_yaxis]()[:set_label_coords](3.0, 0.5)
+
+savefig(joinpath(path, "lwa1.pdf"),
+        bbox_inches="tight", pad_inches=0, transparent=true)
+

### 2017-10-10 paper.tex
re-order some sections of the paper
almost a final draft...

@@
 of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
-\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
+\citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
 \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
@@
 describe our observations with the Owens Valley Long Wavelength Array (OVRO-LWA). In
-\S\ref{sec:results} we present the sky maps, and in \S\ref{sec:error} we discuss some of the sources
-of error present in the maps. Finally in \S\ref{sec:compare} the new sky maps are compared against
-other low-frequency sky maps, and in \S\ref{sec:conclusion} we present our conclusions.
+\S\ref{sec:results} we present the sky maps and compare these maps against other low-frequency sky
+maps.  In \S\ref{sec:error} we discuss some of the sources of error present in the maps, and finally
+in \S\ref{sec:conclusion} we present our conclusions.
 
@@
 Equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well.  We will
-regularize the problem and apply an additional constraint that prefers a unique yet physically
-reasonable solution.
+therefore regularize the problem and apply an additional constraint that prefers a unique yet
+physically reasonable solution.
 
@@
 
-While Tikhonov regularization will force unmeasured modes to zero, if a prior map of the sky already
-exists, it would be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \varepsilon \|\b a-\b
-a_\text{prior}\|^2$.
-
 \subsubsection{L-Curves}
@@
 
-\subsubsection{The Moore-Penrose Pseudoinverse}
-
-The Moore-Penrose pseudoinverse (denoted in this paper with a superscript $\dagger$), is commonly
-applied to find the minimum-norm linear-least squares solution to a set of linear equations. This
-can be used in place of Tikhonov regularization as
+\subsubsection{Other Regularization Schemes}
+
+The choice of applying Tikhonov regularization to $m$-mode analysis imaging is not unique. There
+exists a plethora of alternative regularization schemes that could also be applied. Each
+regularization scheme has its own advantages and disadvantages. For instance Tikhonov regularization
+is simple, independent of prior information, and sets unmeasured modes to zero (a sensible
+expectation). We will now briefly discuss a few other alternatives.
+
+The Moore-Penrose pseudoinverse (denoted with a superscript $\dagger$), is commonly applied to find
+the minimum-norm linear-least squares solution to a set of linear equations. This can be used in
+place of Tikhonov regularization as
 \begin{equation}
@@
 pseudoinverse and Tikhonov regularization is that the pseudoinverse defines a hard transition from
-on to off. Modes are either set to zero or included in the map at their full amplitude. On the other
-hand Tikhonov regularization smoothly interpolates between these behaviors. Because of this,
-Tikhonov regularization tends to produce better results in practical applications.
-
-\subsubsection{Other Regularization Schemes}
-
-In compressed-sensing applications, the $L^1$-norm is used in place of the $L^2$-norm in order to
-encourage sparsity in the reconstructed signal. By expressing the sky in terms of spherical
-harmonics there is no such expectation of sparsity in the solution, and so the $L^1$-norm is
-inappropriate for this application.
-
-Wiener filtering can also be used in place of Tikhonov regularization in the event that the observer
-has a prior expectation on the covariance of the spherical harmonic coefficients in order to
-interpolate missing information. This technique is demonstrated for simulated measurements by
-\citet{2016arXiv161203255B}.
-
-In this work we elect to pursue Tikhonv regularization due to its computational simplicity, smooth
-down-weighting of noisy modes, and independence of prior information.
+``on'' to ``off''. Modes are either set to zero or included in the map at their full amplitude. On
+the other hand Tikhonov regularization smoothly interpolates between these behaviors. Because of
+this, Tikhonov regularization tends to produce better results in practical applications.
+
+In the event that the observer has a prior map of the sky, $\|\b a - \b a_\text{prior}\|^2$ can be
+used as the regularizing norm. This will use the prior map to fill-in missing information instead of
+setting these modes to zero. In this case the minimum is at
+\begin{equation}
+    \b{\hat a}_\text{with prior} = (\b B^*\b B + \varepsilon\b I)^{-1}
+        (\b B^*(\b v - \b B\b a_\text{prior}))
+        + \b a_\text{prior}\,.
+\end{equation}
+If instead the observer has a prior expectation on the covariance of the spherical harmonic
+coefficients, Wiener filtering can also be used.  This technique is demonstrated for simulated
+measurements by \citet{2016arXiv161203255B}.
+
+Alternatively we could opt to regularize the problem by enforcing smoothness in the sky maps. In
+this case, the regularizing norm should be of the form $\|\nabla I(\hat r)\|^2$, where $\nabla I$ is
+the gradient of the sky brightness in the direction $\hat r$. This is actually a generalization of
+Tikhonov regularization where the objective function is $\|\b v-\b B\b a\|^2 + \varepsilon\|\b A\b
+a\|^2$ for some matrix $\b A$. The minimum is at
+\begin{equation}
+    \b{\hat a}_\text{generalized} = (\b B^*\b B + \varepsilon\b A^*\b A)^{-1}\b B^*\b v\,.
+\end{equation}
+
+Finally in many machine learning applications the $L_1$-norm\footnote{
+    $\|\b a\|_1 = \sum_i |a_i|$
+} is used in place of the usual $L_2$-norm in order to encourage sparsity in the reconstructed
+signal. Applying this to $m$-mode analysis imaging would amount to minimizing $\|\b v-\b B\b a\|_2^2
++ \varepsilon\|\b a\|_1$. However, because we have decomposed the sky in terms of spherical
+harmonics, the vector $\b a$ is not expected to be sparse. Consequently the $L_1$-norm is generally
+inappropriate for $m$-mode analysis imaging without an additional change-of-variables designed to
+introduce sparsity.
 
@@
 at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
-model at several frequencies. This process is repeated for each frequency channel.
+model at several frequencies. This process is repeated for each frequency channel. Residuals for
+Cyg~A and Cas~A can be seen in Figure~\ref{fig:scintillation}.
 
@@
 timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
-A to have a measured flux variations of 50\% between adjacent 13 second integrations.  The variance
-at 36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
+A to have measured flux variations of 50\% between adjacent 13 second integrations.  The variance at
+36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
 origin. The measured position offset of each source is a measurement of the ionospheric phase
@@
 
-In order to account for propagation effects through the ionosphere direction-dependent calibration
+In order to account for propagation effects through the ionosphere, direction-dependent calibration
 and peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S} must be used.  Direction-dependent
@@
 
-Other bright sources namely Vir~A, Tau~A, Her~A, Hya~A, Per~B, and 3C~353 are also removed from
-the visibilities prior to imaging. Because these sources are much fainter than Cyg~A and Cas~A, we
-do not need resolved source models to be able to remove these sources from the visibilities without
-residual sidelobes contaminating the image.
+Other bright sources -- namely Vir~A, Tau~A, Her~A, Hya~A, Per~B, and 3C~353 -- are also removed
+from the visibilities prior to imaging. Because these sources are much fainter than Cyg~A and Cas~A,
+we do not need resolved source models to be able to remove these sources from the visibilities
+without residual sidelobes contaminating the image.
 
@@
         combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
-        Therefore regions with a spectral index of $-2.5$ appear white. Areas with a steeper index
-        appear red and areas with a flatter spectral index appear blue.
+        Therefore regions with a spectral index of $-2.5$ will tend to appear white. Areas with a
+        steeper index appear red and areas with a flatter spectral index appear blue.
     }
@@
     \caption{
-        \todo{updated this caption}
-        This plot shows the local spectral index (estimated by means of a local T-T plot) as a
-        contour plot. The contours are overlaid on the three-color image from
-        Figure~\ref{fig:three-color}. The spectral index fit along the galactic plane is masked
-        because T-T plots assume a single emission mechanism operates in a given region. Along the
-        galactic plane free-free dominated regions lie in close proximity to synchrotron dominated
-        regions. This introduces large systematic errors to the power-law fit unless care is taken
-        to cleanly separate the two types of emission mechanisms.
+        The local spectral index measured between the 36.528~MHz map and the 73.152~MHz map
+        estimated by means of a local T-T plot. The color scale gives the spectral index where blue
+        is flat spectrum and red is steep spectrum. The contours give the
+        coefficient-of-determination ($R^2$) for the linear fit to the local T-T plot. If $R^2$ is
+        low, the quality of the fit is low and the estimated spectral index is unreliable. This can
+        be either due to insufficient dynamic range in the local T-T plot or due to multiple
+        emission mechanisms operating in close proximity. Consequently $R^2$ tends to drop at higher
+        galactic latitudes (due to dynamic range), and near \ion{H}{2} regions in the galactic
+        plane (due to multiple emission mechanisms).
     }
     \label{fig:internal-spectral-index}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[height=0.32\textheight]{figures/haslam/better-haslam-spectral-index}
+    \caption{
+        The local spectral index measured between the 73.152~MHz OVRO-LWA map and the reprocessed
+        408~MHz Haslam map \citep{2015MNRAS.451.4311R}.  The color scale gives the spectral index
+        where blue is flat spectrum and red is steep spectrum. The contours give the
+        coefficient-of-determination ($R^2$) for the linear fit to the local T-T plot. See the
+        caption of Figure~\ref{fig:internal-spectral-index} for more details about the
+        coefficient-of-determination..
+    }
+    \label{fig:haslam-spectral-index}
 \end{figure*}
@@
 
-Due to the considerations presented by \citet{2016ApJ...826..116V}, each of these maps is monopole
-subtracted ($a_{00}=0$). Consequently a simple pixel-by-pixel powerlaw fit will be unduly affected
-by the choice of zero-level correction. Instead, temperature-temperature plots (T-T plot) can be
-used to measure the spectral index independently of any zero-level corrections
-\citep{1962MNRAS.124..297T}. This method relies on the assumption that all pixels in a given region
-are described by the same power law. In Figure~\ref{fig:internal-spectral-index} the spectral index
-is locally estimated within a region $\sim10^\circ$ across by constructing a local T-T plot at every
-pixel between the maps at 36.528~MHz and 73.152~MHz. The spectral index contours are overlaid on the
-3-color image from Figure~\ref{fig:three-color} where free-free regions responsible for flattening
-the spectral index in the galactic plane are plainly visible as extended blue blobs.  Similarly the
-spectral index can be seen to steepen as galactic latitude increases (this is a transition from blue
-to white to yellow that is also evident in the spectral index contours).
-
-In order to suppress sources of terrestrial interference, all spherical harmonics with $m=0$, or
-$m=1$ and $l>100$ are filtered from the map (where the spherical harmonics are defined in the J2017
+Each map from Figure~\ref{fig:channel-maps} will be made freely available online in Healpix format
+\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).
+
+Due to the considerations presented by \citet{2016ApJ...826..116V} and discussed in
+\S\ref{sec:mmode-analysis}, each of these maps is monopole subtracted ($a_{00}=0$).  Furthermore, in
+order to suppress sources of terrestrial interference, all spherical harmonics with $m=0$, or $m=1$
+and $l>100$ are filtered from the map (where the spherical harmonics are defined in the J2017
 coordinate system). As will be discussed in \S\ref{sec:rfi}, these spherical harmonics are
@@
 astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
-This filtering creates negative rings around the NCP at the declination of bright point sources.
+This filtering creates negative rings around the NCP at the declination of bright point sources, but
 These rings are naturally removed from the map during CLEANing as long as this filtering step is
-including in the PSF calculation.
+included in the PSF calculation.
 
@@
 jackknife variance estimator. This estimate of the variance includes all sources of error that
-operate on $\sim13$ second timescales (the integration time) such as thermal noise in rapid
+operate on $\sim13$ second timescales (the integration time) such as thermal noise and rapid
 ionospheric fluctuations, but does not account for more slowly varying effects (for example,
@@
 
-Each map from Figure~\ref{fig:channel-maps} is freely available online in Healpix format
-\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).
+In the absence of a zero-level correction, a pixel-by-pixel power law fit to the new maps is
+impossible. In general this zero-level correction requires calibrated total power measurements that
+will be included in future work.  Instead, temperature-temperature plots (T-T plot) can be used to
+measure the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}.
+This method relies on the assumption that all pixels in a given region are described by the same
+power law. In that case there exists a linear relationship between the brightness temperature at
+frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line is a measure of the
+spectral index between the two frequencies. T-T plots can fail to obtain a reliable measure of the
+spectral index in two ways.  First, if there is not enough dynamic range in the emission region
+there may be only a weak correlation between the brightness temperature at $\nu_1$ and $\nu_2$.
+Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free) then
+a single power-law interpretation of the emission in that region will be poor. Consequently spectral
+indices estimated from T-T plots can require careful interpretation.
+
+In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated in each part of
+the sky within a region $\sim10^\circ$ across by constructing local T-T plots between 36.528~MHz and
+73.152~MHz. Contours of constant $R^2$ (the coefficient-of-determination) are overlaid. If $R^2\sim
+1$, the spectral index is reliable because there is locally a strong linear correlation between
+36.528~MHz and 73.152~MHz. However if $R^2\ll 1$, the spectral index calculation is unreliable.
+$R^2$ tends to drop in cold patches of the sky where there is not enough dynamic range to find a
+strong correlation between the two frequencies. $R^2$ also tends to drop in the vicinity of
+\ion{H}{2} regions in the galactic plane due to multiple emission mechanisms violating the
+assumption of a single spectral index. Therefore we should restrict our interpretation of
+Figure~\ref{fig:internal-spectral-index} to the galactic plane and north galactic spur. In the
+galactic plane, the synchrotron spectral index varies between $\sim-2.5$ and $-2.75$. In the
+vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
+can be seen with higher resolution in Figure~\ref{fig:three-color}. Along the galactic plane,
+especially towards the galactic center, \ion{H}{2} regions appear as blue shadows due to free-free
+absorption.
+
+In the literature the spectral index at low frequencies is commonly computed with respect to the
+Haslam 408~MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H}, which was reprocessed by
+\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources.
+Figure~\ref{fig:haslam-spectral-index} displays the spectral index computed between the 73.152~MHz
+map and the reprocessed Haslam map. The spectral index was estimated by degrading the 73.152~MHz map
+to the resolution of the Haslam map and constructing local T-T plots in every direction. The
+coefficient-of-determination is overlaid as a contour plot, however because
+$\log(408\,\text{MHz}/73.152\,\text{MHz}) > \log(73.152\,\text{MHz}/36.528\,\text{MHz})$, the
+spectral indices presented in Figure~\ref{fig:haslam-spectral-index} tend to be more robust than
+those presented in Figure~\ref{fig:internal-spectral-index}. This is reflected by the fact that
+$R^2$ is larger, but the interpretation must still generally be restricted to the galactic plane.
+
+\subsection{Comparisons with Other Sky Maps}\label{sec:compare}
+
+\subsubsection{LWA1 Low Frequency Sky Survey}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/lwa1/lwa1}
+    \caption{\todo{a thing}}
+    \label{fig:lwa1-comparison}
+\end{figure*}
+
+The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced 9 maps of the sky
+between 35~MHz and 80~MHz. 6 of these maps are interior to the frequency range spanned by this work.
+A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In this
+figure the LLFSS maps are filtered to remove the monopole and all modes with $m=0$, and the OVRO-LWA
+maps are interpolated in frequency and blurred to match the angular resolution of the corresponding
+LWA1 map. The dominant feature in this map is a shift of the galactic plane. This feature is also
+seen in comparisons of the LLFSS with the GSM (see for example Figure~9 of
+\citet{2017MNRAS.469.4537D}). Therefore we conclude that this is an artifact of the LLFSS. Otherwise
+at 60~MHz the agreement is generally better than 10\%. However at lower frequencies the agreement
+deterioriates to about 20\%.
+
+The LLFSS incorporates calibrated total power radiometry to estimate the missing flux from short
+spacings. As a result \citet{2017MNRAS.469.4537D} report per-pixel spectral-indices from combining
+all 9 sky maps. Care must be taken in comparing these spectral indices with
+Figure~\ref{fig:internal-spectral-index} because they are susceptible to different systematic
+errors. Both calculations are sensitive to mistakes in the antenna primary beam, but the LLFSS
+spectral indices are additionally sensitive to errors in the zero-level. We will restrict the
+comparison to the galactic plane where the spectral indices are likely to be the most reliable.
+Towards the galactic center both surveys agree that the spectral index is very flat $>-2.2$ due to
+the influence of free-free absorption.  However at galactic latitudes $\sim 180^\circ$ this work
+suggests that the spectral index varies between -2.5 and -2.75, while the LLFSS reports
+substantially flatter indices in the range -2.3 to -2.2. In this region $0.7 < R^2 < 0.9$ so this
+could be an artifact of the comparatively weak correlation between the brightness at 36.528~MHz and
+73.152~MHz, which tends to bias the spectral index towards $-\infty$.
+
+The LLFSS also computes spectral indices with respect to the Haslam 408~MHz map. These spectral
+indices are subject to the same caveats and systematic errors as before. However in general the
+qualitative agreement with Figure~\ref{fig:haslam-spectral-index} is better potentially due to the
+increased robustness associated with estimating spectral indices with a larger fractional bandwidth.
+
+\subsubsection{Guzm\'{a}n 45 MHz Map}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[height=0.32\textheight]{figures/guzman/guzman}
+    \caption{
+        This Mollweide projection map compares the fractional difference between the Guzm\'{a}n 45
+        MHz map, and the OVRO-LWA map at 46.992 MHz (degraded to $5^\circ$ resolution). A positive
+        value indicates regions where the OVRO-LWA map has more emission that the Guzm\'{a}n map,
+        and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
+        OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
+        subtracted from the OVRO-LWA maps but not the Guzm\'{a}n map.
+    }
+    \label{fig:guzman-comparison}
+\end{figure*}
+
+The Guzm\'{a}n 45 MHz map \citep{2011A&A...525A.138G} is compiled from a southern hemisphere survey
+\citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M} with a
+small gap around the NCP. In this work the zero-level is set by comparing against published
+low-frequency measurements in the literature in six different directions.
+
+A direct comparison between the OVRO-LWA maps interpolated to 45 MHz and the Guzm\'{a}n 45 MHz map
+can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this comparison the OVRO-LWA map
+was degraded to a 5$^\circ$ resolution by convolving with a Gaussian kernel, and the Guzm\'{a}n map
+has had spherical harmonics with $m=0$ discarded in order to make it consistent with the maps
+presented in this paper. This figure shows a $\sim20\%$ excess of emission in the galactic plane
+that is consistent with the discrepancy observed between the LLFSS and the Guzm\'{a}n map.  However
+while the LLFSS has an excess of emission near the north galactic pole, no such excess is observed
+in this work. Instead there is a 10\% excess of emission near the south galactic pole. Elsewhere off
+the plane of the galaxy the discrepancy can be as much as $-20\%$.
+
+\citet{2011A&A...525A.138G} compute the spectral index between their 45~MHz map and the 408~MHz
+Haslam map. Along the galactic plane the spectral index varies between -2.2 (in the vicinity of
+\ion{H}{2} regions), and -2.5 (at galactic longitudes $\sim 180^\circ$). The north galactic spur has
+a spectral index of -2.5. This is generally consistent with the results presented in
+Figure~\ref{fig:haslam-spectral-index}.
+
+%\subsection{The Global Sky Model}?
+%\subsection{LWA1 Sky Survey}?
 
@@
 \section{Error Analysis}\label{sec:error}
+
+\subsection{The Ionosphere}\label{sec:ionosphere}
+
+\begin{figure*}[t]
+    \centering
+    \begin{tabular}{cc}
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-4} &
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-18} \\
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-4} &
+        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-18} \\
+    \end{tabular}
+    %\includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
+    \caption{
+        This figure illustrates the corrupting influence of the ionosphere at 36.528~MHz (left
+        column) compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF
+        for a source at the location of Cas~A.  Each panel illustrates the percent difference
+        (relative to the peak flux of the uncorrupted PSF) due to including an ionospheric effect.
+        In the top row, the simulated source scintillates using the measured light-curve for Cas~A
+        in Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
+        its true position using the measured refractive offsets for Cas~A in
+        Figure~\ref{fig:scintillation}.
+    }
+    \label{fig:ionospheric-simulations}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/postage-stamps/3C134}
+    \caption{
+        A zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
+        (right panel). At 36.528~MHz there are $\sim10\%$ artifacts around 3C~134 that persist after
+        CLEANing due to ionospheric effects. As expected for an ionospheric origin, these artifacts
+        decrease in amplitude as frequency increases. Figure~\ref{fig:ionospheric-simulations} shows
+        the typically expected amplitude of these effects for ionospheric scintillation and
+        refractive offsets.
+    }
+    \label{fig:3C134}
+\end{figure*}
+
+One of the key assumptions made by $m$-mode analysis is that the sky is static.  We assume that the
+only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
+fringe patterns of the interferometer. At low frequencies the ionosphere violates this assumption.
+In particular, ionospheric scintillation and refractive offsets will cause even static sources to
+exhibit significant variability (Figure~\ref{fig:scintillation}).
+
+The correlation observed on a given baseline for a single point source is
+\begin{equation}
+    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
+\end{equation}
+where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$ is the baseline transfer
+function defined by Equation~\ref{eq:baseline-transfer-function}. The transfer function is a
+function of the direction to the source, which is in turn a function of the sidereal time
+$t_{\textrm{sidereal}}$. If the source is varying, from intrinsic variability or due to
+scintillation, than the source flux is also a function of the time coordinate $t$ such that
+\begin{equation}
+    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
+\end{equation}
+where $t_{\textrm{sidereal}} = (t \mod 23^h56^m)$.
+
+In order to compute the $m$-modes we must take the Fourier transform with respect to the sidereal
+time. As a consequence of the Fourier convolution theorem we find:
+\begin{equation}\label{eq:no-longer-block-diagonal}
+    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,.
+\end{equation}
+where $V_{\nu, m}^{\textrm{static}}$ is the set of observed $m$-modes if the source was actually
+static, and $I_{\nu, m-m^\prime}$ is the Fourier transform of the light curve $I_{\nu}(t)$.
+Equation~\ref{eq:no-longer-block-diagonal} indicates that power is scattered between different
+values of $m$. As a consequence, the true transfer matrix, which is exactly block diagonal in the
+ideal case, is no longer truly block diagonal \citep{richard_ionosphere_thoughts}.
+
+The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
+arising from ionospheric fluctuations. The effect of this can be seen in
+Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
+at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
+source is always located exactly at the location of Cas A. In the middle panel, the source is
+allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
+the point source is effectively unchanged from the ideal PSF. In the right panel, the source
+position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
+refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
+from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
+obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
+Figure~\ref{fig:3C134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
+expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
+73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
+vicinity of bright point sources.
+
+\subsection{Beam Errors}
+
+A model of the antenna beam is essential for widefield imaging. Because $m$-mode analysis imaging
+operates on a full sidereal day of data, images are constructed after watching each point in the sky
+move through a large slice of the beam (excepting the celestial poles). The beam model therefore
+serves two purposes:
+
+\begin{enumerate}
+    \item setting the flux scale as a function of declination
+    \item reconciling observations from two separate sidereal times
+\end{enumerate}
+
+In the first case, all sources at a given declination take the same path through the antenna primary
+beam. If the antenna response is overestimated along this track then all sources at this declination
+will have their flux underestimated. Similarly if the antenna response is underestimated then all
+the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
+show a clear pattern with declination. Two sources have a clear systematic offset at all
+frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
+southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
+declination to Lyn A, which appears, if anything, to have its flux overestimated. The absence of a
+coherent pattern does not eliminate the possibility of beam errors effecting the flux scale, but it
+does mean that these errors are at least comparable to the errors inherent to the flux scale itself.
+
+The second case is more subtle. Sources are observed at a wide range of locations in the primary
+beam of the antenna. The imaging process must reconcile all of these observations together, and the
+beam model provides the instructions for how to do this. In the event of an error in the beam model,
+it can be expected that the beam will introduce errors into the sky maps that will limit the dynamic
+range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulate the effect of
+beam errors on a cosmological analysis concluding that the beam must be known to one part in $10^4$.
+Our requirements are significantly less stringent because we are estimating the sky brightness
+instead of estimating the amplitude of a faint cosmological signal in the presence of foreground
+emission that dominates the signal by 5 orders of magnitude. In fact in \S\ref{sec:ionosphere} we
+found that ionospheric effects likely dominate over other sources of error that affect the PSF
+shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
+limit the effect of beam errors on the PSF to at least less than those introduced by the ionosphere.
+
+\subsection{Polarization Leakage}
+
+\citet{2015PhRvD..91h3514S} describe how to generalize $m$-mode analysis to account for a polarized
+sky observed with a polarized antenna beam. Heretofore this generalization has been neglected in the
+discussion of $m$-mode analysis imaging.  At low frequencies, increasingly rapid Faraday rotation
+leads to depolarization. Therefore polarization fractions are generally expected to decrease at low
+frequencies (varying with ionospheric conditions). \citet{2016ApJ...830...38L} detected the presence
+of diffuse polarized emission on degree angular scales with the MWA, also finding typical
+depolarization ratios of $\sim0.3$ for pulsars at 154~MHz relative to 1.4~GHz, although there was a
+large variance between pulsars. Even more depolarization is expected at frequencies $\le
+73.152$~MHz, but crossed-dipole antennas with extremely large primary beams will naturally introduce
+large polarization leakage terms at low elevations.  It is instructive to compute what impact this
+will have on the unpolarized imaging process.
+
+In order to understand the effect of polarization leakage, a point source with 10\% polarization in
+Stokes-$Q$ was simulated at the location of Cas A.  The simulated visibilities were computed using
+the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
+every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
+Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
+rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about 7 hours
+every day skirting the horizon where the polarization leakage is large, so by placing the simulated
+source at the location of Cas A, we are engineering a situation where the polarization leakage from
+Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
+maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
+PSF.
 
@@
 
-\subsection{The Ionosphere}\label{sec:ionosphere}
-
-\begin{figure*}[t]
-    \centering
-    \begin{tabular}{cc}
-        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-4} &
-        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-18} \\
-        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-4} &
-        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-18} \\
-    \end{tabular}
-    %\includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
-    \caption{
-        This figure illustrates the corrupting influence of the ionosphere at 36.528~MHz (left
-        column) compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF
-        for a source at the location of Cas~A.  Each panel illustrates the percent difference
-        (relative to the peak flux of the uncorrupted PSF) due to including an ionospheric effect.
-        In the top row, the simulated source scintillates using the measured light-curve for Cas~A
-        in Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
-        its true position using the measured refractive offsets for Cas~A in
-        Figure~\ref{fig:scintillation}.
-    }
-    \label{fig:ionospheric-simulations}
-\end{figure*}
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/postage-stamps/3C134}
-    \caption{
-        A zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
-        (right panel). At 36.528~MHz there are $\sim10\%$ artifacts around 3C~134 that persist after
-        CLEANing due to ionospheric effects. As expected for an ionospheric origin, these artifacts
-        decrease in amplitude as frequency increases.
-    }
-    \label{fig:3C134}
-\end{figure*}
-
-One of the key assumptions made by $m$-mode analysis is that the sky is static.  We assume that the
-only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
-fringe patterns of the interferometer. At low frequencies the ionosphere violates this assumption.
-In particular, ionospheric scintillation and refractive offsets will cause even static sources to
-exhibit significant variability (Figure~\ref{fig:scintillation}).
-
-The correlation observed on a given baseline for a single point source is
-\begin{equation}
-    V_\nu(t_{\textrm{sidereal}}) = I_\nu B_\nu(t_{\textrm{sidereal}}),
-\end{equation}
-where $I_\nu$ is the flux of the source at the frequency $\nu$, and $B_\nu$ is the baseline transfer
-function defined by Equation~\ref{eq:baseline-transfer-function}. The transfer function is a
-function of the direction to the source, which is in turn a function of the sidereal time
-$t_{\textrm{sidereal}}$. If the source is varying, from intrinsic variability or due to
-scintillation, than the source flux is also a function of the time coordinate $t$ such that
-\begin{equation}
-    V_\nu(t_{\textrm{sidereal}}) = I_\nu(t) B_\nu(t_{\textrm{sidereal}}),
-\end{equation}
-where $t_{\textrm{sidereal}} = (t \mod 23^h56^m)$.
-
-In order to compute the $m$-modes we must take the Fourier transform with respect to the sidereal
-time. As a consequence of the Fourier convolution theorem we find:
-\begin{equation}\label{eq:no-longer-block-diagonal}
-    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,.
-\end{equation}
-where $V_{\nu, m}^{\textrm{static}}$ is the set of observed $m$-modes if the source was actually
-static, and $I_{\nu, m-m^\prime}$ is the Fourier transform of the light curve $I_{\nu}(t)$.
-Equation~\ref{eq:no-longer-block-diagonal} indicates that power is scattered between different
-values of $m$. As a consequence, the true transfer matrix, which is exactly block diagonal in the
-ideal case, is no longer truly block diagonal \citep{richard_ionosphere_thoughts}.
-
-The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
-arising from ionospheric fluctuations. The effect of this can be seen in
-Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
-at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
-source is always located exactly at the location of Cas A. In the middle panel, the source is
-allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
-the point source is effectively unchanged from the ideal PSF. In the right panel, the source
-position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
-refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
-from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
-obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
-Figure~\ref{fig:3c134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
-expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
-73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
-vicinity of bright point sources.
-
-\subsection{Beam Errors}
-
-A model of the antenna beam is essential for widefield imaging. Because $m$-mode analysis imaging
-operates on a full sidereal day of data, images are constructed after watching each point in the sky
-move through a large slice of the beam (excepting the celestial poles). The beam model therefore
-serves two purposes:
-
-\begin{enumerate}
-    \item setting the flux scale as a function of declination
-    \item reconciling observations from two separate sidereal times
-\end{enumerate}
-
-In the first case, all sources at a given declination take the same path through the antenna primary
-beam. If the antenna response is overestimated along this track then all sources at this declination
-will have their flux underestimated. Similarly if the antenna response is underestimated then all
-the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
-show a clear pattern with declination. Two sources have a clear systematic offset at all
-frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
-southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
-declination to Lyn A, which appears, if anything, to have its flux overestimated. The absence of a
-coherent pattern does not eliminate the possibility of beam errors effecting the flux scale, but it
-does mean that these errors are at least comparable to the errors inherent to the flux scale itself.
-
-The second case is more subtle. Sources are observed at a wide range of locations in the primary
-beam of the antenna. The imaging process must reconcile all of these observations together, and the
-beam model provides the instructions for how to do this. In the event of an error in the beam model,
-it can be expected that the beam will introduce errors into the sky maps that will limit the dynamic
-range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulate the effect of
-beam errors on a cosmological analysis concluding that the beam must be known to one part in $10^4$.
-Our requirements are significantly less stringent because we are estimating the sky brightness
-instead of estimating the amplitude of a faint cosmological signal in the presence of foreground
-emission that dominates the signal by 5 orders of magnitude. In fact in \S\ref{sec:ionopshere} we
-found that ionospheric effects likely dominate over other sources of error that affect the PSF
-shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
-limit the effect of beam errors on the PSF to at least less than those introduced by the ionosphere.
-
-\subsection{Polarization Leakage}
-
-\citet{2015PhRvD..91h3514S} describe how to generalize $m$-mode analysis to account for a polarized
-sky observed with a polarized antenna beam. Heretofore this generalization has been neglected in the
-discussion of $m$-mode analysis imaging.  At low frequencies, increasingly rapid Faraday rotation
-leads to depolarization. Therefore polarization fractions are generally expected to decrease at low
-frequencies (varying with ionospheric conditions). \citet{2016ApJ...830...38L} detected the presence
-of diffuse polarized emission on degree angular scales with the MWA, also finding typical
-depolarization ratios of $\sim0.3$ for pulsars at 154~MHz relative to 1.4~GHz, although there was a
-large variance between pulsars. Even more depolarization is expected at frequencies $\le
-73.152$~MHz, but crossed-dipole antennas with extremely large primary beams will naturally introduce
-large polarization leakage terms at low elevations.  It is instructive to compute what impact this
-will have on the unpolarized imaging process.
-
-In order to understand the effect of polarization leakage, a point source with 10\% polarization in
-Stokes-$Q$ was simulated at the location of Cas A.  The simulated visibilities were computed using
-the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
-every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
-Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
-rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about 7 hours
-every day skirting the horizon where the polarization leakage is large, so by placing the simulated
-source at the location of Cas A, we are engineering a situation where the polarization leakage from
-Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
-maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
-PSF.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparisons with Other Sky Maps}\label{sec:compare}
-
-\subsection{Guzm\'{a}n 45 MHz Map}
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[height=0.32\textheight]{figures/guzman/guzman}
-    \caption{
-        This Mollweide projection map compares the fractional difference between the Guzm\'{a}n 45
-        MHz map, and the OVRO-LWA map at 46.992 MHz (degraded to $5^\circ$ resolution). A positive
-        value indicates regions where the OVRO-LWA map has more emission that the Guzm\'{a}n map,
-        and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
-        OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
-        subtracted from the OVRO-LWA maps but not the Guzm\'{a}n map.
-    }
-    \label{fig:guzman-comparison}
-\end{figure*}
-
-A direct comparison between the OVRO-LWA maps interpolated to 45 MHz and the Guzm\'{a}n 45 MHz map
-\citep{2011A&A...525A.138G} can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this
-comparison the OVRO-LWA map was degraded to a 5$^\circ$ resolution by convolving with a Gaussian
-kernel, and the Guzm\'{a}n map has had spherical harmonics with $m=0$ discarded in order to make it
-consistent with the maps presented in this paper. This figure shows a $\sim20\%$ excess of emission
-in the galactic plane that is consistent with the discrepancy observed by the LWA1 sky survey
-\citep{2017MNRAS.469.4537D}. However, while the LWA1 sky survey has an excess of emission near the
-north galactic pole, no such excess is observed in this work. Instead there is a 10\% excess of
-emission near the south galactic pole. Elsewhere off the plane of the galaxy the discrepancy can be
-as much as $-20\%$.
-
-\subsection{Haslam 408 MHz Map}
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[height=0.32\textheight]{figures/haslam/better-haslam-spectral-index}
-    \caption{
-        \todo{update caption}
-        The contours show the spectral index between the reprocessed Haslam 408 MHz map and the
-        73.152 MHz map (degraded to 56 arcmin resolution). These contours are overlaid on the same
-        three-color map from Figure~\ref{fig:three-color}. The regions with shallow spectral index
-        between 73.152 MHz and 408 MHz coincide with regions with large free-free absorption that is
-        evident between 36.528 MHz and 73.152 MHz.
-    }
-    \label{fig:haslam-spectral-index}
-\end{figure*}
-
-The Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H} was reprocessed by
-\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources. In
-order to compare the OVRO-LWA maps with the lower resolution Haslam map, the OVRO-LWA maps were
-degraded to 56 arcmin resolution and the spectral index between the 73.152 MHz map and the 408 MHz
-Haslam map was computed by means of a local T-T plot at each pixel in the maps (in order to obviate
-the need for a zero-level correction to the 73.152 MHz map). The results of this computation are
-shown in Figure~\ref{fig:haslam-spectral-index}. Because this comparison uses a local T-T plot to
-estimate the spectral index, the angular resolution of this computation is somewhat degraded
-relative to other comparisons in the literature but the spectral indices in
-Figure~\ref{fig:haslam-spectral-index} are robust to zero-level errors in either map.
-
-The primary difference between the spectral index derived between 73.152 MHz and 408 MHz
-(Figure~\ref{fig:haslam-spectral-index}), and the spectral index derived between 36.528 MHz and
-73.152 MHz (Figure~\ref{fig:internal-spectral-index}) is the appearance of a multitude of \ion{H}{2}
-regions that dot the galactic plane in the latter. The free-free absorption from these \ion{H}{2}
-regions contributes to an overall flattening of the spectral index in the galactic plane that is
-also seen at higher frequencies.
-
-%\subsection{The Global Sky Model}?
-%\subsection{LWA1 Sky Survey}?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-10 figures/antenna-layout/make.jl

@@ -22,7 +22,7 @@ core = setdiff(core, off)
 gca()[:tick_params](axis="both", which="major", labelsize=12)
 
 scatter(east[core], north[core], marker=".", c="k", s=20, lw=0)
-scatter(east[off], north[off], marker=".", c="r", s=20, lw=0)
+scatter(east[off], north[off], marker=".", c="#d62728", s=20, lw=0)
 scatter(east[leda], north[leda], marker="+", c="k", s=50)
 scatter(east[expansion], north[expansion], marker="^", c="k", s=20)
 gca()[:set_aspect]("equal")

### 2017-10-11 paper.tex
now final draft?

@@
 
-Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
-that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
-after averaging over the entire sky (otherwise known as the monopole), and power spectrum
+Current 21~cm cosmology experiments can be broadly separated into two classes: global signal
+experiments that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm
+transition after averaging over the entire sky (otherwise known as the monopole), and power spectrum
 experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
-of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
+of cosmological 21~cm perturbations.  Ongoing global signal experiments include EDGES
 \citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
@@
 In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
-purposes we will assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
+purposes we will assume that $\b N=n\b I$ for some $n>0$. In this case the covariance of the
 Tikhonov-regularized spherical harmonic coefficients is
@@
 increasing the value of $\varepsilon$ can improve the noise properties of the map by down-weighting
-noisy modes. Decreasing the value of $\varepsilon$ can improve the resolution in the map by
+noisy modes. Decreasing the value of $\varepsilon$ can improve the resolution of the map by
 up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
@@
 In general the PSF can be a function of the right ascension and declination. However point sources
-at the same declination take the same track through the sky and therefore (barring any ionospheric
-effects) will have the same PSF. The PSF is therefore only a function of the declination. For
-example, sources at low elevations will tend to have an extended PSF along the north-south axis due
-to baseline foreshortening. For the OVRO-LWA antenna configuration
-(Figure~\ref{fig:antenna-layout}), example PSFs at three separate frequencies are shown in
-Figure~\ref{fig:psf}.  Adapting CLEAN for $m$-mode analysis requires either pre-computing
-Equation~\ref{eq:psf} at a grid of declinations, or a method for rapidly evaluating
-Equation~\ref{eq:psf} on the fly.
-
-%\citep{2011MNRAS.413..411B} % I think Lincoln wants me to cite this paper
+at the same declination take the same track through the sky and (barring any ionospheric effects)
+will have the same PSF. The PSF is therefore only a function of the declination. For example,
+sources at low elevations will tend to have an extended PSF along the north-south axis due to
+baseline foreshortening. For the OVRO-LWA antenna configuration (Figure~\ref{fig:antenna-layout}),
+example PSFs at three separate frequencies are shown in Figure~\ref{fig:psf}.  Adapting CLEAN for
+$m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of declinations, or
+a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.
 
@@
 components are not so close together that sidelobes from one may interact with another.
-
-%\todo{describe blurring to avoid cleaning the diffuse emission}
 
@@
 is when these sources are at high elevations.  The antenna complex gains are measured from a 22
-minute track of data when Cyg~A and Cas are at high elevations. The gains measured in this way are
+minute track of data when Cyg~A and Cas~A are at high elevations. The gains measured in this way are
 then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of Cyg~A
@@
 }, and
-3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
+3C~353) as they pass through the sky, and then fit a beam model composed of Zernike polynomials to
 those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
@@
 origin. The measured position offset of each source is a measurement of the ionospheric phase
-gradient across the array.  This varies on slower 10 minute timescales refracting each source by as
-much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the ionosphere
-pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe $\sim
-1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on similar
-$\sim10$ minute timescales.  The impact of these effects on the sky maps is simulated in
-\S\ref{sec:ionosphere}.
+gradient across the array.  This varies on slower 10 minute timescales, with each source refracting
+by as much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the
+ionosphere pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe
+$\sim 1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on
+similar $\sim10$ minute timescales, which is consistent with what is seen here.  The impact of these
+effects on the sky maps is simulated in \S\ref{sec:ionosphere}.
 
@@
 calibration. However gain calibration is also a function of the beam model and the spectrum used for
-Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival date from the
+Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival data from the
 literature and \citet{2017ApJS..230....7P} (hereafter PB17) using the VLA has expanded the number of
@@
 $l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the observing
-window. The properties of each map, including frequency, bandwidth, angular resolution, and thermal
-noise are presented in Table~\ref{tab:summary}.
+window. The properties of each map -- including frequency, bandwidth, angular resolution, and
+thermal noise -- are presented in Table~\ref{tab:summary}.
 
@@
 The noise in each map is empirically measured using jackknife resampling. The dataset is split into
-even- and odd-numbered integrations. These two groups are imaged and cleaned independently, before
+even- and odd-numbered integrations. These two groups are imaged and CLEANed independently, before
 being compared against the maps constructed from all of the available data using the standard
@@
 impossible. In general this zero-level correction requires calibrated total power measurements that
-will be included in future work.  Instead, temperature-temperature plots (T-T plot) can be used to
+will be included in future work.  Instead, temperature-temperature plots (T-T plots) can be used to
 measure the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}.
@@
 vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
-can be seen with higher resolution in Figure~\ref{fig:three-color}. Along the galactic plane,
-especially towards the galactic center, \ion{H}{2} regions appear as blue shadows due to free-free
-absorption.
+can be seen with higher resolution in Figure~\ref{fig:three-color}. In this figure \ion{H}{2}
+regions appear as blue shadows along the galactic plane due to the increasing impact of free-free
+absorption at lower frequencies.
 
@@
     \includegraphics[width=\textwidth]{figures/lwa1/lwa1}
-    \caption{\todo{a thing}}
+    \caption{
+        The fractional difference between maps from the LWA1 Low Frequency Sky Survey and the
+        OVRO-LWA maps (Figure~\ref{fig:channel-maps}) after interpolating to the corresponding
+        frequency and smoothing to the corresponding resolution. A positive value indicates regions
+        where the OVRO-LWA map has more emission that the corresponding LWA1 Low Frequency Sky
+        Survey map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
+        subtracted from the OVRO-LWA maps.
+    }
     \label{fig:lwa1-comparison}
@@
 maps are interpolated in frequency and blurred to match the angular resolution of the corresponding
-LWA1 map. The dominant feature in this map is a shift of the galactic plane. This feature is also
+LLFSS map. The dominant feature in this map is a shift of the galactic plane. This feature is also
 seen in comparisons of the LLFSS with the GSM (see for example Figure~9 of
@@
     \caption{
-        This Mollweide projection map compares the fractional difference between the Guzm\'{a}n 45
-        MHz map, and the OVRO-LWA map at 46.992 MHz (degraded to $5^\circ$ resolution). A positive
-        value indicates regions where the OVRO-LWA map has more emission that the Guzm\'{a}n map,
-        and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
-        OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
-        subtracted from the OVRO-LWA maps but not the Guzm\'{a}n map.
+        This Mollweide projected map compares the fractional difference between the Guzm\'{a}n 45
+        MHz map, and the OVRO-LWA maps (Figure~\ref{fig:channel-maps}) interpolated to 45~MHz
+        (degraded to $5^\circ$ resolution). A positive value indicates regions where the OVRO-LWA
+        map has more emission that the Guzm\'{a}n map, and a negative value indicates regions where
+        the Guzm\'{a}n map has more emission than the OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A
+        are masked due to the fact that they are subtracted from the OVRO-LWA maps but not the
+        Guzm\'{a}n map.
     }
@@
 small gap around the NCP. In this work the zero-level is set by comparing against published
-low-frequency measurements in the literature in six different directions.
+low-frequency measurements in six different directions.
 
@@
 only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
-fringe patterns of the interferometer. At low frequencies the ionosphere violates this assumption.
+fringe pattern of the interferometer. At low frequencies the ionosphere violates this assumption.
 In particular, ionospheric scintillation and refractive offsets will cause even static sources to
@@
 arising from ionospheric fluctuations. The effect of this can be seen in
-Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
-at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
-source is always located exactly at the location of Cas A. In the middle panel, the source is
-allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
-the point source is effectively unchanged from the ideal PSF. In the right panel, the source
-position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
-refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
-from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
-obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
-Figure~\ref{fig:3C134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
-expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
-73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
-vicinity of bright point sources.
+Figure~\ref{fig:ionospheric-simulations}. In this simulation a point source is placed at the
+location of Cas~A. In one case the source is allowed to scintillate in the same way Cas~A does in
+Figure~\ref{fig:scintillation}, but the source is always located exactly at the location of Cas~A.
+In the second case the source position is allowed to vary in the same way Cas~A does in
+Figure~\ref{fig:scintillation}, but the flux of the source exactly traces the beam model. The
+scintillation, although large, introduces only $<0.3\%$ errors in the vicinity of bright point
+sources. Refractive offsets, however, can introduce $\sim 15\%$ errors at 36.528~MHz and $\sim 5\%$
+errors at 73.152~MHz.  Because the sidelobes of the PSF are altered from that of the ideal PSF,
+refractive offsets will restrict the dynamic range it is possible to obtain with the CLEAN algorithm
+described in \S\ref{sec:clean}. This effect can be clearly seen in Figure~\ref{fig:3C134}, where
+10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As expected for an ionospheric
+effect these errors decrease to a few percent at 52.224~MHz, and less at 73.152~MHz. We therefore
+conclude that ionospheric effects directly limit the dynamic range in the vicinity of bright point
+sources.
 
@@
 southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
-declination to Lyn A, which appears, if anything, to have its flux overestimated. The absence of a
-coherent pattern does not eliminate the possibility of beam errors effecting the flux scale, but it
-does mean that these errors are at least comparable to the errors inherent to the flux scale itself.
+declination to Lyn A, which appears, if anything, to have its flux systematically offset in the
+other direction. The absence of a coherent pattern does not eliminate the possibility of beam errors
+effecting the flux scale, but it does mean that these errors are at least comparable to the errors
+inherent to the flux scale itself.
 

### 2017-10-12 paper.tex
minor cleanups and delete out-of-date outline
update authors and acknowledgements

@@
-% OUTLINE
-% =======
-%
-% 1. Introduction
-%
-%   Here I will introduce the need for a new high-fidelity, low-frequency map of the sky. The
-%   justifications are: 21 cm foreground mapping, galactic structure (?), others?
-%
-% 2. Observations
-%
-%   2.1 - Introduce the Owens Valley LWA
-%   2.2 - Describe the 100 hour dataset
-%   2.3 - Calibration strategy
-%   2.4 - Source removal strategy
-%   2.5 - Horizon RFI suppression strategy
-%   2.6 - Beam fitting work
-%   2.7 - Ionospheric conditions
-%
-% 3. Imaging
-%
-%   Give a brief overview of other widefield imaging algorithms. This should set the context for the
-%   advantages of m-mode analysis.
-%
-%   3.1 - Introduce m-mode analysis imaging
-%   3.2 - Describe my implementation of m-mode analysis on the ASTM
-%   3.3 - L-curves (?)
-%   3.4 - CLEAN
-%
-% 4. Results
-%
-%   Present sky maps with an estimate of the thermal noise in each pixel. Systematic errors will be
-%   described in the following sub-sections.
-%
-%   4.1 - Horizon RFI
-%   4.2 - Ionospheric effects
-%   4.3 - Beam errors
-%   4.4 - Peeling failures
-%
-% 5. Discussion
-%
-%   Compare with the Haslam map and Jayce's map.
-%
-% 6. Conclusion
-%
-% FIGURES
-% =======
-%
-% * Antenna layout of the OVRO-LWA
-% * Before/after snapshot image of the RFI removal
-% * Image of the empirical beam (with source tracks)
-% * Plot of ionospheric scintillation and refraction of an A-team source
-% * Example L-curve
-% * Zoom-in of the dirty PSF
-% * Sky maps with their boot-strapped thermal noise estimates
-% * (Model) image of the horizontal stripes that show up if the horizon RFI is not removed
-% * (Model) image of the PSF distortion from ionospheric effects (scintillation, refraction)
-% * (Model) image of the systematic errors in the map created from beam errors
-% * (Model) image of the errors created from sporadic peeling failures
-
 \documentclass[twocolumn]{aastex61}
@@
 
+\newcommand{\eecaltech}{
+    \affiliation{
+        Department of Electrical Engineering,
+        California Institute of Technology,
+        1200 E California Blvd,
+        Pasadena, CA 91125
+    }
+}
+
+\newcommand{\ovro}{
+    \affiliation{
+        Owens Valley Radio Observatory,
+        California Institute of Technology,
+        Big Pine, CA 93513
+    }
+}
+
+\newcommand{\jpl}{
+    \affiliation{
+        Jet Propulsion Laboratory,
+        California Institute of Technology,
+        4800 Oak Grove Dr,
+        Pasadena, CA 91109
+    }
+}
+
+\newcommand{\harvard}{
+    \affiliation{
+        Harvard-Smithsonian Center for Astrophysics,
+        60 Garden Street,
+        Cambridge, MA 02138
+    }
+}
+
 \begin{document}
@@
 
-\author{Michael W. Eastwood}
-\astrocaltech
-
-\author{Marin M. Anderson}
-\astrocaltech
-
-\author{Ryan M. Monroe}
-\astrocaltech
-
-\author{Gregg Hallinan}
-\astrocaltech
-
-\author{Other People}
-\affiliation{
-    At some institution
-}
-
-%\author{Lincoln Greenhill}
-%\affiliation{Harvard}
-%
+\author{Michael~W.~Eastwood} \astrocaltech
+\author{Marin~M.~Anderson}   \astrocaltech
+\author{Ryan~M.~Monroe}      \eecaltech
+\author{Gregg~Hallinan}      \astrocaltech
+
+% alphabetical by last name
+\author{Lincoln~J.~Greenhill} \harvard
+\author{T.~Joseph~W.~Lazio}   \jpl
+\author{David~P.~Woody}       \ovro
+
 %\author{Hugh Garsden}
@@
 
-%\subsection{The Global Sky Model}?
-%\subsection{LWA1 Sky Survey}?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \end{tabular}
-    %\includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
     \caption{
@@
 
+Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of
+Technology, under a contract with the National Aeronautics and Space Administration, including
+partial funding through the President's and Director's Fund Program.
+
+This work has benefited from open-source technology shared by the Collaboration for Astronomy Signal
+Processing and Electronics Research (CASPER).  We thank the Xilinx University Program for donations;
+NVIDIA for proprietary tools, discounts, and donations; Digicom for collaboration on manufacture and
+testing of DSP processors.
+
+We thank the Smithsonian Astrophysical Observatory Submillimeter Receiver Lab for the collaboration
+of its members.
+
+Development, adaptation, and operation of the LEDA real-time digital signal processing systems at
+OVRO-LWA has been supported in part by NSF grants AST/1106059, PHY/0835713, and OIA/1125087.
+
 \bibliographystyle{apj}

### 2017-10-12 paper.tex
add some more authors

@@
 
+\newcommand{\berkeley}{
+    \affiliation{
+        University of California Berkeley,
+        501 Campbell Hall,
+        Berkeley, CA 94720
+    }
+}
+
+\newcommand{\swinburne}{
+    \affiliation{
+        Centre for Astrophysics \& Supercomputing,
+        Swinburne University of Technology,
+        PO Box 218,
+        Hawthorn, VIC 3122, Australia;
+    }
+}
+
+\newcommand{\vt}{
+    \affiliation{
+        Bradley Department of Electrical \& Computer Engineering,
+        Blacksburg, VA 24061
+    }
+}
+
 \begin{document}
@@
 % alphabetical by last name
+\author{Steven~W.~Ellingson}  \vt
 \author{Lincoln~J.~Greenhill} \harvard
 \author{T.~Joseph~W.~Lazio}   \jpl
+\author{Daniel~C.~Price}      \harvard \berkeley \swinburne
 \author{David~P.~Woody}       \ovro
@@
 
-\bibliographystyle{apj}
+\bibliographystyle{aasjournal}
 \bibliography{paper}

### 2017-10-20 paper.tex
add coauthors and begin to address comments

@@
 
+\newcommand{\nrao}{
+    \affiliation{
+        National Radio Astronomy Observatory,
+        P.O. Box O,
+        Socorro, NM 87801
+    }
+}
+
 \newcommand{\harvard}{
@@
         PO Box 218,
-        Hawthorn, VIC 3122, Australia;
+        Hawthorn, VIC 3122, Australia
+    }
+}
+
+\newcommand{\unm}{
+    \affiliation{
+        Department of Physics and Astronomy,
+        University of New Mexico,
+        Albuquerque, NM 87131
     }
@@
 
+\newcommand{\nvidia}{
+    \affiliation{
+        NVIDIA Corporation,
+        2701 San Tomas Expressway,
+        Santa Clara, CA 95050
+    }
+}
+
 \begin{document}
@@
 % alphabetical by last name
+\author{Benjamin~R.~Barsdell} \harvard \nvidia
+\author{Stephen~A.~Bourke}    \astrocaltech
 \author{Steven~W.~Ellingson}  \vt
+\author{Jayce~Dowell}         \unm
+\author{Hugh~Garsden}         \harvard
 \author{Lincoln~J.~Greenhill} \harvard
+\author{Jonathon~Kocz}        \astrocaltech
 \author{T.~Joseph~W.~Lazio}   \jpl
 \author{Daniel~C.~Price}      \harvard \berkeley \swinburne
+\author{Frank~K.~Schinzel}    \nrao \unm
+\author{Gregory~B.~Taylor}    \unm
 \author{David~P.~Woody}       \ovro
-
-%\author{Hugh Garsden}
-%\affiliation{Harvard}
-%
-%\author{Stephen Bourke}
-%\affiliation{Chalmers}
-%
-%\author{Esayas B. Shume} % contributed ionosphere text
-%\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}
 
@@
 \begin{abstract}
-    A host of new low-frequency radio telescopes are attempting to detect the 21~cm transition at
-    cosmological distances. These measurements hold promise to directly probe star and galaxy
-    formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range they can
-    achieve against foreground sources of low-frequency radio emission. Consequently, there is a
-    growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for use in
-    foreground modeling and removal.  We use the Owens Valley Long Wavelength Array (OVRO-LWA) to
-    generate 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and
-    at frequencies evenly spaced between 36.528~MHz and 73.152~MHz with 24~kHz bandwidth.  Existing
-    full-sky maps at these frequencies have angular resolutions $\ge 2^\circ$ and so these maps are
-    a 10-fold improvement in angular resolution.  The thermal noise in each map is $\sim$800
-    mJy/beam.  Future iterations will incorporate total power radiometry, and additional bandwidth
-    and integration time. This will improve the thermal noise while simultaneously pushing to higher
-    angular resolutions with the planned expansion of the OVRO-LWA to 2.6~km baselines. These maps
-    are generated from the application of a new widefield imaging technique for drift-scanning
-    interferometers, Tikhonov-regularized $m$-mode analysis imaging. This algorithm constructs
-    images of the entire sky in a single synthesis imaging step with exact treatment of widefield
-    effects. We additionally introduce this technique and describe how CLEAN can be adapted to
-    deconvolve maps generated by $m$-mode analysis imaging.  These maps serve as a first step on the
-    path to the use of more sophisticated foreground filters in 21~cm cosmology incorporating the
-    measured angular and frequency structure of all foreground contaminants.
+    A host of new low-frequency radio telescopes seek to measure the 21-cm transition of neutral
+    hydrogen from the early universe.  These telescopes, and the measurements they make, hold
+    promise to directly probe star and galaxy formation at redshifts $20 \gtrsim z \gtrsim 7$, but
+    are limited by the dynamic range they can achieve against foreground sources of low-frequency
+    radio emission. Consequently, there is a growing demand for modern, high-fidelity maps of the
+    sky at frequencies below 200 MHz for use in foreground modeling and removal.  We describe a new
+    widefield imaging technique for drift-scanning interferometers, Tikhonov-regularized $m$-mode
+    analysis imaging.  This technique constructs images of the entire sky in a single synthesis
+    imaging step with exact treatment of widefield effects.  We describe how the CLEAN algorithm can
+    be adapted to deconvolve maps generated by $m$-mode analysis imaging.  We demonstrate
+    Tikhonov-regularized $m$-mode analysis imaging using the Owens Valley Long Wavelength Array
+    (OVRO-LWA) by generating 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin
+    angular resolution and at frequencies evenly spaced between 36.528~MHz and 73.152~MHz. These
+    maps are a 10-fold improvement in angular resolution over existing full-sky maps at comparable
+    frequencies, which have angular resolutions $\ge 2^\circ$. The thermal noise in each map is
+    $\sim$800 mJy/beam -- comparable to the confusion limit. However, each map is constructed
+    exclusively from interferometric observations and does not represent the globally averaged sky
+    brightness. Therefore future improvements will incorporate total power radiometry, and
+    additional bandwidth and integration time to improve the thermal noise.  The angular resolution
+    can also be further improved with the planned expansion of the OVRO-LWA to 2.6~km baselines.
+    These maps serve as a first step on the path to the use of more sophisticated foreground filters
+    in 21-cm cosmology incorporating the measured angular and frequency structure of all foreground
+    contaminants.
 \end{abstract}
@@
 
-At redshifts $20 \gtrsim z \gtrsim 7$ the 21~cm hyperfine structure line of neutral hydrogen is
+At redshifts $20 \gtrsim z \gtrsim 7$ the 21-cm hyperfine structure line of neutral hydrogen is
 expected to produce a 10 to 100 mK perturbation in the Cosmic Microwave Background (CMB) spectrum
@@
 
-Current 21~cm cosmology experiments can be broadly separated into two classes: global signal
-experiments that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm
+Current 21-cm cosmology experiments can be broadly separated into two classes: global signal
+experiments that are aiming to detect the spectral signature of the cosmologically redshifted 21-cm
 transition after averaging over the entire sky (otherwise known as the monopole), and power spectrum
 experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
-of cosmological 21~cm perturbations.  Ongoing global signal experiments include EDGES
+of cosmological 21-cm perturbations.  Ongoing global signal experiments include EDGES
 \citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
@@
 Just as for CMB experiments, foreground removal or suppression is an essential component of both
-classes of 21~cm cosmology experiments. The brightness temperature of the galactic synchrotron
+classes of 21-cm cosmology experiments. The brightness temperature of the galactic synchrotron
 emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
@@
 methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
-emission is spectrally smooth. However the low-frequency radio sky is composed of several
-components: galactic synchrotron emission, supernova remnants, radio galaxies, free-free emission
-and absorption from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally a
-foreground removal strategy should be informed by the measured spatial structure and frequency
-spectrum of all foreground components.  This possibility is limited by the availability of suitable
-high-fidelity low-frequency sky maps on angular scales ranging from tens of degrees to arcminutes.
-
-The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is currently the most
-commonly used foreground model. The GSM is a data-driven interpolation of various maps between 10
-MHz and 100 GHz. However the majority of information contained in the GSM is derived at frequencies
-$>1.4$ GHz where the majority of the modern, high-fidelity input maps are located.  Below 408 MHz,
-the GSM is a strong function of the Haslam 408 MHz map \citep{1981A&A...100..209H,
-1982A&AS...47....1H, 2015MNRAS.451.4311R}. As a consequence, the GSM is not a faithful
-representation of the sky below 200 MHz. For instance, \citet{2017MNRAS.469.4537D} report errors of
-$\pm 50\%$ between the GSM and their own maps at 74 MHz. This is largely due to the increasing
-contribution of free-free absorption and modifications to the synchrotron spectral index at low
-frequencies.
+emission is spectrally smooth. The low-frequency radio sky is composed of several components:
+galactic synchrotron emission, supernova remnants, radio galaxies, free-free emission and absorption
+from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally a foreground removal
+strategy should be informed by the measured spatial structure and frequency spectrum of all
+foreground components. For instance, CMB experiments typically construct several maps at several
+frequencies to enable component separation.  At low frequencies, this possibility is limited by the
+availability of suitable high-fidelity sky maps on angular scales ranging from tens of degrees to
+arcminutes.
 
@@
 
+The Global Sky Model (GSM) \citep{2008MNRAS.388..247D} is currently the most commonly used
+foreground model. The GSM is a non-parametric interpolation of various maps between 10 MHz and 100
+GHz. However the majority of information contained in the GSM is derived at frequencies $>1.4$ GHz
+where the majority of the modern, high-fidelity input maps are located. At 408~MHz the venerable
+Haslam map \citep{1981A&A...100..209H, 1982A&AS...47....1H} covers the entire sky at $1^\circ$
+resolution.  Below 408~MHz the GSM uses 3 input sky maps. \citet{2017MNRAS.464.3486Z} construct an
+improved GSM with 5 maps below 408~MHz, and \citet{2017MNRAS.469.4537D} use the LWA1 to improve the
+GSM with their own sky maps.  However, the GSM generally suffers from low angular resolution ($\sim
+5^\circ$) and systematic errors associated with instrumental artifacts in the input maps.  For
+instance, \citet{2017MNRAS.469.4537D} report errors of $\pm 50\%$ between the GSM and their own maps
+at 74 MHz, which they attribute to the increasing contribution of free-free absorption and
+modifications to the synchrotron spectral index at low frequencies.
+
+One challenge in widefield imaging
+
+\todo{briefly touch on m-mode analysis imaging and spherical harmonic imaging??}
+
 This paper presents a series of new low-frequency maps of the sky between 36.528~MHz and 73.152~MHz,
@@
 resolution of $\sim 15$~arcmin. We aim for these maps to inform foreground removal strategies in
-21~cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
-at these frequencies. We anticipate additional anciliary science taking advantage of the combination
+21-cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
+at these frequencies. We anticipate additional ancillary science taking advantage of the combination
 of high fidelity and high resolution of these maps, including but not limited to studies of the
@@
 polarizations labeled $p$ and $q$ respectively. We will neglect subtleties associated with polarized
-imaging, so the Stokes-$I$ visibilities are constructed from the sum of the $xx$ and $yy$
-correlations such that $V^{ij}_{\nu} = (V^{ij,xx}_{\nu}+V^{ij,yy}_{\nu})/2$.  If the antennas are
+imaging, so the Stokes-$I$ visibilities are constructed from the sum of the $pp$ and $qq$
+correlations such that $V^{ij}_{\nu} = (V^{ij,pp}_{\nu}+V^{ij,qq}_{\nu})/2$.  If the antennas are
 separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes an antenna's response to the
@@
                  A_\nu(\hat r) I_\nu(\hat r)
-                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, .
-\end{equation}
-Constructing an image from the output of a radio interferometer consists of estimating $I_\nu(\hat
-r)$ given the available measurements $V^{ij}_\nu$.
+                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, ,
+\end{equation}
+where the integral runs over solid angle $\Omega$.  Constructing an image from the output of a radio
+interferometer consists of estimating $I_\nu(\hat r)$ given the available measurements $V^{ij}_\nu$.
 
@@
 floating point number).  This matrix equation is therefore prohibitively large, and solving
-Equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
+Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable although
 \citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.
@@
 
-On the other hand, transit telescopes can take advantage of a symmetry in
-Equation~\ref{eq:basic-imaging} that greatly reduces the amount of computer time required to image
-the full-sky with exact incorporation of widefield imaging effects. This technique, called $m$-mode
-analysis, also obviates the need for gridding and mosaicing. Instead the entire sky is imaged in one
-coherent synthesis imaging step.  We will briefly summarize $m$-mode analysis below, but the
-interested reader should consult \citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete
-derivation.
+Transit telescopes can take advantage of a symmetry in Equation~\ref{eq:basic-imaging} that greatly
+reduces the amount of computer time required to image the full-sky with exact incorporation of
+widefield imaging effects. This technique, called $m$-mode analysis, also obviates the need for
+gridding and mosaicing. Instead the entire sky is imaged in one coherent synthesis imaging step.  We
+will briefly summarize $m$-mode analysis below, but the interested reader should consult
+\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete derivation.
 
@@
 
-The power of $m$-mode analysis is the block-diagonal structure of
+The key advantage of $m$-mode analysis is the block-diagonal structure of
 Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
@@
 consequence of this fact is that $\b B$ must have at least one singular value that is equal to zero.
-It is then trivial to show that $\b B^*\b B$ must have at least one eigenvalue that is equal to
-zero, which means it is not an invertible matrix.
+It then follows that $\b B^*\b B$ must have at least one eigenvalue that is equal to zero, which
+means it is not an invertible matrix.
 
@@
 is too large then too much importance is placed on minimizing the norm of the solution and the
-least-squares residuals will suffer. However if $\varepsilon$ is too small then the problem will be
-poorly regularized and the resulting sky map may not represent the true sky. Picking the value of
+least-squares residuals will suffer. Conversely, if $\varepsilon$ is too small then the problem will
+be poorly regularized and the resulting sky map may not represent the true sky. Picking the value of
 $\varepsilon$ therefore requires understanding the trade-off between the two norms.
@@
 \subsubsection{Other Regularization Schemes}
+
+\todo{noise covariance matrix?}
 
@@
 ends for calibrated total power measurements of the global sky brightness.  These antennas are used
-as part of the LEDA experiment \citep{2017arXiv170909313P} to measure the global signal of 21~cm
+as part of the LEDA experiment \citep{2017arXiv170909313P} to measure the global signal of 21-cm
 absorption from the cosmic dawn. In the current configuration 32 antennas (64 signal paths) from the
@@
 24~kHz channels are selected for imaging from this dataset: 36.528~MHz, 41.760~MHz, 46.992~MHz,
-52.224~MHz, 57.456~MHz, 62.688~MHz, 67.920~MHz, and 73.152~MHz.
+52.224~MHz, 57.456~MHz, 62.688~MHz, 67.920~MHz, and 73.152~MHz.  These particular channels are
+chosen due to their location at the exact center of instrumental subbands.
 
@@
 Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
-northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
-is when these sources are at high elevations.  The antenna complex gains are measured from a 22
-minute track of data when Cyg~A and Cas~A are at high elevations. The gains measured in this way are
-then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of Cyg~A
-and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while the flux
-of Cas~A is measured from the data itself (using a preliminary calibration solved for with a
-fiducial Cas~A spectrum).
+northern hemisphere at resolutions lower than 0.25$^\circ$. Therefore the optimal time to solve for
+the interferometer's gain calibration is when these sources are at high elevations.  The antenna
+complex gains are measured from a 22 minute track of data when Cyg~A and Cas~A are at high
+elevations. The gains measured in this way are then used to calibrate the entire 28 hour dataset.
+The calibration sky model consists only of Cyg~A and Cas~A. The model flux of Cyg~A is set to the
+\citet{1977A&A....61...99B} spectrum while the flux of Cas~A is measured from the data itself (using
+a preliminary calibration solved for with a fiducial Cas~A spectrum).
 
@@
 
+\todo{mention temperature variations at the front end}
+
 \subsection{Primary Beam Measurements}\label{sec:beam}
@@
         (middle panel), and 73.152 MHz (right panel). The source tracks used to measure the beam
-        model are overlaid. From north to south, these tracks correspond to Cas~A, Cyg~A, Per~B,
+        model are overlaid. From north to south, these tracks correspond to Cas~A, Cyg~A, 3C~123,
         Tau~A, Vir~A, Her~A, 3C~353, and Hya~A.  The fitting process is described in
@@
 
-We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A,
-Per~B\footnote{
-    At 74~MHz, Per~B is about two times brighter than Per~A.
-}, and
+We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A, 3C~123, and
 3C~353) as they pass through the sky, and then fit a beam model composed of Zernike polynomials to
@@
 integrations before imaging (at least 1 hour) it is possible to smear out the contribution of the
-rest of the sky.  We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a
-source model until the variance within the aperture is minimized. Cyg~A is modeled with 2 Gaussian
-components, while Cas~A is modeled with 3~Gaussian components. Armed with these  source models, both
-sources can be peeled from the dataset to the required dynamic range.
+rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx) \citep{nlopt, sbplx}
+to vary the parameters in a source model until the variance within the aperture is minimized. Cyg~A
+is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian components. Armed with
+these  source models, both sources can be peeled from the dataset to the required dynamic range.
 
@@
 
-Other bright sources -- namely Vir~A, Tau~A, Her~A, Hya~A, Per~B, and 3C~353 -- are also removed
+Other bright sources -- namely Vir~A, Tau~A, Her~A, Hya~A, 3C~123, and 3C~353 -- are also removed
 from the visibilities prior to imaging. Because these sources are much fainter than Cyg~A and Cas~A,
@@
 collected at night. A map of the entire sky can be obtained by using observations spaced 6 months
-apart.  However the dataset used in this paper consists of 28 consecutive hours. Therefore we
-attempt to suppress the contribution of the Sun to the maps with the goal of suppressing its
-sidelobes.  The Sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In
-fact the optical depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new
-model is needed at each frequency. While we could fit a limited number of Gaussian components to
-Cyg~A and Cas~A, this is insufficient for the Sun.  Additionally while most astronomical sources at
-these frequencies have negative spectral indices, the Sun has a positive spectral index. Therefore
-more care will need to be taken in subtracting the Sun at higher frequencies than at lower
-frequencies.
+apart.  However the dataset used in this paper consists of 28 consecutive hours. Fortunately the Sun
+was not active during this period, which could have greatly increased the difficulty involved in
+subtracting the Sun.
+
+We attempt to subtract the Sun from the dataset with the goal of suppressing its sidelobes.  The Sun
+is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the optical
+depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new model is needed
+at each frequency. While we could fit a limited number of Gaussian components to Cyg~A and Cas~A,
+this is insufficient for the Sun.  Additionally while most astronomical sources at these frequencies
+have negative spectral indices, the Sun has a positive spectral index. Therefore more care will need
+to be taken in subtracting the Sun at higher frequencies than at lower frequencies.
 
@@
         \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
+        Cas~A is compared against a spectrum assuming a secular decrease of 0.77\% per year
+        \citep{2009AJ....138..838H}.
     }
@@
         $\sim15$ arcmin. Eight bright sources have been removed from each map (Cyg~A, Cas~A, Vir~A,
-        Tau~A, Her~A, Hya~A, Per~B, and 3C~353). The small blank region near $l=+45.7^\circ$,
+        Tau~A, Her~A, Hya~A, 3C~123, and 3C~353). The small blank region near $l=+45.7^\circ$,
         $b=-47.9^\circ$ corresponds to the location of the Sun during the observation period.  A
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/spectral-index/ovro-lwa-sky-map.pdf}
+    \includegraphics[width=\textwidth]{figures/three-color/ovro-lwa-sky-map.pdf}
     \caption{
@@
     \label{fig:three-color}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/three-color/ovro-lwa-galactic-plane.pdf}
+    \caption{
+        A cutout of the galactic plane from Figure~\ref{fig:three-color}.
+    }
+    \label{fig:galactic-plane-cutout}
 \end{figure*}
@@
     \end{tabular}
-    \caption{A summary of the generated all-sky maps}
+    \caption{A summary of the generated all-sky maps. \todo{more fwhm info?}}
     \label{tab:summary}
@@
 with observations from the OVRO-LWA. Each map is individually shown in
-Figure~\ref{fig:channel-maps}, and Figure~\ref{fig:three-color} is a three-color image constructed
-from the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz. The maps cover the sky north of
-$\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution resolution. The 8 brightest northern
-hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A, Her~A, Hya~A, Per~B,
-and 3C~353) as described in \S\ref{sec:source-removal}, and there is a small blank region near
-$l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the observing
-window. The properties of each map -- including frequency, bandwidth, angular resolution, and
-thermal noise -- are presented in Table~\ref{tab:summary}.
+Figure~\ref{fig:channel-maps}, Figure~\ref{fig:three-color} is a three-color image constructed from
+the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz, and Figure~\ref{fig:galactic-plane-cutout} is a
+cutout of the galactic plane. The maps cover the sky north of $\delta=-30^\circ$ with $\sim 15$
+arcmin angular resolution resolution. The 8 brightest northern hemisphere point sources are removed
+from each map (Cyg~A, Cas~A, Vir~A, Tau~A, Her~A, Hya~A, 3C~123, and 3C~353) as described in
+\S\ref{sec:source-removal}, and there is a small blank region near $l=+45.7^\circ$, $b=-47.9^\circ$
+corresponding to the position of the Sun during the observing window. The properties of each map --
+including frequency, bandwidth, angular resolution, and thermal noise -- are presented in
+Table~\ref{tab:summary}.
 
@@
 astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
-This filtering creates negative rings around the NCP at the declination of bright point sources, but
+This filtering creates negative rings around the NCP at the declination of bright point sources.
 These rings are naturally removed from the map during CLEANing as long as this filtering step is
@@
 vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
-can be seen with higher resolution in Figure~\ref{fig:three-color}. In this figure \ion{H}{2}
-regions appear as blue shadows along the galactic plane due to the increasing impact of free-free
-absorption at lower frequencies.
+can be seen with higher resolution in Figure~\ref{fig:galactic-plane-cutout}. In this figure
+\ion{H}{2} regions appear as blue shadows along the galactic plane due to the increasing impact of
+free-free absorption at lower frequencies.
 
@@
 
+\todo{there is only one subsection here, can it be removed?}
+
 \subsubsection{LWA1 Low Frequency Sky Survey}
+
+\todo{redo the figure and text}
 
@@
         subtracted from the OVRO-LWA maps.
+        \todo{fix this fucking figure}
     }
@@
 
+\todo{compare with obenberger 2015}
+
 \subsection{Terrestrial Interference and Pickup}\label{sec:rfi}
@@
 
+\todo{make sure this emphasizes that this is a first step}
+
 In this work we presented a new imaging technique -- Tikhonov regularized $m$-mode analysis imaging
@@
 maps are primarily intended to be used as part of a foreground modeling and subtraction routine for
-21~cm cosmology experiments.
+21-cm cosmology experiments.
 

### 2017-10-20 figures/flux-scale/make.jl

@@ -1,7 +1,6 @@
 #!/usr/bin/env julia
 
 using JLD, PyPlot
-using CasaCore.Measures
 
 path = dirname(@__FILE__)
 
@@ -14,8 +13,8 @@ everything, odd, even, baars, perley, scaife =
 
 
 # manually spell this out so that we can pick the order of the plots
-names = ("Cyg A", "Hya A", "Lyn A", "Per B", "Vir A", "3C 48", "3C 147", "3C 286", "3C 295",
-         "3C 353", "3C 380")
+names = ("Cas A", "Cyg A", "Hya A", "Lyn A", "Vir A", "3C 48", "Per B", "3C 147", "3C 286",
+         "3C 295", "3C 353", "3C 380")
 
 figure(1, figsize=(12, 10)); clf()
 for (idx, name) in enumerate(names)
@@ -47,14 +46,35 @@ for (idx, name) in enumerate(names)
         plot(model_frequencies[cutoff]/1e6, model[cutoff], "k-.", zorder=3)
         #max_value = max(max_value, maximum(model))
     end
+    if name == "Cas A"
+        cutoff = 35e6 .< model_frequencies .< 75e6
+        model = 10.^(5.625 .- 0.634.*log10.(model_frequencies/1e6)
+                           .- 0.023.*log10.(model_frequencies/1e6).^2)
+        plot(model_frequencies[cutoff]/1e6, model[cutoff], "k-.", zorder=3)
+        text(43, 32000, "1965", rotation=-19, fontsize=12,
+             horizontalalignment="left", verticalalignment="bottom",
+             zorder=2)
+        τ = -1/log10(1-0.0077) # 0.77%/year secular decrease
+        model .*= 10^(-(2017-1965)/τ)
+        plot(model_frequencies[cutoff]/1e6, model[cutoff], "k-.", zorder=3)
+        text(43, 21500, "2017", rotation=-15, fontsize=12,
+             horizontalalignment="left", verticalalignment="top",
+             zorder=2)
+    end
+
+    # Per B is a confusing name (apparently the source is actually in Taurus), so we will relabel
+    # this source as 3C 123.
+    if name == "Per B"
+        name = "3C 123"
+    end
 
     text(0.95, 0.95, name, transform=gca()[:transAxes], fontsize=14,
          horizontalalignment="right", verticalalignment="top",
[…]

### 2017-10-20 figures/three-color/fetch.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw04/glamour-map-restored-registered-rainy.jld spw04.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw10/glamour-map-restored-registered-rainy.jld spw10.jld
+scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/workspace/spw18/glamour-map-restored-registered-rainy.jld spw18.jld
+

### 2017-10-20 figures/three-color/make.jl

@@ -1,0 +1,124 @@
+#!/usr/bin/env julia
+
+using JLD, LibHealpix, PyPlot, PyCall
+
+@pyimport mpl_toolkits.axes_grid1 as tk
+
+path = dirname(@__FILE__)
+
+function allsky()
+    ν1 = 36.528
+    ν2 = 52.224
+    ν3 = 73.152
+    brightness1 = load(joinpath(path, "spw04.jld"), "image")
+    brightness2 = load(joinpath(path, "spw10.jld"), "image")
+    brightness3 = load(joinpath(path, "spw18.jld"), "image")
+    
+    img = zeros(size(brightness1)..., 3)
+    for y = 1:size(img, 2), x = 1:size(img, 1)
+        img[x, y, 1] = brightness1[x, y] * (ν1/ν3)^2.5
+        img[x, y, 2] = brightness2[x, y] * (ν2/ν3)^2.5
+        img[x, y, 3] = brightness3[x, y]
+    end
+
+    figure(1, figsize=(12, 5)); clf()
+
+    θ = linspace(0, 2π, 512)
+    x = 2cos.(θ)
+    y = sin.(θ)
+    ellipse = plt[:Polygon]([x y], alpha=0)
+    gca()[:add_patch](ellipse)
+
+    function decide_on_color_scale(img)
+        pixels = vec(img)
+        pixels = pixels[pixels .!= 0]
+        sort!(pixels)
+        N = length(pixels)
+        min = pixels[round(Int, 0.00001N+1)]
+        max = pixels[round(Int, 0.999N+1)]
+        min, max, (max-min)/10
+    end
+
+    img_min, img_max, img_base = decide_on_color_scale(img)
+    img = clamp.(img, img_min, img_max)
+    img = (log10.(img - img_min + img_base) - log10.(img_base)) ./
+            (log10.(img_max - img_min + img_base) - log10.(img_base))
+    imshow(img, interpolation="nearest",
+           extent=(-2, 2, -1, 1),
+           clip_path=ellipse)
+
+    xlim(-2, 2)
+    ylim(-1, 1)
+    gca()[:set_aspect]("equal")
+    gca()[:get_xaxis]()[:set_visible](false)
+    gca()[:get_yaxis]()[:set_visible](false)
+    axis("off")
+    tight_layout()
+
+    savefig(joinpath(path, "ovro-lwa-sky-map.pdf"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
+end
+
+function cutout(map)
[…]

### 2017-10-22 paper.tex
finish changes and authors

@@
 \author{Stephen~A.~Bourke}    \astrocaltech
+\author{M.~A.~Clark}          \nvidia
 \author{Steven~W.~Ellingson}  \vt
@@
     A host of new low-frequency radio telescopes seek to measure the 21-cm transition of neutral
-    hydrogen from the early universe.  These telescopes, and the measurements they make, hold
-    promise to directly probe star and galaxy formation at redshifts $20 \gtrsim z \gtrsim 7$, but
-    are limited by the dynamic range they can achieve against foreground sources of low-frequency
-    radio emission. Consequently, there is a growing demand for modern, high-fidelity maps of the
-    sky at frequencies below 200 MHz for use in foreground modeling and removal.  We describe a new
-    widefield imaging technique for drift-scanning interferometers, Tikhonov-regularized $m$-mode
-    analysis imaging.  This technique constructs images of the entire sky in a single synthesis
-    imaging step with exact treatment of widefield effects.  We describe how the CLEAN algorithm can
-    be adapted to deconvolve maps generated by $m$-mode analysis imaging.  We demonstrate
-    Tikhonov-regularized $m$-mode analysis imaging using the Owens Valley Long Wavelength Array
-    (OVRO-LWA) by generating 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin
-    angular resolution and at frequencies evenly spaced between 36.528~MHz and 73.152~MHz. These
-    maps are a 10-fold improvement in angular resolution over existing full-sky maps at comparable
-    frequencies, which have angular resolutions $\ge 2^\circ$. The thermal noise in each map is
-    $\sim$800 mJy/beam -- comparable to the confusion limit. However, each map is constructed
-    exclusively from interferometric observations and does not represent the globally averaged sky
-    brightness. Therefore future improvements will incorporate total power radiometry, and
-    additional bandwidth and integration time to improve the thermal noise.  The angular resolution
-    can also be further improved with the planned expansion of the OVRO-LWA to 2.6~km baselines.
-    These maps serve as a first step on the path to the use of more sophisticated foreground filters
-    in 21-cm cosmology incorporating the measured angular and frequency structure of all foreground
-    contaminants.
+    hydrogen from the early universe.  These telescopes have the potential to directly probe star
+    and galaxy formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range
+    they can achieve against foreground sources of low-frequency radio emission. Consequently, there
+    is a growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for
+    use in foreground modeling and removal.  We describe a new widefield imaging technique for
+    drift-scanning interferometers, Tikhonov-regularized $m$-mode analysis imaging.  This technique
+    constructs images of the entire sky in a single synthesis imaging step with exact treatment of
+    widefield effects.  We describe how the CLEAN algorithm can be adapted to deconvolve maps
+    generated by $m$-mode analysis imaging.  We demonstrate Tikhonov-regularized $m$-mode analysis
+    imaging using the Owens Valley Long Wavelength Array (OVRO-LWA) by generating 8 new maps of the
+    sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and at frequencies evenly
+    spaced between 36.528~MHz and 73.152~MHz. These maps are a 10-fold improvement in angular
+    resolution over existing full-sky maps at comparable frequencies, which have angular resolutions
+    $\ge 2^\circ$. The thermal noise in each map is $\sim$800 mJy/beam -- comparable to the
+    confusion limit. However, each map is constructed exclusively from interferometric observations
+    and does not represent the globally averaged sky brightness. Therefore future improvements will
+    incorporate total power radiometry, and additional bandwidth and integration time to improve the
+    thermal noise.  The angular resolution can also be further improved with the planned expansion
+    of the OVRO-LWA to 2.6~km baselines.  These maps serve as a first step on the path to the use of
+    more sophisticated foreground filters in 21-cm cosmology incorporating the measured angular and
+    frequency structure of all foreground contaminants.
 \end{abstract}
@@
 
-At redshifts $20 \gtrsim z \gtrsim 7$ the 21-cm hyperfine structure line of neutral hydrogen is
+At redshifts $20 \gtrsim z \gtrsim 7$, the 21-cm hyperfine structure line of neutral hydrogen is
 expected to produce a 10 to 100 mK perturbation in the Cosmic Microwave Background (CMB) spectrum
@@
 Current 21-cm cosmology experiments can be broadly separated into two classes: global signal
-experiments that are aiming to detect the spectral signature of the cosmologically redshifted 21-cm
+experiments that aim to detect the spectral signature of the cosmologically redshifted 21-cm
 transition after averaging over the entire sky (otherwise known as the monopole), and power spectrum
@@
 \end{equation}
-Therefore experiments conservatively need to achieve 5 orders of dynamic range against this
+Therefore, experiments conservatively need to achieve 5 orders of dynamic range against this
 foreground emission before the cosmological signal can be measured. Current foreground removal
@@
 galactic synchrotron emission, supernova remnants, radio galaxies, free-free emission and absorption
-from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally a foreground removal
+from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally, a foreground removal
 strategy should be informed by the measured spatial structure and frequency spectrum of all
@@
 
-Recently a host of new low-frequency sky surveys have been conducted including MSSS
+Recently, a host of new low-frequency sky surveys have been conducted including MSSS
 \citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
@@
 foreground model. The GSM is a non-parametric interpolation of various maps between 10 MHz and 100
-GHz. However the majority of information contained in the GSM is derived at frequencies $>1.4$ GHz
+GHz. However, the majority of information contained in the GSM is derived at frequencies $>1.4$ GHz
 where the majority of the modern, high-fidelity input maps are located. At 408~MHz the venerable
@@
 
-One challenge in widefield imaging
-
-\todo{briefly touch on m-mode analysis imaging and spherical harmonic imaging??}
-
-This paper presents a series of new low-frequency maps of the sky between 36.528~MHz and 73.152~MHz,
-capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with angular
-resolution of $\sim 15$~arcmin. We aim for these maps to inform foreground removal strategies in
-21-cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
-at these frequencies. We anticipate additional ancillary science taking advantage of the combination
-of high fidelity and high resolution of these maps, including but not limited to studies of the
-cosmic ray emissivity at low frequencies, searches for giant radio galaxies, and constraining the
-galactic synchrotron spectrum. The maps will be made freely available online at the Legacy Archive
-for Microwave Background Data Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.
+Widefield interferometric synthesis imaging is a challenging computational problem, and it has been
+particularly difficult to capture large angular scales $\gg 10^\circ$ and small angular scales $\ll
+1^\circ$ in a single synthesis image. We will derive a new imaging technique -- Tikhonov regularized
+$m$-mode analysis imaging -- that allows a drift-scanning interferometer to image the entire visible
+sky in a single coherent synthesis imaging step with no gridding and no mosaicking.
+
+As a demonstration of this technique we apply Tikhonov regularized $m$-mode analysis imaging to the
+Owens Valley Long Wavelength Array (OVRO-LWA), and generate a series of new low-frequency maps of
+the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky visible from the Owens
+Valley Radio Observatory (OVRO) with angular resolution of $\sim 15$~arcmin.  These new maps
+complement the existing full-sky maps at these frequencies with greatly improved angular resolution.
+
+We aim for these maps to inform foreground removal strategies in 21-cm cosmology, and we anticipate
+additional ancillary science taking advantage of the combination of high fidelity and high
+resolution of these maps, including but not limited to studies of the cosmic ray emissivity at low
+frequencies, searches for giant radio galaxies, and constraining the galactic synchrotron spectrum.
+The maps will be made freely available online at the Legacy Archive for Microwave Background Data
+Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.
 
@@
 floating point number).  This matrix equation is therefore prohibitively large, and solving
-Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable although
+Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable, although
 \citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.
 
-Instead it is common to make mild assumptions that simplify Equation~\ref{eq:basic-imaging} and ease
-the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
+Instead, it is common to make mild assumptions that simplify Equation~\ref{eq:basic-imaging} and
+ease the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
 $\vec b_{ij}$ lie in a plane and the field-of-view is small, Equation~\ref{eq:basic-imaging} can be
@@
 widefield imaging effects. This technique, called $m$-mode analysis, also obviates the need for
-gridding and mosaicing. Instead the entire sky is imaged in one coherent synthesis imaging step.  We
+gridding and mosaicking. Instead the entire sky is imaged in one coherent synthesis imaging step.  We
 will briefly summarize $m$-mode analysis below, but the interested reader should consult
@@
 of the baseline transfer function defined by Equation~\ref{eq:baseline-transfer-function}. These
-transfer coefficients define the interferometers response to the corresponding spherical harmonic
+transfer coefficients define the interferometer's response to the corresponding spherical harmonic
 coefficients.
@@
 
-In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
-an interferometer like the OVRO-LWA with many short baselines, a sensible choice is to use all
+In practice, we now need to pick the set of spherical harmonics we will use to represent the sky.
+For an interferometer like the OVRO-LWA with many short baselines, a sensible choice is to use all
 spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
@@
 frequency $\nu$ is $l \sim \pi b\nu/c$. Based on this estimate for the OVRO-LWA and other
-computational considerations we therefore adapt $l_\text{min}=1$ and $l_\text{max}=1000$ across all
-frequencies. However this choice of $l_\text{max}$ actually limits the angular resolution above
+computational considerations, we therefore adapt $l_\text{min}=1$ and $l_\text{max}=1000$ across all
+frequencies. However, this choice of $l_\text{max}$ actually limits the angular resolution above
 55~MHz, and therefore future work will increase $l_\text{max}$ to obtain better angular resolution.
@@
 other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
-measured and calibrated. Consequently we set $a_{00}=0$ in our analysis. In the future this
+measured and calibrated. Consequently, we set $a_{00}=0$ in our analysis. In the future this
 limitation will be addressed with the inclusion of calibrated total power radiometry.
@@
 imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.
-However, with additional bandwidth these blocks quickly become unwieldy and so as a first pass the
+However, with additional bandwidth these blocks quickly become unwieldy; thus as a first pass, the
 analysis in this paper is restricted to single-channel imaging. Note also that for the OVRO-LWA
@@
 
-However, usually one will find that $\b B$ is not full-rank and hence $\b B^*\b B$ is not an
+However, usually one will find that $\b B$ is not full-rank, and hence $\b B^*\b B$ is not an
 invertible matrix. For example, an interferometer located in the northern hemisphere will never see
@@
 matrix's singularity. By using the singular value decomposition (SVD) of the matrix $\b B = \b U \b
-\Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
+\Sigma \b V^*$, Equation~\ref{eq:tikhonov-solution} becomes
 \begin{equation}
@@
 In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
-purposes we will assume that $\b N=n\b I$ for some $n>0$. In this case the covariance of the
+purposes we will assume that $\b N=n\b I$ for some $n>0$. In this case, the covariance of the
 Tikhonov-regularized spherical harmonic coefficients is
@@
 Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \varepsilon)^2$.  In the
-absence of Tikhonov regularization ($\varepsilon=0$) singular components with the smallest singular
+absence of Tikhonov regularization ($\varepsilon=0$), singular components with the smallest singular
 values -- the ones that the interferometer is the least sensitive to -- actually come to dominate
@@
         solution (in this case the spherical harmonic coefficients) given in arbitrary units, and
-        the $y$-axis is the least-squares norm given in arbitrary units Where the regularization
+        the $y$-axis is the least-squares norm given in arbitrary units. Where the regularization
         parameter is small, the norm of the solution grows rapidly. Where the regularization
@@
 In practice, the L-curve should be used as a guide to estimate a reasonable value of $\varepsilon$.
-However better results can often be obtained by tuning the value of $\varepsilon$. For instance
+However better results can often be obtained by tuning the value of $\varepsilon$. For instance,
 increasing the value of $\varepsilon$ can improve the noise properties of the map by down-weighting
 noisy modes. Decreasing the value of $\varepsilon$ can improve the resolution of the map by
-up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
-choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in traditional
-imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.  For the
-OVRO-LWA we selected $\varepsilon = 0.01$ across all frequency channels. The distribution of
+up-weighting the contribution of longer baselines, which are likely fewer in number. In this
+respect, choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in
+traditional imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.
+For the OVRO-LWA we selected $\varepsilon = 0.01$ across all frequency channels. The distribution of
 singular values of the transfer matrix with respect to $\sqrt{\varepsilon}$ is summarized in
@@
 
-\todo{noise covariance matrix?}
-
 The choice of applying Tikhonov regularization to $m$-mode analysis imaging is not unique. There
 exists a plethora of alternative regularization schemes that could also be applied. Each
-regularization scheme has its own advantages and disadvantages. For instance Tikhonov regularization
-is simple, independent of prior information, and sets unmeasured modes to zero (a sensible
-expectation). We will now briefly discuss a few other alternatives.
+regularization scheme has its own advantages and disadvantages. For instance, Tikhonov
+regularization is simple, independent of prior information, and sets unmeasured modes to zero (a
+sensible expectation). We will now briefly discuss a few other alternatives.
 
@@
 ``on'' to ``off''. Modes are either set to zero or included in the map at their full amplitude. On
-the other hand Tikhonov regularization smoothly interpolates between these behaviors. Because of
+the other hand, Tikhonov regularization smoothly interpolates between these behaviors. Because of
 this, Tikhonov regularization tends to produce better results in practical applications.
+
+If the baselines have a noise covariance matrix $\b N \neq n\b I$ for some scalar $n$ (eg. the
+interferometer is inhomogeneous), then the observer should minimize $(\b v-\b B\b a)^*\b N^{-1}(\b
+v-\b B\b a) + \varepsilon\|\b a\|^2$. The matrix $\b N$ is used to weight the measurements such that
+\begin{equation}
+    \b{\hat a}_\text{min variance} = (\b B^*\b N^{-1}\b B + \varepsilon\b I)^{-1}
+        \b B\b N^{-1}\b v\,.
+\end{equation}
 
@@
 used as the regularizing norm. This will use the prior map to fill-in missing information instead of
-setting these modes to zero. In this case the minimum is at
+setting these modes to zero. In this case, the minimum is at
 \begin{equation}
@@
 
-Alternatively we could opt to regularize the problem by enforcing smoothness in the sky maps. In
+Alternatively, we could opt to regularize the problem by enforcing smoothness in the sky maps. In
 this case, the regularizing norm should be of the form $\|\nabla I(\hat r)\|^2$, where $\nabla I$ is
@@
 
-Finally in many machine learning applications the $L_1$-norm\footnote{
+Finally, in many machine learning applications the $L_1$-norm\footnote{
     $\|\b a\|_1 = \sum_i |a_i|$
@@
 + \varepsilon\|\b a\|_1$. However, because we have decomposed the sky in terms of spherical
-harmonics, the vector $\b a$ is not expected to be sparse. Consequently the $L_1$-norm is generally
+harmonics, the vector $\b a$ is not expected to be sparse. Consequently, the $L_1$-norm is generally
 inappropriate for $m$-mode analysis imaging without an additional change-of-variables designed to
@@
 \end{enumerate}
-As a consequence the final map of the sky is not assembled from a complete set of spherical
-harmonics. Therefore just as in traditional imaging, $m$-mode analysis imaging produces dirty maps
+As a consequence, the final map of the sky is not assembled from a complete set of spherical
+harmonics. Therefore, just as in traditional imaging, $m$-mode analysis imaging produces dirty maps
 in which sources are convolved with a PSF.  This PSF can be improved by increasing the number and
 variety of baselines, which increases the number of modes for which $\sigma_i \gg
-\sqrt{\varepsilon}$.  Alternatively by collecting more data, the signal-noise ratio of the measured
+\sqrt{\varepsilon}$.  Alternatively, by collecting more data, the signal-noise ratio of the measured
 $m$-modes increases, which allows the observer to lower the value of $\varepsilon$ without
@@
 \end{equation}
-In general the PSF can be a function of the right ascension and declination. However point sources
+In general, the PSF can be a function of the right ascension and declination. However, point sources
 at the same declination take the same track through the sky and (barring any ionospheric effects)
@@
 
-Additionally we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
+Additionally, we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
 U^*\b U$, where $\b U$ is an upper-triangular matrix. Inverting an upper triangular matrix is an
@@
     \caption{
-        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
-        within the 200 m diameter core of the array. The 32 triangles are the expansion antennas
-        built in early 2016 in order to increase the longest baseline to $\sim1.5$ km. The red dots
-        are core antennas that are disconnected from the correlator in order to accommodate these
-        antennas. The 5 crosses are antennas equipped with noise-switched front ends.
+        Antenna layout for the OVRO-LWA. Black dots correspond to antennas within the 200 m diameter
+        core of the array. The 32 triangles are the expansion antennas built in early 2016 in order
+        to increase the longest baseline to $\sim1.5$ km. The red dots are core antennas that are
+        disconnected from the correlator in order to accommodate these antennas. The 5 crosses are
+        antennas equipped with noise-switched front ends.
     }
@@
 as part of the LEDA experiment \citep{2017arXiv170909313P} to measure the global signal of 21-cm
-absorption from the cosmic dawn. In the current configuration 32 antennas (64 signal paths) from the
-core are disconnected from the correlator in order to accommodate the 32 antennas on longer
+absorption from the cosmic dawn. In the current configuration, 32 antennas (64 signal paths) from
+the core are disconnected from the correlator in order to accommodate the 32 antennas on longer
 baselines. A final stage of construction will involve 64 additional antennas installed on long
@@
 Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
-northern hemisphere at resolutions lower than 0.25$^\circ$. Therefore the optimal time to solve for
+northern hemisphere at resolutions lower than 0.25$^\circ$. Therefore, the optimal time to solve for
 the interferometer's gain calibration is when these sources are at high elevations.  The antenna
@@
 The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
-per-antenna amplitude correction that is then applied to the cross-correlations.
-
-\todo{mention temperature variations at the front end}
+per-antenna amplitude correction that is then applied to the cross-correlations.  Additionally, the
+ambient temperature at the front-end electronics (located in a box at the top of each dipole)
+fluctuates diurnally, which will generate diurnal gain fluctuations. At this time, no correction is
+made for these diurnal gain fluctuations.
 
@@
 necessary to break the degeneracy between source flux and beam amplitude when the flux of the source
-is unknown. In this work we assume symmetries that are apparent in the antenna design, but
+is unknown. In this work, we assume symmetries that are apparent in the antenna design, but
 real-world defects and coupling with nearby antennas will contribute towards breaking these
@@
     \caption{
-        (a, b) These panels show the measured apparent flux of Cyg~A and Cas~A at 36.528 MHz (red
+        Panels (a) and (b) show the measured apparent flux of Cyg~A and Cas~A at 36.528 MHz (red
         points) and 73.152 MHz (blue points) as a function of time over the observing period. The
@@
         Mountains when it is low on the horizon to the east.
-        (c, d) These panels show the measured position offset of Cyg~A and Cas~A relative to their
-        true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue line).
+        Panels (c) and (d) These panels show the measured position offset of Cyg~A and Cas~A
+        relative to their true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue
+        line).
     }
@@
 electron content (TEC) above OVRO measured from GPS \citep{1999JASTP..61.1205I}. The median is
-computed over all GPS measurements within 200 km of the observatory. Over the observing period the
+computed over all GPS measurements within 200 km of the observatory. Over the observing period, the
 TEC smoothly varies from 20 TECU at midday to 5 TECU during the night. However, this measurement is
@@
 function of time over the entire observing period. Both sources exhibit rapid scintillation on the
-timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
-A to have measured flux variations of 50\% between adjacent 13 second integrations.  The variance at
-36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
-origin. The measured position offset of each source is a measurement of the ionospheric phase
-gradient across the array.  This varies on slower 10 minute timescales, with each source refracting
-by as much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the
-ionosphere pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe
-$\sim 1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on
-similar $\sim10$ minute timescales, which is consistent with what is seen here.  The impact of these
-effects on the sky maps is simulated in \S\ref{sec:ionosphere}.
+timescale of a single integration (13 seconds). For example, at 36.528 MHz, it is not unusual for
+Cyg A to have measured flux variations of 50\% between adjacent 13 second integrations.  The
+variance at 36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric
+$\nu^{-2}$ origin. The measured position offset of each source is a measurement of the ionospheric
+phase gradient across the array.  This varies on slower 10 minute timescales, with each source
+refracting by as much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves
+in the ionosphere pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K}
+observe $\sim 1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the
+day on similar $\sim10$ minute timescales, which is consistent with what is seen here.  The impact
+of these effects on the sky maps is simulated in \S\ref{sec:ionosphere}.
 
@@
 74~MHz Cyg~A is a 15,000~Jy source \citep{1977A&A....61...99B}. A conservative estimate for the
-confusion limit at 74 MHz with a 15~arcmin beam is 1000~mJy \citep{2014MNRAS.440..327L}. Therefore
+confusion limit at 74 MHz with a 15~arcmin beam is 1000~mJy \citep{2014MNRAS.440..327L}. Therefore,
 we require that Cyg~A's sidelobes be at least $-45$~dB down from the main lobe to prevent Cyg~A's
@@
 the timescale of a single integration (13 seconds) are observed (Figure~\ref{fig:scintillation}).
-Therefore the direction dependent calibration changes on these timescales and we must solve for one
-set of complex gains per source per integration.
+Therefore, the direction dependent calibration changes on these timescales, and we must solve for
+one set of complex gains per source per integration.
 
@@
 within an aperture located on each source after peeling. By phasing up a large number of
-integrations before imaging (at least 1 hour) it is possible to smear out the contribution of the
+integrations before imaging (at least 1 hour), it is possible to smear out the contribution of the
 rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx) \citep{nlopt, sbplx}
@@
 We attempt to subtract the Sun from the dataset with the goal of suppressing its sidelobes.  The Sun
-is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the optical
-depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new model is needed
+is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact, the optical
+depth $\tau=1$ surface of the Sun changes with frequency, and as a consequence a new model is needed
 at each frequency. While we could fit a limited number of Gaussian components to Cyg~A and Cas~A,
-this is insufficient for the Sun.  Additionally while most astronomical sources at these frequencies
-have negative spectral indices, the Sun has a positive spectral index. Therefore more care will need
-to be taken in subtracting the Sun at higher frequencies than at lower frequencies.
+this is insufficient for the Sun.  Additionally, while most astronomical sources at these
+frequencies have negative spectral indices, the Sun has a positive spectral index. Therefore, more
+care will need to be taken in subtracting the Sun at higher frequencies than at lower frequencies.
 
@@
 The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg~A during gain
-calibration. However gain calibration is also a function of the beam model and the spectrum used for
-Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival data from the
+calibration. However, gain calibration is also a function of the beam model and the spectrum used
+for Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival data from the
 literature and \citet{2017ApJS..230....7P} (hereafter PB17) using the VLA has expanded the number of
-low-frequency radio sources with calibrated flux measurements from one (just Cyg~A) to eleven in
-total. While the SH12 flux scale is valid between 30 MHz and 300 MHz, the PB17 flux scale is
-somewhat more limited because the lowest frequency observations come from the VLA 4-band system. As
-a consequence the PB17 flux scale is not valid below 50 MHz.
+low-frequency radio sources with calibrated flux measurements from one (Cyg~A) to eleven in total.
+While the SH12 flux scale is valid between 30 MHz and 300 MHz, the PB17 flux scale is somewhat more
+limited because the lowest frequency observations come from the VLA 4-band system. As a consequence,
+the PB17 flux scale is not valid below 50 MHz.
 
@@
 from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
-measurements agree to between 5 and 10\% with the SH12 spectra. Below 50 MHz there can be
-substantial departures with respect to the extrapolated PB17 spectra (for eg.  3C 286, 3C 295, and
-3C 380), but it is usually the case that we have much better agreement with the SH12 spectra. This
-indicates that the PB17 spectra cannot be extrapolated below 50 MHz.
+measurements agree to between 5 and 10\% of the SH12 spectra. Below 50 MHz there can be substantial
+departures with respect to the extrapolated PB17 spectra (for eg.  3C 286, 3C 295, and 3C 380), but
+it is usually the case that we have much better agreement with the SH12 spectra. This indicates that
+the PB17 spectra cannot be extrapolated below 50 MHz.
 
@@
     \caption{
-        These 8 panels illustrate (with a Mollweide projection and logarithmic color scale) the 8
-        full-sky maps generated with Tikhonov-regularized $m$-mode analysis imaging and the
+        These eight panels illustrate (with a Mollweide projection and logarithmic color scale) the
+        eight full-sky maps generated with Tikhonov-regularized $m$-mode analysis imaging and the
         OVRO-LWA.  Each map covers the sky north of $\delta=-30^\circ$ with angular resolution of
@@
     \caption{
-        This Mollweide-projected map is constructed from 3 maps of the sky at 36.528~MHz (red),
+        This Mollweide-projected map is constructed from three maps of the sky at 36.528~MHz (red),
         52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
         combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
-        Therefore regions with a spectral index of $-2.5$ will tend to appear white. Areas with a
-        steeper index appear red and areas with a flatter spectral index appear blue.
+        Therefore, regions with a spectral index of $-2.5$ will tend to appear white, and regions
+        with a flatter spectral index will tend to appear blue.
     }
@@
     \centering
-    \begin{tabular}{ccccccccc}
+    \begin{tabular}{cccccccccc}
         \hline
         \hline
-        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM}\footnote{
-                The full-width half-maximum (FWHM) of the synthesized beam at $\delta=+45^\circ$.
-            }&
-            \multicolumn2c{\tbf{Noise}\footnote{
+        & \tbf{$\b\nu$}
+        & \tbf{$\b\Delta\b\nu$}\footnote{
+            Bandwidth used to construct the map. As described in the text, each map is constructed
+            from a single frequency channel (24~kHz).
+        }
+        & \multicolumn3c{\tbf{FWHM}\footnote{
+            The full-width half-maximum (FWHM) of the synthesized beam at the specified declination
+            (major axis $\times$ minor axis).
+        }}
+        && \multicolumn2c{\tbf{Noise}\footnote{
             Measured with a jackknife and splitting the dataset into even- and odd-numbered
@@
             timescale of a single 13 second integration (eg. thermal, ionospheric, etc.).
-            }} &&
-            \multicolumn2c{\tbf{Fraction of Modes}\footnote{
+        }}
+        & \tbf{Fraction of Modes}\footnote{
             Singular values of the transfer matrix compared with the value of the regularization
             parameter $\varepsilon$ used while solving Equation~\ref{eq:tikhonov-solution}. As
-                discussed in the text, singular vectors with corresponding singular values $\sigma
-                \ll \sqrt{\varepsilon}$ are set to zero by the Tikhonov regularization procedure.
-            }} \\
-        \cline{5-6}
+            discussed in the text, singular vectors with corresponding singular values $\sigma \ll
+            \sqrt{\varepsilon}$ are set to zero by the Tikhonov regularization procedure.
+        } \\
+        \cline{4-6}
         \cline{8-9}
-        \tbf{\#} & MHz & MHz & arcmin &
-            K & mJy/beam &&
-            with $\sigma>\sqrt{\varepsilon}$ &
-            with $\sigma>\sqrt{10\varepsilon}$ \\
+        \tbf{\#}
+            & MHz & MHz
+            & $\delta=0^\circ$ & $\delta=+45^\circ$ & $\delta=+75^\circ$
+            && K & mJy/beam
+            & with $\sigma>\sqrt{\varepsilon}$ \\
         \hline
-        1 & 36.528 & 0.024 & 18.5 & 595. & 799. && 0.391 & 0.077 \\
-        2 & 41.760 & 0.024 & 17.2 & 541. & 824. && 0.480 & 0.070 \\
-        3 & 46.992 & 0.024 & 16.3 & 417. & 717. && 0.504 & 0.056 \\
-        4 & 52.224 & 0.024 & 15.6 & 418. & 814. && 0.535 & 0.053 \\
-        5 & 57.456 & 0.024 & 15.4 & 354. & 819. && 0.542 & 0.049 \\
-        6 & 62.688 & 0.024 & 15.3 & 309. & 843. && 0.540 & 0.046 \\
-        7 & 67.920 & 0.024 & 15.3 & 281. & 894. && 0.529 & 0.047 \\
-        8 & 73.152 & 0.024 & 15.7 & 154. & 598. && 0.512 & 0.051 \\
+        1 & 36.528 & 0.024 & $26.0'\times19.1'$ & $20.2'\times16.9'$ & $19.8'\times18.7'$ && 595. & 799. & 0.391 \\
+        2 & 41.760 & 0.024 & $23.3'\times17.5'$ & $18.5'\times16.0'$ & $18.3'\times17.4'$ && 541. & 824. & 0.480 \\
+        3 & 46.992 & 0.024 & $20.9'\times16.3'$ & $17.4'\times15.2'$ & $17.6'\times16.9'$ && 417. & 717. & 0.504 \\
+        4 & 52.224 & 0.024 & $18.7'\times15.2'$ & $16.2'\times15.0'$ & $16.0'\times15.8'$ && 418. & 814. & 0.535 \\
+        5 & 57.456 & 0.024 & $18.0'\times14.9'$ & $15.9'\times15.0'$ & $15.7'\times15.4'$ && 354. & 819. & 0.542 \\
+        6 & 62.688 & 0.024 & $17.8'\times15.0'$ & $15.8'\times14.9'$ & $15.7'\times15.4'$ && 309. & 843. & 0.540 \\
+        7 & 67.920 & 0.024 & $17.6'\times15.0'$ & $15.9'\times14.7'$ & $15.8'\times15.6'$ && 281. & 894. & 0.529 \\
+        8 & 73.152 & 0.024 & $18.6'\times15.1'$ & $16.8'\times14.6'$ & $16.6'\times16.1'$ && 154. & 598. & 0.512 \\
         \hline \hline
     \end{tabular}
-    \caption{A summary of the generated all-sky maps. \todo{more fwhm info?}}
+    \caption{A summary of the generated all-sky maps.}
     \label{tab:summary}
@@
 
-Eight sky maps were constructed using Tikhonov-regularized $m$-mode analysis imaging and cleaning
-with observations from the OVRO-LWA. Each map is individually shown in
-Figure~\ref{fig:channel-maps}, Figure~\ref{fig:three-color} is a three-color image constructed from
-the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz, and Figure~\ref{fig:galactic-plane-cutout} is a
-cutout of the galactic plane. The maps cover the sky north of $\delta=-30^\circ$ with $\sim 15$
-arcmin angular resolution resolution. The 8 brightest northern hemisphere point sources are removed
-from each map (Cyg~A, Cas~A, Vir~A, Tau~A, Her~A, Hya~A, 3C~123, and 3C~353) as described in
-\S\ref{sec:source-removal}, and there is a small blank region near $l=+45.7^\circ$, $b=-47.9^\circ$
-corresponding to the position of the Sun during the observing window. The properties of each map --
-including frequency, bandwidth, angular resolution, and thermal noise -- are presented in
-Table~\ref{tab:summary}.
+We constructed eight sky maps using Tikhonov-regularized $m$-mode analysis imaging and CLEANing with
+observations from the OVRO-LWA. Each map is individually shown in Figure~\ref{fig:channel-maps},
+Figure~\ref{fig:three-color} is a three-color image constructed from the maps at 36.528~MHz,
+52.224~MHz, and 73.152~MHz, and Figure~\ref{fig:galactic-plane-cutout} is a cutout of the galactic
+plane. The maps cover the sky north of $\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution.
+The eight brightest northern hemisphere point sources are removed from each map (Cyg~A, Cas~A,
+Vir~A, Tau~A, Her~A, Hya~A, 3C~123, and 3C~353) as described in \S\ref{sec:source-removal}, and
+there is a small blank region near $l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of
+the Sun during the observing window. The properties of each map -- including frequency, bandwidth,
+angular resolution, and thermal noise -- are presented in Table~\ref{tab:summary}.
 
@@
 
-The noise in each map is empirically measured using jackknife resampling. The dataset is split into
-even- and odd-numbered integrations. These two groups are imaged and CLEANed independently, before
-being compared against the maps constructed from all of the available data using the standard
-jackknife variance estimator. This estimate of the variance includes all sources of error that
-operate on $\sim13$ second timescales (the integration time) such as thermal noise and rapid
-ionospheric fluctuations, but does not account for more slowly varying effects (for example,
+The noise in each map is empirically measured using jackknife resampling. The dataset is first split
+into even- and odd-numbered integrations. These two groups are then imaged and CLEANed
+independently, before being compared against the maps constructed from all of the available data
+using the standard jackknife variance estimator. This estimate of the variance includes all sources
+of error that operate on $\sim13$ second timescales (the integration time) such as thermal noise and
+rapid ionospheric fluctuations, but does not account for more slowly varying effects (for example,
 sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
@@
 This method relies on the assumption that all pixels in a given region are described by the same
-power law. In that case there exists a linear relationship between the brightness temperature at
+power law. In that case, there exists a linear relationship between the brightness temperature at
 frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line is a measure of the
@@
 there may be only a weak correlation between the brightness temperature at $\nu_1$ and $\nu_2$.
-Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free) then
-a single power-law interpretation of the emission in that region will be poor. Consequently spectral
-indices estimated from T-T plots can require careful interpretation.
-
-In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated in each part of
+Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free), then
+a single power-law interpretation of the emission in that region will be poor. Consequently,
+spectral indices estimated from T-T plots can require careful interpretation.
+
+In Figure~\ref{fig:internal-spectral-index}, the spectral index is locally estimated in each part of
 the sky within a region $\sim10^\circ$ across by constructing local T-T plots between 36.528~MHz and
@@
 1$, the spectral index is reliable because there is locally a strong linear correlation between
-36.528~MHz and 73.152~MHz. However if $R^2\ll 1$, the spectral index calculation is unreliable.
+36.528~MHz and 73.152~MHz. However, if $R^2\ll 1$, the spectral index calculation is unreliable.
 $R^2$ tends to drop in cold patches of the sky where there is not enough dynamic range to find a
@@
 \ion{H}{2} regions in the galactic plane due to multiple emission mechanisms violating the
-assumption of a single spectral index. Therefore we should restrict our interpretation of
+assumption of a single spectral index. Therefore, we should restrict our interpretation of
 Figure~\ref{fig:internal-spectral-index} to the galactic plane and north galactic spur. In the
 galactic plane, the synchrotron spectral index varies between $\sim-2.5$ and $-2.75$. In the
-vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
-can be seen with higher resolution in Figure~\ref{fig:galactic-plane-cutout}. In this figure
-\ion{H}{2} regions appear as blue shadows along the galactic plane due to the increasing impact of
-free-free absorption at lower frequencies.
-
-In the literature the spectral index at low frequencies is commonly computed with respect to the
+vicinity of \ion{H}{2}, regions the spectral index flattens significantly.  These \ion{H}{2} regions
+can be seen with higher resolution in Figure~\ref{fig:galactic-plane-cutout}. In
+Figure~\ref{fig:galactic-plane-cutout}, \ion{H}{2} regions appear as blue shadows along the galactic
+plane due to the increasing impact of free-free absorption at lower frequencies.
+
+In the literature, the spectral index at low frequencies is commonly computed with respect to the
 Haslam 408~MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H}, which was reprocessed by
@@
 
-\todo{there is only one subsection here, can it be removed?}
-
 \subsubsection{LWA1 Low Frequency Sky Survey}
-
-\todo{redo the figure and text}
 
@@
         subtracted from the OVRO-LWA maps.
-        \todo{fix this fucking figure}
     }
@@
 
-The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced 9 maps of the sky
-between 35~MHz and 80~MHz. 6 of these maps are interior to the frequency range spanned by this work.
-A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In this
-figure the LLFSS maps are filtered to remove the monopole and all modes with $m=0$, and the OVRO-LWA
-maps are interpolated in frequency and blurred to match the angular resolution of the corresponding
-LLFSS map. The dominant feature in this map is a shift of the galactic plane. This feature is also
-seen in comparisons of the LLFSS with the GSM (see for example Figure~9 of
-\citet{2017MNRAS.469.4537D}). Therefore we conclude that this is an artifact of the LLFSS. Otherwise
-at 60~MHz the agreement is generally better than 10\%. However at lower frequencies the agreement
-deterioriates to about 20\%.
+The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced nine maps of the sky
+between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
+work.  A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In
+this figure, the LLFSS maps are filtered to remove the monopole and all modes with $m=0$. The
+OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
+corresponding LLFSS map. This comparison uncovered a $\sim45$~arcmin rotation in the LLFSS maps
+about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  60~MHz, the agreement is
+generally better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.
+Typically the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off
+the galactic plane relative to the LLFSS.
 
 The LLFSS incorporates calibrated total power radiometry to estimate the missing flux from short
-spacings. As a result \citet{2017MNRAS.469.4537D} report per-pixel spectral-indices from combining
-all 9 sky maps. Care must be taken in comparing these spectral indices with
+spacings. As a result \citet{2017MNRAS.469.4537D}, report per-pixel spectral-indices from combining
+all nine sky maps. Care must be taken in comparing these spectral indices with
 Figure~\ref{fig:internal-spectral-index} because they are susceptible to different systematic
@@
 comparison to the galactic plane where the spectral indices are likely to be the most reliable.
-Towards the galactic center both surveys agree that the spectral index is very flat $>-2.2$ due to
-the influence of free-free absorption.  However at galactic latitudes $\sim 180^\circ$ this work
+Towards the galactic center both surveys agree that the spectral index is very flat ($>-2.2$) due to
+the influence of free-free absorption.  However, at galactic latitudes $\sim 180^\circ$ this work
 suggests that the spectral index varies between -2.5 and -2.75, while the LLFSS reports
-substantially flatter indices in the range -2.3 to -2.2. In this region $0.7 < R^2 < 0.9$ so this
-could be an artifact of the comparatively weak correlation between the brightness at 36.528~MHz and
-73.152~MHz, which tends to bias the spectral index towards $-\infty$.
+substantially flatter indices in the range -2.3 to -2.2. In this region $0.7 < R^2 < 0.9$ for the
+OVRO-LWA, so this could be an artifact of the comparatively weak correlation between the brightness
+at 36.528~MHz and 73.152~MHz, which tends to bias the spectral index towards $-\infty$.
 
 The LLFSS also computes spectral indices with respect to the Haslam 408~MHz map. These spectral
-indices are subject to the same caveats and systematic errors as before. However in general the
-qualitative agreement with Figure~\ref{fig:haslam-spectral-index} is better potentially due to the
+indices are subject to the same caveats and systematic errors as before. However, in general the
+qualitative agreement with Figure~\ref{fig:haslam-spectral-index} is better, potentially due to the
 increased robustness associated with estimating spectral indices with a larger fractional bandwidth.
@@
 \citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M} with a
-small gap around the NCP. In this work the zero-level is set by comparing against published
+small gap around the NCP. In this work, the zero-level is set by comparing against published
 low-frequency measurements in six different directions.
@@
 A direct comparison between the OVRO-LWA maps interpolated to 45 MHz and the Guzm\'{a}n 45 MHz map
-can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this comparison the OVRO-LWA map
-was degraded to a 5$^\circ$ resolution by convolving with a Gaussian kernel, and the Guzm\'{a}n map
-has had spherical harmonics with $m=0$ discarded in order to make it consistent with the maps
+can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this comparison, the OVRO-LWA
+map was degraded to a 5$^\circ$ resolution by convolving with a Gaussian kernel, and the Guzm\'{a}n
+map has had spherical harmonics with $m=0$ discarded in order to make it consistent with the maps
 presented in this paper. This figure shows a $\sim20\%$ excess of emission in the galactic plane
-that is consistent with the discrepancy observed between the LLFSS and the Guzm\'{a}n map.  However
+that is consistent with the discrepancy observed between the LLFSS and the Guzm\'{a}n map.  However,
 while the LLFSS has an excess of emission near the north galactic pole, no such excess is observed
@@
     \caption{
-        This figure illustrates the corrupting influence of the ionosphere at 36.528~MHz (left
-        column) compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF
-        for a source at the location of Cas~A.  Each panel illustrates the percent difference
-        (relative to the peak flux of the uncorrupted PSF) due to including an ionospheric effect.
-        In the top row, the simulated source scintillates using the measured light-curve for Cas~A
-        in Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
+        Illustration of the corrupting influence of the ionosphere at 36.528~MHz (left column)
+        compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF for a
+        source at the location of Cas~A, and illustrates the percent difference (relative to the
+        peak flux of the uncorrupted PSF) due to including an ionospheric effect.  In the top row,
+        the simulated source scintillates using the measured light-curve for Cas~A in
+        Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
         its true position using the measured refractive offsets for Cas~A in
@@
 only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
-fringe pattern of the interferometer. At low frequencies the ionosphere violates this assumption.
+fringe pattern of the interferometer. At low frequencies, the ionosphere violates this assumption.
 In particular, ionospheric scintillation and refractive offsets will cause even static sources to
@@
 \begin{equation}\label{eq:no-longer-block-diagonal}
-    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,.
+    V_{\nu, m} \sim \sum_{m^\prime} V_{m^\prime}^\textrm{static} I_{\nu, m-m^\prime}\,,
 \end{equation}
@@
 arising from ionospheric fluctuations. The effect of this can be seen in
-Figure~\ref{fig:ionospheric-simulations}. In this simulation a point source is placed at the
+Figure~\ref{fig:ionospheric-simulations}. In this simulation, a point source is placed at the
 location of Cas~A. In one case the source is allowed to scintillate in the same way Cas~A does in
@@
 serves two purposes:
-
 \begin{enumerate}
@@
 In the first case, all sources at a given declination take the same path through the antenna primary
-beam. If the antenna response is overestimated along this track then all sources at this declination
-will have their flux underestimated. Similarly if the antenna response is underestimated then all
-the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
-show a clear pattern with declination. Two sources have a clear systematic offset at all
+beam. If the antenna response is overestimated along this track, then all sources at this
+declination will have underestimated fluxes. Similarly, if the antenna response is underestimated,
+then all the sources will have overestimated fluxes. The errors in Figure~\ref{fig:flux-scale} do
+not show a clear pattern with declination. Two sources have a clear systematic offset at all
 frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
-southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
+southernmost source -- does not exhibit this systematic error. Similarly, 3C 380 is at a comparable
 declination to Lyn A, which appears, if anything, to have its flux systematically offset in the
@@
 instead of estimating the amplitude of a faint cosmological signal in the presence of foreground
-emission that dominates the signal by 5 orders of magnitude. In fact in \S\ref{sec:ionosphere} we
-found that ionospheric effects likely dominate over other sources of error that affect the PSF
+emission that dominates the signal by five orders of magnitude. In fact, in \S\ref{sec:ionosphere}
+we found that ionospheric effects likely dominate over other sources of error that affect the PSF
 shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
@@
 
-In order to understand the effect of polarization leakage, a point source with 10\% polarization in
-Stokes-$Q$ was simulated at the location of Cas A.  The simulated visibilities were computed using
+In order to understand the effect of polarization leakage, we simulated a point source with 10\%
+polarization in Stokes-$Q$ at the location of Cas A.  The simulated visibilities were computed using
 the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
@@
 Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
-rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about 7 hours
-every day skirting the horizon where the polarization leakage is large, so by placing the simulated
-source at the location of Cas A, we are engineering a situation where the polarization leakage from
-Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
-maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
-PSF.
-
-\todo{compare with obenberger 2015}
+rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about seven
+hours every day skirting the horizon where the polarization leakage is large, so by placing the
+simulated source at the location of Cas A, we are engineering a situation where the polarization
+leakage from Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized
+$m$-mode analysis maps is mild, amounting to a 0.5\% error in the flux of the source with no
+measurable effect on the PSF.
 
@@
     \caption{
-        This is a Mollweide-projected image of the artifacts introduced to the $m$-mode analysis
-        maps by the three terrestrial sources shown in Figure~\ref{fig:fitrfi}. Because these
-        sources are not moving through the sky sidereally, they tend to be smeared along rings of
-        constant declination. The spurs seemingly radiating from the north celestial pole are a
-        Moir\'{e} pattern (ie. an artifact of the pixelization).
+        A Mollweide-projected image of the artifacts introduced to the $m$-mode analysis maps by the
+        three terrestrial sources shown in Figure~\ref{fig:fitrfi}. Because these sources are not
+        moving through the sky sidereally, they tend to be smeared along rings of constant
+        declination. The spurs seemingly radiating from the north celestial pole are a Moir\'{e}
+        pattern (ie. an artifact of the pixelization).
     }
@@
 fluctuations measured between pairs of antennas are exclusively generated by astronomical sources of
-radio emission. In practice this assumption can be violated. For instance a low-frequency
+radio emission. In practice, this assumption can be violated. For instance, a low-frequency
 interferometer located in the vicinity of an arcing power line will see an additional contribution
-from the radio-frequency interference (RFI) generated by the arcing process. Similarly common-mode
+from the radio-frequency interference (RFI) generated by the arcing process. Similarly, common-mode
 pickup along the analog signal path of the interferometer may generate an additional spurious
@@
 The Owens Valley is an important source of water and power for the city of Los Angeles.
-Unfortunately this means that high voltage power lines run along the valley $\gtrsim10$~km to the
+Unfortunately, this means that high voltage power lines run along the valley $\gtrsim10$~km to the
 west of the OVRO-LWA. Some of these power line poles have faulty insulators that arc and produce
@@
 
-In the meantime it is possible to suppress their contamination in the dataset. The contribution of
+In the meantime, it is possible to suppress their contamination in the dataset. The contribution of
 these RFI sources to the visibilities can be plainly seen by averaging $>24$ hours of data with the
@@
 the contaminating sources are at extremely low elevations where the antenna response is essentially
-unknown (and inhomogeneous due to antenna shadowing effects). Therefore it is not enough to know the
-physical location of the faulty insulator generating the RFI. In addition we must know the response
-of each antenna (amplitude and phase) in the appropriate direction. This motivates the use of
-peeling, which allows the antenna response to be a free parameter.  Therefore model visibilities for
-the RFI can be obtained by peeling the sources after smearing the visibilities over $>24$ hours.
+unknown (and inhomogeneous due to antenna shadowing effects). It is not enough to know the physical
+location of the faulty insulator generating the RFI. In addition, we must know the response of each
+antenna (amplitude and phase) in the appropriate direction. This motivates the use of peeling, which
+allows the antenna response to be a free parameter.  Therefore, model visibilities for the RFI can
+be obtained by peeling the sources after smearing the visibilities over $>24$ hours.
 Figure~\ref{fig:fitrfi} shows an illustration of some of the removed components at 62.688 MHz.
@@
 Each column of $\b B$ describes the interferometer's response to a corresponding spherical harmonic
-coefficient of the sky brightness distribution. Therefore the act of computing $\b B^*\b v$ is to
+coefficient of the sky brightness distribution. Therefore, the act of computing $\b B^*\b v$ is to
 project the measured $m$-modes onto the space of $m$-modes which could be generated by astronomical
-sources. The degree to which a source of terrestrial interferer will contaminate a map generated
+sources. The degree to which a source of terrestrial interference will contaminate a map generated
 using $m$-mode analysis imaging is determined by its amplitude after projection.
@@
 $\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = \b 0$.
-In practice this is unlikely. In general the contamination is proportional to the overall amplitude
+In practice this is unlikely. In general, the contamination is proportional to the overall amplitude
 of the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
@@
 
-\todo{make sure this emphasizes that this is a first step}
-
 In this work we presented a new imaging technique -- Tikhonov regularized $m$-mode analysis imaging
-and cleaning -- for drift-scanning telescopes like the OVRO-LWA.  This technique exactly corrects
+and CLEANing -- for drift-scanning telescopes like the OVRO-LWA.  This technique exactly corrects
 for widefield effects in interferometric imaging with a single synthesis imaging step.  We applied
-Tikhonov regularized $m$-mode analysis imaging to a 28 hour dataset and generated 8 sky maps between
-36.528~MHz and 73.152~MHz.  These sky maps are a substantial improvement over existing maps at these
-frequencies due to their 15~arcmin angular resolution and $<600$~K thermal noise. The point source
-flux scale is consistent with that defined by \citet{2012MNRAS.423L..30S} to about 5\% and large
-angular scales are consistent with the work of \citet{2011A&A...525A.138G} to within 20\%.  These
-maps are primarily intended to be used as part of a foreground modeling and subtraction routine for
-21-cm cosmology experiments.
+Tikhonov regularized $m$-mode analysis imaging to a 28 hour dataset and generated eight sky maps
+between 36.528~MHz and 73.152~MHz.  These sky maps are a substantial improvement in angular
+resolution over existing maps at these frequencies with $\sim$15~arcmin angular resolution and
+$<600$~K thermal noise. The point source flux scale is consistent with that defined by
+\citet{2012MNRAS.423L..30S} to about 5\% and large angular scales are consistent with the work of
+\citet{2017MNRAS.469.4537D} to within 20\%.
 
@@
 of $l_\text{max}=1000$. Future work will increase $l_\text{max}$ to remove this restriction, as well
-as include more time and bandwidth to improve the thermal noise. The usage of nighttime only data
+as include more time and bandwidth to improve the thermal noise. The usage of nighttime-only data
 can help mitigate dynamic range limitations from the ionosphere and also eliminate solar sidelobe
@@
 
+These maps and future improvements are primarily intended to be used as part of a foreground
+modeling and subtraction routine for 21-cm cosmology experiments. Each map will be made publicly
+available on LAMBDA.
+
 \acknowledgments

### 2017-10-22 figures/lwa1/make.jl

@@ -1,12 +1,32 @@
 #!/usr/bin/env julia
 
 using JLD, PyPlot, LibHealpix
+using CasaCore.Measures
 
 path = dirname(@__FILE__)
 
 originals, lwa1, ovro, masks = load(joinpath(path, "lwa1-comparison.jld"),
                                     "lwa1-original", "lwa1", "ovro", "masks")
 ν = ["38 MHz", "40 MHz", "45 MHz", "50 MHz", "60 MHz", "70 MHz"]
+
+function rotate_to_galactic(map)
+    frame = ReferenceFrame()
+    z = Direction(dir"J2000", 0, 0, 1)
+    z_ = measure(frame, z, dir"GALACTIC")
+    x = Direction(dir"J2000", 1, 0, 0)
+    x_ = measure(frame, x, dir"GALACTIC")
+    zvec = [z_.x, z_.y, z_.z]
+    xvec = [x_.x, x_.y, x_.z]
+    yvec = cross(zvec, xvec)
+    pixels = zeros(length(map))
+    for idx = 1:length(map)
+        vec = pix2vec(map, idx)
+        θ = acos(dot(vec, zvec))
+        ϕ = atan2(dot(vec, yvec), dot(vec, xvec))
+        pixels[idx] = LibHealpix.interpolate(map, θ, ϕ)
+    end
+    RingHealpixMap(pixels)
+end
 
 figure(1, figsize=(12, 8)); clf()
 axes = []
@@ -23,7 +43,9 @@ for idx = 1:6
 
     δ = (ovro[idx]-lwa1[idx])./originals[idx]
     δ[.!masks[idx]] = NaN
-    _im = imshow(mollweide(RingHealpixMap(δ)), interpolation="nearest",
+    δmap = rotate_to_galactic(RingHealpixMap(δ))
+
+    _im = imshow(mollweide(δmap), interpolation="nearest",
                  vmin=-0.5, vmax=+0.5,
                  cmap=get_cmap("RdBu_r"),
                  extent=(-2, 2, -1, 1),

### 2017-10-23 paper.tex
a few more touchups

@@
         1200 E California Blvd,
-        Pasadena, CA 91125
+        Pasadena, CA 91125, USA
     }
@@
     \affiliation{
+        California Institute of Technology,
         Owens Valley Radio Observatory,
-        California Institute of Technology,
-        Big Pine, CA 93513
+        Big Pine, CA 93513, USA
     }
@@
         4800 Oak Grove Dr,
-        Pasadena, CA 91109
+        Pasadena, CA 91109, USA
     }
@@
         P.O. Box O,
-        Socorro, NM 87801
+        Socorro, NM 87801, USA
     }
@@
         60 Garden Street,
-        Cambridge, MA 02138
+        Cambridge, MA 02138, USA
     }
@@
         501 Campbell Hall,
-        Berkeley, CA 94720
+        Berkeley, CA 94720, USA
     }
@@
         University of New Mexico,
-        Albuquerque, NM 87131
+        Albuquerque, NM 87131, USA
     }
@@
         Bradley Department of Electrical \& Computer Engineering,
-        Blacksburg, VA 24061
+        Blacksburg, VA 24061, USA
     }
@@
         2701 San Tomas Expressway,
-        Santa Clara, CA 95050
+        Santa Clara, CA 95050, USA
     }
@@
 \author{T.~Joseph~W.~Lazio}   \jpl
-\author{Daniel~C.~Price}      \harvard \berkeley \swinburne
+\author{Danny~C.~Price}       \harvard \berkeley \swinburne
 \author{Frank~K.~Schinzel}    \nrao \unm
 \author{Gregory~B.~Taylor}    \unm
+\author{Yuankun~Wang}         \astrocaltech
 \author{David~P.~Woody}       \ovro
@@
 corresponding LLFSS map. This comparison uncovered a $\sim45$~arcmin rotation in the LLFSS maps
-about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  60~MHz, the agreement is
+about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  At 60~MHz, the agreement is
 generally better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.
@@
 Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
-rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about seven
-hours every day skirting the horizon where the polarization leakage is large, so by placing the
-simulated source at the location of Cas A, we are engineering a situation where the polarization
-leakage from Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized
-$m$-mode analysis maps is mild, amounting to a 0.5\% error in the flux of the source with no
-measurable effect on the PSF.
+rises to $\gtrsim50\%$ at lower elevations. \citet{2015JAI.....450004O} report similar polarization
+leakage measurements with the LWA1.  Cas A is a circumpolar source and spends about seven hours
+every day skirting the horizon where the polarization leakage is large, so by placing the simulated
+source at the location of Cas A, we are engineering a situation where the polarization leakage from
+Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
+maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
+PSF.
 
@@
 This work is dedicated to the memory of Professor Marjorie Corcoran, who was an influential mentor
-to M.~W.~Eastwood.
+to MWE.
 
@@
 
+GBT, JD and FKS acknowledge support from the National Science Foundation under grant AST-1139974.
+
 \bibliographystyle{aasjournal}

### 2017-10-24 paper.tex
add chalmers affiliation for stephen and acknowledgements from gregg

@@
 
+\newcommand{\chalmers}{
+    \affiliation{
+        Department of Space, Earth and Environment,
+        Chalmers University of Technology,
+        Onsala Space Observatory,
+        43992 Onsala,
+        Sweden
+    }
+}
+
 \begin{document}
@@
 \author{Benjamin~R.~Barsdell} \harvard \nvidia
-\author{Stephen~A.~Bourke}    \astrocaltech
+\author{Stephen~A.~Bourke}    \astrocaltech \chalmers
 \author{M.~A.~Clark}          \nvidia
@@
 
+This material is based in part upon work supported by the National Science Foundation under Grant
+AST-1654815 and AST-1212226. The OVRO-LWA project was initiated through the kind donation of Deborah
+Castleman and Harold Rosen.
+
 Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of

### 2017-10-25 figures/three-color/make.jl
add the paper as it will be submitted

@@ -57,6 +57,8 @@ function allsky()
 
     savefig(joinpath(path, "ovro-lwa-sky-map.pdf"),
             bbox_inches="tight", pad_inches=0, transparent=true)
+    savefig(joinpath(path, "ovro-lwa-sky-map.png"),
+            bbox_inches="tight", pad_inches=0, transparent=true)
 end
 
 function cutout(map)

### 2017-10-26 create_tarball.jl
add script for creating a tarball that grabs only the relevant files

@@ -1,0 +1,32 @@
+#!/usr/bin/env julia
+
+cd(@__DIR__)
+dir = "eastwood-ovro-sky-maps"
+isdir(dir) && rm(dir, recursive=true)
+mkdir(dir)
+mkdir(joinpath(dir, "figures"))
+
+base_files = ["aasjournal.bst", "aastex61.cls", "paper.bib", "paper.tex"]
+foreach(file->cp(file, joinpath(dir, file)), base_files)
+
+lines = readlines("paper.tex")
+figures = String[]
+for line in lines
+    m = match(r"figures\/(.*)\/(.*)}", line)
+    if m !== nothing
+        push!(figures, joinpath("figures", m.captures[1], m.captures[2]))
+    end
+end
+
+for figure in figures
+    if !endswith(figure, ".pdf")
+        figure = figure*".pdf"
+    end
+    @show figure
+    mydir = joinpath(dir, dirname(figure))
+    isdir(mydir) || mkdir(mydir)
+    cp(figure, joinpath(dir, figure))
+end
+
+run(`tar -cvf eastwood-ovro-sky-maps.tar $dir`)
+

### 2017-10-26 paper.tex
add the paper as it will be submitted
package the paper for submission to arxiv

@@
         Onsala Space Observatory,
-        43992 Onsala,
-        Sweden
+        43992 Onsala, Sweden
+    }
+}
+
+\newcommand{\google}{
+    \affiliation{
+        Google,
+        340 Main St,
+        Venice, CA 90291, USA
     }
@@
 \author{Lincoln~J.~Greenhill} \harvard
+\author{Jacob~M.~Hartman}     \google
 \author{Jonathon~Kocz}        \astrocaltech
@@
 \author{Gregory~B.~Taylor}    \unm
+\author{Harish~K.~Vedantham}  \astrocaltech
 \author{Yuankun~Wang}         \astrocaltech
@@
     imaging using the Owens Valley Long Wavelength Array (OVRO-LWA) by generating 8 new maps of the
-    sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and at frequencies evenly
-    spaced between 36.528~MHz and 73.152~MHz. These maps are a 10-fold improvement in angular
-    resolution over existing full-sky maps at comparable frequencies, which have angular resolutions
-    $\ge 2^\circ$. The thermal noise in each map is $\sim$800 mJy/beam -- comparable to the
-    confusion limit. However, each map is constructed exclusively from interferometric observations
-    and does not represent the globally averaged sky brightness. Therefore future improvements will
-    incorporate total power radiometry, and additional bandwidth and integration time to improve the
-    thermal noise.  The angular resolution can also be further improved with the planned expansion
-    of the OVRO-LWA to 2.6~km baselines.  These maps serve as a first step on the path to the use of
-    more sophisticated foreground filters in 21-cm cosmology incorporating the measured angular and
-    frequency structure of all foreground contaminants.
+    sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution, at frequencies evenly spaced
+    between 36.528~MHz and 73.152~MHz, and $\sim$800 mJy/beam thermal noise. These maps are a
+    10-fold improvement in angular resolution over existing full-sky maps at comparable frequencies,
+    which have angular resolutions $\ge 2^\circ$. Each map is constructed exclusively from
+    interferometric observations and does not represent the globally averaged sky brightness. Future
+    improvements will incorporate total power radiometry, improved thermal noise, and improved
+    angular resolution -- due to the planned expansion of the OVRO-LWA to 2.6~km baselines.  These
+    maps serve as a first step on the path to the use of more sophisticated foreground filters in
+    21-cm cosmology incorporating the measured angular and frequency structure of all foreground
+    contaminants.
 \end{abstract}
@@
 classes of 21-cm cosmology experiments. The brightness temperature of the galactic synchrotron
-emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
+emission at high galactic latitudes is measured by \citet{2017MNRAS.464.4995M} as
 \begin{equation}
-    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
+    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.6}\,.
 \end{equation}

### 2017-10-26 package_for_arxiv.jl

@@ -1,0 +1,60 @@
+#!/usr/bin/env julia
+
+cd(@__DIR__)
+dir = "arxiv"
+isdir(dir) && rm(dir, recursive=true)
+mkdir(dir)
+
+run(`make`)
+
+base_files = ["aasjournal.bst", "aastex61.cls", "paper.bbl"]
+foreach(file->cp(file, joinpath(dir, file)), base_files)
+
+lines = readlines("paper.tex", chomp=false)
+file = open(joinpath(dir, "paper.tex"), "w")
+figures = String[]
+for line in lines
+    m = match(r"figures\/(.*)\/(.*)}", line)
+    if m !== nothing
+        subdir = m.captures[1]
+        figure = m.captures[2]
+        line = replace(line, "figures/$subdir/$figure", figure)
+        push!(figures, joinpath("figures", subdir, figure))
+    end
+    write(file, line)
+end
+close(file)
+
+for figure in figures
+    if !endswith(figure, ".pdf")
+        figure = figure*".pdf"
+    end
+    @show figure
+    cp(figure, joinpath(dir, basename(figure)))
+end
+
+run(`tar -cvf $dir.tar $dir`)
+rm(dir, recursive=true)
+
+# Print the abstract in the right format
+abstract_start = 0
+abstract_stop  = 0
+for (number, line) in enumerate(lines)
+    if contains(line, "begin{abstract}")
+        abstract_start = number
+    end
+    if contains(line, "end{abstract}")
+        abstract_stop = number
+        break
+    end
+end
+
+abstract_text = lines[abstract_start+1:abstract_stop-1]
+abstract_text = strip.(abstract_text)
+abstract_text = join(abstract_text, " ")
+abstract_text = replace(abstract_text, "~", " ")
+
+println("Abstract")
+println("========")
+println(abstract_text)
+

### 2018-01-18 paper.tex
begin to address the referee's report

@@
     The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
-    with the Owens Valley Long Wavelength Array
+    with the Owens Valley Radio Observatory Long Wavelength Array
 }
@@
     generated by $m$-mode analysis imaging. We demonstrate Tikhonov-regularized $m$-mode analysis
-    imaging using the Owens Valley Long Wavelength Array (OVRO-LWA) by generating 8 new maps of the
-    sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution, at frequencies evenly spaced
-    between 36.528~MHz and 73.152~MHz, and $\sim$800 mJy/beam thermal noise. These maps are a
-    10-fold improvement in angular resolution over existing full-sky maps at comparable frequencies,
-    which have angular resolutions $\ge 2^\circ$. Each map is constructed exclusively from
-    interferometric observations and does not represent the globally averaged sky brightness. Future
-    improvements will incorporate total power radiometry, improved thermal noise, and improved
-    angular resolution -- due to the planned expansion of the OVRO-LWA to 2.6~km baselines.  These
-    maps serve as a first step on the path to the use of more sophisticated foreground filters in
-    21-cm cosmology incorporating the measured angular and frequency structure of all foreground
-    contaminants.
+    imaging using the Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) by generating
+    8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution, at
+    frequencies evenly spaced between 36.528~MHz and 73.152~MHz, and $\sim$800 mJy/beam thermal
+    noise. These maps are a 10-fold improvement in angular resolution over existing full-sky maps at
+    comparable frequencies, which have angular resolutions $\ge 2^\circ$. Each map is constructed
+    exclusively from interferometric observations and does not represent the globally averaged sky
+    brightness. Future improvements will incorporate total power radiometry, improved thermal noise,
+    and improved angular resolution -- due to the planned expansion of the OVRO-LWA to 2.6~km
+    baselines.  These maps serve as a first step on the path to the use of more sophisticated
+    foreground filters in 21-cm cosmology incorporating the measured angular and frequency structure
+    of all foreground contaminants.
 \end{abstract}
@@
 As a demonstration of this technique we apply Tikhonov regularized $m$-mode analysis imaging to the
-Owens Valley Long Wavelength Array (OVRO-LWA), and generate a series of new low-frequency maps of
-the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky visible from the Owens
-Valley Radio Observatory (OVRO) with angular resolution of $\sim 15$~arcmin.  These new maps
-complement the existing full-sky maps at these frequencies with greatly improved angular resolution.
+Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA), and generate a series of new
+low-frequency maps of the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky
+visible from the Owens Valley Radio Observatory (OVRO) with angular resolution of $\sim 15$~arcmin.
+These new maps complement the existing full-sky maps at these frequencies with greatly improved
+angular resolution.
 
@@
 one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
-describe our observations with the Owens Valley Long Wavelength Array (OVRO-LWA). In
-\S\ref{sec:results} we present the sky maps and compare these maps against other low-frequency sky
-maps.  In \S\ref{sec:error} we discuss some of the sources of error present in the maps, and finally
-in \S\ref{sec:conclusion} we present our conclusions.
+describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
+compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss some of
+the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present our
+conclusions.
 
@@
 Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
-operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$.  By splitting the
-equation into $N$ independent blocks, the number of floating point operations required to operate on
-the full matrix is reduced by a factor of $N^2$. This computational savings is what makes this
-matrix algebra approach to interferometric imaging feasible.
+operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the linear
+size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
+point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$
+because each block can be manipulated independently of the other blocks. This computational savings
+is what makes this matrix algebra approach to interferometric imaging feasible.
 
@@
 
-\subsection{The Owens Valley Long Wavelength Array}
+\subsection{The Owens Valley Radio Observatory Long Wavelength Array}
 
@@
 
-The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
-Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The OVRO-LWA is a
-low-frequency instrument with instantaneous bandwidth covering 27~MHz to 85~MHz and with 24~kHz
-channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
-$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
-\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
-single snapshot image.
+The Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) is a 288-element interferometer
+located at the Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The
+OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27~MHz to 85~MHz and
+with 24~kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
+there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
+correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
+hemisphere in a single snapshot image.
 

### 2018-02-05 paper.tex
minor fixes in wording

@@
 size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
-point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$
+point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$,
 because each block can be manipulated independently of the other blocks. This computational savings
-is what makes this matrix algebra approach to interferometric imaging feasible.
+is what makes this matrix algebra approach to interferometric imaging feasible. For the dataset
+presented in this paper, computing the elements of the transfer matrix takes $\sim$10 hours per
+frequency channel on a 10-node cluster, but once the matrix has been computed the imaging process
+described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the deconvolution process
+described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.
 
@@
 independently, before being compared against the maps constructed from all of the available data
-using the standard jackknife variance estimator. This estimate of the variance includes all sources
-of error that operate on $\sim13$ second timescales (the integration time) such as thermal noise and
-rapid ionospheric fluctuations, but does not account for more slowly varying effects (for example,
-sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
-noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
+using the jackknife standard error estimator. This estimate of the standard error includes all
+sources of error that operate on $\sim13$ second timescales (the integration time) such as thermal
+noise and rapid ionospheric fluctuations, but does not account for more slowly varying effects (for
+example, sidereal variation in the system temperature or day-night fluctuations in the ionosphere).
+These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
 \citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular

### 2018-03-06 figures/three-color/make.jl
updated three-color images

@@ -21,7 +21,9 @@ function allsky()
         img[x, y, 3] = brightness3[x, y]
     end
 
-    figure(1, figsize=(12, 5)); clf()
+    dpi = 256
+    figure(1, figsize=(size(img, 2)÷dpi, size(img, 1)÷dpi), dpi=dpi); clf()
+    gcf()[:subplots_adjust](left=0, right=1, bottom=0, top=1)
 
     θ = linspace(0, 2π, 512)
     x = 2cos.(θ)

### 2018-03-06 paper.tex
mark revisions from the submitted version in red

@@
 \newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
+\newcommand{\revision}[1]{\textcolor{red}{\textbf{#1}}}
 
@@
     The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
-    with the Owens Valley Radio Observatory Long Wavelength Array
+    with the Owens Valley \revision{Radio Observatory} Long Wavelength Array
 }
@@
 classes of 21-cm cosmology experiments. The brightness temperature of the galactic synchrotron
-emission at high galactic latitudes is measured by \citet{2017MNRAS.464.4995M} as
-\begin{equation}
+emission at high galactic latitudes is measured by \revision{\citet{2017MNRAS.464.4995M}} as
+\revision{\begin{equation}
     T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.6}\,.
-\end{equation}
+\end{equation}}
 Therefore, experiments conservatively need to achieve 5 orders of dynamic range against this
@@
 As a demonstration of this technique we apply Tikhonov regularized $m$-mode analysis imaging to the
-Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA), and generate a series of new
+Owens Valley \revision{Radio Observatory} Long Wavelength Array (OVRO-LWA), and generate a series of new
 low-frequency maps of the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky
@@
 one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
-describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
-compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss some of
-the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present our
-conclusions.
+describe our observations with the \revision{OVRO-LWA}. In \S\ref{sec:results} we present the sky
+maps and compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss
+some of the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present
+our conclusions.
 
@@
 Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
-operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the linear
-size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
-point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$,
-because each block can be manipulated independently of the other blocks. This computational savings
-is what makes this matrix algebra approach to interferometric imaging feasible. For the dataset
-presented in this paper, computing the elements of the transfer matrix takes $\sim$10 hours per
-frequency channel on a 10-node cluster, but once the matrix has been computed the imaging process
-described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the deconvolution process
-described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.
+operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, \revision{where $N$ is
+the linear size of the matrix.  By splitting the equation into $M$ independent blocks, the number of
+floating point operations required to solve the linear system of equations is now
+$\mathcal{O}(N^3M^{-2})$, because each block can be manipulated independently of the other blocks.
+This computational savings is what makes this matrix algebra approach to interferometric imaging
+feasible. For the dataset presented in this paper, computing the elements of the transfer matrix
+takes $\sim$10 hours per frequency channel on a 10-node cluster, but once the matrix has been
+computed the imaging process described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the
+deconvolution process described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.}
 
@@
 
-\subsection{The Owens Valley Radio Observatory Long Wavelength Array}
+\subsection{The Owens Valley \revision{Radio Observatory} Long Wavelength Array}
 
@@
 
-The Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) is a 288-element interferometer
-located at the Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The
-OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27~MHz to 85~MHz and
-with 24~kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
-there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
-correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
-hemisphere in a single snapshot image.
+The Owens Valley \revision{Radio Observatory} Long Wavelength Array (OVRO-LWA) is a 288-element
+interferometer located at the Owens Valley Radio Observatory near Big Pine, California
+\citep{hallinan_2017}.  The OVRO-LWA is a low-frequency instrument with instantaneous bandwidth
+covering 27~MHz to 85~MHz and with 24~kHz channelization.  Each antenna stand hosts two
+perpendicular broadband dipoles so that there are $288\times2$ signal paths in total. These signal
+paths feed into the 512-input LEDA correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA
+to capture the entire visible hemisphere in a single snapshot image.
 
@@
 independently, before being compared against the maps constructed from all of the available data
-using the jackknife standard error estimator. This estimate of the standard error includes all
-sources of error that operate on $\sim13$ second timescales (the integration time) such as thermal
-noise and rapid ionospheric fluctuations, but does not account for more slowly varying effects (for
-example, sidereal variation in the system temperature or day-night fluctuations in the ionosphere).
-These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
-\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
-resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
-noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
+using the jackknife \revision{standard error} estimator. This estimate of the \revision{standard
+error} includes all sources of error that operate on $\sim13$ second timescales (the integration
+time) such as thermal noise and rapid ionospheric fluctuations, but does not account for more slowly
+varying effects (for example, sidereal variation in the system temperature or day-night fluctuations
+in the ionosphere).  These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr
+source counts \citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin
+angular resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves
+thermal noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
 

### 2018-04-25 paper.tex
update lwa1 comparison and ionospheric text

@@
 
-\subsection{Ionospheric Conditions}
+\subsection{Ionospheric Conditions}\label{sec:ionosphere-conditions}
 
@@
 
-In order to account for propagation effects through the ionosphere, direction-dependent calibration
-and peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S} must be used.  Direction-dependent
-calibration allows the per-antenna amplitude and phase towards a bright astronomical source to be
-free parameters. In the dataset used in this paper, scintillation and refractive-offset events on
-the timescale of a single integration (13 seconds) are observed (Figure~\ref{fig:scintillation}).
-Therefore, the direction dependent calibration changes on these timescales, and we must solve for
-one set of complex gains per source per integration.
-
-The largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale of Cyg~A is
-$\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at 73~MHz, the OVRO-LWA
-marginally resolves both sources. A resolved source model is needed for both sources. We fit a
-self-consistent resolved source model to each source. This is performed by minimizing the variance
-within an aperture located on each source after peeling. By phasing up a large number of
-integrations before imaging (at least 1 hour), it is possible to smear out the contribution of the
-rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx) \citep{nlopt, sbplx}
-to vary the parameters in a source model until the variance within the aperture is minimized. Cyg~A
-is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian components. Armed with
-these  source models, both sources can be peeled from the dataset to the required dynamic range.
+\revision{To achieve this dynamic range at low frequencies, it is important to account for
+propagation effects through the ionosphere. In the weak scattering regime ($b_\text{max} \ll 2\pi
+r_\text{diff}$, where $b_\text{max}$ is the maximum baseline length, and $r_\text{diff}$ is the
+diffractive scale of the ionosphere), fluctuations within the ionosphere contribute amplitude and
+phase scintillations that can be described by a direction-dependent complex-gain calibration. This
+justifies the use of ``peeling'', which incorporates a direction-dependent calibration to subtract
+sources in the presence of ionospheric scintillation.  \citep[eg.][]{2008ISTSP...2..707M,
+2015MNRAS.449.2668S}.}
+
+\revision{In the strong scattering regime ($b_\text{max} \gtrsim 2\pi r_\text{diff}$), the image of
+a point source can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.
+Attempting to peel a source in the strong scattering regime will lead to source subtraction
+artifacts in the final sky map.  \citet{2016RaSc...51..927M} measured that from the location of
+LOFAR at 150 MHz, the diffractive scale of the ionosphere is $>5$ km 90\% of the time. This implies
+that at 73 MHz, the diffractive scale is typically $>2$ km, and at 36 MHz, the diffractive scale is
+typically $>1$ km. The maximum baseline length of the OVRO-LWA is $\sim 1.5$ km, and therefore we do
+not generally expect to see strong scattering from the ionosphere.  Furthermore, ionospheric
+conditions during the observing period were mild (see \S\ref{sec:ionosphere-conditions}), but we
+still observe scintillation and refractive-offset events on the timescale of a single integration
+(13 seconds, see Figure~\ref{fig:scintillation}). Consequently we peeled Cyg~A and Cas~A from the
+dataset using a new solution for each integration.}
+
+\revision{In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular
+scale of Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at
+73~MHz, the OVRO-LWA marginally resolves both sources. A resolved source model is needed for both
+sources. We fit a self-consistent resolved source model to each source. This is performed by
+minimizing the variance within an aperture located on each source after peeling. By phasing up a
+large number of integrations before imaging (at least 1 hour), it is possible to smear out the
+contribution of the rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx)
+\citep{nlopt, sbplx} to vary the parameters in a source model until the variance within the aperture
+is minimized. Cyg~A is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian
+components.  Ultimately, these multi-component models are used to peel Cyg~A and Cas~A, but residual
+errors from this model and from the ionosphere (particularly while these sources are at low
+elevations) contribute residual artifacts that are largely localized to within 1$^\circ$ of each
+source.}
 
@@
 between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
-work.  A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In
-this figure, the LLFSS maps are filtered to remove the monopole and all modes with $m=0$. The
-OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
-corresponding LLFSS map. This comparison uncovered a $\sim45$~arcmin rotation in the LLFSS maps
-about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  At 60~MHz, the agreement is
-generally better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.
-Typically the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off
-the galactic plane relative to the LLFSS.
+work. \revision{Initial comparisons with the LLFSS helped characterize a systematic rotation in the
+LWA1's antenna positions. After phase-calibration, this manifested itself as a systematic rotation
+and translation in the snapshot images that were mosaicked to form the final sky map. This
+systematic error has been corrected in the comparisons presented here and in the latest version of
+the LLFSS\footnote{
+    Available for download at: \url{http://lda10g.alliance.unm.edu/LWA1LowFrequencySkySurvey/}
+}.}
+
+\revision{A direct comparison with these updated LLFSS maps can be seen in
+Figure~\ref{fig:lwa1-comparison}.  In this figure, the LLFSS maps are filtered to remove the
+monopole and all modes with $m=0$. The OVRO-LWA maps are interpolated in frequency and blurred to
+match the angular resolution of the corresponding LLFSS map.  At 60~MHz, the agreement is generally
+better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.  Typically
+the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off the
+galactic plane relative to the LLFSS.}
 

### 2018-04-25 figures/guzman/fetch.sh

@@ -1,4 +1,4 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/comparison-with-guzman.jld .
+scp mweastwood@astm13.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/comparison-with-guzman.jld .
 

### 2018-04-25 figures/guzman/make.jl

@@ -1,11 +1,12 @@
 #!/usr/bin/env julia
 
-using JLD, PyPlot, LibHealpix, PerceptualColourMaps
+using JLD, PyPlot, LibHealpix
 
 path = dirname(@__FILE__)
 
 δ = load(joinpath(path, "comparison-with-guzman.jld"), "difference")
-img = mollweide(RingHealpixMap(δ))
+img = mollweide(RingHealpixMap(δ), (256, 512))
+img[img .== 0] = NaN # this deletes contours around the edge of the map
 
 figure(1, figsize=(12, 5)); clf()
 
@@ -15,11 +16,15 @@ y = sin.(θ)
 
 ellipse = plt[:Polygon]([x y], alpha=0)
 gca()[:add_patch](ellipse)
-imshow(img, interpolation="nearest", cmap=get_cmap("RdBu_r"),
-                                    #cmap=ColorMap(cmap("D4")),
-       vmin=-0.5, vmax=+0.5,
-       extent=(-2, 2, -1, 1),
-       clip_path=ellipse, zorder=10)
+_im = imshow(img, interpolation="nearest", cmap=get_cmap("RdBu_r"),
+             vmin=-0.5, vmax=+0.5,
+             extent=(-2, 2, -1, 1),
+             clip_path=ellipse)
+cs = contour(img, -0.5:0.1:0.5,
+             extent=(-2, 2, 1, -1), origin="lower",
+             linewidths=0.5,
+             colors=("k", "k"),
+             clip_path=ellipse)
 xlim(-2, 2)
 ylim(-1, 1)
 gca()[:set_aspect]("equal")
@@ -27,7 +32,7 @@ gca()[:get_xaxis]()[:set_visible](false)
 gca()[:get_yaxis]()[:set_visible](false)
 axis("off")
 
-cbar = colorbar()
+cbar = colorbar(_im)
 cbar[:ax][:tick_params](labelsize=12)
 cbar[:set_label]("fractional difference", fontsize=12, rotation=270)
 cbar[:ax][:get_yaxis]()[:set_label_coords](4.0, 0.5)

### 2018-04-25 figures/lwa1/fetch.sh

@@ -1,4 +1,4 @@
 #!/bin/bash
 
-scp mweastwood@astm01.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/lwa1-comparison.jld .
+scp mweastwood@astm13.lwa.ovro.caltech.edu:/lustre/mweastwood/mmode-analysis/pipeline/Comparisons/lwa1-comparison.jld .
 

### 2018-04-25 figures/lwa1/make.jl

@@ -45,11 +45,18 @@ for idx = 1:6
     δ[.!masks[idx]] = NaN
     δmap = rotate_to_galactic(RingHealpixMap(δ))
 
-    _im = imshow(mollweide(δmap), interpolation="nearest",
+    img = mollweide(δmap)
+    img[img .== 0] = NaN # this deletes contours around the edge of the map
+    _im = imshow(img, interpolation="nearest",
                  vmin=-0.5, vmax=+0.5,
                  cmap=get_cmap("RdBu_r"),
                  extent=(-2, 2, -1, 1),
                  clip_path=ellipse, zorder=1)
+    cs = contour(img, -0.1:0.1:0.1,
+                 extent=(-2, 2, 1, -1), origin="lower",
+                 linewidths=0.5,
+                 colors=("k", "k"),
+                 clip_path=ellipse)
     xlim(-2, 2)
     ylim(-1, 1)
     gca()[:set_aspect]("equal")

### 2018-04-26 paper.tex
update the ionospheric text and other minor edits

@@
 of cosmological 21-cm perturbations.  Ongoing global signal experiments include EDGES
-\citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
-\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
-\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
-\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
-\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.
+\citep{2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS \citep{2015PASA...32....4S},
+SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum
+experiments include PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
+\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}. Recently,
+EDGES reported the first detection of 21-cm absorption in the globally averaged sky-signal
+\citep{2018Natur.555...67B}.
 
@@
 foreground emission before the cosmological signal can be measured. Current foreground removal
-methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
-emission is spectrally smooth. The low-frequency radio sky is composed of several components:
-galactic synchrotron emission, supernova remnants, radio galaxies, free-free emission and absorption
-from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally, a foreground removal
-strategy should be informed by the measured spatial structure and frequency spectrum of all
-foreground components. For instance, CMB experiments typically construct several maps at several
-frequencies to enable component separation.  At low frequencies, this possibility is limited by the
-availability of suitable high-fidelity sky maps on angular scales ranging from tens of degrees to
-arcminutes.
+methods (for example, \citealt{2012ApJ...756..165P} and \citealt{2013MNRAS.429..165C}) rely on the
+assumption that the foreground emission is spectrally smooth. The low-frequency radio sky is
+composed of several components: galactic synchrotron emission, supernova remnants, radio galaxies,
+free-free emission and absorption from \ion{H}{2} regions, and a confusing background of radio
+sources.  Ideally, a foreground removal strategy should be informed by the measured spatial
+structure and frequency spectrum of all foreground components. For instance, CMB experiments
+typically construct several maps at several frequencies to enable component separation.  At low
+frequencies, this possibility is limited by the availability of suitable high-fidelity sky maps on
+angular scales ranging from tens of degrees to arcminutes.
 
@@
 
-In the context of $m$-mode analysis a transit telescope is any interferometer for which the response
-pattern of the individual elements does not change with respect to time. This may be an
+In the context of $m$-mode analysis, a transit telescope is any interferometer for which the
+response pattern of the individual elements does not change with respect to time. This may be an
 interferometer like the OVRO-LWA where the correlation elements are fixed dipoles, but it may also
@@
 
-If the baselines have a noise covariance matrix $\b N \neq n\b I$ for some scalar $n$ (eg. the
-interferometer is inhomogeneous), then the observer should minimize $(\b v-\b B\b a)^*\b N^{-1}(\b
-v-\b B\b a) + \varepsilon\|\b a\|^2$. The matrix $\b N$ is used to weight the measurements such that
+If the measured $m$-modes have a noise covariance matrix $\b N \neq n\b I$ for some scalar $n$ (eg.
+the interferometer is inhomogeneous), then the observer should minimize $(\b v-\b B\b a)^*\b
+N^{-1}(\b v-\b B\b a) + \varepsilon\|\b a\|^2$. The noise covariance matrix $\b N$ is used to weight
+the measurements such that
 \begin{equation}
@@
         Mountains when it is low on the horizon to the east.
-        Panels (c) and (d) These panels show the measured position offset of Cyg~A and Cas~A
-        relative to their true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue
-        line).
+        Panels (c) and (d) show the measured position offset of Cyg~A and Cas~A relative to their
+        true astronomical positions at 36.528 MHz (red line) and 73.152 MHz (blue line).
     }
@@
 
-\revision{To achieve this dynamic range at low frequencies, it is important to account for
-propagation effects through the ionosphere. In the weak scattering regime ($b_\text{max} \ll 2\pi
-r_\text{diff}$, where $b_\text{max}$ is the maximum baseline length, and $r_\text{diff}$ is the
-diffractive scale of the ionosphere), fluctuations within the ionosphere contribute amplitude and
-phase scintillations that can be described by a direction-dependent complex-gain calibration. This
-justifies the use of ``peeling'', which incorporates a direction-dependent calibration to subtract
-sources in the presence of ionospheric scintillation.  \citep[eg.][]{2008ISTSP...2..707M,
-2015MNRAS.449.2668S}.}
-
-\revision{In the strong scattering regime ($b_\text{max} \gtrsim 2\pi r_\text{diff}$), the image of
-a point source can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.
+\revision{
+    To achieve this dynamic range at low frequencies, it is important to account for propagation
+    effects through the ionosphere. In the weak scattering regime ($r_\text{diff} \gg r_\text{f}$,
+    where $r_\text{diff}$ is the diffractive scale of the ionosphere, $r_\text{f} =
+    \sqrt{\lambda D / 2\pi}$ is the Fresnel scale, $\lambda$ is the wavelength, and $D$ is the
+    distance to the ionosphere), fluctuations within the ionosphere contribute
+    amplitude and phase scintillations that can be described by a direction-dependent complex-gain
+    calibration. This justifies the use of ``peeling'', which incorporates a direction-dependent
+    calibration to subtract sources in the presence of ionospheric scintillation.
+    \citep[eg.][]{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.
+}
+
+\revision{
+    In the strong scattering regime ($r_\text{diff} \lesssim r_\text{f}$), the image of a point
+    source can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.
     Attempting to peel a source in the strong scattering regime will lead to source subtraction
     artifacts in the final sky map.  \citet{2016RaSc...51..927M} measured that from the location of
-LOFAR at 150 MHz, the diffractive scale of the ionosphere is $>5$ km 90\% of the time. This implies
-that at 73 MHz, the diffractive scale is typically $>2$ km, and at 36 MHz, the diffractive scale is
-typically $>1$ km. The maximum baseline length of the OVRO-LWA is $\sim 1.5$ km, and therefore we do
-not generally expect to see strong scattering from the ionosphere.  Furthermore, ionospheric
-conditions during the observing period were mild (see \S\ref{sec:ionosphere-conditions}), but we
-still observe scintillation and refractive-offset events on the timescale of a single integration
-(13 seconds, see Figure~\ref{fig:scintillation}). Consequently we peeled Cyg~A and Cas~A from the
-dataset using a new solution for each integration.}
-
-\revision{In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular
-scale of Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at
-73~MHz, the OVRO-LWA marginally resolves both sources. A resolved source model is needed for both
-sources. We fit a self-consistent resolved source model to each source. This is performed by
-minimizing the variance within an aperture located on each source after peeling. By phasing up a
-large number of integrations before imaging (at least 1 hour), it is possible to smear out the
-contribution of the rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx)
-\citep{nlopt, sbplx} to vary the parameters in a source model until the variance within the aperture
-is minimized. Cyg~A is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian
-components.  Ultimately, these multi-component models are used to peel Cyg~A and Cas~A, but residual
-errors from this model and from the ionosphere (particularly while these sources are at low
-elevations) contribute residual artifacts that are largely localized to within 1$^\circ$ of each
-source.}
+    LOFAR at 150 MHz, the diffractive scale of the ionosphere is $>5$ km 90\% of the time. This
+    implies that at 73 MHz, the diffractive scale is typically $>2$ km, and at 36 MHz, the
+    diffractive scale is typically $>1$ km. These limits are comparable to the Fresnel scale for the
+    OVRO-LWA (ie. $r_\text{diff} > r_\text{f}$), and therefore we do not generally expect to see
+    strong scattering from the ionosphere.  Ionospheric conditions during the observing period were
+    mild (see \S\ref{sec:ionosphere-conditions}). However, we do observe scintillation and
+    refractive-offset events on the timescale of a single integration (13 seconds, see
+    Figure~\ref{fig:scintillation}). Consequently we peeled Cyg~A and Cas~A from the dataset using a
+    new solution for each integration.
+}
+
+\revision{
+    In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale
+    of Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at
+    73~MHz, the OVRO-LWA marginally resolves both sources. A resolved source model is needed for
+    both sources. We fit a self-consistent resolved source model to each source. This is performed
+    by minimizing the variance within an aperture located on each source after peeling. By phasing
+    up a large number of integrations before imaging (at least 1 hour), it is possible to smear out
+    the contribution of the rest of the sky.  We then use a non-linear optimization routine (NLopt
+    Sbplx) \citep{nlopt, sbplx} to vary the parameters in a source model until the variance within
+    the aperture is minimized. Cyg~A is modeled with 2 Gaussian components, while Cas~A is modeled
+    with 3~Gaussian components.  Ultimately, these multi-component models are used to peel Cyg~A and
+    Cas~A, but residual errors from this model and from the ionosphere (particularly while these
+    sources are at low elevations) contribute residual artifacts that are largely localized to
+    within 1$^\circ$ of each source.
+}
 
@@
 Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
-maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
-PSF.
+maps is mild, amounting to a 0.5\% error in the flux of the source.
 

### 2018-05-09 paper.tex
minor revisions

@@
     The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
-    with the Owens Valley \revision{Radio Observatory} Long Wavelength Array
+    with the \revision{OVRO-LWA}
 }
@@
 The maps will be made freely available online at the Legacy Archive for Microwave Background Data
-Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.
+Analysis (LAMBDA)\footnote{
+    \url{https://lambda.gsfc.nasa.gov/product/foreground/fg_ovrolwa_radio_maps_info.cfm}
+}.
 
@@
 Each map from Figure~\ref{fig:channel-maps} will be made freely available online in Healpix format
-\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).
+\citep{2005ApJ...622..759G} on LAMBDA.
 

### 2018-06-15 cover-letter.tex
cover letter

\documentclass{article}

\usepackage{hyperref}
\usepackage{color}
\newcommand{\revision}[1]{\textcolor{red}{\textbf{#1}}}

\begin{document}

\section{Cover Letter}

We appreciated the reviewer's helpful comments, particularly the concern about ionospheric
scintillation resolving to antenna gains.  We interpreted this concern as primarily applicable to
direction-dependent calibration, which is used during the removal of bright point sources (primarily
Cyg A and Cas A).

The relevant length scales in the ionosphere are the diffractive scale (essentially the length over
which the ionosphere imparts a 1 radian phase difference) and the Fresnel scale. In the usual case
where the diffractive scale is much larger than the Fresnel scale, you can see phase and amplitude
scintillation, but these effects can be absorbed into direction-dependent complex gains. However,
when the diffractive scale is less than the Fresnel scale, you can see a point source break apart
into multiple images. This cannot be entirely absorbed into direction-dependent complex gains, but
the error you make during source removal leads to residual artifacts in the vicinity of the source.
We added additional text to Section 3.5.1 that addresses this possibility.

The second-to-last paragraph in Section 2.1 explains why we restricted ourselves to single channel
imaging (reproduced below):

\begin{quote}
    If each element of the matrix is stored as a 64-bit complex floating point number, a single
    block is 500 MB for the case of single-channel imaging with the OVRO-LWA, which a modern
    computer can easily store and manipulate in memory.  However, with additional bandwidth these
    blocks quickly become unwieldy; thus as a first pass, the analysis in this paper is restricted
    to single-channel imaging.
\end{quote}

However, additional text and explicit runtimes have been added to clarify how additional bandwidth
impacts the amount of processing time necessary to generate the maps presented in this work.

Changes to the text are highlighted with \revision{red font and boldface}. These changes are listed
below.

\section{List of Changes}

\begin{enumerate}
    \item The "Owens Valley Radio Observatory Long Wavelength Array" (OVRO-LWA) was incorrectly
        referred to as the "Owens Valley Long Wavelength Array". This has been corrected throughout
        the article.

    \item A URL pointing to where the final sky maps can be downloaded from LAMBDA has been added
        (\url{https://lambda.gsfc.nasa.gov/product/foreground/fg_ovrolwa_radio_maps_info.cfm}).

    \item In Section 1, the brightness temperature of the galactic synchrotron emission was updated
        to reference a more recent measurement.

    \item In Section 2.1, additional text clarifies the use of multiple ``N''s and gives some
        explicit examples typical runtime for each step of the analysis. There is also an additional
        sentence mentioning that for a block diagonal matrices, all of the blocks can be manipulated
        independently.

    \item In Section 3.5.1 we added additional text discussing the impact of the ionosphere in the
        strong scattering regime (summarized above).

    \item In Section 4, the text incorrectly mentioned estimating the variance with a jackknife
        estimator.  We are actually estimating the standard error, and the standard error is
        reported in Table 1.

    \item The original text described a $\sim$45 arcmin rotation that was apparent in comparisons
        with the LWA1 Low Frequency Sky Survey. This rotation was confirmed to originate from a
        rotation in the LWA1's antenna coordinates, and has been fixed.  Section 4.1.1 has been
        updated accordingly, and Figure 13 has also been updated to provide comparisons with the
        corrected LWA1 maps.
\end{enumerate}

\end{document}

### 2018-07-06 paper.tex
remove revision markup

@@
     The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
-    with the \revision{OVRO-LWA}
+    with the OVRO-LWA
 }
@@
 classes of 21-cm cosmology experiments. The brightness temperature of the galactic synchrotron
-emission at high galactic latitudes is measured by \revision{\citet{2017MNRAS.464.4995M}} as
-\revision{\begin{equation}
+emission at high galactic latitudes is measured by \citet{2017MNRAS.464.4995M} as
+\begin{equation}
     T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.6}\,.
-\end{equation}}
+\end{equation}
 Therefore, experiments conservatively need to achieve 5 orders of dynamic range against this
@@
 As a demonstration of this technique we apply Tikhonov regularized $m$-mode analysis imaging to the
-Owens Valley \revision{Radio Observatory} Long Wavelength Array (OVRO-LWA), and generate a series of new
+Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA), and generate a series of new
 low-frequency maps of the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky
@@
 one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
-describe our observations with the \revision{OVRO-LWA}. In \S\ref{sec:results} we present the sky
-maps and compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss
-some of the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present
-our conclusions.
+describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
+compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss some of
+the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present our
+conclusions.
 
@@
 Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
-operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, \revision{where $N$ is
-the linear size of the matrix.  By splitting the equation into $M$ independent blocks, the number of
-floating point operations required to solve the linear system of equations is now
-$\mathcal{O}(N^3M^{-2})$, because each block can be manipulated independently of the other blocks.
-This computational savings is what makes this matrix algebra approach to interferometric imaging
-feasible. For the dataset presented in this paper, computing the elements of the transfer matrix
-takes $\sim$10 hours per frequency channel on a 10-node cluster, but once the matrix has been
-computed the imaging process described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the
-deconvolution process described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.}
+operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the linear
+size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
+point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$,
+because each block can be manipulated independently of the other blocks.  This computational savings
+is what makes this matrix algebra approach to interferometric imaging feasible. For the dataset
+presented in this paper, computing the elements of the transfer matrix takes $\sim$10 hours per
+frequency channel on a 10-node cluster, but once the matrix has been computed the imaging process
+described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the deconvolution process
+described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.
 
@@
 
-\subsection{The Owens Valley \revision{Radio Observatory} Long Wavelength Array}
+\subsection{The Owens Valley Radio Observatory Long Wavelength Array}
 
@@
 
-The Owens Valley \revision{Radio Observatory} Long Wavelength Array (OVRO-LWA) is a 288-element
-interferometer located at the Owens Valley Radio Observatory near Big Pine, California
-\citep{hallinan_2017}.  The OVRO-LWA is a low-frequency instrument with instantaneous bandwidth
-covering 27~MHz to 85~MHz and with 24~kHz channelization.  Each antenna stand hosts two
-perpendicular broadband dipoles so that there are $288\times2$ signal paths in total. These signal
-paths feed into the 512-input LEDA correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA
-to capture the entire visible hemisphere in a single snapshot image.
+The Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) is a 288-element interferometer
+located at the Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The
+OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27~MHz to 85~MHz and
+with 24~kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
+there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
+correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
+hemisphere in a single snapshot image.
 
@@
 
-\revision{
-    To achieve this dynamic range at low frequencies, it is important to account for propagation
-    effects through the ionosphere. In the weak scattering regime ($r_\text{diff} \gg r_\text{f}$,
-    where $r_\text{diff}$ is the diffractive scale of the ionosphere, $r_\text{f} =
-    \sqrt{\lambda D / 2\pi}$ is the Fresnel scale, $\lambda$ is the wavelength, and $D$ is the
-    distance to the ionosphere), fluctuations within the ionosphere contribute
-    amplitude and phase scintillations that can be described by a direction-dependent complex-gain
-    calibration. This justifies the use of ``peeling'', which incorporates a direction-dependent
-    calibration to subtract sources in the presence of ionospheric scintillation.
-    \citep[eg.][]{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.
-}
-
-\revision{
-    In the strong scattering regime ($r_\text{diff} \lesssim r_\text{f}$), the image of a point
-    source can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.
-    Attempting to peel a source in the strong scattering regime will lead to source subtraction
-    artifacts in the final sky map.  \citet{2016RaSc...51..927M} measured that from the location of
-    LOFAR at 150 MHz, the diffractive scale of the ionosphere is $>5$ km 90\% of the time. This
-    implies that at 73 MHz, the diffractive scale is typically $>2$ km, and at 36 MHz, the
-    diffractive scale is typically $>1$ km. These limits are comparable to the Fresnel scale for the
-    OVRO-LWA (ie. $r_\text{diff} > r_\text{f}$), and therefore we do not generally expect to see
-    strong scattering from the ionosphere.  Ionospheric conditions during the observing period were
-    mild (see \S\ref{sec:ionosphere-conditions}). However, we do observe scintillation and
-    refractive-offset events on the timescale of a single integration (13 seconds, see
-    Figure~\ref{fig:scintillation}). Consequently we peeled Cyg~A and Cas~A from the dataset using a
-    new solution for each integration.
-}
-
-\revision{
-    In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale
-    of Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at
-    73~MHz, the OVRO-LWA marginally resolves both sources. A resolved source model is needed for
-    both sources. We fit a self-consistent resolved source model to each source. This is performed
-    by minimizing the variance within an aperture located on each source after peeling. By phasing
-    up a large number of integrations before imaging (at least 1 hour), it is possible to smear out
-    the contribution of the rest of the sky.  We then use a non-linear optimization routine (NLopt
-    Sbplx) \citep{nlopt, sbplx} to vary the parameters in a source model until the variance within
-    the aperture is minimized. Cyg~A is modeled with 2 Gaussian components, while Cas~A is modeled
-    with 3~Gaussian components.  Ultimately, these multi-component models are used to peel Cyg~A and
-    Cas~A, but residual errors from this model and from the ionosphere (particularly while these
-    sources are at low elevations) contribute residual artifacts that are largely localized to
-    within 1$^\circ$ of each source.
-}
+To achieve this dynamic range at low frequencies, it is important to account for propagation effects
+through the ionosphere. In the weak scattering regime ($r_\text{diff} \gg r_\text{f}$, where
+$r_\text{diff}$ is the diffractive scale of the ionosphere, $r_\text{f} = \sqrt{\lambda D / 2\pi}$
+is the Fresnel scale, $\lambda$ is the wavelength, and $D$ is the distance to the ionosphere),
+fluctuations within the ionosphere contribute amplitude and phase scintillations that can be
+described by a direction-dependent complex-gain calibration. This justifies the use of ``peeling'',
+which incorporates a direction-dependent calibration to subtract sources in the presence of
+ionospheric scintillation.  \citep[eg.][]{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.
+
+In the strong scattering regime ($r_\text{diff} \lesssim r_\text{f}$), the image of a point source
+can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.  Attempting to
+peel a source in the strong scattering regime will lead to source subtraction artifacts in the final
+sky map.  \citet{2016RaSc...51..927M} measured that from the location of LOFAR at 150 MHz, the
+diffractive scale of the ionosphere is $>5$ km 90\% of the time. This implies that at 73 MHz, the
+diffractive scale is typically $>2$ km, and at 36 MHz, the diffractive scale is typically $>1$ km.
+These limits are comparable to the Fresnel scale for the OVRO-LWA (ie. $r_\text{diff} >
+r_\text{f}$), and therefore we do not generally expect to see strong scattering from the ionosphere.
+Ionospheric conditions during the observing period were mild (see
+\S\ref{sec:ionosphere-conditions}). However, we do observe scintillation and refractive-offset
+events on the timescale of a single integration (13 seconds, see Figure~\ref{fig:scintillation}).
+Consequently we peeled Cyg~A and Cas~A from the dataset using a new solution for each integration.
+
+In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale of
+Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at 73~MHz, the
+OVRO-LWA marginally resolves both sources. A resolved source model is needed for both sources. We
+fit a self-consistent resolved source model to each source. This is performed by minimizing the
+variance within an aperture located on each source after peeling. By phasing up a large number of
+integrations before imaging (at least 1 hour), it is possible to smear out the contribution of the
+rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx) \citep{nlopt, sbplx}
+to vary the parameters in a source model until the variance within the aperture is minimized. Cyg~A
+is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian components.
+Ultimately, these multi-component models are used to peel Cyg~A and Cas~A, but residual errors from
+this model and from the ionosphere (particularly while these sources are at low elevations)
+contribute residual artifacts that are largely localized to within 1$^\circ$ of each source.
 
@@
 independently, before being compared against the maps constructed from all of the available data
-using the jackknife \revision{standard error} estimator. This estimate of the \revision{standard
-error} includes all sources of error that operate on $\sim13$ second timescales (the integration
-time) such as thermal noise and rapid ionospheric fluctuations, but does not account for more slowly
-varying effects (for example, sidereal variation in the system temperature or day-night fluctuations
-in the ionosphere).  These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr
-source counts \citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin
-angular resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves
-thermal noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
+using the jackknife standard error estimator. This estimate of the standard error includes all
+sources of error that operate on $\sim13$ second timescales (the integration time) such as thermal
+noise and rapid ionospheric fluctuations, but does not account for more slowly varying effects (for
+example, sidereal variation in the system temperature or day-night fluctuations in the ionosphere).
+These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
+\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
+resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
+noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
 
@@
 between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
-work. \revision{Initial comparisons with the LLFSS helped characterize a systematic rotation in the
-LWA1's antenna positions. After phase-calibration, this manifested itself as a systematic rotation
-and translation in the snapshot images that were mosaicked to form the final sky map. This
-systematic error has been corrected in the comparisons presented here and in the latest version of
-the LLFSS\footnote{
+work. Initial comparisons with the LLFSS helped characterize a systematic rotation in the LWA1's
+antenna positions. After phase-calibration, this manifested itself as a systematic rotation and
+translation in the snapshot images that were mosaicked to form the final sky map. This systematic
+error has been corrected in the comparisons presented here and in the latest version of the
+LLFSS\footnote{
     Available for download at: \url{http://lda10g.alliance.unm.edu/LWA1LowFrequencySkySurvey/}
-}.}
-
-\revision{A direct comparison with these updated LLFSS maps can be seen in
-Figure~\ref{fig:lwa1-comparison}.  In this figure, the LLFSS maps are filtered to remove the
-monopole and all modes with $m=0$. The OVRO-LWA maps are interpolated in frequency and blurred to
-match the angular resolution of the corresponding LLFSS map.  At 60~MHz, the agreement is generally
-better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.  Typically
-the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off the
-galactic plane relative to the LLFSS.}
+}.
+
+A direct comparison with these updated LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}.
+In this figure, the LLFSS maps are filtered to remove the monopole and all modes with $m=0$. The
+OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
+corresponding LLFSS map.  At 60~MHz, the agreement is generally better than 10\%. However at lower
+frequencies the agreement deteriorates to about 20\%.  Typically the OVRO-LWA maps have excess
+emission in the galactic plane and a deficit of emission off the galactic plane relative to the
+LLFSS.
 

### 2018-07-06 paper.tex
add corrections from the editor

@@
 \begin{abstract}
-    A host of new low-frequency radio telescopes seek to measure the 21-cm transition of neutral
+    A host of new low-frequency radio telescopes seek to measure the 21~cm transition of neutral
     hydrogen from the early universe.  These telescopes have the potential to directly probe star
@@
     is a growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for
-    use in foreground modeling and removal.  We describe a new widefield imaging technique for
-    drift-scanning interferometers, Tikhonov-regularized $m$-mode analysis imaging.  This technique
+    use in foreground modeling and removal.  We describe a new wide-field imaging technique for
+    drift-scanning interferometers: Tikhonov-regularized $m$-mode analysis imaging.  This technique
     constructs images of the entire sky in a single synthesis imaging step with exact treatment of
-    widefield effects.  We describe how the CLEAN algorithm can be adapted to deconvolve maps
+    wide-field effects.  We describe how the CLEAN algorithm can be adapted to deconvolve maps
     generated by $m$-mode analysis imaging. We demonstrate Tikhonov-regularized $m$-mode analysis
     imaging using the Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) by generating
-    8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution, at
-    frequencies evenly spaced between 36.528~MHz and 73.152~MHz, and $\sim$800 mJy/beam thermal
-    noise. These maps are a 10-fold improvement in angular resolution over existing full-sky maps at
+    eight new maps of the sky north of $\delta=-30^\circ$ with 15\arcmin angular resolution at
+    frequencies evenly spaced between 36.528 and 73.152~MHz, and $\sim$800 mJy/beam thermal noise.
+    These maps are a 10-fold improvement in angular resolution over existing full-sky maps at
     comparable frequencies, which have angular resolutions $\ge 2^\circ$. Each map is constructed
@@
     brightness. Future improvements will incorporate total power radiometry, improved thermal noise,
-    and improved angular resolution -- due to the planned expansion of the OVRO-LWA to 2.6~km
+    and improved angular resolution due to the planned expansion of the OVRO-LWA to 2.6~km
     baselines.  These maps serve as a first step on the path to the use of more sophisticated
-    foreground filters in 21-cm cosmology incorporating the measured angular and frequency structure
+    foreground filters in 21~cm cosmology incorporating the measured angular and frequency structure
     of all foreground contaminants.
@@
 
-At redshifts $20 \gtrsim z \gtrsim 7$, the 21-cm hyperfine structure line of neutral hydrogen is
-expected to produce a 10 to 100 mK perturbation in the Cosmic Microwave Background (CMB) spectrum
-\citep{2006PhR...433..181F, 2012RPPh...75h6901P}. The amplitude of this perturbation on a given
-line-of-sight is a function of the neutral fraction of hydrogen, the baryon overdensity, the spin
+At redshifts $20 \gtrsim z \gtrsim 7$, the 21~cm hyperfine structure line of neutral hydrogen is
+expected to produce a 10 to 100 mK perturbation in the cosmic microwave background (CMB) spectrum
+\citep{2006PhR...433..181F, 2012RPPh...75h6901P}. The amplitude of this perturbation on a given line
+of sight is a function of the neutral fraction of hydrogen, the baryon overdensity, the spin
 temperature relative to the CMB temperature at the given redshift, and the line-of-sight peculiar
 velocity of the gas.  The spatial power spectrum of this perturbation is thought to be dominated by
-inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized
-bubbles during the EoR at $z\sim 7$ where a detection can constrain the ionizing efficiency of early
-galaxies, the UV photon mean-free-path, and the minimum halo mass that can support star formation
-\citep{2015MNRAS.449.4246G}.
-
-Current 21-cm cosmology experiments can be broadly separated into two classes: global signal
-experiments that aim to detect the spectral signature of the cosmologically redshifted 21-cm
-transition after averaging over the entire sky (otherwise known as the monopole), and power spectrum
+inhomogeneous heating of the intergalactic medium (IGM) at $z\sim 20$ \citep{2014MNRAS.437L..36F},
+and by growing ionized bubbles during the epoch of reionization (EoR) at $z\sim 7$, where a
+detection can constrain the ionizing efficiency of early galaxies, the UV photon mean-free path, and
+the minimum halo mass that can support star formation \citep{2015MNRAS.449.4246G}.
+
+Current 21~cm cosmology experiments can be broadly separated into two classes: global signal
+experiments that aim to detect the spectral signature of the cosmologically redshifted 21~cm
+transition after averaging over the entire sky (otherwise known as the monopole) and power spectrum
 experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
-of cosmological 21-cm perturbations.  Ongoing global signal experiments include EDGES
+of cosmological 21~cm perturbations.  Ongoing global signal experiments include EDGES
 \citep{2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS \citep{2015PASA...32....4S},
@@
 \citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}. Recently,
-EDGES reported the first detection of 21-cm absorption in the globally averaged sky-signal
+EDGES reported the first detection of 21~cm absorption in the globally averaged sky signal
 \citep{2018Natur.555...67B}.
@@
 Just as for CMB experiments, foreground removal or suppression is an essential component of both
-classes of 21-cm cosmology experiments. The brightness temperature of the galactic synchrotron
+classes of 21~cm cosmology experiments. The brightness temperature of the galactic synchrotron
 emission at high galactic latitudes is measured by \citet{2017MNRAS.464.4995M} as
@@
 \end{equation}
-Therefore, experiments conservatively need to achieve 5 orders of dynamic range against this
+Therefore, experiments conservatively need to achieve five orders of dynamic range against this
 foreground emission before the cosmological signal can be measured. Current foreground removal
@@
 
-Recently, a host of new low-frequency sky surveys have been conducted including MSSS
+Recently, a host of new low-frequency sky surveys have been conducted, including MSSS
 \citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
@@
 captures the diffuse emission with 5$^\circ$ resolution.  The LWA1 Low Frequency Sky Survey
-\citep{2017MNRAS.469.4537D} similarly maps the sky at a range of frequencies between 35~MHz and
-80~MHz with resolution between 4.5$^\circ$ and 2$^\circ$.
-
-The Global Sky Model (GSM) \citep{2008MNRAS.388..247D} is currently the most commonly used
-foreground model. The GSM is a non-parametric interpolation of various maps between 10 MHz and 100
-GHz. However, the majority of information contained in the GSM is derived at frequencies $>1.4$ GHz
-where the majority of the modern, high-fidelity input maps are located. At 408~MHz the venerable
+\citep[LLFSS;][]{2017MNRAS.469.4537D} similarly maps the sky at a range of frequencies between
+35 and 80~MHz with resolution between 4.5$^\circ$ and 2$^\circ$.
+
+The Global Sky Model \citep[GSM;][]{2008MNRAS.388..247D} is currently the most commonly used
+foreground model. The GSM is a nonparametric interpolation of various maps between 10 MHz and 100
+GHz. However, the majority of information contained in the GSM is derived at frequencies $>1.4$~GHz,
+where the majority of the modern, high-fidelity input maps are located. At 408~MHz, the venerable
 Haslam map \citep{1981A&A...100..209H, 1982A&AS...47....1H} covers the entire sky at $1^\circ$
-resolution.  Below 408~MHz the GSM uses 3 input sky maps. \citet{2017MNRAS.464.3486Z} construct an
-improved GSM with 5 maps below 408~MHz, and \citet{2017MNRAS.469.4537D} use the LWA1 to improve the
-GSM with their own sky maps.  However, the GSM generally suffers from low angular resolution ($\sim
-5^\circ$) and systematic errors associated with instrumental artifacts in the input maps.  For
-instance, \citet{2017MNRAS.469.4537D} report errors of $\pm 50\%$ between the GSM and their own maps
-at 74 MHz, which they attribute to the increasing contribution of free-free absorption and
-modifications to the synchrotron spectral index at low frequencies.
-
-Widefield interferometric synthesis imaging is a challenging computational problem, and it has been
+resolution.  Below 408~MHz, the GSM uses three input sky maps. \citet{2017MNRAS.464.3486Z}
+constructed an improved GSM with five maps below 408~MHz, and \citet{2017MNRAS.469.4537D} used the
+LWA1 to improve the GSM with their own sky maps.  However, the GSM generally suffers from low
+angular resolution ($\sim 5^\circ$) and systematic errors associated with instrumental artifacts in
+the input maps.  For instance, \citet{2017MNRAS.469.4537D} reported errors of $\pm 50\%$ between the
+GSM and their own maps at 74 MHz, which they attribute to the increasing contribution of free-free
+absorption and modifications to the synchrotron spectral index at low frequencies.
+
+Wide-field interferometric synthesis imaging is a challenging computational problem, and it has been
 particularly difficult to capture large angular scales $\gg 10^\circ$ and small angular scales $\ll
-1^\circ$ in a single synthesis image. We will derive a new imaging technique -- Tikhonov regularized
+1^\circ$ in a single synthesis image. We will derive a new imaging technique -- Tikhonov-regularized
 $m$-mode analysis imaging -- that allows a drift-scanning interferometer to image the entire visible
@@
 
-As a demonstration of this technique we apply Tikhonov regularized $m$-mode analysis imaging to the
-Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA), and generate a series of new
-low-frequency maps of the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky
-visible from the Owens Valley Radio Observatory (OVRO) with angular resolution of $\sim 15$~arcmin.
-These new maps complement the existing full-sky maps at these frequencies with greatly improved
-angular resolution.
-
-We aim for these maps to inform foreground removal strategies in 21-cm cosmology, and we anticipate
+As a demonstration of this technique, we apply Tikhonov-regularized $m$-mode analysis imaging to the
+Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) and generate a series of new
+low-frequency maps of the sky between 36.528 and 73.152~MHz.  These maps capture the full sky
+visible from OVRO with an angular resolution of $\sim 15$~arcmin.  These new maps complement the
+existing full-sky maps at these frequencies with greatly improved angular resolution.
+
+We aim for these maps to inform foreground removal strategies in 21~cm cosmology, and we anticipate
 additional ancillary science taking advantage of the combination of high fidelity and high
-resolution of these maps, including but not limited to studies of the cosmic ray emissivity at low
+resolution of these maps, including but not limited to studies of the cosmic-ray emissivity at low
 frequencies, searches for giant radio galaxies, and constraining the galactic synchrotron spectrum.
@@
 $m$-mode analysis imaging, a new imaging technique that allows us to image the entire visible sky in
-one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
-describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
-compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss some of
-the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present our
+one coherent synthesis imaging step with exact wide-field corrections. In \S\ref{sec:observations}
+we describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
+compare these maps against other low-frequency sky maps.  In \S\ref{sec:error}, we discuss some of
+the sources of error present in the maps, and finally, in \S\ref{sec:conclusion} we present our
 conclusions.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{All-Sky Imaging}\label{sec:imaging}
+\section{All-sky Imaging}\label{sec:imaging}
 
@@
 polarizations labeled $p$ and $q$ respectively. We will neglect subtleties associated with polarized
-imaging, so the Stokes-$I$ visibilities are constructed from the sum of the $pp$ and $qq$
+imaging, so the Stokes~$I$ visibilities are constructed from the sum of the $pp$ and $qq$
 correlations such that $V^{ij}_{\nu} = (V^{ij,pp}_{\nu}+V^{ij,qq}_{\nu})/2$.  If the antennas are
 separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes an antenna's response to the
-incident Stokes-$I$ radiation (here assumed to be the same for each antenna), then
+incident Stokes~$I$ radiation (here assumed to be the same for each antenna), then
 \begin{equation}\label{eq:basic-imaging}
@@
 \end{equation}
-where the integral runs over solid angle $\Omega$.  Constructing an image from the output of a radio
-interferometer consists of estimating $I_\nu(\hat r)$ given the available measurements $V^{ij}_\nu$.
-
-For later convenience we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
+where the integral runs over the solid angle $\Omega$.  Constructing an image from the output of a
+radio interferometer consists of estimating $I_\nu(\hat r)$ given the available measurements
+$V^{ij}_\nu$.
+
+For later convenience, we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
 \begin{equation}\label{eq:baseline-transfer-function}
@@
 \end{equation}
-The baseline transfer function defines the response of a single baseline to the sky, and is a
+The baseline transfer function defines the response of a single baseline to the sky and is a
 function of the antenna primary beam, and baseline length and orientation.
 
-Naively one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing, and subsequently
-solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
-baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations, then
-the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
-sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
-$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
-the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
-floating point number).  This matrix equation is therefore prohibitively large, and solving
-Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable, although
-\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.
+Naively, one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing and
+subsequently solving the resulting matrix equation. If the interferometer is composed of
+$N_\text{base}$ baselines and measures $N_\text{freq}$ frequency channels over $N_\text{time}$
+integrations, then the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex
+numbers. If the sky is discretized into $N_\text{pix}$ pixels, then the relevant matrix has
+dimensions of $(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making
+single-channel maps with the OVRO-LWA, this becomes a 5 PB array (assuming each matrix element
+is a 64 bit complex floating point number).  This matrix equation is therefore prohibitively large,
+and solving Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable,
+although \citet{2017MNRAS.465.2901Z} demonstrated this technique with the MITEOR telescope.
 
@@
 ease the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
-$\vec b_{ij}$ lie in a plane and the field-of-view is small, Equation~\ref{eq:basic-imaging} can be
-well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
-restriction on baseline co-planarity and field-of-view can be relaxed by using W-projection
+$\vec b_{ij}$ lie in a plane and the field of view is small, Equation~\ref{eq:basic-imaging} can be
+well approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
+restriction on baseline coplanarity and field of view can be relaxed by using W-projection
 \citep{2008ISTSP...2..647C}. Known primary beam effects can also be accounted for during imaging by
@@
 
-\subsection{$m$-Mode Analysis}\label{sec:mmode-analysis}
+\subsection{$m$-mode Analysis}\label{sec:mmode-analysis}
 
 Transit telescopes can take advantage of a symmetry in Equation~\ref{eq:basic-imaging} that greatly
-reduces the amount of computer time required to image the full-sky with exact incorporation of
-widefield imaging effects. This technique, called $m$-mode analysis, also obviates the need for
-gridding and mosaicking. Instead the entire sky is imaged in one coherent synthesis imaging step.  We
-will briefly summarize $m$-mode analysis below, but the interested reader should consult
+reduces the amount of computer time required to image the full sky with exact incorporation of
+wide-field imaging effects. This technique, called $m$-mode analysis, also obviates the need for
+gridding and mosaicking. Instead, the entire sky is imaged in one coherent synthesis imaging step.
+We will briefly summarize $m$-mode analysis below, but the interested reader should consult
 \citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete derivation.
@@
 response pattern of the individual elements does not change with respect to time. This may be an
-interferometer like the OVRO-LWA where the correlation elements are fixed dipoles, but it may also
+interferometer like the OVRO-LWA, where the correlation elements are fixed dipoles, but it may also
 be an interferometer like LOFAR or the MWA if the steerable beams are held in a fixed position (not
@@
 }
-Therefore it is a natural operation to compute the Fourier transform of the visibilities with
+Therefore, it is a natural operation to compute the Fourier transform of the visibilities with
 respect to sidereal time $\phi\in[0,2\pi)$.
@@
 $m=0,\,\pm1,\,\pm2,\,\ldots$ is the Fourier conjugate variable to the sidereal time. The $m$-mode
-corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly $m=1$
+corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly, $m=1$
 corresponds to the component of the visibilities that varies over half-day timescales. Larger values
@@
 
-\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} show that there is a discrete linear relationship
+\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} showed that there is a discrete linear relationship
 between the measured $m$-modes $V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky
@@
 
-Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation where the transfer
-matrix $\b B$ is block-diagonal.
+Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation, where the transfer
+matrix $\b B$ is block-diagonal:
 \begin{equation}\label{eq:m-mode-matrix-equation}
@@
 The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
-\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that a baseline with
+\citet{2016ApJ...826..116V} proveed -- under fairly general assumptions -- that a baseline with
 nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
-fact the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
+fact, the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
 baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
-case the antennas are so close together that voltage fluctuations in one antenna can couple into the
+case, the antennas are so close together that voltage fluctuations in one antenna can couple into the
 other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
-measured and calibrated. Consequently, we set $a_{00}=0$ in our analysis. In the future this
+measured and calibrated. Consequently, we set $a_{00}=0$ in our analysis. In the future, this
 limitation will be addressed with the inclusion of calibrated total power radiometry.
@@
 $(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
-64-bit complex floating point number, a single block is 500 MB for the case of single-channel
+64 bit complex floating point number, a single block is 500 MB for the case of single-channel
 imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.
-However, with additional bandwidth these blocks quickly become unwieldy; thus as a first pass, the
-analysis in this paper is restricted to single-channel imaging. Note also that for the OVRO-LWA
+However, with additional bandwidth, these blocks quickly become unwieldy; thus, as a first pass, the
+analysis in this paper is restricted to single-channel imaging. Note also that for the OVRO-LWA,
 $N_\text{base} \gg l_\text{max}$, so there are more measurements than unknowns in
@@
 Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
-operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the linear
-size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
-point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$,
-because each block can be manipulated independently of the other blocks.  This computational savings
-is what makes this matrix algebra approach to interferometric imaging feasible. For the dataset
-presented in this paper, computing the elements of the transfer matrix takes $\sim$10 hours per
-frequency channel on a 10-node cluster, but once the matrix has been computed the imaging process
-described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the deconvolution process
-described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.
-
-\subsection{$m$-Mode Analysis Imaging}\label{sec:mmode-imaging}
+operations (e.g., solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the
+linear size of the matrix.  By splitting the equation into $M$ independent blocks, the number of
+floating point operations required to solve the linear system of equations is now
+$\mathcal{O}(N^3M^{-2})$, because each block can be manipulated independently of the other blocks.
+This computational savings is what makes this matrix algebra approach to interferometric imaging
+feasible. For the data set presented in this paper, computing the elements of the transfer matrix
+takes $\sim$10 hours per frequency channel on a 10-node cluster, but once the matrix has been
+computed, the imaging process described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the
+deconvolution process described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.
+
+\subsection{$m$-mode Analysis Imaging}\label{sec:mmode-imaging}
 
@@
 Equation~\ref{eq:m-mode-matrix-equation} to solve for the spherical harmonic coefficients $\b a$.
-The linear-least squares solution, which minimizes $\|\b v - \b B\b a\|^2$, is given by
+The linear least-squares solution, which minimizes $\|\b v - \b B\b a\|^2$, is given by
 \begin{equation}
@@
 
-However, usually one will find that $\b B$ is not full-rank, and hence $\b B^*\b B$ is not an
+However, usually one will find that $\b B$ is not full rank, and hence $\b B^*\b B$ is not an
 invertible matrix. For example, an interferometer located in the northern hemisphere will never see
@@
 
-In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
-purposes we will assume that $\b N=n\b I$ for some $n>0$. In this case, the covariance of the
+In practice, the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
+purposes, we will assume that $\b N=n\b I$ for some $n>0$. In this case, the covariance of the
 Tikhonov-regularized spherical harmonic coefficients is
@@
 the covariance of the measured spherical harmonic coefficients. Tikhonov regularization improves
-this situation by downweighting these components.
-
-\subsubsection{L-Curves}
+this situation by down-weighting these components.
+
+\subsubsection{L Curves}
 
@@
     \caption{
-        An example L-curve computed from OVRO-LWA data at 36.528~MHz by trialing 200 different
-        values of the regularization parameter $\varepsilon$. The $x$-axis is the norm of the
-        solution (in this case the spherical harmonic coefficients) given in arbitrary units, and
-        the $y$-axis is the least-squares norm given in arbitrary units. Where the regularization
-        parameter is small, the norm of the solution grows rapidly. Where the regularization
-        parameter is large, the least-squares norm grows rapidly.
+        Example L curve computed from OVRO-LWA data at 36.528~MHz by trialing 200 different values
+        of the regularization parameter $\varepsilon$. The $x$-axis is the norm of the solution (in
+        this case, the spherical harmonic coefficients) given in arbitrary units, and the $y$-axis
+        is the least-squares norm given in arbitrary units. Where the regularization parameter is
+        small, the norm of the solution grows rapidly. Where the regularization parameter is large,
+        the least-squares norm grows rapidly.
     }
@@
 Tikhonov regularization requires the observer to pick the value of $\varepsilon$. If $\varepsilon$
-is too large then too much importance is placed on minimizing the norm of the solution and the
-least-squares residuals will suffer. Conversely, if $\varepsilon$ is too small then the problem will
-be poorly regularized and the resulting sky map may not represent the true sky. Picking the value of
-$\varepsilon$ therefore requires understanding the trade-off between the two norms.
+is too large, then too much importance is placed on minimizing the norm of the solution and the
+least-squares residuals will suffer. Conversely, if $\varepsilon$ is too small, then the problem
+will be poorly regularized and the resulting sky map may not represent the true sky. Picking the
+value of $\varepsilon$ therefore requires understanding the trade-off between the two norms.
 
@@
 computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in
-Figure~\ref{fig:lcurve}. The shape of this curve has a characteristic L-shape, and as a result this
-type of plot is called an L-curve. The ideal value of $\varepsilon$ lies near the turning point of
+Figure~\ref{fig:lcurve}. The shape of this curve has a characteristic L shape, and as a result, this
+type of plot is called an L curve. The ideal value of $\varepsilon$ lies near the turning point, of
 the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired rapid increase
@@
 
-In practice, the L-curve should be used as a guide to estimate a reasonable value of $\varepsilon$.
-However better results can often be obtained by tuning the value of $\varepsilon$. For instance,
+In practice, the L curve should be used as a guide to estimate a reasonable value of $\varepsilon$.
+However, better results can often be obtained by tuning the value of $\varepsilon$. For instance,
 increasing the value of $\varepsilon$ can improve the noise properties of the map by down-weighting
@@
 up-weighting the contribution of longer baselines, which are likely fewer in number. In this
-respect, choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in
+respect, choosing the value of $\varepsilon$ is analogous to picking the weighting scheme in
 traditional imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.
-For the OVRO-LWA we selected $\varepsilon = 0.01$ across all frequency channels. The distribution of
-singular values of the transfer matrix with respect to $\sqrt{\varepsilon}$ is summarized in
+For the OVRO-LWA, we selected $\varepsilon = 0.01$ across all frequency channels. The distribution
+of singular values of the transfer matrix with respect to $\sqrt{\varepsilon}$ is summarized in
 Table~\ref{tab:summary}.
@@
 
-The Moore-Penrose pseudoinverse (denoted with a superscript $\dagger$), is commonly applied to find
-the minimum-norm linear-least squares solution to a set of linear equations. This can be used in
+The Moore--Penrose pseudo-inverse (denoted with a superscript $\dagger$) is commonly applied to find
+the minimum-norm linear least-squares solution to a set of linear equations. This can be used in
 place of Tikhonov regularization as
@@
 \end{equation}
-Much like Tikhonov regularization, the Moore-Penrose pseudoinverse sets components with small
+Much like Tikhonov regularization, the Moore--Penrose pseudo-inverse sets components with small
 singular values (below some user-defined threshold) to zero. Components with large singular values
 (above the user-defined threshold) are included in the calculation at their full amplitude with no
-down-weighting of modes near the threshold. The essential difference between using the Moore-Penrose
-pseudoinverse and Tikhonov regularization is that the pseudoinverse defines a hard transition from
-``on'' to ``off''. Modes are either set to zero or included in the map at their full amplitude. On
-the other hand, Tikhonov regularization smoothly interpolates between these behaviors. Because of
-this, Tikhonov regularization tends to produce better results in practical applications.
-
-If the measured $m$-modes have a noise covariance matrix $\b N \neq n\b I$ for some scalar $n$ (eg.
-the interferometer is inhomogeneous), then the observer should minimize $(\b v-\b B\b a)^*\b
+down-weighting of modes near the threshold. The essential difference between using the
+Moore--Penrose pseudo-inverse and Tikhonov regularization is that the pseudo-inverse defines a hard
+transition from ``on'' to ``off.'' Modes are either set to zero or included in the map at their full
+amplitude. On the other hand, Tikhonov regularization smoothly interpolates between these behaviors.
+Because of this, Tikhonov regularization tends to produce better results in practical applications.
+
+If the measured $m$-modes have a noise covariance matrix $\b N \neq n\b I$ for some scalar $n$
+(e.g., the interferometer is inhomogeneous), then the observer should minimize $(\b v-\b B\b a)^*\b
 N^{-1}(\b v-\b B\b a) + \varepsilon\|\b a\|^2$. The noise covariance matrix $\b N$ is used to weight
@@
 In the event that the observer has a prior map of the sky, $\|\b a - \b a_\text{prior}\|^2$ can be
-used as the regularizing norm. This will use the prior map to fill-in missing information instead of
+used as the regularizing norm. This will use the prior map to fill in missing information instead of
 setting these modes to zero. In this case, the minimum is at
@@
 the gradient of the sky brightness in the direction $\hat r$. This is actually a generalization of
-Tikhonov regularization where the objective function is $\|\b v-\b B\b a\|^2 + \varepsilon\|\b A\b
+Tikhonov regularization, where the objective function is $\|\b v-\b B\b a\|^2 + \varepsilon\|\b A\b
 a\|^2$ for some matrix $\b A$. The minimum is at
@@
 
-Finally, in many machine learning applications the $L_1$-norm\footnote{
+Finally, in many machine-learning applications the $L_1$-norm\footnote{
     $\|\b a\|_1 = \sum_i |a_i|$
@@
 harmonics, the vector $\b a$ is not expected to be sparse. Consequently, the $L_1$-norm is generally
-inappropriate for $m$-mode analysis imaging without an additional change-of-variables designed to
+inappropriate for $m$-mode analysis imaging without an additional change of variables designed to
 introduce sparsity.
@@
 In traditional radio astronomy imaging, CLEAN \citep{1974A&AS...15..417H} is a physically motivated
-algorithm that interpolates between measured visibilities on the $uv$-plane. In the absence of this
-interpolation, gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the
+algorithm that interpolates between measured visibilities on the $uv$ plane. In the absence of this
+interpolation, gaps in the interferometer's $uv$ coverage are assumed to be zero, and -- in the
 image plane -- sources are convolved with a point spread function (PSF) that is characteristic of
-the $uv$-coverage.  Fundamentally, the interferometer's PSF is determined by which modes were
+the $uv$ coverage.  Fundamentally, the interferometer's PSF is determined by which modes were
 assumed to be zero in the initial imaging process.
 
-In $m$-mode analysis imaging, we assumed modes were zero in two separate ways:
+In $m$-mode analysis imaging, we assumed modes were zero in two separate ways.
 \begin{enumerate}
-    \item We selected a set of spherical harmonic coefficients $a_{lm}$ to describe the sky
-        brightness distribution. All modes with $l>l_\text{max}$ are neglected and assumed to be
+    \item We selected a set of spherical harmonic coefficients $a_{lm}$ to describe the
+        sky-brightness distribution. All modes with $l>l_\text{max}$ are neglected and assumed to be
         zero.
     \item Tikhonov regularization forces linear combinations of spherical harmonic coefficients with
-        $\sigma_i \lesssim \sqrt{\varepsilon}$ towards zero.
+        $\sigma_i \lesssim \sqrt{\varepsilon}$ toward zero.
 \end{enumerate}
@@
 variety of baselines, which increases the number of modes for which $\sigma_i \gg
-\sqrt{\varepsilon}$.  Alternatively, by collecting more data, the signal-noise ratio of the measured
-$m$-modes increases, which allows the observer to lower the value of $\varepsilon$ without
+\sqrt{\varepsilon}$.  Alternatively, by collecting more data, the signal-to-noise ratio of the
+measured $m$-modes increases, which allows the observer to lower the value of $\varepsilon$ without
 increasing the noise in the maps.  Finally, the CLEAN algorithm can be applied to interpolate some
@@
 will have the same PSF. The PSF is therefore only a function of the declination. For example,
-sources at low elevations will tend to have an extended PSF along the north-south axis due to
+sources at low elevations will tend to have an extended PSF along the north--south axis due to
 baseline foreshortening. For the OVRO-LWA antenna configuration (Figure~\ref{fig:antenna-layout}),
 example PSFs at three separate frequencies are shown in Figure~\ref{fig:psf}.  Adapting CLEAN for
-$m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of declinations, or
+$m$-mode analysis requires either precomputing Equation~\ref{eq:psf} at a grid of declinations, or
 a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.
 
-For an interferometer with more baselines than spherical harmonics used in the maps (eg. the
-OVRO-LWA), $\b B^*\b B$ can be a much smaller matrix than the full transfer matrix $\b B$. Therefore
-pre-computing $\b B^*\b B$ can allow the entire matrix to fit into memory on a single machine. This
-greatly reduces the amount of disk I/O necessary for solving Equation~\ref{eq:psf}.
-
-Additionally, we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
-U^*\b U$, where $\b U$ is an upper-triangular matrix. Inverting an upper triangular matrix is an
+For an interferometer with more baselines than spherical harmonics used in the maps (e.g., the
+OVRO-LWA), $\b B^*\b B$ can be a much smaller matrix than the full transfer matrix $\b B$.
+Therefore, precomputing $\b B^*\b B$ can allow the entire matrix to fit into memory on a single
+machine. This greatly reduces the amount of disk I/O necessary for solving Equation~\ref{eq:psf}.
+
+Additionally, we can precompute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
+U^*\b U$, where $\b U$ is an upper triangular matrix. Inverting an upper triangular matrix is an
 $\mathcal{O}(N^2)$ operation (instead of $\mathcal{O}(N^3)$ for a general matrix inverse).\footnote{
@@
 }
-Equation~\ref{eq:psf} can then be rapidly evaluated from right to left as:
+Equation~\ref{eq:psf} can then be rapidly evaluated from right to left as
 \begin{equation}\label{eq:rapid-psf}
@@
 Furthermore, Equation~\ref{eq:rapid-psf} does not need to be separately evaluated for each CLEAN
-component. Instead we can identify $N$ CLEAN components, accumulate $\b a_\text{PS}$ for each
+component. Instead, we can identify $N$ CLEAN components, accumulate $\b a_\text{PS}$ for each
 component, and evaluate Equation~\ref{eq:rapid-psf} on the accumulation. This can greatly reduce the
@@
 
-Altogether the adaptation of CLEAN applied to the maps presented in this paper is summarized below.
+Altogether, the adaptation of CLEAN applied to the maps presented in this paper is summarized below.
 \begin{algorithmic}[1]
@@
 
-In summary, Tikhonov-regularized $m$-mode analysis imaging constructs a widefield synthesis image of
-the sky from a complete earth rotation, and  with exact treatment of widefield-effects. This is
+In summary, Tikhonov-regularized $m$-mode analysis imaging constructs a wide-field synthesis image of
+the sky from a complete Earth rotation, and  with exact treatment of wide-field effects. This is
 accomplished by solving a regularized block-diagonal matrix equation
@@
 
-\subsection{The Owens Valley Radio Observatory Long Wavelength Array}
+\subsection{The OVRO-LWA}
 
@@
         to increase the longest baseline to $\sim1.5$ km. The red dots are core antennas that are
-        disconnected from the correlator in order to accommodate these antennas. The 5 crosses are
-        antennas equipped with noise-switched front ends.
+        disconnected from the correlator in order to accommodate these antennas. The five crosses
+        are antennas equipped with noise-switched front ends.
     }
@@
 
-The Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) is a 288-element interferometer
-located at the Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The
-OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27~MHz to 85~MHz and
-with 24~kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
-there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
-correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
-hemisphere in a single snapshot image.
+The OVRO-LWA is a 288-element interferometer located at OVRO near Big Pine, California
+\citep{hallinan_2017}.  The OVRO-LWA is a low-frequency instrument with instantaneous bandwidth
+covering 27 to 85~MHz and with 24~kHz channelization.  Each antenna stand hosts two perpendicular
+broadband dipoles so that there are $288\times2$ signal paths in total. These signal paths feed into
+the 512-input LEDA correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the
+entire visible hemisphere in a single snapshot image.
 
 The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
-snapshot imaging (see Figure~\ref{fig:antenna-layout}).  Of these 288 antennas, 251 are contained
-within a 200 m diameter core, 32 are placed outside of the core in order to extend the maximum
-baseline length to $\sim$1.5~km, and the final 5 antennas are equipped with noise-switched front
-ends for calibrated total power measurements of the global sky brightness.  These antennas are used
-as part of the LEDA experiment \citep{2017arXiv170909313P} to measure the global signal of 21-cm
-absorption from the cosmic dawn. In the current configuration, 32 antennas (64 signal paths) from
-the core are disconnected from the correlator in order to accommodate the 32 antennas on longer
-baselines. A final stage of construction will involve 64 additional antennas installed on long
-baselines out to a maximum length of 2.6~km.
-
-The dataset used in this paper spans 28 consecutive hours beginning at 2017-02-17 12:00:00 UTC time.
-During this time the OVRO-LWA operated as a zenith-pointing drift scanning interferometer.  The
-correlator dump time was selected to be 13 seconds such that the correlator output evenly divides a
+snapshot imaging (see Figure~\ref{fig:antenna-layout}).  Of these 288 antennas, 251~are contained
+within a 200~m diameter core, 32~are placed outside of the core in order to extend the maximum
+baseline length to $\sim$1.5~km, and five are equipped with noise-switched front ends for calibrated
+total power measurements of the global sky brightness.  These antennas are used as part of the LEDA
+experiment \citep{2017arXiv170909313P} to measure the global signal of 21~cm absorption from the
+cosmic dawn. In the current configuration, 32 antennas (64 signal paths) from the core are
+disconnected from the correlator in order to accommodate the 32 antennas on longer baselines. A
+final stage of construction will involve 64 additional antennas installed on long baselines out to a
+maximum length of 2.6~km.
+
+The data set used in this paper spans 28 consecutive hours beginning at 2017 February 17 12:00:00 UTC
+time.  During this time, the OVRO-LWA operated as a zenith-pointing drift-scanning interferometer.
+The correlator dump time was selected to be 13~s such that the correlator output evenly divides a
 sidereal day. Due to the computational considerations presented in \S\ref{sec:mmode-analysis}, eight
-24~kHz channels are selected for imaging from this dataset: 36.528~MHz, 41.760~MHz, 46.992~MHz,
-52.224~MHz, 57.456~MHz, 62.688~MHz, 67.920~MHz, and 73.152~MHz.  These particular channels are
-chosen due to their location at the exact center of instrumental subbands.
+24~kHz channels are selected for imaging from this data set: 36.528, 41.760, 46.992, 52.224, 57.456,
+62.688, 67.920, and 73.152~MHz.  These particular channels are chosen due to their location at the
+exact center of instrumental subbands.
 
@@
 The complex gain calibration is responsible for correcting per-antenna amplitude and phase errors.
-This is accomplished using a sky model and a variant of alternating least squares colloquially known
+This is accomplished using a sky model and a variant of alternating least-squares colloquially known
 as ``Stefcal''
@@
 the interferometer's gain calibration is when these sources are at high elevations.  The antenna
-complex gains are measured from a 22 minute track of data when Cyg~A and Cas~A are at high
-elevations. The gains measured in this way are then used to calibrate the entire 28 hour dataset.
+complex gains are measured from a 22~minute track of data when Cyg~A and Cas~A are at high
+elevations. The gains measured in this way are then used to calibrate the entire 28 hour data set.
 The calibration sky model consists only of Cyg~A and Cas~A. The model flux of Cyg~A is set to the
-\citet{1977A&A....61...99B} spectrum while the flux of Cas~A is measured from the data itself (using
+\citet{1977A&A....61...99B} spectrum, while the flux of Cas~A is measured from the data itself (using
 a preliminary calibration solved for with a fiducial Cas~A spectrum).
 
-Calibrating in this manner generates $\sim$ arcminute errors in the astrometry of the final sky maps
-due to ionospheric refractive offsets during the time of calibration.  These residual errors in the
-astrometry are corrected post-imaging by registering the images with respect to all VLSSr
-\citep{2014MNRAS.440..327L} sources that are bright ($>30$~Jy with a consistent flux density
-measured with the OVRO-LWA), and not too close to other bright sources (at least $1^\circ$
-separation).
+Calibrating in this manner generates approximately arcminute errors in the astrometry of the final
+sky maps due to ionospheric refractive offsets during the time of calibration.  These residual
+errors in the astrometry are corrected post-imaging by registering the images with respect to all
+Very Large Array Low-frequency Sky Survey Redux (VLSSr) \citep{2014MNRAS.440..327L} sources that are
+bright ($>30$~Jy with a consistent flux density measured with the OVRO-LWA) and not too close to
+other bright sources (at least $1^\circ$ separation).
 
 Temperature fluctuations of the analog electronics generate 0.1~dB sawtooth oscillations in the
-analog gain. These oscillations occur with a variable 15 to 17 minute period associated with HVAC
+analog gain. These oscillations occur with a variable 15 to 17~minute period associated with HVAC
 cooling cycles within the electronics shelter that houses these electronics.  The amplitude of these
-gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
-The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
+gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45~minute timescales.
+The ratio of the measured autocorrelation power to the smoothed autocorrelation power defines a
 per-antenna amplitude correction that is then applied to the cross-correlations.  Additionally, the
@@
     \caption{
-        Empirical fits to the OVRO-LWA Stokes-I primary beam (the response of the $x$- and
-        $y$-dipoles has been summed) at three frequencies: 36.528 MHz (left panel), 52.224 MHz
+        Empirical fits to the OVRO-LWA Stokes $I$ primary beam (the response of the $x$ and
+        $y$ dipoles has been summed) at three frequencies: 36.528 MHz (left panel), 52.224 MHz
         (middle panel), and 73.152 MHz (right panel). The source tracks used to measure the beam
@@
 is unknown. In this work, we assume symmetries that are apparent in the antenna design, but
-real-world defects and coupling with nearby antennas will contribute towards breaking these
-symmetries at some level. In particular we assume that the $x$- and $y$-dipoles have the same
-response to the sky after rotating one by 90$^\circ$, and that the beam is invariant under
-north-south and east-west flips.
+real-world defects and coupling with nearby antennas will contribute toward breaking these
+symmetries at some level. In particular, we assume that the $x$ and $y$ dipoles have the same
+response to the sky after rotating one by $90^\circ$, and that the beam is invariant under
+north--south and east--west flips.
 
 We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A, 3C~123, and
-3C~353) as they pass through the sky, and then fit a beam model composed of Zernike polynomials to
+3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
 those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
-$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$) and the beam amplitude
+$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$), and the beam amplitude
 at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
@@
     \caption{
-        The median vertical TEC within 200 km of OVRO during the time of the observation. The gray
+        Median vertical TEC within 200 km of OVRO during the time of the observation. The gray
         shaded regions indicate times outside of the observing period. The gray vertical lines
@@
     The Dst index was obtained from the World Data Center for Geomagnetism, Kyoto University
-    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}). Accessed 2017-07-25.
+    (\url{http://swdcwww.kugi.kyoto-u.ac.jp/}). Accessed 2017 July 25.
 }
@@
 
-Despite the mild conditions, low frequency interferometric observations are still affected by the
+Despite the mild conditions, low-frequency interferometric observations are still affected by the
 index of refraction in the ionosphere.  Figure~\ref{fig:vtec} shows the median vertical total
@@
 TEC smoothly varies from 20 TECU at midday to 5 TECU during the night. However, this measurement is
-only sensitive to large scale fluctuations in the ionosphere and does not capture small scale
+only sensitive to large-scale fluctuations in the ionosphere and does not capture small-scale
 fluctuations.
 
-Small scale fluctuations are best characterized by source scintillation and refractive offsets.
+Small-scale fluctuations are best characterized by source scintillation and refractive offsets.
 Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
 function of time over the entire observing period. Both sources exhibit rapid scintillation on the
-timescale of a single integration (13 seconds). For example, at 36.528 MHz, it is not unusual for
+timescale of a single integration (13~s). For example, at 36.528~MHz, it is not unusual for
 Cyg A to have measured flux variations of 50\% between adjacent 13 second integrations.  The
@@
 $\nu^{-2}$ origin. The measured position offset of each source is a measurement of the ionospheric
-phase gradient across the array.  This varies on slower 10 minute timescales, with each source
-refracting by as much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves
+phase gradient across the array.  This varies on slower 10~minute timescales, with each source
+refracting by as much as 20\arcmin (at 36.528 MHz) from its true astronomical position as waves
 in the ionosphere pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K}
-observe $\sim 1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the
-day on similar $\sim10$ minute timescales, which is consistent with what is seen here.  The impact
+observed $\sim 1\arcmin$ refractive offsets during the night, and $\sim 4\arcmin$ offsets during the
+day on similar $\sim10$~minute timescales, which is consistent with what is seen here.  The impact
 of these effects on the sky maps is simulated in \S\ref{sec:ionosphere}.
@@
 
-\subsubsection{Cygnus A and Cassiopeia A}
+\subsubsection{Cyg A and Cas A}
 
@@
 sources from the data, sidelobes from these sources will dominate the variance in the sky maps.  At
-74~MHz Cyg~A is a 15,000~Jy source \citep{1977A&A....61...99B}. A conservative estimate for the
-confusion limit at 74 MHz with a 15~arcmin beam is 1000~mJy \citep{2014MNRAS.440..327L}. Therefore,
+74~MHz, Cyg~A is a 15,000~Jy source \citep{1977A&A....61...99B}. A conservative estimate for the
+confusion limit at 74~MHz with a 15\arcmin beam is 1000~mJy \citep{2014MNRAS.440..327L}. Therefore,
 we require that Cyg~A's sidelobes be at least $-45$~dB down from the main lobe to prevent Cyg~A's
@@
 fluctuations within the ionosphere contribute amplitude and phase scintillations that can be
-described by a direction-dependent complex-gain calibration. This justifies the use of ``peeling'',
+described by a direction-dependent complex gain calibration. This justifies the use of ``peeling,''
 which incorporates a direction-dependent calibration to subtract sources in the presence of
-ionospheric scintillation.  \citep[eg.][]{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.
+ionospheric scintillation \citep[e.g.,][]{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.
 
@@
 can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.  Attempting to
-peel a source in the strong scattering regime will lead to source subtraction artifacts in the final
+peel a source in the strong scattering regime will lead to source-subtraction artifacts in the final
 sky map.  \citet{2016RaSc...51..927M} measured that from the location of LOFAR at 150 MHz, the
@@
 diffractive scale is typically $>2$ km, and at 36 MHz, the diffractive scale is typically $>1$ km.
-These limits are comparable to the Fresnel scale for the OVRO-LWA (ie. $r_\text{diff} >
+These limits are comparable to the Fresnel scale for the OVRO-LWA (i.e., $r_\text{diff} >
 r_\text{f}$), and therefore we do not generally expect to see strong scattering from the ionosphere.
@@
 \S\ref{sec:ionosphere-conditions}). However, we do observe scintillation and refractive-offset
-events on the timescale of a single integration (13 seconds, see Figure~\ref{fig:scintillation}).
-Consequently we peeled Cyg~A and Cas~A from the dataset using a new solution for each integration.
-
-In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale of
-Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at 73~MHz, the
+events on the timescale of a single integration (13~s; see Figure~\ref{fig:scintillation}).
+Consequently, we peeled Cyg~A and Cas~A from the data set using a new solution for each integration.
+
+In addition, the largest angular scale of Cas~A is $\sim8\arcmin$, and the largest angular scale of
+Cyg~A is $\sim2\arcmin$. With an $\sim10\arcmin$ resolution on its longest baselines at 73~MHz, the
 OVRO-LWA marginally resolves both sources. A resolved source model is needed for both sources. We
@@
 integrations before imaging (at least 1 hour), it is possible to smear out the contribution of the
-rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx) \citep{nlopt, sbplx}
+rest of the sky.  We then use a nonlinear optimization routine \citep[NLopt Sbplx;][]{sbplx, nlopt}
 to vary the parameters in a source model until the variance within the aperture is minimized. Cyg~A
-is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian components.
-Ultimately, these multi-component models are used to peel Cyg~A and Cas~A, but residual errors from
+is modeled with two Gaussian components, while Cas~A is modeled with three Gaussian components.
+Ultimately, these multicomponent models are used to peel Cyg~A and Cas~A, but residual errors from
 this model and from the ionosphere (particularly while these sources are at low elevations)
@@
 subtracted from the visibilities using the updated position and flux of the source. The brightest of
-these sources (Vir~A and Tau~A) are peeled using a direction dependent calibration when they are at
+these sources (Vir~A and Tau~A) are peeled using a direction-dependent calibration when they are at
 high elevations.
@@
 collected at night. A map of the entire sky can be obtained by using observations spaced 6 months
-apart.  However the dataset used in this paper consists of 28 consecutive hours. Fortunately the Sun
-was not active during this period, which could have greatly increased the difficulty involved in
+apart.  However, the data set used in this paper consists of 28 consecutive hours. Fortunately, the
+Sun was not active during this period, which could have greatly increased the difficulty involved in
 subtracting the Sun.
 
-We attempt to subtract the Sun from the dataset with the goal of suppressing its sidelobes.  The Sun
-is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact, the optical
-depth $\tau=1$ surface of the Sun changes with frequency, and as a consequence a new model is needed
+We attempt to subtract the Sun from the data set with the goal of suppressing its sidelobes.  The Sun
+is well-resolved by the OVRO-LWA, and hence a detailed source model is needed. In fact, the optical
+depth $\tau=1$ surface of the Sun changes with frequency, and as a consequence, a new model is needed
 at each frequency. While we could fit a limited number of Gaussian components to Cyg~A and Cas~A,
@@
 The strategy used for removing the Sun below 55 MHz involves fitting a shapelet
-\citep{2003MNRAS.338...35R} model to the Sun and subtracting without the use of direction dependent
-gains. The shapelet fitting is performed in the visibility space. Above 55 MHz a model is fit to the
-Sun by minimizing the residuals after peeling (in the same way that models are obtained for Cyg~A
-and Cas~A). The Sun is then peeled from each integration using direction dependent gains.
+\citep{2003MNRAS.338...35R} model to the Sun and subtracting without the use of direction-dependent
+gains. The shapelet fitting is performed in the visibility space. Above 55~MHz, a model is fit to
+the Sun by minimizing the residuals after peeling (in the same way that models are obtained for
+Cyg~A and Cas~A). The Sun is then peeled from each integration using direction-dependent gains.
 
@@
         \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line below 50 MHz),
-        \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
-        Cas~A is compared against a spectrum assuming a secular decrease of 0.77\% per year
+        \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B} (dot-dashed
+        line).  Cas~A is compared against a spectrum assuming a secular decrease of 0.77\% per year
         \citep{2009AJ....138..838H}.
@@
 literature and \citet{2017ApJS..230....7P} (hereafter PB17) using the VLA has expanded the number of
-low-frequency radio sources with calibrated flux measurements from one (Cyg~A) to eleven in total.
-While the SH12 flux scale is valid between 30 MHz and 300 MHz, the PB17 flux scale is somewhat more
-limited because the lowest frequency observations come from the VLA 4-band system. As a consequence,
+low-frequency radio sources with calibrated flux measurements from one (Cyg~A) to 11 in total.
+While the SH12 flux scale is valid between 30 and 300~MHz, the PB17 flux scale is somewhat more
+limited because the lowest-frequency observations come from the VLA 4-band system. As a consequence,
 the PB17 flux scale is not valid below 50 MHz.
@@
 Figure~\ref{fig:flux-scale} shows a comparison between flux measurements made using the all-sky maps
-from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
-measurements agree to between 5 and 10\% of the SH12 spectra. Below 50 MHz there can be substantial
-departures with respect to the extrapolated PB17 spectra (for eg.  3C 286, 3C 295, and 3C 380), but
+from this work and spectra from the aforementioned flux scales. Generally, the OVRO-LWA flux
+measurements agree to between 5\% and 10\% of the SH12 spectra. Below 50 MHz, there can be substantial
+departures with respect to the extrapolated PB17 spectra (e.g.,  3C 286, 3C 295, and 3C 380), but
 it is usually the case that we have much better agreement with the SH12 spectra. This indicates that
@@
         OVRO-LWA.  Each map covers the sky north of $\delta=-30^\circ$ with angular resolution of
-        $\sim15$ arcmin. Eight bright sources have been removed from each map (Cyg~A, Cas~A, Vir~A,
+        $\sim15\arcmin$. Eight bright sources have been removed from each map (Cyg~A, Cas~A, Vir~A,
         Tau~A, Her~A, Hya~A, 3C~123, and 3C~353). The small blank region near $l=+45.7^\circ$,
@@
         52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
-        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
+        combining, and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
         Therefore, regions with a spectral index of $-2.5$ will tend to appear white, and regions
@@
     \caption{
-        A cutout of the galactic plane from Figure~\ref{fig:three-color}.
+        Cutout of the galactic plane from Figure~\ref{fig:three-color}.
     }
@@
     \caption{
-        The local spectral index measured between the 36.528~MHz map and the 73.152~MHz map
-        estimated by means of a local T-T plot. The color scale gives the spectral index where blue
-        is flat spectrum and red is steep spectrum. The contours give the
-        coefficient-of-determination ($R^2$) for the linear fit to the local T-T plot. If $R^2$ is
-        low, the quality of the fit is low and the estimated spectral index is unreliable. This can
-        be either due to insufficient dynamic range in the local T-T plot or due to multiple
-        emission mechanisms operating in close proximity. Consequently $R^2$ tends to drop at higher
-        galactic latitudes (due to dynamic range), and near \ion{H}{2} regions in the galactic
-        plane (due to multiple emission mechanisms).
+        Local spectral index measured between the 36.528~MHz map and the 73.152~MHz map estimated by
+        means of a local T--T plot. The color scale gives the spectral index, where blue is flat
+        spectrum and red is steep spectrum. The contours give the coefficient of determination
+        ($R^2$) for the linear fit to the local T--T plot. If $R^2$ is low, the quality of the fit
+        is low, and the estimated spectral index is unreliable. This can be due to either
+        insufficient dynamic range in the local T--T plot or multiple emission mechanisms operating
+        in close proximity. Consequently, $R^2$ tends to drop at higher galactic latitudes (due to
+        dynamic range) and near \ion{H}{2} regions in the galactic plane (due to multiple emission
+        mechanisms).
     }
@@
     \caption{
-        The local spectral index measured between the 73.152~MHz OVRO-LWA map and the reprocessed
-        408~MHz Haslam map \citep{2015MNRAS.451.4311R}.  The color scale gives the spectral index
-        where blue is flat spectrum and red is steep spectrum. The contours give the
-        coefficient-of-determination ($R^2$) for the linear fit to the local T-T plot. See the
-        caption of Figure~\ref{fig:internal-spectral-index} for more details about the
-        coefficient-of-determination..
+        Local spectral index measured between the 73.152~MHz OVRO-LWA map and the reprocessed
+        408~MHz Haslam map \citep{2015MNRAS.451.4311R}.  The color scale gives the spectral index,
+        where blue is flat spectrum and red is steep spectrum. The contours give the coefficient of
+        determination ($R^2$) for the linear fit to the local T--T plot. See the caption of
+        Figure~\ref{fig:internal-spectral-index} for more details about the coefficient of
+        determination.
     }
@@
         & \multicolumn3c{\tbf{FWHM}\footnote{
-            The full-width half-maximum (FWHM) of the synthesized beam at the specified declination
+            The full width at half maximum (FWHM) of the synthesized beam at the specified declination
             (major axis $\times$ minor axis).
@@
         && \multicolumn2c{\tbf{Noise}\footnote{
-            Measured with a jackknife and splitting the dataset into even- and odd-numbered
+            Measured with a jackknife and splitting the data set into even- and odd-numbered
             integrations. This estimate therefore includes all noise sources that act on the
-            timescale of a single 13 second integration (eg. thermal, ionospheric, etc.).
+            timescale of a single 13~s integration (e.g., thermal, ionospheric, etc.).
         }}
@@
 observations from the OVRO-LWA. Each map is individually shown in Figure~\ref{fig:channel-maps},
-Figure~\ref{fig:three-color} is a three-color image constructed from the maps at 36.528~MHz,
-52.224~MHz, and 73.152~MHz, and Figure~\ref{fig:galactic-plane-cutout} is a cutout of the galactic
-plane. The maps cover the sky north of $\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution.
+Figure~\ref{fig:three-color} is a three-color image constructed from the maps at 36.528,
+52.224, and 73.152~MHz, and Figure~\ref{fig:galactic-plane-cutout} is a cutout of the galactic
+plane. The maps cover the sky north of $\delta=-30^\circ$ with $\sim 15\arcmin$ angular resolution.
 The eight brightest northern hemisphere point sources are removed from each map (Cyg~A, Cas~A,
-Vir~A, Tau~A, Her~A, Hya~A, 3C~123, and 3C~353) as described in \S\ref{sec:source-removal}, and
+Vir~A, Tau~A, Her~A, Hya~A, 3C~123, and 3C~353), as described in \S\ref{sec:source-removal}, and
 there is a small blank region near $l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of
@@
 Due to the considerations presented by \citet{2016ApJ...826..116V} and discussed in
-\S\ref{sec:mmode-analysis}, each of these maps is monopole subtracted ($a_{00}=0$).  Furthermore, in
+\S\ref{sec:mmode-analysis}, each of these maps is monopole-subtracted ($a_{00}=0$).  Furthermore, in
 order to suppress sources of terrestrial interference, all spherical harmonics with $m=0$, or $m=1$
@@
 coordinate system). As will be discussed in \S\ref{sec:rfi}, these spherical harmonics are
-particularly susceptible to contamination by RFI and common-mode pickup. As a consequence,
-astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
-This filtering creates negative rings around the NCP at the declination of bright point sources.
-These rings are naturally removed from the map during CLEANing as long as this filtering step is
-included in the PSF calculation.
-
-The noise in each map is empirically measured using jackknife resampling. The dataset is first split
+particularly susceptible to contamination by radio-frequency interference (RFI) and common-mode
+pickup. As a consequence, astronomical emission that circles the J2017 north celestial pole (NCP) is
+filtered from the maps.  This filtering creates negative rings around the NCP at the declination of
+bright point sources.  These rings are naturally removed from the map during CLEANing as long as
+this filtering step is included in the PSF calculation.
+
+The noise in each map is empirically measured using jackknife resampling. The data set is first split
 into even- and odd-numbered integrations. These two groups are then imaged and CLEANed
-independently, before being compared against the maps constructed from all of the available data
+independently before being compared against the maps constructed from all of the available data
 using the jackknife standard error estimator. This estimate of the standard error includes all
-sources of error that operate on $\sim13$ second timescales (the integration time) such as thermal
+sources of error that operate on $\sim13$~s timescales (the integration time), such as thermal
 noise and rapid ionospheric fluctuations, but does not account for more slowly varying effects (for
-example, sidereal variation in the system temperature or day-night fluctuations in the ionosphere).
+example, sidereal variation in the system temperature or day--night fluctuations in the ionosphere).
 These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
-\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
+\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15\arcmin angular
 resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
-noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
-
-In the absence of a zero-level correction, a pixel-by-pixel power law fit to the new maps is
-impossible. In general this zero-level correction requires calibrated total power measurements that
-will be included in future work.  Instead, temperature-temperature plots (T-T plots) can be used to
-measure the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}.
-This method relies on the assumption that all pixels in a given region are described by the same
-power law. In that case, there exists a linear relationship between the brightness temperature at
-frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line is a measure of the
-spectral index between the two frequencies. T-T plots can fail to obtain a reliable measure of the
-spectral index in two ways.  First, if there is not enough dynamic range in the emission region
-there may be only a weak correlation between the brightness temperature at $\nu_1$ and $\nu_2$.
-Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free), then
-a single power-law interpretation of the emission in that region will be poor. Consequently,
-spectral indices estimated from T-T plots can require careful interpretation.
+noise $<900$~mJy; therefore, each map is likely at or near the confusion limit.
+
+In the absence of a zero-level correction, a pixel-by-pixel power-law fit to the new maps is
+impossible. In general, this zero-level correction requires calibrated total power measurements that
+will be included in future work.  Instead, temperature--temperature plots (T--T plots) can be used
+to measure the spectral index independently of any zero-level corrections
+\citep{1962MNRAS.124..297T}.  This method relies on the assumption that all pixels in a given region
+are described by the same power law. In that case, there exists a linear relationship between the
+brightness temperature at frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line
+is a measure of the spectral index between the two frequencies. The T--T plot can fail to obtain a
+reliable measure of the spectral index in two ways.  First, if there is not enough dynamic range in
+the emission region, there may be only a weak correlation between the brightness temperature at
+$\nu_1$ and $\nu_2$.  Second, if two emission mechanisms operate in close proximity (i.e.,
+synchrotron and free-free), then a single power-law interpretation of the emission in that region
+will be poor. Consequently, spectral indices estimated from T--T plots can require careful
+interpretation.
 
 In Figure~\ref{fig:internal-spectral-index}, the spectral index is locally estimated in each part of
-the sky within a region $\sim10^\circ$ across by constructing local T-T plots between 36.528~MHz and
-73.152~MHz. Contours of constant $R^2$ (the coefficient-of-determination) are overlaid. If $R^2\sim
+the sky within a region $\sim10^\circ$ across by constructing local T--T plots between 36.528 and
+73.152~MHz. Contours of constant $R^2$ (the coefficient of determination) are overlaid. If $R^2\sim
 1$, the spectral index is reliable because there is locally a strong linear correlation between
-36.528~MHz and 73.152~MHz. However, if $R^2\ll 1$, the spectral index calculation is unreliable.
-$R^2$ tends to drop in cold patches of the sky where there is not enough dynamic range to find a
-strong correlation between the two frequencies. $R^2$ also tends to drop in the vicinity of
-\ion{H}{2} regions in the galactic plane due to multiple emission mechanisms violating the
-assumption of a single spectral index. Therefore, we should restrict our interpretation of
+36.528 and 73.152~MHz. However, if $R^2\ll 1$, the spectral index calculation is unreliable.  $R^2$
+tends to drop in cold patches of the sky where there is not enough dynamic range to find a strong
+correlation between the two frequencies. It also  ends to drop in the vicinity of \ion{H}{2} regions
+in the galactic plane due to multiple emission mechanisms violating the assumption of a single
+spectral index. Therefore, we should restrict our interpretation of
 Figure~\ref{fig:internal-spectral-index} to the galactic plane and north galactic spur. In the
 galactic plane, the synchrotron spectral index varies between $\sim-2.5$ and $-2.75$. In the
-vicinity of \ion{H}{2}, regions the spectral index flattens significantly.  These \ion{H}{2} regions
+vicinity of \ion{H}{2} regions, the spectral index flattens significantly.  These \ion{H}{2} regions
 can be seen with higher resolution in Figure~\ref{fig:galactic-plane-cutout}. In
@@
 map and the reprocessed Haslam map. The spectral index was estimated by degrading the 73.152~MHz map
-to the resolution of the Haslam map and constructing local T-T plots in every direction. The
-coefficient-of-determination is overlaid as a contour plot, however because
+to the resolution of the Haslam map and constructing local T--T plots in every direction. The
+coefficient of determination is overlaid as a contour plot; however, because
 $\log(408\,\text{MHz}/73.152\,\text{MHz}) > \log(73.152\,\text{MHz}/36.528\,\text{MHz})$, the
@@
     \caption{
-        The fractional difference between maps from the LWA1 Low Frequency Sky Survey and the
-        OVRO-LWA maps (Figure~\ref{fig:channel-maps}) after interpolating to the corresponding
-        frequency and smoothing to the corresponding resolution. A positive value indicates regions
-        where the OVRO-LWA map has more emission that the corresponding LWA1 Low Frequency Sky
-        Survey map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
-        subtracted from the OVRO-LWA maps.
+        Fractional difference between maps from the LLFSS and the OVRO-LWA maps
+        (Figure~\ref{fig:channel-maps}) after interpolating to the corresponding frequency and
+        smoothing to the corresponding resolution. A positive value indicates regions where the
+        OVRO-LWA map has more emission that the corresponding LLFSS map. Cas A, Cyg A, Vir A, and
+        Tau A are masked due to the fact that they are subtracted from the OVRO-LWA maps.
     }
@@
 
-The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced nine maps of the sky
-between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
+The LWA1 Low Frequency Sky Survey \citep[LLFSS;][]{2017MNRAS.469.4537D} produced nine maps of the
+sky between 35 and 80~MHz. Six of these maps are interior to the frequency range spanned by this
 work. Initial comparisons with the LLFSS helped characterize a systematic rotation in the LWA1's
-antenna positions. After phase-calibration, this manifested itself as a systematic rotation and
+antenna positions. After phase calibration, this manifested itself as a systematic rotation and
 translation in the snapshot images that were mosaicked to form the final sky map. This systematic
 error has been corrected in the comparisons presented here and in the latest version of the
-LLFSS\footnote{
-    Available for download at: \url{http://lda10g.alliance.unm.edu/LWA1LowFrequencySkySurvey/}
-}.
+LLFSS.\footnote{
+    Available for download at \url{http://lda10g.alliance.unm.edu/LWA1LowFrequencySkySurvey/}
+}
 
@@
 OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
-corresponding LLFSS map.  At 60~MHz, the agreement is generally better than 10\%. However at lower
-frequencies the agreement deteriorates to about 20\%.  Typically the OVRO-LWA maps have excess
+corresponding LLFSS map.  At 60~MHz, the agreement is generally better than 10\%. However, at lower
+frequencies the agreement deteriorates to about 20\%.  Typically, the OVRO-LWA maps have excess
 emission in the galactic plane and a deficit of emission off the galactic plane relative to the
@@
 The LLFSS incorporates calibrated total power radiometry to estimate the missing flux from short
-spacings. As a result \citet{2017MNRAS.469.4537D}, report per-pixel spectral-indices from combining
+spacings. As a result, \citet{2017MNRAS.469.4537D} reported per-pixel spectral indices from combining
 all nine sky maps. Care must be taken in comparing these spectral indices with
@@
 errors. Both calculations are sensitive to mistakes in the antenna primary beam, but the LLFSS
-spectral indices are additionally sensitive to errors in the zero-level. We will restrict the
+spectral indices are additionally sensitive to errors in the zero level. We will restrict the
 comparison to the galactic plane where the spectral indices are likely to be the most reliable.
-Towards the galactic center both surveys agree that the spectral index is very flat ($>-2.2$) due to
+Toward the galactic center, both surveys agree that the spectral index is very flat ($>-2.2$) due to
 the influence of free-free absorption.  However, at galactic latitudes $\sim 180^\circ$ this work
 suggests that the spectral index varies between -2.5 and -2.75, while the LLFSS reports
-substantially flatter indices in the range -2.3 to -2.2. In this region $0.7 < R^2 < 0.9$ for the
+substantially flatter indices in the range -2.3 to -2.2. In this region, $0.7 < R^2 < 0.9$ for the
 OVRO-LWA, so this could be an artifact of the comparatively weak correlation between the brightness
-at 36.528~MHz and 73.152~MHz, which tends to bias the spectral index towards $-\infty$.
+at 36.528 and 73.152~MHz, which tends to bias the spectral index toward $-\infty$.
 
 The LLFSS also computes spectral indices with respect to the Haslam 408~MHz map. These spectral
-indices are subject to the same caveats and systematic errors as before. However, in general the
+indices are subject to the same caveats and systematic errors as before. However, in general, the
 qualitative agreement with Figure~\ref{fig:haslam-spectral-index} is better, potentially due to the
@@
     \caption{
-        This Mollweide projected map compares the fractional difference between the Guzm\'{a}n 45
-        MHz map, and the OVRO-LWA maps (Figure~\ref{fig:channel-maps}) interpolated to 45~MHz
+        This Mollweide-projected map compares the fractional difference between the Guzm\'{a}n 45
+        MHz map and the OVRO-LWA maps (Figure~\ref{fig:channel-maps}) interpolated to 45~MHz
         (degraded to $5^\circ$ resolution). A positive value indicates regions where the OVRO-LWA
-        map has more emission that the Guzm\'{a}n map, and a negative value indicates regions where
+        map has more emission than the Guzm\'{a}n map, and a negative value indicates regions where
         the Guzm\'{a}n map has more emission than the OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A
@@
 The Guzm\'{a}n 45 MHz map \citep{2011A&A...525A.138G} is compiled from a southern hemisphere survey
-\citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M} with a
-small gap around the NCP. In this work, the zero-level is set by comparing against published
+\citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M}, with a
+small gap around the NCP. In this work, the zero level is set by comparing against published
 low-frequency measurements in six different directions.
@@
 map has had spherical harmonics with $m=0$ discarded in order to make it consistent with the maps
-presented in this paper. This figure shows a $\sim20\%$ excess of emission in the galactic plane
+presented in this paper. This figure shows an $\sim20\%$ excess of emission in the galactic plane
 that is consistent with the discrepancy observed between the LLFSS and the Guzm\'{a}n map.  However,
 while the LLFSS has an excess of emission near the north galactic pole, no such excess is observed
-in this work. Instead there is a 10\% excess of emission near the south galactic pole. Elsewhere off
-the plane of the galaxy the discrepancy can be as much as $-20\%$.
-
-\citet{2011A&A...525A.138G} compute the spectral index between their 45~MHz map and the 408~MHz
-Haslam map. Along the galactic plane the spectral index varies between -2.2 (in the vicinity of
-\ion{H}{2} regions), and -2.5 (at galactic longitudes $\sim 180^\circ$). The north galactic spur has
+in this work. Instead, there is a 10\% excess of emission near the south galactic pole. Elsewhere off
+the plane of the galaxy, the discrepancy can be as much as $-20\%$.
+
+\citet{2011A&A...525A.138G} computed the spectral index between their 45~MHz map and the 408~MHz
+Haslam map. Along the galactic plane, the spectral index varies between -2.2 (in the vicinity of
+\ion{H}{2} regions) and -2.5 (at galactic longitudes $\sim 180^\circ$). The north galactic spur has
 a spectral index of -2.5. This is generally consistent with the results presented in
@@
         Illustration of the corrupting influence of the ionosphere at 36.528~MHz (left column)
-        compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF for a
-        source at the location of Cas~A, and illustrates the percent difference (relative to the
-        peak flux of the uncorrupted PSF) due to including an ionospheric effect.  In the top row,
-        the simulated source scintillates using the measured light-curve for Cas~A in
+        compared with 73.152~MHz (right column). Each panel shows the simulated PSF for a source at
+        the location of Cas~A and illustrates the percent difference (relative to the peak flux of
+        the uncorrupted PSF) due to including an ionospheric effect.  In the top row, the simulated
+        source scintillates using the measured light curve for Cas~A in
         Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
@@
     \caption{
-        A zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
+        Zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
         (right panel). At 36.528~MHz there are $\sim10\%$ artifacts around 3C~134 that persist after
@@
 $t_{\textrm{sidereal}}$. If the source is varying, from intrinsic variability or due to
-scintillation, than the source flux is also a function of the time coordinate $t$ such that
+scintillation, then the source flux is also a function of the time coordinate $t$ such that
 \begin{equation}
@@
 
-In order to compute the $m$-modes we must take the Fourier transform with respect to the sidereal
-time. As a consequence of the Fourier convolution theorem we find:
+In order to compute the $m$-modes, we must take the Fourier transform with respect to the sidereal
+time. As a consequence of the Fourier convolution theorem, we find
 \begin{equation}\label{eq:no-longer-block-diagonal}
@@
 Figure~\ref{fig:ionospheric-simulations}. In this simulation, a point source is placed at the
-location of Cas~A. In one case the source is allowed to scintillate in the same way Cas~A does in
+location of Cas~A. In one case, the source is allowed to scintillate in the same way Cas~A does in
 Figure~\ref{fig:scintillation}, but the source is always located exactly at the location of Cas~A.
-In the second case the source position is allowed to vary in the same way Cas~A does in
+In the second case, the source position is allowed to vary in the same way Cas~A does in
 Figure~\ref{fig:scintillation}, but the flux of the source exactly traces the beam model. The
@@
 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As expected for an ionospheric
-effect these errors decrease to a few percent at 52.224~MHz, and less at 73.152~MHz. We therefore
+effect, these errors decrease to a few percent at 52.224~MHz, and less at 73.152~MHz. We therefore
 conclude that ionospheric effects directly limit the dynamic range in the vicinity of bright point
@@
 
-A model of the antenna beam is essential for widefield imaging. Because $m$-mode analysis imaging
+A model of the antenna beam is essential for wide-field imaging. Because $m$-mode analysis imaging
 operates on a full sidereal day of data, images are constructed after watching each point in the sky
@@
 \begin{enumerate}
-    \item setting the flux scale as a function of declination
-    \item reconciling observations from two separate sidereal times
+    \item setting the flux scale as a function of declination and
+    \item reconciling observations from two separate sidereal times.
 \end{enumerate}
@@
 not show a clear pattern with declination. Two sources have a clear systematic offset at all
-frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
-southernmost source -- does not exhibit this systematic error. Similarly, 3C 380 is at a comparable
-declination to Lyn A, which appears, if anything, to have its flux systematically offset in the
-other direction. The absence of a coherent pattern does not eliminate the possibility of beam errors
-effecting the flux scale, but it does mean that these errors are at least comparable to the errors
-inherent to the flux scale itself.
+frequencies: 3C 353 and 3C 380. Source 3C 353 is the second southernmost source, but Hya A -- the
+first southernmost source -- does not exhibit this systematic error. Similarly, 3C 380 is at a
+comparable declination to Lyn A, which appears, if anything, to have its flux systematically offset
+in the other direction. The absence of a coherent pattern does not eliminate the possibility of beam
+errors affecting the flux scale, but it does mean that these errors are at least comparable to the
+errors inherent to the flux scale itself.
 
@@
 it can be expected that the beam will introduce errors into the sky maps that will limit the dynamic
-range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulate the effect of
-beam errors on a cosmological analysis concluding that the beam must be known to one part in $10^4$.
+range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulated the effect of
+beam errors on a cosmological analysis, concluding that the beam must be known to one part in $10^4$.
 Our requirements are significantly less stringent because we are estimating the sky brightness
@@
 we found that ionospheric effects likely dominate over other sources of error that affect the PSF
-shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
+shape. Therefore, we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
 limit the effect of beam errors on the PSF to at least less than those introduced by the ionosphere.
@@
 
-\citet{2015PhRvD..91h3514S} describe how to generalize $m$-mode analysis to account for a polarized
-sky observed with a polarized antenna beam. Heretofore this generalization has been neglected in the
+\citet{2015PhRvD..91h3514S} described how to generalize $m$-mode analysis to account for a polarized
+sky observed with a polarized antenna beam. Heretofore, this generalization has been neglected in the
 discussion of $m$-mode analysis imaging.  At low frequencies, increasingly rapid Faraday rotation
-leads to depolarization. Therefore polarization fractions are generally expected to decrease at low
+leads to depolarization. Therefore, polarization fractions are generally expected to decrease at low
 frequencies (varying with ionospheric conditions). \citet{2016ApJ...830...38L} detected the presence
@@
 In order to understand the effect of polarization leakage, we simulated a point source with 10\%
-polarization in Stokes-$Q$ at the location of Cas A.  The simulated visibilities were computed using
-the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
-every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
-Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
-rises to $\gtrsim50\%$ at lower elevations. \citet{2015JAI.....450004O} report similar polarization
-leakage measurements with the LWA1.  Cas A is a circumpolar source and spends about seven hours
+polarization in Stokes $Q$ at the location of Cas A.  The simulated visibilities were computed using
+the measured beams for the $x$ and $y$ dipoles. Because the amplitudes of the two beams are not equal in
+every direction on the sky, this introduces a direction-dependent leakage of Stokes $Q$ into
+Stokes $I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation but rapidly
+rises to $\gtrsim50\%$ at lower elevations. \citet{2015JAI.....450004O} reported similar polarization
+leakage measurements with the LWA1.  Cas A is a circumpolar source and spends about 7 hours
 every day skirting the horizon where the polarization leakage is large, so by placing the simulated
 source at the location of Cas A, we are engineering a situation where the polarization leakage from
-Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
+Stokes $Q$ into Stokes $I$ will be large. However, the impact on the unpolarized $m$-mode analysis
 maps is mild, amounting to a 0.5\% error in the flux of the source.
@@
         Terrestrial sources of correlated noise that are apparent after averaging the visibilities
-        at 62.688 MHz over the entire 28 hour observing period (keeping the phase center at zenith
+        at 62.688~MHz over the entire 28 hour observing period (keeping the phase center at zenith
         such that astronomical sources of radio emission are smeared along tracks of constant
@@
         weighting, and only baselines longer than 15 wavelengths. Panels (a) and (b) illustrate
-        components that appear noise-like in image-space, but are in fact a constant-offset to the
+        components that appear noise-like in image space, but are in fact a constant offset to the
         measured visibilities likely associated with cross-talk or common-mode pickup. Panel (c)
         illustrates a component that is clearly associated with an RFI source on the horizon to the
-        west-north-west of the OVRO-LWA. This RFI source is likely an arcing power line.
-        Figure~\ref{fig:rings} illustrates the characteristic ring-like artifacts introduced into
-        the maps if these 3 components are not removed prior to $m$-mode analysis imaging. The
+        west--northwest of the OVRO-LWA. This RFI source is likely an arcing power line.
+        Figure~\ref{fig:rings} illustrates the characteristic ringlike artifacts introduced into the
+        maps if these three components are not removed prior to $m$-mode analysis imaging. The
         component shown in panel (a) has about twice the amplitude ($\|\b v_\text{terrestrial}\|$)
-        of panels (b) and (c), and for all three components $\|\b B^*\b v_\text{terrestrial}\|/(\|\b
-        B\|\|\b v_\text{terrestrial}\|) \sim 0.035$.
+        of those in panels (b) and (c), and for all three components, $\|\b B^*\b
+        v_\text{terrestrial}\|/(\|\b B\|\|\b v_\text{terrestrial}\|) \sim 0.035$.
     }
@@
         moving through the sky sidereally, they tend to be smeared along rings of constant
-        declination. The spurs seemingly radiating from the north celestial pole are a Moir\'{e}
-        pattern (ie. an artifact of the pixelization).
+        declination. The spurs seemingly radiating from the NCP are a Moir\'{e} pattern (i.e., an
+        artifact of the pixelization).
     }
@@
 interferometer located in the vicinity of an arcing power line will see an additional contribution
-from the radio-frequency interference (RFI) generated by the arcing process. Similarly, common-mode
+from the RFI generated by the arcing process. Similarly, common-mode
 pickup along the analog signal path of the interferometer may generate an additional spurious
@@
 The Owens Valley is an important source of water and power for the city of Los Angeles.
-Unfortunately, this means that high voltage power lines run along the valley $\gtrsim10$~km to the
-west of the OVRO-LWA. Some of these power line poles have faulty insulators that arc and produce
+Unfortunately, this means that high-voltage power lines run along the valley $\gtrsim10$~km to the
+west of the OVRO-LWA. Some of these power-line poles have faulty insulators that arc and produce
 pulsed, broadband RFI. Because these poles exist in the near-field of the array, we have been able
@@
 
-In the meantime, it is possible to suppress their contamination in the dataset. The contribution of
+In the meantime, it is possible to suppress their contamination in the data set. The contribution of
 these RFI sources to the visibilities can be plainly seen by averaging $>24$ hours of data with the
 phase center set to zenith. In this way, true sky components are smeared along tracks of constant
-declination while terrestrial sources (ie. the arcing power lines or any contribution due to
+declination while terrestrial sources (i.e., the arcing power lines or any contribution due to
 common-mode pickup) are not smeared.  Obtaining a model for the RFI is complicated by the fact that
-the contaminating sources are at extremely low elevations where the antenna response is essentially
+the contaminating sources are at extremely low elevations, where the antenna response is essentially
 unknown (and inhomogeneous due to antenna shadowing effects). It is not enough to know the physical
@@
 some form of common-mode pickup. If these components are not subtracted from the measured
-visibilities, they contribute ring-like structures into the sky maps as seen in
-Figure~\ref{fig:rings}. This figure is not a simulation, but rather a difference between maps
-created before and after measuring and subtracting the components in Figure~\ref{fig:fitrfi} from
-each integration.
-
-The first step in Equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step we
+visibilities, they contribute ringlike structures to the sky maps, as seen in
+Figure~\ref{fig:rings}. This figure is not a simulation but rather a difference between maps created
+before and after measuring and subtracting the components in Figure~\ref{fig:fitrfi} from each
+integration.
+
+The first step in Equation~\ref{eq:tikhonov-solution} is to compute $\b B^*\b v$. In this step, we
 compute the projection of the measurement $\b v$ onto the space spanned by the columns of $\b B$.
 Each column of $\b B$ describes the interferometer's response to a corresponding spherical harmonic
-coefficient of the sky brightness distribution. Therefore, the act of computing $\b B^*\b v$ is to
-project the measured $m$-modes onto the space of $m$-modes which could be generated by astronomical
+coefficient of the sky-brightness distribution. Therefore, the act of computing $\b B^*\b v$ is to
+project the measured $m$-modes onto the space of $m$-modes that could be generated by astronomical
 sources. The degree to which a source of terrestrial interference will contaminate a map generated
@@
 $\b B$, there will be no contamination in the map because $\b B^*\b v_\text{terrestrial} = \b 0$.
-In practice this is unlikely. In general, the contamination is proportional to the overall amplitude
+In practice, this is unlikely. In general, the contamination is proportional to the overall amplitude
 of the interference ($\|\b v_\text{terrestrial}\|$) and the degree to which the interference mimics
@@
 
-These terrestrial sources do not rotate with the sky and hence their contamination tends to be
-restricted to modes with small $m$. In this dataset the contamination is largely restricted to $m
-\lesssim 1$. Although the RFI is capable of fluctuating on short timescales, in this case the
+These terrestrial sources do not rotate with the sky, and hence their contamination tends to be
+restricted to modes with small $m$. In this data set the contamination is largely restricted to $m
+\lesssim 1$. Although the RFI is capable of fluctuating on short timescales, in this case, the
 artifacts it introduces seem to be restricted to small $m$ (presumably because the phase is not
-fluctuating).  As a result if the contamination is not suppressed, it will manifest itself as rings
+fluctuating).  As a result, if the contamination is not suppressed, it will manifest itself as rings
 along stripes of constant declination. This effect is plainly visible in Figure~\ref{fig:fitrfi}.
-Because of the distinctive ring-like pattern created by terrestrial sources, we additionally chose
-to discard spherical harmonics with either $m=0$ or $m=1$ and $l>100$ in order to further suppress
-the contamination.
+Because of the distinctive ringlike pattern created by terrestrial sources, we additionally chose to
+discard spherical harmonics with either $m=0$ or $m=1$ and $l>100$ in order to further suppress the
+contamination.
 
@@
 
-In this work we presented a new imaging technique -- Tikhonov regularized $m$-mode analysis imaging
+In this work, we presented a new imaging technique -- Tikhonov-regularized $m$-mode analysis imaging
 and CLEANing -- for drift-scanning telescopes like the OVRO-LWA.  This technique exactly corrects
-for widefield effects in interferometric imaging with a single synthesis imaging step.  We applied
-Tikhonov regularized $m$-mode analysis imaging to a 28 hour dataset and generated eight sky maps
-between 36.528~MHz and 73.152~MHz.  These sky maps are a substantial improvement in angular
-resolution over existing maps at these frequencies with $\sim$15~arcmin angular resolution and
-$<600$~K thermal noise. The point source flux scale is consistent with that defined by
-\citet{2012MNRAS.423L..30S} to about 5\% and large angular scales are consistent with the work of
-\citet{2017MNRAS.469.4537D} to within 20\%.
+for wide-field effects in interferometric imaging with a single synthesis imaging step.  We applied
+Tikhonov-regularized $m$-mode analysis imaging to a 28 hour data set and generated eight sky maps
+between 36.528 and 73.152~MHz.  These sky maps are a substantial improvement in angular resolution
+over existing maps at these frequencies with $\sim15\arcmin$ angular resolution and $<600$~K thermal
+noise. The point-source flux scale is consistent with that defined by \citet{2012MNRAS.423L..30S} to
+about 5\%, and large angular scales are consistent with the work of \citet{2017MNRAS.469.4537D} to
+within 20\%.
 
@@
 particularly interesting in order to maximize the overlap with the MWA in the southern hemisphere,
-which could be used to fill-in the hole around the southern celestial pole.
+which could be used to fill in the hole around the southern celestial pole.
 
 These maps and future improvements are primarily intended to be used as part of a foreground
-modeling and subtraction routine for 21-cm cosmology experiments. Each map will be made publicly
+modeling and subtraction routine for 21~cm cosmology experiments. Each map will be made publicly
 available on LAMBDA.
@@
 
-This material is based in part upon work supported by the National Science Foundation under Grant
+This material is based in part upon work supported by the National Science Foundation under grants
 AST-1654815 and AST-1212226. The OVRO-LWA project was initiated through the kind donation of Deborah
@@
 Processing and Electronics Research (CASPER).  We thank the Xilinx University Program for donations;
-NVIDIA for proprietary tools, discounts, and donations; Digicom for collaboration on manufacture and
-testing of DSP processors.
+NVIDIA for proprietary tools, discounts, and donations; and Digicom for collaboration on the
+manufacture and testing of DSP processors.
 
@@
 
-Development, adaptation, and operation of the LEDA real-time digital signal processing systems at
-OVRO-LWA has been supported in part by NSF grants AST/1106059, PHY/0835713, and OIA/1125087.
-
-GBT, JD and FKS acknowledge support from the National Science Foundation under grant AST-1139974.
+Development, adaptation, and operation of the LEDA real-time digital signal-processing systems at
+OVRO-LWA have been supported in part by NSF grants AST/1106059, PHY/0835713, and OIA/1125087.
+
+GBT, JD, and FKS acknowledge support from the National Science Foundation under grant AST-1139974.
 
